### 2023-03-30 paper/paper.tex
Initial commit

% Created 2023-03-30 Thu 17:04
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{breakcites}
\usepackage{apacite}
\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} % define (reduced) margin size
\usepackage[parfill]{parskip} % insert whitespace between new paragraphs
\setlength\parindent{0pt}
\tolerance=9999
\emergencystretch=10pt
\hyphenpenalty=10000
\exhyphenpenalty=100
\author[1]{Patrick O'Toole}
\author[1,2]{Matthew L. Thomas}
\author[1]{Oliver Stevens}
\author[1,3]{Kevin Lam}
\author[4]{Katherine Kripke}
\author[1]{Rachel Esra}
\author[5]{Ian Wanyeki}
\author[5]{Lycias Zembe}
\author[1]{Jeffrey W. Eaton}
\affil[1]{\emph{Imperial College London, London, United Kingdom}} \\
\affil[2]{\emph{Joint Centre for Excellence in Environmental Intelligence, University of Exeter and Met Office}} \\
\affil[3]{\emph{Department of Statistics, University of British Columbia}} \\
\affil[4]{\emph{Avenir Health, Takoma Park, MD, USA}} \\
\affil[5]{\emph{Joint United Nations Programme on HIV/AIDS (UNAIDS)}} \\
\date{17th October 2022}
\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
\begin{document}

\maketitle

\clearpage

\begin{abstract}
  \noindent \textbf{Background} \\
  \noindent In 2016, UNAIDS developed a Fast-Track strategy that targeted 90\% coverage
  male circumcision (MC) among men aged 10-29 years by 2021 in priority countries in sub-Saharan 
  Africa (SSA) to reduce HIV incidence. There is substantial variation across subnational 
  regions within countries in both traditional male circumcision (TMC) practices and progress
  towards implementation of voluntary medical male circumcision (VMMC). Tracking progress and
  remaining gaps towards VMMC HIV prevention targets requires detailed district-level circumcision
  coverage data.

  \noindent \textbf{Methods} \\
  \noindent We analysed self-reported data on male circumcision from x nationally representative household
  surveys conducted in x SSA countries between 2006-2020. A spatio-temporal Bayesian
  competing-risks time-to-event model was used to estimate rates of traditional and medical
  circumcision by age, location, and time. Circumcision coverage in 2020 was projected assuming
  continuation of estimated age-specific rates, with probabilistic uncertainty.

  \noindent \textbf{Results} \\
  \noindent Across x countries, from 2010 to 2020 an estimated x million men (x\% CI x-x million)
  were newly circumcised, of whom x million (x - x million) were medically circumcised, and
  x million (x - x million) traditionally circumcised. In 2020, MC coverage among men 10-29
  years ranged from x\% (x\% - x\%) in Zimbabwe (?) to x\% (x\%-x\%) in Togo. MMC coverage
  ranged from x\% (x\%-x\%) in Malawi to x\% (x\%-x\%) in Tanzania, and TMC coverage
  from x\% (x\%-x\%) in Eswatini to x\% (x\%-x\%) in Ethiopia. The largest increase in MMC
  coverage was in Lesotho from x\% to x\%. Within countries, the median difference in MC
  coverage between the districts with lowest and highest coverage was x\%, with the smallest
  variation in Eswatini (x\% to x\%) and largest in Zambia (x\% to x\%). x million men aged
  10-29 need to be circumcised to reach 90\% coverage in all countries.

  \noindent \textbf{Conclusions} \\
  \noindent VMMC programmes have made substantial, but uneven, progress towards male circumcision targets. Granular district and age-stratified data provide information for focusing further programme implementation.

\end{abstract}

\newpage

\section{Background}
\label{sec:org3a33a7d}

HIV remains the single largest cause of years of life lost among adolescent boys and men of reproductive age in eastern and southern Africa.

Voluntary Male medical circumcision (VMMC) reduces the rate of male-to-female HIV incidence by 60\%.
Efficient, cost-effective, one-time procedure for preventing HIV transmission.

Matt's model \ldots{} (Thomas, Matthew L. and Zuma, Khangelani and Loykissoonlal, Dayanund and Dube, Bridget and Vranken, Peter and Porter, Sarah E. and Kripke, Katharine and Seatlhodi, Thapelo and Meyer-Rath, Gesine and Johnson, Leigh F. and Eaton, Jeffrey W., 2021)

\newpage
\section{Data}
\label{sec:org0422724}

120 household surveys conducted in 33 SSA countries 2002-2019
Self-reported circumcision:
o Status (MC vs uncircumcised), 
o Type (MMC vs TMC), 
o Year, and
o Age 
recorded
Sub-national populations from WorldPop (reference)

Major survey series (DHS, AIS, PHIA, MICS, HSRC in ZAF)
Individual-level data: self-reported circumcision status  by male respondents
Respondents located to districts using cluster geocoordinates
Located to admin 1 (province) where coordinates not available (MICS)
VMMC programme data not used

Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC
Otherwise, circumcisions are TMC
Where no data is present on location or provider, circumcision type  Missing

Individual-level household survey data provide direct estimates of circumcision rates over time and by type for years preceding survey

 Direct estimates of TMC practices, age at circumcision, VMMC impact

\newpage

\section{Methods}
\label{sec:org69a085f}

\subsection{Model}
\label{sec:org2077286}

Bayesian spatio-temporal, competing-risks, time-to-event model
Stratified by age, location and time
Rates of TMC and medical male circumcision (MMC) estimated
Coverage in 2020 projected assuming continuation of estimated age-specific rates with probabilistic uncertainty
Important assumption: Probability of traditional male initiation ceremonies (TMICs) constant over time (needed? Might lead to a lot of questions!)

Model stratified by:
Age
District
circumcision type (traditional / medical)

TMC \& MMC rates estimated (by age, district, and time)
Spatial smoothing allows for district level estimates

Circumcision coverage since most recent HH survey: projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty

Important assumption: TMC rate assumed constant over time

\newpage

Samples drawn from model fit, weighted by population and aggregated, to produce estimates for less granular regions (e.g. District to Province aggregation).
Computed posterior summary statistics for coverage, circumcision incidence and probability of being circumcised. 
Done for all strata, for both discrete ages and “binned” age groups.

\section{Results}
\label{sec:org634cf32}

\#+latex \newpage

\section{Discussion}
\label{sec:orgce42292}

\textbf{Challenges}
Inconsistent MC self-reporting by same cohort in successive surveys
E.g. in 2017 survey, men 30-34 report higher \% circumcised in 2012 than ‘same’ men age 25-29 in 2012 survey
Affects circumcision level, and distribution by type

‘Replacement’ of traditional circumcision by medical circumcision
Evidence of this in surveys from several countries; work in progress
Also not fully accounted for in DMPPT2 baseline coverage inputs

Surveys imply different level of scale-up than programme data
Several countries: surveys suggest fewer VMMCs conducted than programme data

\#+latex \newpage

\section{References}
\label{sec:org38b7f8b}

\#+PRINT\textsubscript{BIBLIOGRAPHY}
\end{document}

### 2023-03-30 aids_2022_poster/poster_results.R

@@ -1,0 +1,1236 @@
+#### Plots for Poster ####
+
+#### libs ####
+
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+# library(reactablefmtr)
+library(sf)
+# library(threemc)
+devtools::load_all("../threemc")
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+source("Shiny/src/functions.R")
+
+#### Metadata ####
+
+orderly_root <- here::here()
+
+spec_age_group <- "10-29"
+spec_years <- c(2010, 2020)
+
+## for tabulating surveys
+# remove circumcisions with missing type?
+rm_missing_type <- FALSE
+
+start_year <- 2002
+cens_age <- 59
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
+ssa_countries <- case_when(
+  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
+  ssa_countries == "Congo - Brazzaville" ~ "Congo",
+  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
+  ssa_countries == "Gambia"              ~ "The Gambia",
+  TRUE                                   ~ ssa_countries
+)
+
+# countries/regions which have been targeted for 90% circumcision by 2021
+target_iso3 <- c(
+  # In Ethiopia Gambella is the only target province
+  "BWA", "ETH_1_15", "KEN", "LSO", "MWI", "MOZ", "NAM", 
+  "RWA", "ZAF", "SWZ", "UGA", "TZA", "ZMB", "ZWE"
+)
+
[…]

### 2023-03-30 paper/temp.R

@@ -1,0 +1,362 @@
+
+* Initial Code                                                     :noexport:
+
+#+begin_src R :exports none :session
+# set directory to top level of git repo
+setwd(system("git rev-parse --show-toplevel", intern = TRUE))
+#+end_src
+
+#+RESULTS:
+: /home/paddy7wb/imperial_repos/threemc-orderly
+
+** Load Libraries
+#+begin_src R :exports none :session
+
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+source(here::here("Shiny/src/functions.R")) # plotting functions
+#+end_src
+#+RESULTS:
+
+**  Define Metadata
+
+#+begin_src R :exports none :session
+
+orderly_root <- here::here()
+
+spec_age_group <- "10-29"
+# spec_age_groups <- c("15-29", "15-49")
+spec_years <- c(2010, 2020)
+
+# for tabulating surveys: 
+rm_missing_type <- FALSE # remove circumcisions with missing type?
+start_year <- 2000 # minimum survey year
+cens_age <- 59 # maximum circumcision age
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
+ssa_countries <- dplyr::case_when(
+  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
+  ssa_countries == "Congo - Brazzaville" ~ "Congo",
+  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
+  ssa_countries == "Gambia"              ~ "The Gambia",
[…]

### 2023-03-30 poster_plots_no_shiny_consolidation.R

@@ -1,0 +1,1285 @@
+#### Plots for Poster ####
+
+#### libs ####
+
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+# library(reactablefmtr)
+library(sf)
+# library(threemc)
+library(data.table)
+devtools::load_all("../threemc")
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+source("Shiny/src/functions.R")
+
+#### Metadata ####
+
+orderly_root <- here::here()
+
+spec_age_group <- "10-29"
+spec_years <- c(2010, 2020)
+
+## for tabulating surveys
+# remove circumcisions with missing type?
+rm_missing_type <- FALSE
+
+start_year <- 2002
+cens_age <- 59
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
+ssa_countries <- case_when(
+  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
+  ssa_countries == "Congo - Brazzaville" ~ "Congo",
+  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
+  ssa_countries == "Gambia"              ~ "The Gambia",
+  TRUE                                   ~ ssa_countries
+)
+
+# countries/regions which have been targeted for 90% circumcision by 2021
+target_iso3 <- c(
+  # In Ethiopia Gambella is the only target province
+  "BWA", "ETH_1_15", "KEN", "LSO", "MWI", "MOZ", "NAM", 
+  "RWA", "ZAF", "SWZ", "UGA", "TZA", "ZMB", "ZWE"
+)
+
[…]

### 2023-04-27 paper/outline/paper_outline.tex
Add Jeff's notes to paper outline, which is basically finished

% Created 2023-03-30 Thu 18:31
% Intended LaTeX compiler: pdflatex
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{30th March 2023}
\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
\begin{document}

\maketitle

\section*{Abstract}
\label{sec:org9ed8edd}
\subsection*{Background}
\label{sec:org1fc78ed}
In 2016, UNAIDS developed a Fast-Track strategy that targeted 90$\backslash$% coverage
male circumcision (MC) among men aged 10-29 years by 2021 in priority countries in sub-Saharan 
Africa (SSA) to reduce HIV incidence. There is substantial variation across subnational 
regions within countries in both traditional male circumcision (TMC) practices and progress
towards implementation of voluntary medical male circumcision (VMMC). Tracking progress and
remaining gaps towards VMMC HIV prevention targets requires detailed district-level circumcision
coverage data.

\subsection*{Methods}
\label{sec:org72fee94}
We analysed self-reported data on male circumcision from 120 nationally representative household
surveys conducted in 33 SSA countries between 2006-2020. A spatio-temporal Bayesian
competing-risks time-to-event model was used to estimate rates of traditional and medical
circumcision by age, location, and time. Circumcision coverage in 2020 was projected assuming
continuation of estimated age-specific rates, with probabilistic uncertainty. An R package was
developed to ??? reproducible.

\subsection*{Results}
\label{sec:orgb447b73}
Across 33 countries, from 2010 to 2020 an estimated x million men (x$\backslash$% CI x-x million)
were newly circumcised, of whom x million (x - x million) were medically circumcised, and
x million (x - x million) traditionally circumcised. In 2020, MC coverage among men 10-29
years ranged from x$\backslash$% (x$\backslash$% - x$\backslash$%) in Zimbabwe (?) to x$\backslash$% (x$\backslash$%-x$\backslash$%) in Togo. MMC coverage
ranged from x$\backslash$% (x$\backslash$%-x$\backslash$%) in Malawi to x$\backslash$% (x$\backslash$%-x$\backslash$%) in Tanzania, and TMC coverage
from x$\backslash$% (x$\backslash$%-x$\backslash$%) in Eswatini to x$\backslash$% (x$\backslash$%-x$\backslash$%) in Ethiopia. The largest increase in MMC
coverage was in Lesotho from x$\backslash$% to x$\backslash$%. Within countries, the median difference in MC
coverage between the districts with lowest and highest coverage was x$\backslash$%, with the smallest
variation in Eswatini (x$\backslash$% to x$\backslash$%) and largest in Zambia (x$\backslash$% to x$\backslash$%). x million men aged
10-29 need to be circumcised to reach 90$\backslash$% coverage in all countries. By 2020, x countries
achieved their 90\% circumcision coverage target.

\subsection*{Conclusions}
\label{sec:orge3e6bd2}
VMMC programmes have made substantial, but uneven, progress towards male circumcision targets. Granular district and age-stratified data provide information for focusing further programme implementation.

\section*{Background}
\label{sec:org526972c}

\begin{itemize}
\item Section on HIV in SSA
\item Section on circumcision (VMMC reduces male to female incidence by 60\%, etc)
\item Section on existing efforts to estimate circumcision (Cork model, DMPPT2, threemc developed by
Matthew Thomas)
\end{itemize}

\section*{Data}
\label{sec:org697fb8d}

\begin{itemize}
\item Anything on shapefiles and area boundary classification needed?
\end{itemize}

\subsection*{Surveys}
\label{sec:orgfecf39a}

\begin{itemize}
\item 120 household surveys conducted in 33 SSA countries 2002-2019
\item Self-reported circumcision:
\begin{itemize}
\item Status (MC vs uncircumcised),
\item Type (MMC vs TMC),
\item Year, and
\item Age
\end{itemize}
\end{itemize}
recorded.
\begin{itemize}
\item Major survey series (DHS, AIS, PHIA, MICS, HSRC in ZAF)
\item Individual-level data: self-reported circumcision status by male respondents
\item Respondents located to districts using cluster geocoordinates
\item Located to admin 1 (province) where coordinates not available (MICS)
VMMC programme data not used

\item Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC. Otherwise, circumcisions are TMC. Where no data is present on location or provider, circumcision type is treated as "Missing".
Note: Can I use Jeff's images of DHS and PHIA survey questions in presentations?
Would be useful in explaining this point.

\item Individual-level household survey data provide direct estimates of circumcision rates over time and by type for years preceding survey.

\item Direct estimates of TMC practices, age at circumcision, VMMC impact

\item Also include participation rates from surveys.

\item Figure: Figure from poster with surveys of each provider for each country, caption:
"Figure 1: Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type."
\end{itemize}

\subsection*{Populations}
\label{sec:org8e38f82}

\begin{itemize}
\item Sub-national populations from WorldPop (reference) (also are they all from WorldPop??)
\end{itemize}

\section*{Methods}
\label{sec:org8e2d064}

\subsection*{Threemc}
\label{sec:orgc2fd8b2}
\begin{itemize}
\item Used threemc developed in Thomas et. al. to model 33 countries. Circumcision rates, incidence and coverage (i.e. cumulative incidence) estimated, with associated 95\% uncertainty bounds.
Countries modelled at the PSNU area level, or the most granular level used in surveys, and poststratifed to produce estimates for "parent" regions. 
Some changes in the model from the original threemc model include:
\begin{itemize}
\item Allowing for survey results for less granular areas to inform likelihood estimation within model (Matt said he would write an explanation of this, possibly for the Appendix)
\item Including a temporal effect for TMC, which was previously assumed to be constant over time in
the case of South Africa, but in many countries, particularly in WCA, can be seen to decrease
(possibly refer to empirical rates plots for TMC in the appendix).
\end{itemize}
\end{itemize}

\subsection*{Choice of model specification}
\label{sec:org85fb5a7}

\begin{itemize}
\item Choose best model specification (i.e. which terms to include (TMC, paediatric MMC, etc)) for
each country using within-sample validation.
\item Include figures comparing models for each country in appendix, refer to them here.
\item Credible interval coverage, ELPD, CRPS and fit statistics (ME, MSE, RMSE) used to inform
decision.
\end{itemize}

\subsubsection*{(Very!) Rough draft (without figures and conclusions from validations on model choice)}
\label{sec:org2a43f36}

Qualitatively, we can make some presumptions about certain countries and their circumcision patterns.

\begin{itemize}
\item Non-VMMC countries
\label{sec:orgd0f7914}
Firstly, in non-VMMC countries, traditional circumcision will likely make up the bulk of circumcision (or at least has done historically).
Therefore, most medical circumcisions in these countries will likely be MMC-T, and so likely also be performed on paediatric individuals in traditional settings.
Also, because much of MMC performed in non-VMMC countries will be as a result of converting TMC to MMC-T, the assumption that traditional circumcision rates in these countries have been relatively constant is likely inaccurate.
Instead, it is likely that circumcision patterns have undergone a generational change as a result of general development in their countries (could definitely say this better). As such, a time effect for TMC in non-VMMC countries is very important for accurately modelling and understanding their circumcision patterns, particularly in how the relative makeup of M
(Note: would be a good idea to look into surveys for these countries to see if this checks out! I.e. for non-VMMC and VMMC surveys, it might be a good idea to compare the number of people with different circumcision types for location and provider,  to substantiate this assumption)

\item VMMC countries
\label{sec:orgec5a9ea}
For VMMC countries, changes (i.e. increases) in circumcision have, naturally, been driven by the VMMC programmes themselves in these countries.
As such, we can be confident that MMC of paediatric individuals is minimal, in line with UNAIDS VMMC policies (reference, word better, probably too confident!), and so we assume a constant rate of paedaitric MMC over time, that is to say, none.
TMC is slightly more complicated.
In some VMMC countries TMC appears to have stayed relatively stable, while in others, particularly Mozambique and Zambia (any more? Could show map of negative changes in TMC), MMC-T, i.e. conversion of MMC to TMC, appears to have occured (again, word better?)
Rather than treating each VMMC countries' TMC rate on an individual basis, merely for the sake of a slightly more parsimonious process model and a less computationally expensive modelling process, we decided it was much simpler to allow TMC to vary over time, as we have done for non-VMMC countries.

\item ?
\label{sec:orga66d62a}

We have also performed a quantitative analysis on how the choice of including a constant paediatric MMC rate and a constant TMC rate effect the fit of our model, by looking at the within-sample posterior predictive distribution and some error statistics associated with this distribution when compared to our survey estimates of circumcision coverage. (\ldots{}?)
\end{itemize}

\subsection*{Model Calibration and choice of temporal prior}
\label{sec:orgd257719}

\begin{itemize}
\item Calibrated MMC-related variance hyperparameters using grid search. Idea is to use information
from countries with more surveys to inform variance (which was suspected to be underestimated)
in countries with fewer surveys, analagous to using a model with partial pooling for each
country in the Sub-Saharan region, which would be much too computationally expensive to fit.
\end{itemize}

\subsubsection*{Another very rough draft}
\label{sec:org23cd822}

For some VMMC priority countries, we do not have access to more recent survey data. 
One particular country where this is the case is Tanzania, whose most recent survey is a 2016 PHIA survey.
In these circumstances, VMMC programme data is an available source of more recent data.
The DMPPT2 model explicitly uses this data to estimate MMC. 
\sout{Putting aside suspected problems associated with the programme data, such as individuals availing of VMMC in districts in which they are not residents, and suspected reporting biases with countries like TZA and Zimbabwe,} the results of DMPPT2, particularly at the national level, where travel between districts is ignored, suggest that VMMC may have scaled up at a rate not anticipated by our
model fit using older surveys.
This is consistent with the out-of-sample (OOS) evaluations of our model fit to countries like ZWE, where removing access to the most recent (2018 DHS) survey similarly
underestimates VMMC scale up (???!!!).
Hence, we feel that our model likely underestimates it's own uncertainty with regards to predicting circumcision coverage for progressively later years than our last
available surveys, particularly in the case of VMMC priority countries which started with a low circumcision coverage. What we desire is a more dramatic "fanning" out of
our prediction interval as we forecast further from the last available survey data, again, particularly for VMMC countries in which there may have been a large scale up
in circumcision coverage since the last available survey, representing an intervention via VMMC programmes which our model, fit for each country separately, is not equipped to
handle.

Due to computational constraints, we cannot model each country together as one singular area hierarchy, which, through the neighbourhood correlation structure inherent in the model,
would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older surveys.
One "next best thing" we can do is use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries
with less recent survey data available.

To qualitively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data and comparing posterior predictions
to the survey-estimated circumcision coverage. 
(Something about this incorporating survey design/effective sample sizes etc should probably be here)
These comparisons consisted of comparisons of mean predictions, using ELPD and CRPS scores, as well as error statistics such as the ME, RME and RMSE, and evaluations of the
"calibration" of our model with regards to it's posterior predictive uncertainty, for each unique region-year-age-type (what does Matt use for this) stratum of our data.

This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution. A "good" calibration
was regarded as one in which roughly 50\% of (training) survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range. In general.

Two principal components of the model largely determine how the uncertainty of our model predicitions scale up over time: 
\begin{enumerate}
\item \textbf{The choice of temporal prior}: threemc uses an AR 1 temporal prior. However, this is easily replaceable with, for example, a random walk (RW) prior. These temporal priors
differ consireably in how they use previous estimates to inform future predictions, and so we appraised a number of choices for our temporal prior to determine if there
was a preferable alternative to our default AR 1 temporal prior, with regards to the particular context of increasing year-on-year uncertainty bounds.
\item The choice of (log) time variance hyperparameters: The "naive" optimised time-related variance hyperparameters varied significantly, but in general certain patterns and values
for these hyperparameters could be associated with larger uncertainty bounds over time, and a greater "fanning" out of these bounds for successive prediction years. (Give
examples here!!)
\end{enumerate}

\emph{For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were}
\emph{ignored in our calibration efforts with this model} (need to show proof of this!!!)

\section*{Results}
\label{sec:org0ad58a5}

\section*{}
\label{sec:org4d19a77}

\section*{Discussion}
\label{sec:org69af492}

\begin{itemize}
\item ???
\ldots{}
\end{itemize}
\subsection*{Limitations}
\label{sec:org98b70b2}
\begin{itemize}
\item Computational constraints mean we can not include a spacetime interaction effect for TMC, and
also means we must calibrate our model in the method described above, rather than performing a
partially pooled model for the entire SSA region, as would be optimal for using information
from countries with more surveys to inform predicitons for countries with less available data.
\item Of threemc: If number of circumcisions increases (such as when population increases), this may
cause TMCs to increase, when they're supposed to stay constant or decrease.
\end{itemize}

\subsection*{Challenges:}
\label{sec:org217c727}
\begin{itemize}
\item Inconsistent MC self-reporting by same cohort in successive surveys, e.g. in 2017 survey, men
30-34 report higher \% circumcised in 2012 than ‘same’ men age 25-29 in 2012 survey.
Affects circumcision level, and distribution by type.
\begin{itemize}
\item ‘Replacement’ of traditional circumcision by medical circumcision
Evidence of this in surveys from several countries; work in progress
Also not fully accounted for in DMPPT2 baseline coverage inputs.
\item In some cases, survey providers report different coverage (such as in Lesotho and Uganda for DHS and PHIA)
\item Surveys imply different level of scale-up than programme data
For several countries, surveys suggest fewer VMMCs conducted than programme data.
Possibly points to biases in programme data.
\item Some countries have only one usable survey available, providing less data to the model and for
our out-of-sample validations.
\item More!!
\end{itemize}
\end{itemize}

\section*{Appendix}
\label{sec:org7cc2c04}

\begin{itemize}
\item Table of surveys
\item Empirical rates plots from each survey
\item Methods section about threemc (think Matt is going to write this)
\item Plots for choice of model specification:
\begin{itemize}
\item Comparing different model specifications for each country, plotting coverage against time
and age group, respectively
\end{itemize}
\item Plots for model calibration and choice of temporal prior:
\begin{itemize}
\item Calibration plots: Boxplots (and/or violin plots?), possibly 3D plots such as 3d dot plot  and/or ternary plot
\end{itemize}
\item Country-specific plots from Matt's paper
\item Country-specific comparison plots to survey and DMPPT2 results
\item 
\end{itemize}
\end{document}

### 2023-04-27 paper/scripts/02_methods_data.R
Script to produce figure 1

@@ -1,0 +1,376 @@
+#### Pull through data and plots required for Data subsection of Methods ####
+
+# May end up joining this with other scripts or even copying to org file
+
+# This script also contains info on missing values etc which may be of 
+# interest in our appendices
+
+# stopifnot(dirname(getwd()) == "threemc-orderly")
+
+#### Libs ####
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+source("Shiny/src/functions.R") # plotting functions
+
+#### Metadata ####
+
+# TODO: remove unneeded here 
+orderly_root <- getwd()
+
+spec_age_group <- "10-29" # change? 
+spec_years <- c(2010, 2020)
+
+# for tabulating surveys: 
+rm_missing_type <- FALSE # remove circumcisions with missing type?
+start_year <- 2000 # minimum survey year
+cens_age <- 59 # maximum circumcision age
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
+ssa_countries <- dplyr::case_when(
+  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
+  ssa_countries == "Congo - Brazzaville" ~ "Congo",
+  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
+  ssa_countries == "Gambia"              ~ "The Gambia",
+  TRUE                                   ~ ssa_countries
+)
+
+#### Load Data ####
+
+# pull most recent results for age groups
+archives <- orderly::orderly_list_archive()
+
+# function to load data from orderly archive
+load_archive <- function(task, 
[…]

### 2023-04-27 paper/scripts/02_methods_data.R
Add data of interest in data section of Methods to output

@@ -5,7 +5,11 @@
 # This script also contains info on missing values etc which may be of 
 # interest in our appendices
 
+# TODO: Check number of surveys, seems very low
+# TODO: Remove BWA from plot
+
 # stopifnot(dirname(getwd()) == "threemc-orderly")
+while(basename(getwd()) != "threemc-orderly") setwd("../.")
 
 #### Libs ####
 library(dplyr, warn.conflicts = FALSE)
@@ -45,6 +49,9 @@ ssa_iso3 <- sort(c(
   "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
 ))
 
+# countries for which we have no results
+no_mod_iso3 <- c("BWA", "CAF", "GNB")
+
 ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
 ssa_countries <- dplyr::case_when(
   ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
@@ -53,6 +60,7 @@ ssa_countries <- dplyr::case_when(
   ssa_countries == "Gambia"              ~ "The Gambia",
   TRUE                                   ~ ssa_countries
 )
+
 
 #### Load Data ####
 
@@ -96,12 +104,14 @@ areas <- load_archive(
 )
 
 # pull surveys
-survey_circumcision <- load_archive(
+survey_circumcision_orig <- survey_circumcision <- load_archive(
   "00b3_survey_join", 
   orderly_root, 
   "survey_circumcision.csv.gz", 
   query = "latest(parameter:is_paper == TRUE)"
-)
+) %>% 
+  filter(!iso3 %in% no_mod_iso3)
+
 # pull agegroup populations
 populations <- load_archive(
   "00c4_pops_aggregate", 
@@ -139,7 +149,7 @@ provider_key <- tibble::tribble(
   "DHS",     "Demographic and Health Survey",
   "PHIA",    "Population-Based HIV Impact Assessment",
   "HSRC",    "Human Sciences Research Council",
-  "BAIS",    "Botswana Aids Impact Survey",
+  # "BAIS",    "Botswana Aids Impact Survey",
   "MICS",    "Multiple Indicator Cluster Survey",
   "SBS",     "Sexual Behavior Survey"
 )
[…]

### 2023-06-19 paper/scripts/00_funs.R
Add funs to source file

@@ -26,3 +26,89 @@ load_archive <- function(task,
     file 
   ))
 }
+
+# takes a data frame of parameters and performs an orderly search on each row.
+# By default, can also load these files (also ran parallel)
+load_orderly_data <- function(
+    # parameters fed to orderly::orderly_search
+  task,
+  parameters = NULL, # needs to be a df, not a list!
+  query = NULL, 
+  filenames = NULL, # name of specific artefact file to load, if desired
+  dirs = NULL, # optionally just provide dirs to skip orderly_search
+  load_fun = readr::read_csv, # function to load data with, if so desired
+  ncores = max(1, parallel::detectCores() - 2), 
+  ...
+) {
+  
+  # check that either parameters & query or just dirs have been provided
+  # (could also add a query parser here for the parameters!)
+  # stopifnot((!is.null(parameters) & !is.null(query)) || !is.null(dirs))
+  
+  if (is.null(dirs)) {
+    # search parameter space specified for previously run orderly tasks
+    if (!is.null(parameters)) {
+      dirs <- unlist(parallel::mclapply(seq_len(nrow(parameters)), function(i) {
+        # give progress (no longer works properly w/ mclapply rather than lapply)
+        # message(100 * (i / nrow(parameters)), "% completed") 
+        system(sprintf(
+          'echo "\n%s\n"', 
+          paste0(100 * (i / nrow(parameters)), "% completed", collapse = "")
+        ))
+        orderly::orderly_search(
+          query = query, 
+          name = task, 
+          parameters = c(parameters[i, ]) # coerces pars df to a list 
+        )
+      }, mc.cores = ncores))  
+    } else {
+      dirs <- orderly::orderly_search(
+        query = query, 
+        name = task
+      )
+    }
+  }
+  
+  # return NAs in parameters search, but only load files from found directories
+  dirs_return <- dirs
+  dirs <- dirs[!is.na(dirs)]
+  # return dirs if filenames unspecified
+  if (is.null(filenames)) return(list("dirs" = dirs_return))
+  files <- file.path(
+    "archive", 
+    task,
+    dirs, 
+    "artefacts/", # prob don't need this? I just structure my tasks this way
+    filenames
+  )
+  # return filenames if load_fun isn't specified
[…]

### 2023-06-19 paper/scripts/032_results.R
rates plot for all ages

@@ -645,9 +645,9 @@ p5 <- plt_coverage_year_national(
   results_agegroup = results_agegroup_rate,
   areas            = areas,
   last_surveys     = last_surveys,
-  spec_age_group   = spec_age_group,
+  spec_age_group   = "0+",
   # spec_years       = spec_years,
-  spec_years       = spec_years[1]:last(spec_years),
+  spec_years       = spec_years,
   spec_model       = "No program data", 
   spec_types = paste(c("MC", "MMC", "TMC"), "probability"),
   main             = "",
@@ -716,9 +716,12 @@ p5_geo +
     legend.text = element_text(size = 20, face = "bold")
   )
 
-saveRDS(p5_geo, "paper_poster_plots/paper/data/0x_circ_type_vs_age_2020.RDS")
-p5_geo <- readRDS("paper_poster_plots/paper/data/0x_circ_type_vs_age_2020.RDS")
-
+saveRDS(p5_geo, "paper_poster_plots/paper/data/05_circ_rates.RDS")
+ggsave("paper_poster_plots/paper/plots/05_circ_rates.png",
+       p5_geo,
+       width = 12, 
+       height = 10,
+       units = "in")
 
 #### Figure x: National Level Coverage 2010-2020 10-29 year olds ####
 

### 2023-06-19 paper/paper.tex
Add more references to paper
Upload paper tex file

@@
-% Created 2023-03-30 Thu 17:04
+% Created 2023-05-30 Tue 07:57
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{hyperref}
+\usepackage{color}
+\usepackage{listings}
+\usepackage{minted}
 \usepackage{authblk}
@@
 
-\section{Background}
-\label{sec:org3a33a7d}
+\section{Methods}
+\label{sec:orga131cc6}
 
-HIV remains the single largest cause of years of life lost among adolescent boys and men of reproductive age in eastern and southern Africa.
+\subsection{Data}
+\label{sec:org020fc8c}
 
-Voluntary Male medical circumcision (VMMC) reduces the rate of male-to-female HIV incidence by 60\%.
-Efficient, cost-effective, one-time procedure for preventing HIV transmission.
+Several major survey series included questions on male circumcision status, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys.
 
-Matt's model \ldots{} (Thomas, Matthew L.
-and Zuma, Khangelani and Loykissoonlal, Dayanund and Dube, Bridget and Vranken, Peter and Porter, Sarah E.
-and Kripke, Katharine and Seatlhodi, Thapelo and Meyer-Rath, Gesine and Johnson, Leigh F.
-and Eaton, Jeffrey W., 2021)
+These surveys provided individual-level data on self-reported circumcision status by male respondents, and from this we estimated circumcision rates over time and by type for the years proceeding each survey.
+The following questions were of interest:
+\begin{itemize}
+\item The circumcision status of the male individual,
+\item The circumcision provider: whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown,
+\item The circumcision location: whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown
+\item The circumcision year, and
+\item The date of birth and age at response and circumcision.
+\end{itemize}
 
-\newpage
-\section{Data}
-\label{sec:org0422724}
+The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates.
+PHIA surveys did not include a question for circumcision location.
+Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC.
+Otherwise, circumcisions are TMC.
+Where no data is present on location or provider, circumcision type is treated as "Missing".
 
-120 household surveys conducted in 33 SSA countries 2002-2019
-Self-reported circumcision:
-o Status (MC vs uncircumcised), 
-o Type (MMC vs TMC), 
-o Year, and
-o Age 
-recorded
-Sub-national populations from WorldPop (reference)
+Respondents were located to their districts using masked cluster geocoordinates.
+Where these coordinates were unavailable, as in several MICS surveys, respondents were located to their admin level 1 area hierarchy, most often corresponding to a province.
 
-Major survey series (DHS, AIS, PHIA, MICS, HSRC in ZAF)
-Individual-level data: self-reported circumcision status  by male respondents
-Respondents located to districts using cluster geocoordinates
-Located to admin 1 (province) where coordinates not available (MICS)
-VMMC programme data not used
-
-Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC
-Otherwise, circumcisions are TMC
-Where no data is present on location or provider, circumcision type  Missing
-
-Individual-level household survey data provide direct estimates of circumcision rates over time and by type for years preceding survey
-
- Direct estimates of TMC practices, age at circumcision, VMMC impact
-
-\newpage
-
-\section{Methods}
-\label{sec:org69a085f}
+Sub-national populations from WorldPop were used to calculate circumcision coverage from circumcision rates. (reference)
 
 \subsection{Model}
-\label{sec:org2077286}
+\label{sec:org681dda6}
 
-Bayesian spatio-temporal, competing-risks, time-to-event model
-Stratified by age, location and time
-Rates of TMC and medical male circumcision (MMC) estimated
-Coverage in 2020 projected assuming continuation of estimated age-specific rates with probabilistic uncertainty
-Important assumption: Probability of traditional male initiation ceremonies (TMICs) constant over time (needed? Might lead to a lot of questions!)
+"threemc" (Matt's model for male circumcision) (or "Multi-level model for male circumcision"?) is
+a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). We have extended
+this model from its initial application in South Africa to
+33
+countries within the SSA region.
+The model produces estimates of circumcision rates, incidence and coverage (i.e.
+cumulative indidence), with associated uncertainty bounds, stratified by type, year, age and location.
+Circumcision rates are projected after their most recent household survey
+assuming continuation of estimated age-specific rates, with probabilistic uncertainty. Estimates
+for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
 
-Model stratified by:
-Age
-District
-circumcision type (traditional / medical)
+A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practises and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
+MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the  main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
 
-TMC \& MMC rates estimated (by age, district, and time)
-Spatial smoothing allows for district level estimates
+Countries were modelled at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
+Model estimates were weighted by population and post-stratified to produce estimates for their "parent" regions.
 
-Circumcision coverage since most recent HH survey: projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty
+Some additional features were added to threemc during the course of this analysis: 
+\begin{itemize}
+\item Where no information on circumcision type was available for every survey in a given country, a type-agnostic version of the model was used,
+\item Survey estimates for less granular areas were used to inform likelihood estimation for their "child" areas, where previously they were ignored,
+\item optional addition of a temporal effect for TMC, due to the suggestion of survey estimates that TMC practices may be changing, even in non-VMMC target countries, over time, and
+\item an optional random walk (RW) temporal prior was implemented, where previously only an auto-regressive (AR1) temporal prior was available.
+\end{itemize}
 
-Important assumption: TMC rate assumed constant over time
+\subsection{Model Specification}
+\label{sec:orgaf7fa2a}
 
-\newpage
+In our choice of model specification, we were interested in two main assumptions/features of the
+model:
+\begin{itemize}
+\item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
+\item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
+\end{itemize}
 
-Samples drawn from model fit, weighted by population and aggregated, to produce estimates for less granular regions (e.g. District to Province aggregation).
-Computed posterior summary statistics for coverage, circumcision incidence and probability of being circumcised. 
-Done for all strata, for both discrete ages and “binned” age groups.
+If possible, we hoped to use the same model for every country, or failing that, come up with a
+satisfactory choice of model specification which would make sense both qualitatively and
+quantitatively.
+
+Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
+In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
+Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
+This suggests that MMCs in these countries are likely to be on paediatric individuals in traditional settings, so the assumption of constant and
+negligible paedaitric MMC could be a poor one. 
+Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
+It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
+patterns in non-VMMC countries.
+
+Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
+As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
+It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
+Historical TMC patterns in these countries, differ significantly, even subnationally.
+It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
+In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
+We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
+
+We have also performed a quantitative analysis of the different model specifications available
+to us. A more detailed treatment of this can be found in section x of the appendix.
+
+For each country, we fit a model for each possible model specification for threemc, that is:
+\begin{itemize}
+\item for each choice of temporal prior, namely AR1, RW1 and RW2,
+\item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
+\item a choice of whether to include a temporal effect for TMC.
+\end{itemize}
+Thus totalling 12 possible models for each country.
+These models were fit to all of the survey data available, rather than a subset of the data.
+This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
+As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
+
+The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
+Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
+
+Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
+Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
+This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
+A "good" calibration was regarded as one in which roughly 50\% of survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range.
+Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
+
+Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
+
+For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
+The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
+This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
+It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
+Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
+These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
+
+In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
+This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
+However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
+As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
+
+Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
+In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
+For completeness, we decided to include a temporal effect for TMC in the model specification for VMMC priority countries.
+
+It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
+A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
+
+\subsection{Model Calibration and Choice of Temporal Prior}
+\label{sec:orga44afa6}
+
+For some VMMC priority countries, we did not have access to more recent survey data. 
+One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
+In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
+VMMC programme data was an available source of more recent circumcision data.
+The DMPPT2 model explicitly used this data to estimate MMC. 
+The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
+This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
+Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
+A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
+
+The two main drivers of uncertainty over time in threemc were:
+\begin{itemize}
+\item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
+\item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
+\end{itemize}
+The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
+
+Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
+One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
+To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
+A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
+For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
+
+TODO: Finish this write up!
+TODO: Add results! Also add ternary plot
 
 \section{Results}
-\label{sec:org634cf32}
+\label{sec:orgfc68fc8}
+Our data consisted of 109 nationally representative household surveys conducted in 33 SSA countries between 2002 and 2019.
+x sub-national areas amongst these coutries were included in these surveys and modelled.
+Of these 109 surveys, 104 contained sufficent information on circumcision, as outlined in the Methods section of this paper.
 
-\#+latex \newpage
+These remaining surveys consisted of 711,715 individuals respondents from 108 birth cohorts from 1903 to 2016.
+The sample size per survey ranged from 21,114 in the South Africa 2017 HSRC survey to 1,459 in the Eswatini 2014 MICS survey.
+
+There was significant censoring and missing data even in the remaining surveys. 
+Left censoring of circumcision status, analagous to unknown circumcision age, averaged  34.438\% across all surveys, and ranged from 0\% in the Rwanda 2008 DHS survey to 99.408\% in the Niger 2006 DHS survey.
+17 surveys had more than 90\% left censoring of circumcision age, with 42 surveys having less than 10\% left censoring.
+No information on age at circumcision was present in the 2004 and 2008 Botswana Aids Impact Surveys.
+This complete left censoring of circumcised individuals meant that threemc could not be fit to Botswana.
+Right censoring of circumcision status, indicating as of yet uncircumcised individuals, averaged 35.299\% across all surveys, ranging from 0.399\% in the The Gambia 2018 MICS survey to 91.432\% in the Eswatini 2006 DHS survey.
+
+On average across all surveys, 1.788\% of respondents did not respond to either the circumcision location or provider question, and so had unknown circumcision type. 
+This was lowest in the Burundi 2010 DHS survey, at 0\%, and highest in the South Africa 2002 HSRC survey, at 29.545\%.
+5 countries had unknown circumcision type; DR Congo, Guinea, Liberia, Niger and Senegal. 
+Amongst these countries, left censoring averaged 98.457\%. 
+However, the mean survey circumcision coverage amongst these same countries was 98.457\%, which may explain the relative lack of circumcision information available in their surveys.
+
+In addition to Botswana, Guinea-Bissau, Equitorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit threemc in these countries either.
+
+More information on individual surveys, including participation rates, can be found in section x of the appendix.
+
+\begin{center}
+\includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
+\end{center}
+
+\emph{Figure 1: Household surveys detailing circumcision patterns in SSA.
+The colour and size of points are determined by the provider and sample size of each respective survey.
+Triangular points have no information on circumcision type.}
+
+\subsection{Subnational Variation in Total, Medical \& Traditional Circumcision over time}
+\label{sec:org0d1ffe6}
+
+\emph{Figure 2: Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries.} 
+\emph{Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana.}
+
+TODO: Remove superfluous whitespace here!
+
+Between 2007, the year VMMC programme implementation began, and 2020, an estimated x million men(95\% CI: x - x million) were newly circumcised. 
+Of these, x million (x - x million) were MMCS, along with x million (x - x million) TMCS. 
+This translated to an increase in MC for the SSA region of x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in  2020. 
+MC in 2020 ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x, while MMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x and TMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x.
+The largest percentage increase in MC coverage from 2010 to 2020 was x\% (x\% - x\%) in x, from x\% (x\% - x\%) to x (x\% - x\%), while for MMC it was x\% (x\% - x\%) in x. 
+The number of annual MCs performed increased from x (x to x) in 2006 to x (x to x) in 2020, a growth of x (x to x) annually. 
+Amongst these, x (x to x) were MMCs in 2006, while in 2020 x (x to x) MMCs were performed, representing an increase in x (x to x) in MMCs performed annually. 
+TMC did not increase anywhere,  and actually decreased in several countries from 2010 to 2020. 
+This is the focus of a later section of our results.
+
+For VMMC countries, MC increased from x\% (x\% - x\%) to x\% (x\% - x\%), largely driven by an increase in MMC from x\% (x\% to x\%)  to x\% (x\% - x\%). 
+In constrast, for the non-VMMC countries, MC increased from x\% (x\% - x\%) to x\% (x\% - x\%), with MMC going from x\% (x\% to x\%)  to x\% (x\% - x\%). 
+TMC in 2020 for VMMC countries averaged x\% (x\% - x\%), compared to x\% (x\% - x\%) in non-VMMC countries.
+
+Increases in MC coverage from 2010 to 2020 were very heterogeneous, with VMMC programmes generally targeting subnational regions where HIV burden is high and where VMMC as a HIV prevention method is better acknowledged (ref.
+42 in Matt's paper)
+In ESA countries, MC in 2010 averaged x\% (x\% - x\%). 
+This increased to x\% (x\% - x\%) in 2020. MMC increased from x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in 2020. 
+In constant, in WCA MC in 2010 averaged x\% (x\% - x\%), while in 2020 it averaged x\% (x\% - x\%).
+MMC in WCA increased from x\% (x\% - x\%)
+2020 TMC in ESA countries averaged x\% (x\% - x\%), compared to x\% (x\% - x\%) in WCA countries.
+
+\emph{Figure 3: District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.}
+\emph{Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).}
+\emph{Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}
+
+Within countries, the median difference in MC coverage between the districts with lowest and highest coverage in 2020 was x\% (x\% - x\%).
+For ESA countries, this was x\% (x\% - x\%), in contrast to WCA countries, where it was x\% (x\% - x\%).
+The largest variation overall (and ESA) was in x, from x\% in x to x\% in x, while the largest variation for WCA countries was x, from x\% in x to x\% in x. 
+In total, the mean percentage of districts in each country with greater than 90\% MC coverage amongst those aged 10-29 was x\%. In ESA, this was x\%, while in WCA, this was x\%.
+
+\subsection{Subnational Variation in Total, Medical \& Traditional Circumcision Across Different Ages}
+\label{sec:org92e0f37}
+
+\emph{Figure 4: Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020.
+The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy.
+Purple areas represent countries where circumcision type could not be ascertained from surveys.}
+
+Age at circumcision differed greatly by circumcision type and location. 
+The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was x, reflecting VMMC focus on these ages. 
+The age group with the highest MC coverage in 2020 was x, in contrast to 2006, where this age group was x. 
+The age group with the highest MMC coverage in 2020 was x, while for TMC coverage this age group was x. 
+The average age of MC in 2020 in SSA was x, compared to x in 2006. 
+For MMC, the average age at circumcision in 2020 was x, compared to x in 2006, while for TMC the average age was x in 2020, compared to x in 2006. 
+The average age of MC in 2020 for ESA was x, while in WCA it was x.
+
+\subsection{Decrease in TMC in SSA region Over Time}
+\label{sec:org5fb5e18}
+\emph{Figure 6: Number of men aged 10-29 years who were medically circumcised and traditionally circumcised each year between 2010 and 2020.
+The lighter shaded area represents projection after the most recent household survey.
+Purple areas represent countries where circumcision type could not be ascertained from surveys.}
+
+The average TMC coverage in SSA in 2006 was x\% (x\% to x\%). 
+This fell to x\% (x\% to x\%) in 2020, representing a decrease of x\% (x\% to x\%). 
+In ESA, TMC coverage was x\% (x\% to x\%) in 2006, compared to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) decrease.
+In constrast, TMC coverage in WCA was x\% (x\% to x\%) versus x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) fall.
+In 2006, x (x to x) TMCs were performed, while in 2020 this was reduced to x (x to x), representing a x (x to x) decrease in annual TMCs.
+In ESA, the annual number of TMCs performed dropped from x (x to x) in 2006 to x (x to x) in 2020, a x (x to x) drop. 
+In WSA, this number fell from x (x to x) in 2006 to x (x to x) in 2020, a fall of x (x to x).
+For the 10-29 age group, TMC coverage was reduced from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a drop of x\% (x\% to x\%).
+In VMMC countries, this was reduced from x\% (x\% to x\%) to x\% (x\% to x\%) from 2006 to 2020, while even in non-VMMC countries this decreased from x\% (x\% to x\%) to x\% (x\% to x\%). 
+The largest decrease in TMC coverage from 2006 to 2020 was in x, from x\% (x\% to x\%) to x\% (x\% to x\%). 
+[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from x\% (x\% to x\%) to x\% (x\% to x\%) in x.
+
+\subsection{UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries}
+\label{sec:orgf9204d9}
+
+Amongst the 13 VMMC priority countries modelled, just x countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, x and x. 
+MC coverage across these countries increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020. 
+X (x to x) circumcisions were performed between 2007 and 2020 in these countries. 
+Of these, x (x to x) were MMCs. 
+No countries were expected to have reached this goal in all districts. 
+The number of annual MCs increased from x (x to x) in 2006 to x (x to x) in 2020. 
+x (x to x) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, x (x to x) times the projected number of MCs for 2020. 
+The largest increase in MC coverage amongst VMMC priority countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase. 
+In contrast, the lowest increase in MC coverage in these countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.
+
+However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries. 
+x/x districts in these countries were expected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from x/x in 2006, before VMMC programmes began. 
+Even in x, where MC was projected to be lowest in 2020, x/x districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
+MC coverage there increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.
+
+TODO: Add some kind of table here!
+
+\subsection{Comparison to results of DMPPT2 model}
+\label{sec:orge0178ca}
+
+TODO: Write this section!
 
 \section{Discussion}
-\label{sec:orgce42292}
+\label{sec:orgca35e01}
 
-\textbf{Challenges}
-Inconsistent MC self-reporting by same cohort in successive surveys
-E.g. in 2017 survey, men 30-34 report higher \% circumcised in 2012 than ‘same’ men age 25-29 in 2012 survey
-Affects circumcision level, and distribution by type
+Sub-national MC has increased significantly from 2006 to 2020. 
+However, there is sharp national and sub-national differences in MC coverage and type. 
+Despite this, some obvious regional patterns can be observed to have emerged over this time period. 
+Broadly speaking, WCA has much higher MC coverage, in line with greater cultural practice of TMC associated with these countries. 
+MC coverage is generally more homogeneous in WCA countries. 
+Even in WCA, where VMMC programmes have not been implemented, there has been significant growth in the number of MMCs peformed. 
+In contrast, in ESA MC and particularly TMC coverage is generally lower, although this varies substantially, both nationally and sub-nationally. 
+This variability may in part be attributed to efforts to focus VMMC programmes on areas of high disease burden and a lack of historical TMC practice. 
+However, there have been significant increases in MC coverage in ESA as a result of VMMC programme implementation in many of these countries.
 
-‘Replacement’ of traditional circumcision by medical circumcision
-Evidence of this in surveys from several countries; work in progress
-Also not fully accounted for in DMPPT2 baseline coverage inputs
+Since 2006, MMCs have increased significantly for younger ages, particularly amongst the 10-29 age group which has been focused on by VMMC implementation. 
+A circumcised individual is much more likely to have undergone MMC for progressively younger ages, while the converse is true for TMC.
+Over time, this pattern has become more pronounced, particularly amongst VMMC countries.
 
-Surveys imply different level of scale-up than programme data
-Several countries: surveys suggest fewer VMMCs conducted than programme data
+TODO: Flesh this out! Mention how this differs for VMMC and non-VMMC countries, and maybe there is some pattern for TMC-MMCs?
 
-\#+latex \newpage
+TMC has decreased, both in VMMC target countries and elsewhere. 
+In priority countries, this is presumably largely due to the implementation of VMMC programs in districts which traditionally practised TMC. 
+It is interesting that TMC has also also, non-uniformely, declined in many countries and regions elsewhere in SSA. 
+This could possibly be in response to general economic upliftment and development in these countries, and an increased willingness to accept VMMC as an effective, cheap HIV prevention strategy.
 
-\section{References}
-\label{sec:org38b7f8b}
+Significant, but uneven progress has been made towards achieving the UNAIDS target of 90\% 
+MC coverage amongst 10-29 year olds in 14 VMMC priority countries by 2021.  
+However, this has resulted in just x country, x, expected to have realised this goal.
+Granular district and age-stratified estimates for MC, as provided by threemc, provide a key source of information for focusing further programme implementation in these VMMC priority countries, in addition to subnational HIV burden estimates which identify the areas most in need of HIV prevention interventions such as VMMC.
 
-\#+PRINT\textsubscript{BIBLIOGRAPHY}
+In the majority of VMMC countries, the results of threemc and DMPPT2 largely agree. 
+However, for several countries, namely Tanzania, Zimbabwe and parts of Kenya, we can see that DMPPT2 estimates far exceed empirical survey and threemc estimates, and indeed the population of many districts, suggesting that they may be adversely affected by
+\begin{enumerate}
+\item people travelling from their home districts to others to avail of VMMC programmes, and
+\item ii) possible misreporting occurring in programmatic data due to incentives to report higher numbers of circumcisions for VMMC clinics.
+\end{enumerate}
+Where it is desired to incorporate VMMC programme data in estimates of MC coverage, threemc may provide a useful "baseline" circumcision estimate for DMPPT2 up until the last household survey was performed, with programme data taking over as the main data source thereafter.
+threemc may also complement DMPPT2 in it's inclusion of estimates for TMC, since DMPPT2 and the programme data only concern MMC.
+
+There were several limitations inherint in the threemc model, and in this analysis. 
+TODO: Write these out!
+There is much scope for further developments from this analysis. 
+One obvious, though difficult possibility is the incorporation of programme data within threemc. 
+Efforts to do so in South Africa were successful in the original threemc paper, but further implementation of the model including programme data in Malawi has struggled to ?
+survey and programme data.
+In the face of these difficulties, a viable compromise may be to use threemc to provide baseline MC and estimates for TMC to the DMPPT2 tool, as described above. 
+The results of this analysis can also provide circumcision coverage covariates to eligible models which seek to estimate and predict HIV incidence and prevalence, such as Naomi. 
+Finally, we hope that threemc can continue to incorporate new household surveys as they become available, which will be useful for both providing new circumcision estimates, and validating current predictions.
+In particular, a new DHS survey is expected for Botswana in ?, a welcome development which will allow the model to be extended to this VMMC priority country.
+
+TODO: Good conclusion of one line?
+
+\section{Availability of data and materials}
+\label{sec:orgd999c87}
+\subsection{Data Availability}
+\label{sec:org953a659}
+\subsection{Code Availability}
+\label{sec:org2a96da6}
+threemc is implemented in an R package, which can be found on Github at \url{https://github.com/mrc-ide/threemc}.
+The code used to generate the results of this paper is located at \url{https://github.com/mrc-ide/threemc-orderly}, and makes heavy use of the orderly R package [include reference!].
 \end{document}

### 2023-06-19 paper/supp_figs.tex

--- 2023-03-30 paper/paper.tex
@@
-% Created 2023-03-30 Thu 17:04
+% Created 2023-06-19 Mon 09:45
 % Intended LaTeX compiler: pdflatex
@@
 \usepackage{apacite}
+\usepackage{pifont}
+\usepackage{multirow}
 \usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} % define (reduced) margin size
@@
 \affil[5]{\emph{Joint United Nations Programme on HIV/AIDS (UNAIDS)}} \\
-\date{17th October 2022}
+\date{18th June 2023}
 \title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
@@
 
-\begin{abstract}
-  \noindent \textbf{Background} \\
-  \noindent In 2016, UNAIDS developed a Fast-Track strategy that targeted 90\% coverage
-  male circumcision (MC) among men aged 10-29 years by 2021 in priority countries in sub-Saharan 
-  Africa (SSA) to reduce HIV incidence. There is substantial variation across subnational 
-  regions within countries in both traditional male circumcision (TMC) practices and progress
-  towards implementation of voluntary medical male circumcision (VMMC). Tracking progress and
-  remaining gaps towards VMMC HIV prevention targets requires detailed district-level circumcision
-  coverage data.
+\section{Methods}
+\label{sec:org8802288}
 
-  \noindent \textbf{Methods} \\
-  \noindent We analysed self-reported data on male circumcision from x nationally representative household
-  surveys conducted in x SSA countries between 2006-2020. A spatio-temporal Bayesian
-  competing-risks time-to-event model was used to estimate rates of traditional and medical
-  circumcision by age, location, and time. Circumcision coverage in 2020 was projected assuming
-  continuation of estimated age-specific rates, with probabilistic uncertainty.
+\subsection{Data}
+\label{sec:orga1d1a98}
+\subsubsection{Survey Data}
+\label{sec:org09db5e8}
 
-  \noindent \textbf{Results} \\
-  \noindent Across x countries, from 2010 to 2020 an estimated x million men (x\% CI x-x million)
-  were newly circumcised, of whom x million (x - x million) were medically circumcised, and
-  x million (x - x million) traditionally circumcised. In 2020, MC coverage among men 10-29
-  years ranged from x\% (x\% - x\%) in Zimbabwe (?) to x\% (x\%-x\%) in Togo. MMC coverage
-  ranged from x\% (x\%-x\%) in Malawi to x\% (x\%-x\%) in Tanzania, and TMC coverage
-  from x\% (x\%-x\%) in Eswatini to x\% (x\%-x\%) in Ethiopia. The largest increase in MMC
-  coverage was in Lesotho from x\% to x\%. Within countries, the median difference in MC
-  coverage between the districts with lowest and highest coverage was x\%, with the smallest
-  variation in Eswatini (x\% to x\%) and largest in Zambia (x\% to x\%). x million men aged
-  10-29 need to be circumcised to reach 90\% coverage in all countries.
+The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Demorcratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa".
+We excluded 4 countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana.
+These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on circumcision.
 
-  \noindent \textbf{Conclusions} \\
-  \noindent VMMC programmes have made substantial, but uneven, progress towards male circumcision targets.
-Granular district and age-stratified data provide information for focusing further programme implementation.
+We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
+These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \textbf{[Citations]}.
+Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
+\textbf{[Expand on reasons for exclusions]} [Link in your survey figure] Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
 
-\end{abstract}
+\begin{center}
+\includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
+\end{center}
 
-\newpage
+\emph{Figure 1: Household surveys detailing circumcision patterns in SSA.
+The colour and size of points are determined by the provider and sample size of each respective survey.
+Triangular points have no information on circumcision type.}
 
-\section{Background}
-\label{sec:org3a33a7d}
+Demographic variables such as age, residence and survey sampling weight were extracted from all surveys, alongside information related to circumcision: self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown)  and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
+\textbf{[Write and link in survey table].}
 
-HIV remains the single largest cause of years of life lost among adolescent boys and men of reproductive age in eastern and southern Africa.
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
-Voluntary Male medical circumcision (VMMC) reduces the rate of male-to-female HIV incidence by 60\%.
-Efficient, cost-effective, one-time procedure for preventing HIV transmission.
+\begin{longtable}{l|llll}
+\toprule
+\multicolumn{1}{l}{} &  &  & \multicolumn{2}{c}{Circumcision Type} \\ 
+\cmidrule(lr){4-5}
+% \multicolumn{1}{l}{} & Self-reported circumcision status & Age at circumcision & Who performed the circumcision? & Where did the circumcision take place? \\ 
+\multicolumn{1}{l}{} & \begin{tabular}{c}Self-reported \\[-5pt] circumcision status\end{tabular} & Age at circumcision & \begin{tabular}{c}Who performed \\[-5pt] the circumcision?\end{tabular} & \begin{tabular}{c}Where did \\[-5pt] the circumcision take place?\end{tabular} \\
+% \begin{tabular}{c}Healthcare\\[-5pt] Professional\end{tabular}
+\midrule
+AGO 2015 DHS & \cmark & \cmark & \cmark & \cmark \\ 
+BDI 2010 DHS & \cmark & \cmark & \cmark & \cmark \\ 
+BDI 2016 DHS & \cmark & \cmark & \cmark & \cmark \\ 
+\bottomrule
+\end{longtable}
 
-Matt's model \ldots{} (Thomas, Matthew L.
-and Zuma, Khangelani and Loykissoonlal, Dayanund and Dube, Bridget and Vranken, Peter and Porter, Sarah E.
-and Kripke, Katharine and Seatlhodi, Thapelo and Meyer-Rath, Gesine and Johnson, Leigh F.
-and Eaton, Jeffrey W., 2021)
+The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates. 
+Survey respondents were located to their districts using masked cluster geocoordinates. 
+Where these coordinates were unavailable (as in several MICS surveys) respondents were located to their level 1 administrative boundaries, most often corresponding to a province.
 
-\newpage
-\section{Data}
-\label{sec:org0422724}
+Circumcisions were classed as a medical male circumcision (MMC) and traditional male circumcision (TMC) sing responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
+Respondents that did not have any information related to the type of circumcision were classified as having an “unknown” male circumcision (MC).   
+\begin{table}[htbp]
+	\centering
+	\caption{Criteria used to classify circumcisions from the survey data as MMC or TMC.}
+	\label{tab::MCclassification}
+	\begin{tabular}{c l | c c c}
+	\multirow{2}{*}{} & & \multicolumn{3}{c}{Who performed the circumcision?} \\
+	                    &      & \begin{tabular}{c}Healthcare\\[-5pt] Professional\end{tabular} & \begin{tabular}{c}Traditional \\[-5pt] Practioner\end{tabular} & \begin{tabular}{c}Missing\end{tabular} \\
+	                          \hline
+		% \multirow{3}{*}{\rotatebox{90}{Where performed?}}  & \begin{tabular}{l}Healthcare Facility\end{tabular} & MMC & MMC & MMC \\
+		\multirow{3}{*}{\rotatebox{90}{\begin{tabular}{c}Where\\[-5pt] Performed?\end{tabular}}}  & \begin{tabular}{l}Healthcare Facility\end{tabular} & MMC & MMC & MMC \\
+		& \begin{tabular}{l}Home/Ritual Site\end{tabular} & MMC & TMC & TMC \\
+		& \begin{tabular}{l}Missing\end{tabular} & MMC & TMC & Missing \\
+	\end{tabular}	
+\end{table}
 
-120 household surveys conducted in 33 SSA countries 2002-2019
-Self-reported circumcision:
-o Status (MC vs uncircumcised), 
-o Type (MMC vs TMC), 
-o Year, and
-o Age 
-recorded
-Sub-national populations from WorldPop (reference)
+In total, information was extracted from XXX, XXX respondents from all surveys.
+\textbf{[Participation rates table]}
 
-Major survey series (DHS, AIS, PHIA, MICS, HSRC in ZAF)
-Individual-level data: self-reported circumcision status  by male respondents
-Respondents located to districts using cluster geocoordinates
-Located to admin 1 (province) where coordinates not available (MICS)
-VMMC programme data not used
+\subsubsection{Administrative boundaries}
+\label{sec:org0995c95}
 
-Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC
-Otherwise, circumcisions are TMC
-Where no data is present on location or provider, circumcision type  Missing
+[Add in information about the boundaries]
 
-Individual-level household survey data provide direct estimates of circumcision rates over time and by type for years preceding survey
+\subsubsection{Population}
+\label{sec:org0d7d6e9}
 
- Direct estimates of TMC practices, age at circumcision, VMMC impact
-
-\newpage
-
-\section{Methods}
-\label{sec:org69a085f}
+Estimates for the male population size by district and five-year age group from 2002 through 2019 were sourced from XXX. 
+Distributed (?) to single-year of age according to ???
 
 \subsection{Model}
-\label{sec:org2077286}
+\label{sec:org38d457a}
 
-Bayesian spatio-temporal, competing-risks, time-to-event model
-Stratified by age, location and time
-Rates of TMC and medical male circumcision (MMC) estimated
-Coverage in 2020 projected assuming continuation of estimated age-specific rates with probabilistic uncertainty
-Important assumption: Probability of traditional male initiation ceremonies (TMICs) constant over time (needed? Might lead to a lot of questions!)
+\emph{Put a general discussion element for the model giving an overview}
 
-Model stratified by:
-Age
-District
-circumcision type (traditional / medical)
+"threemc"("Multi-level model for male circumcision") is a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). 
+We have extended this model from its initial application in South Africa to 33 countries within the SSA region. 
+The model produces estimates of circumcision rates, incidence and coverage (i.e. cumulative indidence), with associated uncertainty bounds, stratified by type, year, age and location.
+Circumcision rates are projected after their most recent household survey assuming continuation of estimated age-specific rates, with probabilistic uncertainty. 
+Estimates for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
 
-TMC \& MMC rates estimated (by age, district, and time)
-Spatial smoothing allows for district level estimates
+\emph{Traditional Circumcision}
 
-Circumcision coverage since most recent HH survey: projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty
+A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practices and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
+MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
 
-Important assumption: TMC rate assumed constant over time
+[Technical details]
 
-\newpage
+Explain the TMC with time and TMC with no time.
 
-Samples drawn from model fit, weighted by population and aggregated, to produce estimates for less granular regions (e.g. District to Province aggregation).
-Computed posterior summary statistics for coverage, circumcision incidence and probability of being circumcised. 
-Done for all strata, for both discrete ages and “binned” age groups.
+\emph{Medical Circumcision}
 
-\section{Results}
-\label{sec:org634cf32}
+Explain paed cut off and no paed cut off
 
-\#+latex \newpage
+\subsection{Model Specification}
+\label{sec:org40f2f33}
 
-\section{Discussion}
-\label{sec:orgce42292}
+In our choice of model specification, we were interested in two main assumptions/features of the
+model:
+\begin{itemize}
+\item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
+\item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
+\end{itemize}
 
-\textbf{Challenges}
-Inconsistent MC self-reporting by same cohort in successive surveys
-E.g. in 2017 survey, men 30-34 report higher \% circumcised in 2012 than ‘same’ men age 25-29 in 2012 survey
-Affects circumcision level, and distribution by type
+If possible, we hoped to use the same model for every country, or failing that, come up with a
+satisfactory choice of model specification which would make sense both qualitatively and
+quantitatively.
 
-‘Replacement’ of traditional circumcision by medical circumcision
-Evidence of this in surveys from several countries; work in progress
-Also not fully accounted for in DMPPT2 baseline coverage inputs
+Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
+In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
+Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
+This suggests that MMCs in these countries are likely to be on paediatric individuals in traditional settings, so the assumption of constant and
+negligible paedaitric MMC could be a poor one. 
+Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
+It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
+patterns in non-VMMC countries.
 
-Surveys imply different level of scale-up than programme data
-Several countries: surveys suggest fewer VMMCs conducted than programme data
+Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
+As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
+It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
+Historical TMC patterns in these countries, differ significantly, even subnationally.
+It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
+In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
+We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
 
-\#+latex \newpage
+We have also performed a quantitative analysis of the different model specifications available
+to us. A more detailed treatment of this can be found in section x of the appendix.
 
-\section{References}
-\label{sec:org38b7f8b}
+For each country, we fit a model for each possible model specification for threemc, that is:
+\begin{itemize}
+\item for each choice of temporal prior, namely AR1, RW1 and RW2,
+\item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
+\item a choice of whether to include a temporal effect for TMC.
+\end{itemize}
+Thus totalling 12 possible models for each country.
+These models were fit to all of the survey data available, rather than a subset of the data.
+This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
+As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
 
-\#+PRINT\textsubscript{BIBLIOGRAPHY}
+The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
+Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
+
+Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
+Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
+This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
+A "good" calibration was regarded as one in which roughly 50\% of survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range.
+Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
+
+Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
+
+For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
+The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
+This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
+It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
+Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
+These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
+
+In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
+This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
+However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
+As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
+
+Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
+In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
+For completeness, we decided to include a temporal effect for TMC in the model specification for VMMC priority countries.
+
+It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
+A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
+
+\subsection{Model Calibration and Choice of Temporal Prior}
+\label{sec:orgbbc65cb}
+
+For some VMMC priority countries, we did not have access to more recent survey data. 
+One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
+In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
+VMMC programme data was an available source of more recent circumcision data.
+The DMPPT2 model explicitly used this data to estimate MMC. 
+The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
+This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
+Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
+A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
+
+The two main drivers of uncertainty over time in threemc were:
+\begin{itemize}
+\item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
+\item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
+\end{itemize}
+The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
+
+Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
+One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
+To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
+A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
+For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
+
+TODO: Finish this write up!
+TODO: Add results! Also add ternary plot 
 \end{document}

### 2023-06-20 paper/paper.tex
Matt additions to supplementary figures: 1) Formatting improvements (need to convert this back to org) 2) Addition of technical appendix 3) In red, still to do

@@
-% Created 2023-05-30 Tue 07:57
-% Intended LaTeX compiler: pdflatex
-\documentclass[a4paper, 12pt]{article}
+\documentclass{article}
+
+\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{bbm}
+\usepackage{todonotes}
+\usepackage{pdflscape}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
+\usepackage{authblk}
+\usepackage{pdfpages}
+\usepackage{setspace} 
+\usepackage{booktabs}
 \usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage{color}
-\usepackage{listings}
-\usepackage{minted}
-\usepackage{authblk}
-\usepackage{breakcites}
-\usepackage{apacite}
-\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} % define (reduced) margin size
-\usepackage[parfill]{parskip} % insert whitespace between new paragraphs
-\setlength\parindent{0pt}
-\tolerance=9999
-\emergencystretch=10pt
-\hyphenpenalty=10000
-\exhyphenpenalty=100
-\author[1]{Patrick O'Toole}
-\author[1,2]{Matthew L. Thomas}
-\author[1]{Oliver Stevens}
-\author[1,3]{Kevin Lam}
-\author[4]{Katherine Kripke}
-\author[1]{Rachel Esra}
-\author[5]{Ian Wanyeki}
-\author[5]{Lycias Zembe}
-\author[1]{Jeffrey W. Eaton}
-\affil[1]{\emph{Imperial College London, London, United Kingdom}} \\
-\affil[2]{\emph{Joint Centre for Excellence in Environmental Intelligence, University of Exeter and Met Office}} \\
-\affil[3]{\emph{Department of Statistics, University of British Columbia}} \\
-\affil[4]{\emph{Avenir Health, Takoma Park, MD, USA}} \\
-\affil[5]{\emph{Joint United Nations Programme on HIV/AIDS (UNAIDS)}} \\
-\date{17th October 2022}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
+\usepackage{multirow}
+\setlength{\tabcolsep}{5pt}
+%%\setlength{\parindent}{0pt}
+\usepackage[parfill]{parskip}
+\renewcommand{\arraystretch}{1.5}
+
+\renewcommand\Affilfont{\itshape\footnotesize}
+\def\ci{\perp\!\!\!\perp}
+
+\renewcommand\Affilfont{\itshape\footnotesize}
+\linespread{1.5}
+
+% \usepackage{lineno}
+% \linenumbers
+
+% Nature Bibliography style
+\usepackage[backend=biber,style=nature]{biblatex}
+\addbibresource{library.bib}
+
+%%%%%%%%%%%%%
+%%% Title %%%
+%%%%%%%%%%%%%
 \title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
+
+\author{}
+\date{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{center}
-\includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
-\end{center}
-
-\emph{Figure 1: Household surveys detailing circumcision patterns in SSA.
+\begin{figure}
+    \centering
+    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
+    \caption{Household surveys detailing circumcision patterns in SSA.
 The colour and size of points are determined by the provider and sample size of each respective survey.
 Triangular points have no information on circumcision type.}
+\end{figure}
 

### 2023-06-20 paper/supp_figs.tex
Matt additions to supplementary figures: 1) Formatting improvements (need to convert this back to org) 2) Addition of technical appendix 3) In red, still to do

--- 2023-03-30 paper/paper.tex
@@
-% Created 2023-03-30 Thu 17:04
-% Intended LaTeX compiler: pdflatex
-\documentclass[a4paper, 12pt]{article}
+\documentclass{article}
+
+\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage{graphicx}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{bbm}
+\usepackage{todonotes}
+\usepackage{pdflscape}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
+\usepackage{authblk}
+\usepackage{pdfpages}
+\usepackage{setspace} 
+\usepackage{booktabs}
 \usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage{authblk}
-\usepackage{breakcites}
-\usepackage{apacite}
-\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} % define (reduced) margin size
-\usepackage[parfill]{parskip} % insert whitespace between new paragraphs
-\setlength\parindent{0pt}
-\tolerance=9999
-\emergencystretch=10pt
-\hyphenpenalty=10000
-\exhyphenpenalty=100
-\author[1]{Patrick O'Toole}
-\author[1,2]{Matthew L. Thomas}
-\author[1]{Oliver Stevens}
-\author[1,3]{Kevin Lam}
-\author[4]{Katherine Kripke}
-\author[1]{Rachel Esra}
-\author[5]{Ian Wanyeki}
-\author[5]{Lycias Zembe}
-\author[1]{Jeffrey W. Eaton}
-\affil[1]{\emph{Imperial College London, London, United Kingdom}} \\
-\affil[2]{\emph{Joint Centre for Excellence in Environmental Intelligence, University of Exeter and Met Office}} \\
-\affil[3]{\emph{Department of Statistics, University of British Columbia}} \\
-\affil[4]{\emph{Avenir Health, Takoma Park, MD, USA}} \\
-\affil[5]{\emph{Joint United Nations Programme on HIV/AIDS (UNAIDS)}} \\
-\date{17th October 2022}
-\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
+\usepackage{float}
+\usepackage{tikz}
+\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
+\usepackage{multirow}
+\setlength{\tabcolsep}{5pt}
+%%\setlength{\parindent}{0pt}
+\usepackage[parfill]{parskip}
+\renewcommand{\arraystretch}{1.5}
+
+\renewcommand\Affilfont{\itshape\footnotesize}
+\def\ci{\perp\!\!\!\perp}
+
+\renewcommand\Affilfont{\itshape\footnotesize}
+\linespread{1.5}
+
+% \usepackage{lineno}
+% \linenumbers
+
+% Nature Bibliography style
+\usepackage[backend=biber,style=nature]{biblatex}
+\addbibresource{library.bib}
+
+%%%%%%%%%%%%%
+%%% Title %%%
+%%%%%%%%%%%%%
+\title{Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
+
+\author{}
+\date{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\clearpage
+\vspace{-1cm}
 
-\begin{abstract}
-  \noindent \textbf{Background} \\
-  \noindent In 2016, UNAIDS developed a Fast-Track strategy that targeted 90\% coverage
-  male circumcision (MC) among men aged 10-29 years by 2021 in priority countries in sub-Saharan 
-  Africa (SSA) to reduce HIV incidence. There is substantial variation across subnational 
-  regions within countries in both traditional male circumcision (TMC) practices and progress
-  towards implementation of voluntary medical male circumcision (VMMC). Tracking progress and
-  remaining gaps towards VMMC HIV prevention targets requires detailed district-level circumcision
-  coverage data.
+Patrick O'Toole\textsuperscript{1},
+Matthew L. Thomas\textsuperscript{1,2},
+Oliver Stevens\textsuperscript{1},
+Kevin Lam\textsuperscript{1,3},
+Katharine Kripke\textsuperscript{4},
+Rachel Esra\textsuperscript{1},
+Ian Wanyeki\textsuperscript{5},
+Lycias Zembe\textsuperscript{5},
+Jeffrey W. Eaton\textsuperscript{1,6} \\
+\smallskip
 
-  \noindent \textbf{Methods} \\
-  \noindent We analysed self-reported data on male circumcision from x nationally representative household
-  surveys conducted in x SSA countries between 2006-2020. A spatio-temporal Bayesian
-  competing-risks time-to-event model was used to estimate rates of traditional and medical
-  circumcision by age, location, and time. Circumcision coverage in 2020 was projected assuming
-  continuation of estimated age-specific rates, with probabilistic uncertainty.
+\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial Colleg  e London, London, United Kingdom\\
+\textbf{2} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{3} Department of Statistics, University of British Columbia, Vancouver, Canada\\
+\textbf{4} Avenir Health, Washington, District of Columbia, United States of America\\
+\textbf{5} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
+\textbf{6} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
 
-  \noindent \textbf{Results} \\
-  \noindent Across x countries, from 2010 to 2020 an estimated x million men (x\% CI x-x million)
-  were newly circumcised, of whom x million (x - x million) were medically circumcised, and
-  x million (x - x million) traditionally circumcised. In 2020, MC coverage among men 10-29
-  years ranged from x\% (x\% - x\%) in Zimbabwe (?) to x\% (x\%-x\%) in Togo. MMC coverage
-  ranged from x\% (x\%-x\%) in Malawi to x\% (x\%-x\%) in Tanzania, and TMC coverage
-  from x\% (x\%-x\%) in Eswatini to x\% (x\%-x\%) in Ethiopia. The largest increase in MMC
-  coverage was in Lesotho from x\% to x\%. Within countries, the median difference in MC
-  coverage between the districts with lowest and highest coverage was x\%, with the smallest
-  variation in Eswatini (x\% to x\%) and largest in Zambia (x\% to x\%). x million men aged
-  10-29 need to be circumcised to reach 90\% coverage in all countries.
+\smallskip
 
-  \noindent \textbf{Conclusions} \\
-  \noindent VMMC programmes have made substantial, but uneven, progress towards male circumcision targets.
-Granular district and age-stratified data provide information for focusing further programme implementation.
-
-\end{abstract}
+* Corresponding Author Email
 
@@
 
-\section{Background}
-\label{sec:org3a33a7d}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-HIV remains the single largest cause of years of life lost among adolescent boys and men of reproductive age in eastern and southern Africa.
+\begin{appendix}
 
-Voluntary Male medical circumcision (VMMC) reduces the rate of male-to-female HIV incidence by 60\%.
-Efficient, cost-effective, one-time procedure for preventing HIV transmission.
-
-Matt's model \ldots{} (Thomas, Matthew L.
-and Zuma, Khangelani and Loykissoonlal, Dayanund and Dube, Bridget and Vranken, Peter and Porter, Sarah E.
-and Kripke, Katharine and Seatlhodi, Thapelo and Meyer-Rath, Gesine and Johnson, Leigh F.
-and Eaton, Jeffrey W., 2021)
-
-\newpage
-\section{Data}
-\label{sec:org0422724}
-
-120 household surveys conducted in 33 SSA countries 2002-2019
-Self-reported circumcision:
-o Status (MC vs uncircumcised), 
-o Type (MMC vs TMC), 
-o Year, and
-o Age 
-recorded
-Sub-national populations from WorldPop (reference)
-
-Major survey series (DHS, AIS, PHIA, MICS, HSRC in ZAF)
-Individual-level data: self-reported circumcision status  by male respondents
-Respondents located to districts using cluster geocoordinates
-Located to admin 1 (province) where coordinates not available (MICS)
-VMMC programme data not used
-
-Circumcisions performed by a medical professional and/or in a medical setting are categorised as MMC
-Otherwise, circumcisions are TMC
-Where no data is present on location or provider, circumcision type  Missing
-
-Individual-level household survey data provide direct estimates of circumcision rates over time and by type for years preceding survey
-
- Direct estimates of TMC practices, age at circumcision, VMMC impact
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Resetting figure and table count for the appendix %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}}
+%\setcounter{table}{0} \renewcommand{\thetable}{A.\arabic{table}}
 
@@
 
-\section{Methods}
-\label{sec:org69a085f}
-
-\subsection{Model}
-\label{sec:org2077286}
-
-Bayesian spatio-temporal, competing-risks, time-to-event model
-Stratified by age, location and time
-Rates of TMC and medical male circumcision (MMC) estimated
-Coverage in 2020 projected assuming continuation of estimated age-specific rates with probabilistic uncertainty
-Important assumption: Probability of traditional male initiation ceremonies (TMICs) constant over time (needed? Might lead to a lot of questions!)
-
-Model stratified by:
-Age
-District
-circumcision type (traditional / medical)
-
-TMC \& MMC rates estimated (by age, district, and time)
-Spatial smoothing allows for district level estimates
-
-Circumcision coverage since most recent HH survey: projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty
-
-Important assumption: TMC rate assumed constant over time
+\tableofcontents
 
@@
 
-Samples drawn from model fit, weighted by population and aggregated, to produce estimates for less granular regions (e.g. District to Province aggregation).
-Computed posterior summary statistics for coverage, circumcision incidence and probability of being circumcised. 
-Done for all strata, for both discrete ages and “binned” age groups.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Results}
-\label{sec:org634cf32}
+\section{Data}
+\label{sec:org8802288}
 
-\#+latex \newpage
+% \subsection{Data}
+% \label{sec:orga1d1a98}
 
-\section{Discussion}
-\label{sec:orgce42292}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\textbf{Challenges}
-Inconsistent MC self-reporting by same cohort in successive surveys
-E.g. in 2017 survey, men 30-34 report higher \% circumcised in 2012 than ‘same’ men age 25-29 in 2012 survey
-Affects circumcision level, and distribution by type
+\subsection{Survey Data}
+\label{sec:org09db5e8}
 
-‘Replacement’ of traditional circumcision by medical circumcision
-Evidence of this in surveys from several countries; work in progress
-Also not fully accounted for in DMPPT2 baseline coverage inputs
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Surveys imply different level of scale-up than programme data
-Several countries: surveys suggest fewer VMMCs conducted than programme data
+The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Demorcratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa".
+We excluded 4 countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana.
+These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on circumcision.
 
-\#+latex \newpage
+We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
+These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \textbf{[Citations]}.
+Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
+\textbf{[Expand on reasons for exclusions]} [Link in your survey figure] Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
 
-\section{References}
-\label{sec:org38b7f8b}
+\begin{figure}[H]
+    \centering
+    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
+    \caption{Household surveys detailing circumcision patterns in SSA.
+The colour and size of points are determined by the provider and sample size of each respective survey.
+Triangular points have no information on circumcision type.}
+    \label{fig:enter-label}
+\end{figure}
 
-\#+PRINT\textsubscript{BIBLIOGRAPHY}
+Demographic variables such as age, residence and survey sampling weight were extracted from all surveys, alongside information related to circumcision: self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown)  and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
+\textbf{[Write and link in survey table].}
+
+% \begin{landscape}
+{\linespread{1}
+\small
+\begin{longtable}[c]{ll ccc ccc ccc ccc}
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table header %%%
+      %%%%%%%%%%%%%%%%%%%%
+      % Upper layer of table header
+      \hline
+      % Lines inside the header
+      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
+      \cmidrule(lr){5-7}
+       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
+       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
+      % Lower lines
+      \hline
+      \vspace{-5pt}
+      \endhead
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table footer %%%
+      %%%%%%%%%%%%%%%%%%%%
+      \\[-5pt]\hline
+      \caption{Table caption}
+      \endfoot
+      %%%%%%%%%%%%%%%%%%%%%%
+      %%% Table contents %%%
+      %%%%%%%%%%%%%%%%%%%%%%
+      \multicolumn{2}{l}{\textbf{Angola}} \\
+      & 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt]
+      \multicolumn{2}{l}{\textbf{Burundi}} \\
+      & 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+      & 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt]
+      \multicolumn{2}{l}{\textbf{South Africa}} \\
+      & 2002 (HSRC) &  \\
+      & 2008 (HSRC) &  \\
+      & 2012 (HSRC) &  \\
+      & 2016 (DHS)  &  \\
+      & 2017 (HSRC) &  
+\end{longtable}
+}
+% \end{landscape}
+
+The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates. 
+Survey respondents were located to their districts using masked cluster geocoordinates. 
+Where these coordinates were unavailable (as in several MICS surveys) respondents were located to their level 1 administrative boundaries, most often corresponding to a province.
+
+Circumcisions were classed as a medical male circumcision (MMC) and traditional male circumcision (TMC) sing responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
+Respondents that did not have any information related to the type of circumcision were classified as having an “unknown” male circumcision (MC).
+
+{\linespread{1}
+\small
+\begin{table}[htbp]
+	\centering
+	\caption{Criteria used to classify circumcisions from the survey data as MMC or TMC.}
+	\label{tab::MCclassification}
+	\begin{tabular}{c l | c c c}
+	\multirow{2}{*}{} & & \multicolumn{3}{c}{\bf Who performed the circumcision?} \\
+	                    &      & \begin{tabular}{c}\bf Healthcare\\[-5pt] \bf Professional\end{tabular} & \begin{tabular}{c}\bf Traditional \\[-5pt] \bf Practioner\end{tabular} & \begin{tabular}{c}\bf Missing\end{tabular} \\
+	                          \hline
+		% \multirow{3}{*}{\rotatebox{90}{Where performed?}}  & \begin{tabular}{l}Healthcare Facility\end{tabular} & MMC & MMC & MMC \\
+		\multirow{3}{*}{\rotatebox{90}{\begin{tabular}{c}\bf Where was it\\[-5pt] \bf performed?\end{tabular}}}  & \begin{tabular}{l}\bf Healthcare\\[-5pt] \bf Facility \end{tabular} & MMC & MMC & MMC \\
+		& \begin{tabular}{l}\bf Home, School \\[-5pt] \bf or Ritual Site \end{tabular} & MMC & TMC & TMC \\
+		& \begin{tabular}{l} \bf Missing\end{tabular} & MMC & TMC & MC \\
+	\end{tabular}	
+\end{table}
+}
+
+In total, information was extracted from XXX, XXX respondents from all surveys.
+\textbf{[Participation rates table]}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Administrative boundaries}
+\label{sec:org0995c95}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+[Add in information about the boundaries]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Population}
+\label{sec:org0d7d6e9}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Estimates for the male population size by district and five-year age group from 2002 through 2019 were sourced from XXX. 
+Distributed (?) to single-year of age according to ???
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Model}
+\label{sec:org38d457a}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+{\color{red} \bf
+To do:
+\begin{itemize}
+    \item Add in typeless model
+    \item Aggregated areas
+    \item Model calibration
+    \item Prior choice
+    \item Citations
+\end{itemize}}
+
+\noindent Following a similar approach to \cite{thomas2021multilevel}, we used a Bayesian hierarchical model with small area estimation methods to model probabilities of
+circumcision.
+The Multi-level Model for Male Circumcision (threemc) uses survey data to estimates the probabilities and coverage of of circumcision were estimated using a competing risk discrete time-to-event model stratified by region, age, and time for two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Probabilities of circumcision (by type)}
+\label{sec::tradcirc}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We used survey data to model the probabilities of recieving a TMC, MMC or MC of any time for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection*{Traditional circumcision}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in region $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
+\begin{equation} 
+		\lambda^{\text{TMC}}_{iat} = \mathbb{P}(\text{TMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
+	\label{eqn::TMC}
+\end{equation}
+A key assumption of \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa but an assumption of a constant probability of TMC might not be feasible everywhere.
+For example, in some countries the level of TMC has changed through time due to demographic shifts and practices over time.
+There has also been a shift (or a replacement) of TMCs through MMCs, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations.
+There may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
+
+Therefore, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e.
+constant over time) and (ii) time variant (i.e.
+non-constant over time).
+The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function,
+\begin{equation*} 
+	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\gamma}_{ia}
+\end{equation*}
+where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC across regions.
+The {\it time-variant} probability of TMC was also modelled using a piece-wise logit-linear function,
+\begin{equation*} 
+	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\theta}_t + \hat{\gamma}_{ia} + \hat{\delta}_{at}
+\end{equation*}
+where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, $\theta_i$ is a temporal random effect,  $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC  across regions and $\hat{\delta}_{at}$ is an age-time interaction term to allow for different age patterns of TMCs over time.
+We did not include a space-time interaction into due to computational reasons.
+
+The choice of whether a country used a time-invariant or time-variant probability of circumcision was decided through {\color{red}\bf[Need more information]}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection*{Medical circumcision}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
+\begin{equation}
+		\lambda^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
+	\label{eqn::mmc}
+\end{equation}
+
+To ensure the overall probability of circumcision $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the probability of TMC occurred before MMC in each time step.
+Therefore, we practically model the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
+\begin{equation*}
+		\tilde{\lambda}^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1) \text{ and no TMC in} \; (i,a, t))
+\end{equation*}
+such that
+\begin{equation*}
+		\lambda^{\text{MMC}}_{iat} = \tilde{\lambda}^{\text{MMC}}_{iat}\cdot (1-\lambda^{\text{TMC}}_{iat}).
+\end{equation*}
+
+{\color{red}\bf[CITE]} included VMMC programmatic data in their model and programmes only provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision tends to occur through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
+Therefore, to ensure any increase in MMC for those aged 10 and over did not affect the probability of MMC in those under 10, $\tilde{\lambda}^{\text{MMC}}_{iat}$ was separated into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
+
+Here, we consider two models {\color{red}\bf[Need more information]}
+
+We modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:
+
+\begin{equation*}
+	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
+\end{equation*}
+where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MMCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions.
+
+Therefore, we modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:
+\begin{equation*}
+	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) =
+	\begin{cases}
+		\bar{\alpha} + \bar{\psi}_i + \bar{\phi}_a + \bar{\gamma}_{ia} & \text{for } 0 \leq a \leq 9\\
+		\alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} & \text{for } a \geq 10
+	\end{cases} 
+\end{equation*}
+where $\bar{\alpha}$ and $\alpha$ are intercepts, $\bar{\psi}_i$ and $\psi_i$ are regional random effects, $\theta_i$ are temporal random effects, $\bar{\phi}_a$ and $\phi_a$ are age random effects, $\bar{\gamma}_{ia}$ and $\gamma_{ia}$ are age-space interaction terms to allow for different age patterns of MMCs between regions, for paediatric circumcision and adolescent and adult circumcision respectively.
+The $\delta_{at}$ is an age-time interaction term to allow for different age patterns of MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions, in adolescent and adult men.
+We assume that the probabilities of MMC among those aged 0--9 were constant over time, (i.e.
+$\lambda^{\text{MMC}}_{iat} \equiv \lambda^{\text{MMC}}_{ia}$ when $0\leq a \leq 9$), as paediatric medical circumcision practices are unrelated to VMMC for HIV prevention and are relatively stable.
+
+The choice of whether a country used a {\color{red}\bf[Need more information]} or {\color{red}\bf[Need more information]} probability of circumcision was decided through {\color{red}\bf[Need more information]}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection*{Male circumcision}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability of circumcision of any type, at age $a$ and time $t$ given they were uncircumcised by age $a-1$ and time $t-1$ as
+\begin{equation}
+	\begin{split}
+	\lambda^{\text{MC}}_{iat} &= \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1,t-1)) \\ 
+	              &= \lambda^{\text{TMC}}_{ia} + \lambda^{\text{MMC}}_{iat}. 
+	\end{split}
+	\label{eqn::tot}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Circumcision coverage}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The probability $S_{iat}$ of remaining uncircumcised up to age $a$ and time $t$,  typically referred to as the survivor function, was expressed as
+\begin{equation}
+	\begin{split}
+		S_{iat} &= \mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
+				&= \prod_{(0,(t-a))}^{(a-1,t-1)}\lambda^{\text{UC}}_{iat} \\
+				&= \lambda^{\text{UC}}_{i,0,t-a}\cdot \lambda^{\text{UC}}_{i,1,t-a+1}\cdot\ldots \cdot\lambda^{\text{UC}}_{i,a-1,t-1}
+	\end{split}
+	\label{eqn::survfunc}
+\end{equation}
+where $\lambda^{\text{UC}}_{iat}$ is the probability an individual in region $i$ remained uncircumcised at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$, was
+\begin{equation*}
+	\begin{split}
+		\lambda^{\text{UC}}_{iat} &= \mathbb{P}(\text{Uncircumcised in}  \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),\\
+		&= 1 - \lambda^{\text{MC}}_{iat} 
+	\end{split}
+	\label{eqn::uncirc}
+\end{equation*}
+
+The cumulative incidence function (CIF) defines the marginal probability (or coverage/proportion) of individuals who received a TMC, a MMC or a MC of any type by age $a$ and time $t$, accounting for the competing risk of other circumcision types.
+This was calculated as the sum of incidence of circumcision by type $k$ at each age up to $a$:
+\begin{equation*}
+	\begin{split}
+		\text{CIF}_{iat}^k &= \mathbb{P}(k \; \text{by} \; (i,a,t)) \\
+		&= \sum_{(0,(t-a))}^{(a,t)} I^k_{iat}
+	\end{split}
+	\label{eqn::cuminc}
+\end{equation*}
+where $I^k_{iat}$ is the incidence of circumcision of type $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, in region $i$, at age $a$ and time $t$, 
+\begin{equation*}
+	\begin{split}
+		I_{iat}^k &= \mathbb{P}(k \; \text{in} \; (i,a,t)) \\
+		       &= \mathbb{P}(k \; \text{in} \; (i,a,t) | \; \text{Uncircumcised in} \; (i,a-1,t-1))\times \\
+		       & \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
+	    	   &= \lambda_{iat}^k \cdot S_{iat} 
+	\end{split}
+	\label{eqn::inc}
+\end{equation*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Model priors}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In space, we assigned the random effects $\hat{\psi}_i$, $\bar{\psi}_i$, $\psi_i$, $\hat{\gamma}_{ia}$, $\gamma_{ia}$ and $\zeta_{it}$, intrinsic conditional autoregressive (ICAR) priors in space \cite{besag1995conditional}.
+An ICAR model allows us to encodes spatial dependence between neighbouring regions which allows information on the probability and coverage of circumcision in areas where data is sparse or non-existent to be borrowed.
+For a generic parameter $\beta_i$, an ICAR model assumes that the mean of $\beta_i$ is a weighted average its neighbours,
+\begin{equation*}
+	\beta_i \;|\; \beta_{j}, j \sim i, \tau_{\beta} \sim \text{N}\left(\frac{1}{n_i} \sum_{j \sim i} \beta_j, \frac{1}{n_i\tau_{\beta}} \right) \;\;\; i = 1, 2, 3,\ldots, N_I
+\end{equation*}
+Here, $j \sim i$ refers to the neighbours of region $i$, $n_i$ is the number of neighbours and $\tau_{\beta}$ is the marginal precision \cite{rue2005gaussian}.
+
+In age, we modelled the random effects ($\hat{\phi}_a$, $\bar{\phi}_a$, $\phi_a$, $\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$ and $\delta_{at}$) using penalised B-splines.
+For a generic parameter $\beta_a$, penalised B-splines assumes that $\beta_a$ is a sum of basis functions,
+\begin{align*} 
+	\beta_a = \sum_{j = 1}^{J} w_{j}b_{aj}
+\end{align*} 
+where $b_{aj}$ are B-spline basis functions with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $\omega_{j}$ are the spline weight parameters to be estimated.
+The weights $w_{j}$ are penalised using an AR1 process
+\begin{align*} 
+  w_{j} \; | \; w_{j-1}, \rho_{w}, \tau_{w} &\sim N(\rho_{w} \cdot w_{j-1}, \;\; \tau^{-1}_{w}) \;\;\;  j = 2, 3,\ldots, J \\
+  w_{1} \; | \; \rho_{w}, \tau_{w} &\sim N(0, \tau^{-1}_{w}) 
+\end{align*}
+where $|\rho_{w}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{w}$ is the precision.
+
+In time, we consider three possible prior distirbution choices: an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2).
+{\color{red} \bf [Need more information]}
+% \noindent In time, we assigned the random effects $\theta_t$, $\delta_{at}$ and $\zeta_{it}$ an autoregressive process of order 1 (AR1) priors,
+\begin{align*} 
+  \beta_t \; | \; \beta_{t-1},  \rho_{\beta}, \tau_{\beta} &\sim
+  \begin{cases}
+  	N(0, \tau^{-1}_{\phi}) & t = 1\\
+  	N(\rho_{\beta} \cdot \beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 2, 3,\ldots, T
+  \end{cases}
+\end{align*}
+
+\begin{align*} 
+  \beta_t \; | \; \beta_{t-1}, \rho_{\beta}, \tau_{\beta} &\sim
+  \begin{cases}
+  	N(0, \tau^{-1}_{\phi}) & t = 1\\
+  	N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 2, 3,\ldots, T
+  \end{cases}
+\end{align*}
+
+\begin{align*} 
+  \beta_t \; | \; \beta_{t-1}, \beta_{t-2}, \rho_{\beta}, \tau_{\beta} &\sim
+  \begin{cases}
+  	N(0, \tau^{-1}_{\phi}) & t = 1, 2\\
+  	N(2\beta_{t-1} - \beta_{t-2}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 3, 4,\ldots, T
+  \end{cases}
+\end{align*}
+
+% where $|\rho_{\phi}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{\beta}$ is the precision.
+
+Moreover, age-space, age-time, and space-time interaction terms ($\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$, $\delta_{at}$ and $\zeta_{it}$) are modelled using a Type IV interactions as defined by Knorr-Held and Leonard \cite{knorr2000bayesian},
+
+We assigned Gaussian priors to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$.
+Exponential priors were placed on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$.
+Gaussian priors were set for all correlation parameters on the logit scale, such that
+\begin{align*} 
+  \hat{\rho}_{(\cdot)} = \frac{2}{1 + \exp(-\rho_{(\cdot)})} - 1 \sim N(3, 1^2)
+\end{align*}
+corresponding to 95\% CI prior weight that the autocorrelation parameters are between 0.48 and 0.99 on the real scale.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Likelihood}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Survey data consists of individual observations of self-reported age at circumcision, date of birth, and circumcision type (medical or traditional) from male survey respondents.
+Circumcision status observations were right censored if the respondent reported not being circumcised at the time of the survey or left censored if the individual reported being circumcised at the time of survey but did not report their age at circumcision.\\
+
+\noindent Each survey $s \in S = \{1, 2, \ldots, N_S\}$ consists of sampled individuals $j \in J_s = \{0, 1, 2, \ldots, N_{J_s}\}$ residing in region $i \in I = \{1, 2, \ldots, N_I\}$.
+Surveyed individuals were followed from their year of birth until their year of circumcision or their year of censoring.
+For circumcised individuals, the year of circumcision was calculated as the year of birth plus the age at circumcision.
+It was assumed that no circumcisions occurred after age 59, so for uncircumcised individuals, censoring occurred either in the survey year or when they were 59.
+Individuals who self-reported they were circumcised but have a missing age at circumcision were included in the analysis through left censoring.
+\\
+
+\noindent The likelihood function for each individual is this defined by the following groups:
+\begin{itemize}
+	\item[(1)] \textbf{TMC observed (TMC)}: Individuals in region $i$ reporting an TMC at age $a$ and time $t$.
+The likelihood of this outcome was the probability an individual in region $i$ reported a TMC at age $a$ and time $t$, $I^{\text{TMC}}_{iat} = \lambda^{\text{TMC}}_{iat}\cdot S_{iat}$.
+	\item[(2)] \textbf{MMC observed (MMC)}: Individuals in region $i$ reporting an MMC at age $a$ at time $t$.
+The likelihood of this outcome was the incidence of MMC in region $i$, at age $a$ and time $t$, $I^{\text{MMC}}_{iat} = \lambda^{\text{MMC}}_{iat}\cdot S_{iat}$.
+	\item[(3)] \textbf{MC observed (MC)}: Individuals in region $i$ reporting they were circumcised but had a missing or unknown type at age $a$ and time $t$.
+The likelihood of this outcome was the incidence of MC in region $i$, at age $a$ and time $t$, $I^{\text{MC}}_{iat} = \lambda^{\text{MC}}_{iat}\cdot S_{iat}$.
+	\item[(4)] \textbf{Right censored (RC)}: Individuals in region $i$ who remained uncircumcised by age $a$ at time $t$.
+The likelihood of this outcome was the probability of remaining uncircumcised in region $i$, at age $a$ and time $t$,$S_{iat}$
+	\item[(5)] \textbf{TMC left censored (TMCLC)}: Individuals in region $i$ reporting a TMC at an unknown age and time between birth at time $t-a$ and age $a$ at time $t$.
+The likelihood of this outcome was the probability of receiving a TMC in region $i$ before age $a$ at time $t$, $\text{CIF}^{\text{TMC}}_{iat}$
+	\item[(6)] \textbf{MMC left censored (MMCLC)}: Individuals in region $i$ reporting a MMC at an unknown age and time between birth at time $t-a$ and age $a$ at time $t$.
+The likelihood of this outcome was the probability of receiving a MMC in region $i$ before age $a$ at time $t$, $\text{CIF}^{\text{MMC}}_{iat}$
+	\item[(7)] \textbf{MC left censored (MCLC)}: Individuals in region $i$ reporting a circumcision, of unknown type at an unknown age and time, between birth at time $t-a$ and age $a$ at time $t$.
+The likelihood of this outcome was the probability of being circumcised in region $i$ before age $a$ at time $t$, $(1-S_{iat}) = \text{CIF}^{\text{MMC}}_{iat}$
+\end{itemize}
+
+\noindent Taken together, the partial likelihood for the discrete time-to-event model may be expressed as 
+\begin{eqnarray*}
+	L(\boldsymbol{\Theta}) &= \displaystyle\prod_{(i,a,t)} \prod_{s=1}^{N_s} \prod_{j=1}^{J_s}  \underbrace{\left(\lambda^{\text{TMC}}_{iat}\cdot S_{iat}\right)^{\mathbbm{1}^{\text{TMC}}_{sjiat}}}_{\text{(1)}} \cdot  \underbrace{ \left(\lambda^{\text{MMC}}_{iat} \cdot S_{iat}\right)^{\mathbbm{1}^\text{MMC}_{sjiat}}}_{\text{(2)}} \cdot\underbrace{\left(\lambda^{\text{MC}}_{iat} \cdot S_{iat}\right)^{\mathbbm{1}^\text{MC}_{sjiat}}}_{\text{(3)}} \cdot \\
+ & \hspace{1cm}  \underbrace{\left(S_{iat}\right)^{\mathbbm{1}^{RC}_{sjiat}}}_{\text{(4)}} \cdot \underbrace{\left(\text{CIF}^{\text{TMC}}_{iat}\right)^{\mathbbm{1}^{\text{TMCLC}}_{sjiat}}}_{\text{(5)}} \cdot \underbrace{\left(\text{CIF}^{\text{MMC}}_{iat}\right)^{\mathbbm{1}^{\text{MMCLC}}_{sjiat}}}_{\text{(6)}} \cdot \underbrace{\left(\text{CIF}^{\text{MC}}_{iat}\right)^{\mathbbm{1}^{\text{MCLC}}_{sjiat}}}_{\text{(7)}} \\
+	   &= \displaystyle\prod_{(i,a,t)} 
+    \left(\lambda^{\text{TMC}}_{iat}\cdot S_{iat}\right)^{\text{N}^{\text{TMC}}_{iat}} \cdot  
+    \left(\lambda^{\text{MMC}}_{iat} \cdot S_{iat}\right)^{\text{N}^\text{MMC}_{iat}} \cdot 
+    \left(\lambda^{\text{MC}}_{iat} \cdot S_{iat}\right)^{\text{N}^\text{MC}_{iat}}  \cdot \\ & \hspace{1cm}  \left(S_{iat}\right)^{\text{N}^{RC}_{iat}} \cdot \left(\text{CIF}^{\text{TMC}}_{iat}\right)^{\text{N}^{\text{TMCLC}}_{iat}} \cdot \left(\text{CIF}^{\text{MMC}}_{iat}\right)^{\text{N}^{\text{MMCLC}}_{iat}}\cdot
+    \left(\text{CIF}^{\text{MC}}_{iat}\right)^{\text{N}^{\text{MCLC}}_{iat}}
+\end{eqnarray*}
+where $\mathbbm{1}^{l}_{sjiat}$ is an indicator variable indicating whether individual $j$ in survey $s$ and region $i$ reported outcome $l$ at age $a$ and time $t$ and $\text{N}^{l}_{sjiat}$ denotes the total number of individuals reporting outcome (l) in region $i$ at age $a$ and time $t$.
+\begin{equation*}
+	\text{N}^{l}_{iat} = \sum_{s=1}^{N_s}\sum_{j=1}^{J_s} \mathbbm{1}^k_{sjiat}
+\end{equation*}
+where $l$ is TMC, MMC, MC, RC, MMCLC, TMCLC or MCLC which correspond to the outcomes (1)-(7) above.\\
+
+\noindent Survey data are collected through a complex two-stage cluster sampling design with unequal sampling probabilities.
+Performing model inference using a standard likelihood may lead to biased estimates so to account for these survey designs, the probabilities of circumcision were estimated using a weighted pseudo-likelihood in which we replaced the observed counts $\text{N}^l_{iat}$ with weighted counts $\tilde{\text{N}}^l_{iat}$, calculated using survey weights.
+Each individual $j$ in survey $s$ residing in region $i$ had sampling weight $\omega_{sji}$ which were normalised using the Kish effective sample size,
+\begin{equation*}
+	\tilde\omega_{sji} = \frac{\omega_{sji}}{\bar{\omega}_{si}}\cdot \frac{M_s}{M^{\text{eff}}_s} 
+\end{equation*}
+Here, $\bar{\omega}_{si}$ is the arithmetic mean of all survey weights from the individuals sampled in survey $s$ and region $i$ and $M_s$ is the total sample size in survey $s$ and $M^{\text{eff}}_s$ is the Kish effective sample size which accounts for heterogeneity in sampling weights and is calculated using
+\begin{equation*}
+	M^{\text{eff}}_s = \frac{(\sum_j \omega_{sji})^2}{\sum_j \omega_{sji}^{2}}.
+\end{equation*}
+Using the normalised sampling weights, $\tilde\omega_{sji}$, we calculate the weighted counts, $\tilde{\text{N}}^l_{iat}$, for each region, age and time stratum using 
+\begin{equation*}
+	\tilde{\text{N}}^{l}_{iat} = \sum_{s=1}^{N_S}\sum_{j=1}^{N_{J_s}}\tilde\omega_{sji} \mathbbm{1}^{\text{l}}_{sjiat}.
+\end{equation*}
+where $l$ is TMC, MMC, MC, RC, MMCLC, TMCLC or MCLC which correspond to the outcomes (1)-(7) above.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Model checking}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Inference}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \emph{Put a general discussion element for the model giving an overview}
+
+% "threemc"("Multi-level model for male circumcision") is a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). 
+% We have extended this model from its initial application in South Africa to 33 countries within the SSA region. 
+% The model produces estimates of circumcision rates, incidence and coverage (i.e. cumulative indidence), with associated uncertainty bounds, stratified by type, year, age and location.
+% Circumcision rates are projected after their most recent household survey assuming continuation of estimated age-specific rates, with probabilistic uncertainty. 
+% Estimates for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
+
+% \emph{Traditional Circumcision}
+
+% A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practices and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
+% MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
+
+% [Technical details]
+
+% Explain the TMC with time and TMC with no time.
+
+% \emph{Medical Circumcision}
+
+% Explain paed cut off and no paed cut off
+
+% \subsection{Model Specification}
+% \label{sec:org40f2f33}
+
+% In our choice of model specification, we were interested in two main assumptions/features of the
+% model:
+% \begin{itemize}
+% \item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
+% \item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
+% \end{itemize}
+
+% If possible, we hoped to use the same model for every country, or failing that, come up with a
+% satisfactory choice of model specification which would make sense both qualitatively and
+% quantitatively.
+
+% Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
+% In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
+% Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
+This suggests that MMCs in these countries are likely to be on paediatric individuals in traditional settings, so the assumption of constant and
+% negligible paedaitric MMC could be a poor one. 
+% Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
+% It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
+% patterns in non-VMMC countries.
+
+% Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
+% As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
+% It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
+% Historical TMC patterns in these countries, differ significantly, even subnationally.
+% It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
+% In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
+% We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
+
+% We have also performed a quantitative analysis of the different model specifications available
+% to us. A more detailed treatment of this can be found in section x of the appendix.
+
+% For each country, we fit a model for each possible model specification for threemc, that is:
+% \begin{itemize}
+% \item for each choice of temporal prior, namely AR1, RW1 and RW2,
+% \item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
+% \item a choice of whether to include a temporal effect for TMC.
+% \end{itemize}
+% Thus totalling 12 possible models for each country.
+% These models were fit to all of the survey data available, rather than a subset of the data.
+% This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
+% As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
+
+% The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
+% Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
+
+% Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
+% Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
+% This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
+A "good" calibration was regarded as one in which roughly 50\% of survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range.
+% Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
+
+% Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
+
+% For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
+% The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
+% This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
+% It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
+% Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
+% These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
+
+% In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
+% This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
+% However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
+% As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
+
+% Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
+% In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
+For completeness, we decided to include a temporal effect for TMC in the model specification for VMMC priority countries.
+
+% It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
+% A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
+
+% \subsection{Model Calibration and Choice of Temporal Prior}
+% \label{sec:orgbbc65cb}
+
+% For some VMMC priority countries, we did not have access to more recent survey data. 
+% One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
+% In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
+% VMMC programme data was an available source of more recent circumcision data.
+% The DMPPT2 model explicitly used this data to estimate MMC. 
+% The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
+% This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
+% Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
+% A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
+
+% The two main drivers of uncertainty over time in threemc were:
+% \begin{itemize}
+% \item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
+% \item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
+% \end{itemize}
+% The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
+
+% Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
+% One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
+% To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
+% A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
+% For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
+
+% TODO: Finish this write up!
+% TODO: Add results! Also add ternary plot
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-09 paper/scripts/032_results.R
Only have NAs for type-specific circumcision

@@ -365,7 +365,9 @@ tmp <- bind_rows(tmp, diff_df) %>%
 
 # finally, change 0s for countries with no type info to NAs
 tmp <- tmp %>% 
-  mutate(mean = ifelse(iso3 %in% no_type_iso3 & mean == 0, NA, mean))
+  mutate(mean = ifelse(
+    iso3 %in% no_type_iso3 & type != "Total", NA, mean
+  ))
 
 # for testing plot
 # spec_results <- tmp

### 2023-08-09 paper/figures/supp_figs/PPC_P1_Tables.tex
Add paper and supplementary figures drafts in TeX from Matt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.75cm} >{\bfseries}p{3cm} p{1cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{10}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-13} 
  & & & \multicolumn{5}{c}{\bf Time invariant} & \multicolumn{5}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-8} 
  \cmidrule(lr){9-13} 
  & {\bf MMC Model} & {\bf Type} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
  \hline 
AR1 & No cut-off & MC & 21.14 &  0.18 & 41.67 & 61.11 & 70.83 &  2.59 &  0.03 & 68.75 & \bf86.11 & 93.75 \\ 
  &  & MMC & 29.85 &  0.27 & 15.97 & 32.64 & 50.00 & \bf10.87 & \bf 0.14 & \bf50.00 & \bf72.92 & \bf86.11 \\ 
  &  & TMC & 29.78 &  0.27 & 18.75 & 34.03 & 53.47 & \bf11.45 &  0.14 & \bf45.83 & \bf67.36 & \bf84.03 \\ 
  & Paediatric cut-off & MC & 19.95 &  0.16 & 52.08 & 61.81 & 68.75 & \bf 2.50 & \bf 0.03 & \bf72.92 & \bf86.11 & \bf95.14 \\ 
  &  & MMC & 29.86 &  0.27 & 14.58 & 32.64 & 47.22 & 11.13 &  0.14 & 49.31 & 68.06 & 85.42 \\ 
  &  & TMC & 29.68 &  0.27 & 16.67 & 31.25 & 49.31 & 11.65 & \bf 0.14 & 43.75 & \bf67.36 & 82.64 \\ 
 RW1 & No cut-off & MC & 20.80 &  0.20 & 58.33 & 70.83 & 78.47 &  2.58 &  0.03 & 69.44 & \bf86.81 & \bf95.14 \\ 
  &  & MMC & 25.13 &  0.28 & 34.72 & 60.42 & 72.92 & \bf10.84 & \bf 0.14 & \bf50.69 & \bf70.83 & \bf86.11 \\ 
  &  & TMC & 29.30 &  0.29 & 27.08 & 47.22 & 64.58 & \bf11.40 &  0.14 & \bf47.92 & \bf68.06 & \bf84.72 \\ 
  & Paediatric cut-off & MC & 19.23 &  0.17 & 57.64 & 68.06 & 75.69 & \bf 2.52 & \bf 0.03 & \bf71.53 & \bf86.81 & \bf95.14 \\ 
  &  & MMC & 25.64 &  0.28 & 36.81 & 60.42 & 70.83 & 11.14 &  0.14 & 46.53 & 68.75 & 84.03 \\ 
  &  & TMC & 27.11 &  0.28 & 27.78 & 52.08 & 68.75 & 11.69 & \bf 0.14 & 42.36 & 65.28 & 81.94 \\ 
 RW2 & No cut-off & MC & 19.33 &  0.20 & 65.97 & 75.00 & 79.17 &  2.61 &  0.03 & 69.44 & \bf86.11 & 94.44 \\ 
  &  & MMC & 25.38 &  0.29 & 41.67 & 62.50 & 75.00 & \bf11.03 &  0.14 & \bf49.31 & \bf70.14 & \bf86.81 \\ 
  &  & TMC & 33.52 &  0.31 & 27.08 & 43.06 & 54.17 & \bf11.64 &  0.14 & \bf46.53 & \bf69.44 & \bf82.64 \\ 
  & Paediatric cut-off & MC & 18.08 &  0.17 & 61.81 & 70.83 & 79.17 & \bf 2.54 & \bf 0.03 & \bf72.22 & \bf86.11 & \bf95.14 \\ 
  &  & MMC & 24.08 &  0.29 & 47.92 & 65.97 & 76.39 & 11.16 & \bf 0.14 & 47.92 & 68.75 & 84.72 \\ 
  &  & TMC & 27.61 &  0.29 & 32.64 & 51.39 & 72.22 & 11.66 & \bf 0.14 & 44.44 & 67.36 & \bf82.64 \\ 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in Angola. Combinations include (i) Time invariant or Time variant TMC, (ii) No cut off vs. Paediatric cut-off in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), mean absolute error (MAE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1AGO} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.75cm} >{\bfseries}p{3cm} p{1cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{10}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-13} 
  & & & \multicolumn{5}{c}{\bf Time invariant} & \multicolumn{5}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-8} 
  \cmidrule(lr){9-13} 
  & {\bf MMC Model} & {\bf Type} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
  \hline 
AR1 & No cut-off & MC & 268.00 &   0.21 &  31.50 &  43.85 &  55.65 & \bf107.35 & \bf  0.12 & \bf 48.67 & \bf 74.98 & \bf 88.63 \\ 
  &  & MMC &  25.63 & \bf  0.02 &  79.80 &  84.25 &  89.68 &  21.41 &   0.03 & \bf 82.71 & \bf 90.74 &  96.42 \\ 
  &  & TMC & 243.98 &   0.19 &  32.86 &  45.27 &  58.12 & \bf 93.94 & \bf  0.10 & \bf 51.76 &  75.79 & \bf 90.24 \\ 
  & Paediatric cut-off & MC & 264.10 &   0.20 &  31.81 &  43.42 &  55.90 & 108.18 &   0.12 &  48.12 &  74.12 &  88.33 \\ 
  &  & MMC &  25.89 &   0.02 &  79.93 &  84.74 &  89.93 & \bf 21.38 &   0.03 & \bf 82.71 &  90.61 & \bf 96.48 \\ 
  &  & TMC & 239.65 &   0.19 &  32.18 &  45.09 &  58.55 &  94.77 &   0.11 &  51.51 & \bf 76.03 & \bf 90.24 \\ 
 RW1 & No cut-off & MC & 273.42 &   0.22 &  31.87 &  46.51 &  61.52 & \bf107.12 & \bf  0.11 & \bf 48.86 & \bf 74.31 & \bf 88.39 \\ 
  &  & MMC &  36.74 &   0.06 &  82.15 & \bf 92.09 & \bf 96.66 &  21.42 &   0.03 &  82.46 &  90.61 &  96.05 \\ 
  &  & TMC & 242.12 &   0.19 &  33.60 &  45.71 &  59.36 & \bf 93.67 & \bf  0.10 & \bf 52.38 & \bf 76.53 & \bf 90.55 \\ 
  & Paediatric cut-off & MC & 389.36 &   0.33 &  24.21 &  40.83 &  61.46 & 108.10 &   0.12 &  48.49 &  74.24 &  88.20 \\ 
  &  & MMC & 299.80 &   0.28 &  25.39 &  55.84 &  83.57 & \bf 21.30 & \bf  0.03 & \bf 82.71 &  90.55 &  96.36 \\ 
  &  & TMC & 225.52 &   0.18 &  36.50 &  51.76 &  65.29 &  94.65 &   0.11 &  51.95 &  76.22 &  90.43 \\ 
 RW2 & No cut-off & MC & 286.12 &   0.23 &  31.81 &  46.82 &  58.86 & \bf108.16 & \bf  0.12 & \bf 48.73 & \bf 73.19 & \bf 87.83 \\ 
  &  & MMC &  41.89 &   0.06 &  77.95 &  90.36 &  95.37 &  21.29 &   0.03 &  82.33 & \bf 90.61 & \bf 96.85 \\ 
  &  & TMC & 240.47 &   0.20 &  36.07 &  49.35 &  64.48 & \bf 94.72 & \bf  0.10 & \bf 52.01 & \bf 75.73 & \bf 89.56 \\ 
  & Paediatric cut-off & MC & 527.08 &   0.39 &  10.99 &  20.38 &  50.59 & 109.14 &   0.12 &  47.93 &  73.13 &  87.71 \\ 
  &  & MMC & 395.15 &   0.33 &  16.99 &  43.85 &  90.06 & \bf 21.22 & \bf  0.03 & \bf 82.89 & \bf 90.61 &  96.48 \\ 
  &  & TMC & 220.06 &   0.20 &  43.55 &  61.83 &  72.76 &  95.62 &   0.11 &  51.95 &  75.48 &  89.38 \\ 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in Rwanda. Combinations include (i) Time invariant or Time variant TMC, (ii) No cut off vs. Paediatric cut-off in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), mean absolute error (MAE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1RWA} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.75cm} >{\bfseries}p{3cm} p{1cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{10}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-13} 
  & & & \multicolumn{5}{c}{\bf Time invariant} & \multicolumn{5}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-8} 
  \cmidrule(lr){9-13} 
  & {\bf MMC Model} & {\bf Type} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & {\bf CRPS} & {\bf RMSE} & {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
  \hline 
AR1 & No cut-off & MC & 732.22 &   0.36 &  29.80 &  44.62 &  59.30 & 269.82 &   0.20 &  60.34 & \bf 84.32 &  95.41 \\ 
  &  & MMC & 628.01 &   0.30 &  38.39 &  49.81 &  60.90 & 208.34 &   0.15 & \bf 68.75 &  86.52 & \bf 95.86 \\ 
  &  & TMC & 323.98 &   0.17 &  50.41 &  64.94 &  77.93 & \bf193.70 &   0.15 & \bf 66.77 & \bf 87.68 &  96.15 \\ 
  & Paediatric cut-off & MC & 688.81 &   0.34 &  32.19 &  48.62 &  63.14 & \bf269.35 & \bf  0.20 & \bf 60.75 &  83.91 & \bf 95.44 \\ 
  &  & MMC & 557.80 &   0.28 &  38.95 &  52.58 &  64.53 & \bf208.27 & \bf  0.15 &  68.63 & \bf 86.56 & \bf 95.86 \\ 
  &  & TMC & 316.33 &   0.17 &  49.78 &  65.38 &  78.45 & 195.04 & \bf  0.15 & \bf 66.77 &  86.82 & \bf 96.45 \\ 
 RW1 & No cut-off & MC & 729.32 &   0.36 &  29.61 &  45.07 &  59.22 & \bf268.14 &   0.20 &  60.38 & \bf 84.91 & \bf 95.86 \\ 
  &  & MMC & 622.26 &   0.30 &  38.35 &  50.45 &  60.94 & 207.60 &   0.15 &  68.60 &  86.63 & \bf 96.23 \\ 
  &  & TMC & 316.37 &   0.17 &  51.12 &  66.58 &  79.31 & \bf189.39 & \bf  0.15 & \bf 67.74 & \bf 88.69 & \bf 97.01 \\ 
  & Paediatric cut-off & MC & 693.76 &   0.35 &  32.41 &  47.87 &  63.14 & 268.53 & \bf  0.20 & \bf 60.72 &  84.54 &  95.71 \\ 
  &  & MMC & 561.28 &   0.28 &  38.76 &  52.80 &  65.09 & \bf207.50 & \bf  0.15 & \bf 68.97 & \bf 86.74 &  96.04 \\ 
  &  & TMC & 308.61 &   0.17 &  51.61 &  67.33 &  80.92 & 192.05 &   0.15 &  67.36 &  88.01 &  96.83 \\ 
 RW2 & No cut-off & MC & 727.28 &   0.36 &  29.91 &  45.07 &  59.60 & 269.03 &   0.20 &  60.53 & \bf 84.76 & \bf 95.71 \\ 
  &  & MMC & 619.68 &   0.30 &  38.20 &  50.86 &  61.61 & \bf207.68 & \bf  0.15 & \bf 68.93 &  86.56 & \bf 96.27 \\ 
  &  & TMC & 315.40 &   0.17 &  50.75 &  66.88 &  79.84 & \bf190.27 & \bf  0.15 & \bf 68.00 & \bf 88.13 & \bf 96.68 \\ 
  & Paediatric cut-off & MC & 732.75 &   0.36 &  29.80 &  44.47 &  59.26 & \bf268.89 & \bf  0.20 & \bf 60.60 &  84.35 &  95.63 \\ 
  &  & MMC & 623.19 &   0.30 &  38.35 &  50.93 &  62.02 & 208.20 &   0.15 &  68.45 & \bf 86.67 &  96.23 \\ 
  &  & TMC & 320.20 &   0.17 &  50.34 &  65.38 &  78.04 & 192.74 &   0.15 &  66.95 &  87.90 &  96.60 \\ 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in South Africa. Combinations include (i) Time invariant or Time variant TMC, (ii) No cut off vs. Paediatric cut-off in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), mean absolute error (MAE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1ZAF} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-09 paper/paper.tex
Add paper and supplementary figures drafts in TeX from Matt

@@
 
+\vspace{-1cm}
+
+Patrick O'Toole\textsuperscript{1},
+Matthew L. Thomas\textsuperscript{1,2},
+Oliver Stevens\textsuperscript{1},
+Kevin Lam\textsuperscript{1,3},
+Katharine Kripke\textsuperscript{4},
+Rachel Esra\textsuperscript{1},
+Ian Wanyeki\textsuperscript{5},
+Lycias Zembe\textsuperscript{5},
+Jeffrey W. Eaton\textsuperscript{1,6} \\
+\smallskip
+
+\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial Colleg  e London, London, United Kingdom\\
+\textbf{2} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{3} Department of Statistics, University of British Columbia, Vancouver, Canada\\
+\textbf{4} Avenir Health, Washington, District of Columbia, United States of America\\
+\textbf{5} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
+\textbf{6} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
+
+\smallskip
+
+* Corresponding Author Email
+
 \clearpage
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+HIV epidemic continues to to be a problem. Many interventions available etc. VMMC has been proven to be an effective way of doing this.
+
+The World Health Organization (WHO) and the Joint United Nations Programme on HIV/AIDS (UNAIDS) have identified fifteen countries in sub-Saharan Africa that have a high HIV prevalence and low male circumcision (MC) coverage as priority countries which should scale-up VMMC for HIV prevention: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \todo{Check this and the citations} \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
+Since 2007, there have been XX\todo{Find this number and cite} million VMMCs conducted in these countries with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR) and the Global Fund to Fight AIDS, Tuberculosis and Malaria.
+Targets were set by UNAIDS to reach 80\% circumcision coverage among men aged 15--49 years in priority countries by 2015 which have since been updated to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework}.
+
+The landscape of male circumcision in sub-Saharan Africa is complex and highly heterogeneous.
+Despite the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries.
+The provision of traditional male circumcision (TMC), such as the typical age at circumcision and what it entails, can vary considerably and is influenced by community, religious, ethnic and cultural led values.
+There is substantial sub-national heterogeneity in the proportion and average of men receiving TMC between at a district level in South Africa.
+Even on a national level TMC is universally practiced in {\color{red}\bf XXX} and is barely conducted in {\color{red}\bf XXX}.
+TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training.
+The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, due to TMC may not involve a complete circumcision and instead be only partial removal of the foreskin or a simple incision in the prepuce in some populations.
+\todo{Cite this paragraph.}
+
+Why is understanding this important? DMPPT2 and Cork et al. and Thomas et al. have been approaches
+
+In this paper,...
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Methods}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Data}
 \label{sec:org020fc8c}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-08-09 paper/supp_figs.tex
Add paper and supplementary figures drafts in TeX from Matt

@@
 \usepackage{authblk}
+\usepackage{array}
+\usepackage{multirow}
 \usepackage{pdfpages}
@@
 \linespread{1.5}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 \label{sec:org8802288}
-
-% \subsection{Data}
-% \label{sec:orga1d1a98}
 
@@
 \begin{itemize}
-    \item Add in typeless model
     \item Aggregated areas
@@
 
-\noindent Following a similar approach to \cite{thomas2021multilevel}, we used a Bayesian hierarchical model with small area estimation methods to model probabilities of
-circumcision.
-The Multi-level Model for Male Circumcision (threemc) uses survey data to estimates the probabilities and coverage of of circumcision were estimated using a competing risk discrete time-to-event model stratified by region, age, and time for two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+Following a similar approach to \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type.
+
+We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
+
+In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+In countries that did not have a survey that contained information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type.
+Therefore, we consider a used survey data to estimates the probabilities and coverage of circumcision of any or (unknown) type (MC).
 
@@
 \subsection{Probabilities of circumcision (by type)}
-\label{sec::tradcirc}
+\label{sec::bytype}
 
@@
 
-We used survey data to model the probabilities of recieving a TMC, MMC or MC of any time for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
+We used survey data to model the probabilities of receiving a TMC, MMC or MC for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
 
@@
 A key assumption of \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa but an assumption of a constant probability of TMC might not be feasible everywhere.
-For example, in some countries the level of TMC has changed through time due to demographic shifts and practices over time.
-There has also been a shift (or a replacement) of TMCs through MMCs, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations.
-There may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
-
-Therefore, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e.
+For example, in some countries the level and practices of TMC has changed through time due to demographic shifts.
+There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
+Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
+Here, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e.
 constant over time) and (ii) time variant (i.e.
-non-constant over time).
+varying over time).
 The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function,
@@
 
-The choice of whether a country used a time-invariant or time-variant probability of circumcision was decided through {\color{red}\bf[Need more information]}
+Whether a country used a time-invariant or time-variant probability of TMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
 
@@
 \noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
-\begin{equation}
+\begin{equation*}
 		\lambda^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
-	\label{eqn::mmc}
-\end{equation}
-
-To ensure the overall probability of circumcision $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the probability of TMC occurred before MMC in each time step.
-Therefore, we practically model the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
+\end{equation*}
+To ensure $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the TMC prior to MMC in each time step.
+Therefore, we condition on this and practically model the probability an individual in region $i$ received an MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
 \begin{equation*}
@@
 \end{equation*}
-such that
+It then follows that 
 \begin{equation*}
@@
 
-{\color{red}\bf[CITE]} included VMMC programmatic data in their model and programmes only provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision tends to occur through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
-Therefore, to ensure any increase in MMC for those aged 10 and over did not affect the probability of MMC in those under 10, $\tilde{\lambda}^{\text{MMC}}_{iat}$ was separated into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
-
-Here, we consider two models {\color{red}\bf[Need more information]}
+The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed  since 2008 in countries that have programmes to scale-up MMC for HIV prevention.
+VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
+Due to this, Thomas et al.
+\cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
+This ensured that any increase in MMC for those aged 10 and over did not affect the probability of MMC in those under 10 in South Africa.
+However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage.
+Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) [Need a name] and (ii) [Need a name].
 
@@
 
-The choice of whether a country used a {\color{red}\bf[Need more information]} or {\color{red}\bf[Need more information]} probability of circumcision was decided through {\color{red}\bf[Need more information]}
+The choice of whether a country used a {\color{red}\bf[Need a name]} or {\color{red}\bf[Need a name]} probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
 
@@
 
-\subsubsection*{Male circumcision}
+\subsubsection*{Circumcision of any (or unknown) type}
 
@@
 
-\noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability of circumcision of any type, at age $a$ and time $t$ given they were uncircumcised by age $a-1$ and time $t-1$ as
+\noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability of circumcision of any (or unknown) type, at age $a$ and time $t$ given they were uncircumcised by age $a-1$ and time $t-1$ 
+\begin{equation*}
+	\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1,t-1))
+\end{equation*}
+and this is modelled using the sum of having either a TMC or MMC at age $a$ and time $t$ given they were uncircumcised by age $a-1$ and time $t-1$,
+\begin{equation*}
+	\lambda^{\text{MC}}_{iat} = \lambda^{\text{TMC}}_{ia} + \lambda^{\text{MMC}}_{iat}. 
+\end{equation*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Probabilities of circumcision (typeless)}
+\label{sec::typeless}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Some countries did not have a survey that collected information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type.
+In this case, we use survey data to model the probabilities of receiving a MC of any type for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
+
+We defined $\lambda^{\text{MC}}_{iat}$ as the probability an individual in region $i$ received a circumcision  at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
 \begin{equation}
-	\begin{split}
-	\lambda^{\text{MC}}_{iat} &= \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1,t-1)) \\ 
-	              &= \lambda^{\text{TMC}}_{ia} + \lambda^{\text{MMC}}_{iat}. 
-	\end{split}
-	\label{eqn::tot}
+		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
+	\label{eqn::mc}
 \end{equation}
+Here, we model $\lambda^{\text{MC}}_{iat}$ using a piece-wise logit-linear function:
+\begin{equation*}
+	\text{logit}(\lambda^{\text{MC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
+\end{equation*}
+where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MCs over time across regions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Including aggregated estimates}
+\label{sec::aggregated}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{equation*}
+	\lambda^{\text{MC}}_{Rat} = \frac{\sum_{i\in R}P_{iat}\lambda^{\text{MC}}_{iat}}{\sum_{i\in R}P_{iat}}
+\end{equation*}
 
@@
 \subsection{Circumcision coverage}
+\label{sec::coverage}
 
@@
 
-The probability $S_{iat}$ of remaining uncircumcised up to age $a$ and time $t$,  typically referred to as the survivor function, was expressed as
+The probability $S_{iat}$ of remaining uncircumcised up to age $a$ and time $t$,  typically referred to as the survivor function, is expressed as
 \begin{equation}
@@
 \subsection{Model priors}
+\label{sec::priors}
 
@@
 \end{align*} 
-where $b_{aj}$ are B-spline basis functions with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $\omega_{j}$ are the spline weight parameters to be estimated.
+where $b_{aj}$ are B-spline basis functions {\color{red}[CITE]} with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $\omega_{j}$ are the spline weight parameters to be estimated.
 The weights $w_{j}$ are penalised using an AR1 process
@@
 \begin{align*} 
-  \beta_t \; | \; \beta_{t-1},  \rho_{\beta}, \tau_{\beta} &\sim
-  \begin{cases}
-  	N(0, \tau^{-1}_{\phi}) & t = 1\\
-  	N(\rho_{\beta} \cdot \beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 2, 3,\ldots, T
-  \end{cases}
+  \beta_{t} \; | \; \beta_{t-1}, \rho_{\beta}, \tau_{\beta} &\sim N(\rho_{\beta} \cdot \beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 2, 3,\ldots, N_T \\
+  \beta_{1} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1
 \end{align*}
@@
 \begin{align*} 
-  \beta_t \; | \; \beta_{t-1}, \rho_{\beta}, \tau_{\beta} &\sim
-  \begin{cases}
-  	N(0, \tau^{-1}_{\phi}) & t = 1\\
-  	N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 2, 3,\ldots, T
-  \end{cases}
+  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 2, 3,\ldots, N_T \\
+  \beta_{1} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1
 \end{align*}
@@
 \begin{align*} 
-  \beta_t \; | \; \beta_{t-1}, \beta_{t-2}, \rho_{\beta}, \tau_{\beta} &\sim
-  \begin{cases}
-  	N(0, \tau^{-1}_{\phi}) & t = 1, 2\\
-  	N(2\beta_{t-1} - \beta_{t-2}, \;\; \tau^{-1}_{\beta}) \;\;\; & t = 3, 4,\ldots, T
-  \end{cases}
+  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 3, 4,\ldots, N_T \\
+  \beta_{t} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1, 2
 \end{align*}
@@
 \subsection{Likelihood}
+\label{sec::likelihood}
 
@@
 Survey data consists of individual observations of self-reported age at circumcision, date of birth, and circumcision type (medical or traditional) from male survey respondents.
-Circumcision status observations were right censored if the respondent reported not being circumcised at the time of the survey or left censored if the individual reported being circumcised at the time of survey but did not report their age at circumcision.\\
+Circumcision status observations were right censored if the respondent reported not being circumcised at the time of the survey or left censored if the individual reported being circumcised at the time of survey but did not report their age at circumcision.
 
@@
 Individuals who self-reported they were circumcised but have a missing age at circumcision were included in the analysis through left censoring.
-\\
 
@@
 \end{equation*}
-where $l$ is TMC, MMC, MC, RC, MMCLC, TMCLC or MCLC which correspond to the outcomes (1)-(7) above.\\
+where $l$ is TMC, MMC, MC, RC, MMCLC, TMCLC or MCLC which correspond to the outcomes (1)-(7) above.
 
@@
 \subsection{Model checking}
+\label{sec::modelcheck}
 
@@
 \subsection{Inference}
+\label{sec::inference}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+All models were implemented and fitted in R \cite{rcore} using Template Model Builder (TMB) \cite{kristensen2016tmb}.
+TMB is a software package that performs approximate Bayesian inference by uses automatic differentiation and Laplace approximations to estimate posterior distributions for model parameters.
+Models were optimised using the {\color{red}quasi-newton L-BFGS-B} optimisation method \cite{byrd1995limited}.
+
+Using the final models from each country, we estimated full posterior distributions of the annual probabilities of becoming circumcised and the corresponding circumcision coverage {\color{red}between 2008 and 2021}, by circumcision type, single-year age group, and the PSNU level.
+Posterior predictive distributions for aggregates were obtained using Monte Carlo sampling with samples drawn from the joint posterior distributions, conditional on the optimised hyper-parameters \cite{eaton2021naomi}.
+Joint samples of the annual probabilities of becoming circumcised and the corresponding circumcision coverage in each region-age-time-type stratum were aggregated to produce samples from the posterior distribution of any quantity of interest.
+For each aggregate, the posterior mean, median, standard deviation, and quantile-based 95\% credible intervals (CI) were computed from the corresponding posterior distribution.
+Samples were aggregated: (1) from PSNU level to coarser administrative boundaries (e.g.
+province, national) and (2) from single-year age groups to five-year age group (0--4, 5--9, etc.) and coarser priority age groups (15--49, 15--29, etc.).
+A full list of model outputs can be found in Table \ref{tab::inputsoutputs}.
+
+{\linespread{1} 
+\begin{table}[H]
+	\small
+	\centering	
+	\caption{Summary of model inputs and outputs.}
+    \label{tab::inputsoutputs}
+	\begin{tabular}{| p{0.45\linewidth} | p{0.45\linewidth} |}
+		\hline
+
+			\textbf{\underline{Model inputs}} & \textbf{\underline{Model outputs}} \\
+
+			{\bf Area hierarchy.} List of administrative areas used for health planning ("districts"), geographic boundaries, and nesting in higher level administrative areas.
+			\vspace{5pt}
+
+			{\bf Population.} Population estimate stratified by district, sex, and single-year age group (0,1, $\cdots$, 59) covering the period of interest. 
+			\vspace{5pt}
+
+			{\bf Household surveys.} Data related to age, residence, (self-reported) circumcision status, age at circumcision and type of circumcision (medical/traditional) from recent HIV household surveys.
+
+		& 
+			{\bf Indicators.}  The model produces outputs for the following indicators:
+			\begin{itemize}
+				\item {\it Probabilities of circumcision}
+                \item {\it Incidence of circumcision}
+				\item {\it Circumcision coverage (cumulative incidence)}
+				\item {\it Male population}
+				\item {\it Number circumcised}
+				\item {\it Number uncircumcised}
+			\end{itemize}
+			\vspace{5pt}
+			{\bf Stratifications.} All indicators are stratified according to: 
+			\begin{itemize}
+				\item {\it Geographic}: 
+				\begin{itemize}
+					\item All levels of the area hierarchy (e.g. national, province, district)
+				\end{itemize}
+				\item {\it Age groups}: 
+				\begin{itemize}
+					\item Single-year age group (0, 1, $\cdots$, 59)
+					\item Five-year age groups (0-4, 5-9, $\cdots$, 55-59)
+					\item {\color{red}\bf Others (0+, 10+, 15+, 15-24, 10-24, 15-29, 10-29, 15-39, 10-39, 15-49, 10-49 and 25-49)}
+				\end{itemize}
+				\item {\it Type}: 
+				\begin{itemize}
+					\item Traditional
+					\item Medical 
+					\item Any (or unknown) type 
+				\end{itemize}
+				\item {\it Time}: 
+				\begin{itemize}
+					\item Annual, {\color{red}\bf 2008-2021}
+				\end{itemize}
+			\end{itemize}
+			\vspace{5pt}
+			{\bf Statistics.} Posterior summary statistics are computed for:
+			\begin{itemize}
+				\item Point estimates: 
+				\begin{itemize}
+					\item Mean 
+					\item Median
+				\end{itemize}
+				\item Uncertainty: 
+				\begin{itemize}
+					\item Standard deviation
+					\item 95\% credible interval (quantile-based)
+				\end{itemize}
+			\end{itemize}\\
+		\hline 
+	\end{tabular}
+\end{table}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\section{Model Calibration}
+\label{sec::PPC1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{landscape}
+
+\include{paper/figures/supp_figs/PPC_P1_Tables.tex}
+
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\section{Model Selection}
+\label{sec::PPC2}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-09 paper/figures/supp_figs/PPC_P1_Tables.R

@@ -1,0 +1,131 @@
+#####################
+### Preliminaries ###
+#####################
+# Clearing Workspace
+rm(list = ls())
+
+# Loading required packages
+require(tidyverse)
+require(dplyr)
+require(reshape2)
+require(xtable)
+require(plyr)
+require(sf)
+
+# Reading in tables 
+results <- read_csv("~/Desktop/01e_new_final_ppc_models_fit_stats.csv")
+
+# Loading shapefiles 
+areas <- read_sf("~/Desktop/areas.geojson")
+
+####################################
+### Outputting PPC Part 1 Tables ###
+####################################
+# List of countries
+# cntry <- unique(results$cntry)
+cntry <- c('AGO', 'RWA', 'ZAF')
+
+# Opening text file
+sink('~/Desktop/PPC_P1_Tables.txt')
+
+cat("%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \n")
+
+# Loop for each country 
+for (i in cntry){
+  # filtering for country
+  tmp <- results %>%
+    filter(cntry == i) %>%
+    as.data.frame()
+  
+  # Multiplying the coverage by 100 and rounding 
+  tmp[,c("ppd_0.500", "ppd_0.800", "ppd_0.950")] <- 100 * tmp[,c("ppd_0.500", "ppd_0.800", "ppd_0.950")]
+  
+  # Formatting dataset for output
+  tmp <- tmp %>%
+    # Altering labels 
+    mutate(rw = case_when(rw_order == 0 ~ "AR1",
+                          rw_order == 1 ~ "RW1",
+                          rw_order == 2 ~ "RW2"),
+           paed = case_when(paed_age_cutoff == "10" ~ "Paediatric cut-off",
+                            paed_age_cutoff == "Inf" ~ "No cut-off"),
+           type = case_when(type == "MC coverage" ~ "MC",
+                            type == "TMC coverage" ~ "MMC",
+                            type == "MMC coverage" ~ 'TMC'),
+           tmc = case_when(inc_time_tmc == TRUE ~ "Time invariant",
+                           inc_time_tmc == FALSE ~ 'Time variant')) %>%
+    # selecting relevant columns
[…]

### 2023-08-10 paper/scripts/032_results.R
No longer using geofaceted rates plot

@@ -464,10 +464,10 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
     )
 }
 
-p2final <- map_plot(tmp1, areas_plot, colourPalette, colourPalette2) + 
+p2final <- map_plot(tmp, areas_plot, colourPalette, colourPalette2) + 
   ggtitle(main_title)
  
-p2final
+# p2final
 
 # save plots
 # ggsave(plot = p2a, filename = "poster/plots/p2a.png", width = 1980, height = 1060, units = "px")
@@ -696,7 +696,7 @@ p3 <- plt_data %>%
   # scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
   # coord_flip(ylim = c(0.04, 0.975), clip = "off")
   coord_flip(clip = "off")
-p3
+# p3
 
 p3$plot_order <- plot_order
 
@@ -802,89 +802,6 @@ ggplot2::ggsave(
 
 saveRDS(p4_geo, "paper_poster_plots/paper/plots/04_geo_age.RDS")
 
-#### Figure 5: Geofaceted plot for circ rates (i.e. n circs by type) ####
-
-p5 <- plt_coverage_year_national(
-  results_agegroup = results_agegroup_rate,
-  areas            = areas,
-  last_surveys     = last_surveys,
-  spec_age_group   = "0+",
-  # spec_years       = spec_years,
-  spec_years       = spec_years,
-  spec_model       = "No program data", 
-  spec_types = paste(c("MC", "MMC", "TMC"), "probability"),
-  main             = "",
-  n_plots          = length(unique(results_agegroup_rate$iso3))
-)[[1]]
-
-# grid for geofaceting, standardise country names
-ssa_grid <- geofacet::africa_countries_grid1 %>%
-  mutate(
-    name = case_when(
-      grepl("Ivoire", name)                      ~ "Cote d'Ivoire",
-      name == "Gambia"                           ~ "The Gambia",
-      name == "Democratic Republic of the Congo" ~ "DR Congo",
-      name == "Republic of the Congo"            ~ "Congo",
-      name == "Equatorial Guinea"                ~ "Eq. Guinea",
-      name == "Central African Republic"          ~ "Cent. Af. Rep.",
-      TRUE                                       ~ name
-    )
-  ) %>%
[…]

### 2023-08-10 paper/scripts/032_results.R
Add info

@@ -1,6 +1,8 @@
 #### Create plots for results ####
 
 # Produce summary stats here as well
+# must be run in threemc-orderly https://github.com/mrc-ide/threemc-orderly 
+# Orderly `archive/` found on Sharepoint https://tinyurl.com/ufpxymmb
 
 # stopifnot(dirname(getwd()) == "threemc-orderly")
 while(basename(getwd()) != "threemc-orderly") setwd("../.")

### 2023-08-10 paper/scripts/032_results.R
py now p5

@@ -804,8 +804,7 @@ ggplot2::ggsave(
 
 saveRDS(p4_geo, "paper_poster_plots/paper/plots/04_geo_age.RDS")
 
-
-#### Figure y: Change in MC/MMC/TMC from 2000 ####
+#### Figure 5: Change in MC/MMC/TMC from 2000 ####
 
 no_type_iso3 <- c("LBR", "SEN", "NER", "GIN", "COD")
 vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
@@ -934,7 +933,7 @@ tmp_long <- tmp %>%
 tmp_long_lower <- tmp_long %>% filter(year == 2000)
 tmp_long_upper <- tmp_long %>% filter(year == 2020)
 
-py <- tmp_long %>%
+p5 <- tmp_long %>%
   ggplot() +
   geom_point(aes(x = country_idx, y = value, colour = factor(year)), size = 3) +
   geom_segment(
@@ -1002,11 +1001,11 @@ py <- tmp_long %>%
   ) +
   coord_flip(clip = "off")
 
-py
+p5
 
 ggplot2::ggsave(
-  "paper_poster_plots/paper/plots/0y_change_00_20.png",
-  py,
+  "paper_poster_plots/paper/plots/05_change_00_20.png",
+  p5,
   width = 16,
   height = 10,
   units = "in"

### 2023-08-10 paper/paper.tex
Add plots to TeX file

@@
 \usepackage{multirow}
+\usepackage{todonotes}
 \setlength{\tabcolsep}{5pt}
@@
 
+% Surveys Plot (may be moved to supp. figs)
 \begin{figure}
@@
     % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
-    \caption{Household surveys detailing circumcision patterns in SSA.
+    \includegraphics[width=.9\linewidth]
+    {plots/01_survey_table.png}
+    \caption{\emph{Household surveys detailing circumcision patterns in SSA.
 The colour and size of points are determined by the provider and sample size of each respective survey.
-Triangular points have no information on circumcision type.}
+Triangular points have no information on circumcision type.}}
 \end{figure}
@@
 
-\emph{Figure 2: Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries.} 
-\emph{Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana.}
-
-TODO: Remove superfluous whitespace here!
+% Map Plot
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\linewidth]
+    {plots/02_map_plot_facet.png}
+    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years.
+Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively.
+Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
+\end{figure}
 
@@
 
-\emph{Figure 3: District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.}
-\emph{Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).}
-\emph{Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}
+% Subnational coverage plot
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\linewidth]
+    {plots/03_subnat_plot.png}
+    \caption{\emph{District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.
+    Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).
+    Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}}
+\end{figure}
 
@@
 
-\emph{Figure 4: Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020.
+% Geofaceted plot of 2020 coverage by age
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\linewidth]
+    {plots/04_geo_age.png}
+    \caption{\emph{Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020.
 The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy.
-Purple areas represent countries where circumcision type could not be ascertained from surveys.}
+Purple areas represent countries where circumcision type could not be ascertained from surveys.}}
+\end{figure}
 
@@
 \label{sec:org5fb5e18}
-\emph{Figure 6: Number of men aged 10-29 years who were medically circumcised and traditionally circumcised each year between 2010 and 2020.
-The lighter shaded area represents projection after the most recent household survey.
-Purple areas represent countries where circumcision type could not be ascertained from surveys.}
+
+% Dumbbell of type-specific cov change 00'-20'
+% todo: Rewrite caption
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\linewidth]
+    {plots/05_change_00_20.png}
+    \caption{\emph{Absolute difference, with associated errors, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region.
+Plots are split by circumcision type.
+Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.
+}}
+\end{figure}
 

### 2023-08-11 paper/scripts/032_results.R
Update colour scheme for map plot

@@ -70,10 +70,21 @@ colourPalette <- rev(colorRampPalette(
     "#e6f598", "#abdda4", "#66c2a5", "#3288bd", 
     "#5e4fa2")
 )(100))
+# change mint green as it's awful looking in % Change facets of map plot
+# colourPalette <- rev(colorRampPalette(
+#   c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
+#     "#e6f598", 
+#     # "#66c2a5", 
+#     "#54bb9a",
+#     "#46af8e",  
+#     "#3288bd", "#5e4fa2")
+# )(100))
+
 
 # colourPalette for % changeR
-colourPalette2 <- rev(heat.colors(100))
+# colourPalette2 <- rev(heat.colors(100))
 # colourPalette2 <- viridis::viridis(100)
+colourPalette2 <- viridis::plasma(100)
 
 
 #### Load Data ####
@@ -372,9 +383,11 @@ tmp <- tmp %>%
   ))
 
 # for testing plot
-# spec_results <- tmp
-# spec_areas <- areas_plot
+spec_results <- tmp
+spec_areas <- areas_plot
 
+rm(results_agegroup1, areas1); gc()
+   
 map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
 
   spec_results$type <- factor(
@@ -406,18 +419,16 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       limits = c(0, 1),
       label = scales::label_percent(accuracy = 1), 
       guide = guide_colourbar(
-        # direction = "vertical",
+        direction = "horizontal",
         label = TRUE,
         draw.ulim = TRUE,
         draw.llim = TRUE,
         frame.colour = "black",
         ticks = TRUE,
-        # barheight = 1,
-        barheight = 15,
-        # barwidth = 30
-        # barwidth = 20
-        barwidth = 1,
-        title.position = "right"
+        barheight = 1,
+        # barwidth = 20,
+        barwidth = 22,
+        title.position = "bottom"
       )
     ) +
     # guides(fill = guide_colourbar(title.position = "right")) +
@@ -433,22 +444,20 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
     scale_fill_gradientn(
[…]

### 2023-08-14 paper/scripts/020_methods_data.R
Add table contents for table 1 of supp figs

@@ -1,0 +1,290 @@
+#### Tables for Data section of Methods (and Sup. Figures) ####
+
+#### Initial ####
+
+### Libs ###
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(purrr)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+# source("Shiny/src/functions.R") # plotting functions
+source("paper_poster_plots/paper/scripts/00_funs.R") # shared functions
+
+### Metadata ###
+
+orderly_root <- getwd()
+
+# for tabulating surveys: 
+rm_missing_type <- FALSE # remove circumcisions with missing type?
+start_year <- 2000 # minimum survey year
+cens_age <- 59 # maximum circumcision age
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+### Load Data ###
+
+# pull most recent results for age groups
+archives <- orderly::orderly_list_archive()
+
+# pull shapefiles
+areas <- load_archive(
+  "00a2_areas_join", 
+  orderly_root, 
+  "areas.geojson", 
+  archives = archives, 
+  load_fun = read_sf
+)
+
+# pull surveys
+survey_circumcision_orig <- survey_circumcision <- load_archive(
+  "00b3_survey_join", 
+  orderly_root, 
+  "survey_circumcision.csv.gz", 
+  query = "latest(parameter:is_paper == TRUE)"
+)
+
+# survey_circumcision <- survey_circumcision %>% 
+  # filter(!iso3 %in% no_mod_iso3)
+
+# pull agegroup populations
+populations <- load_archive(
+  "00c4_pops_aggregate", 
+  orderly_root, 
+  "population_agegroup_aggr.csv.gz", 
+  archives = archives
+)
+
+# last surveys
+# TODO: Update these
+last_surveys <- readr::read_csv("global/most_recent_surveys.csv")
+
+# Prepare circ data, normalise survey weights and apply Kish coefficients.
+survey_circumcision <- prepare_survey_data(
+  areas               = areas,
+  survey_circumcision = select(survey_circumcision, -matches("area_level")),
+  area_lev            = threemc::datapack_psnu_area_level,
+  start_year          = start_year,
+  cens_year           = TRUE,
+  cens_age            = cens_age,
[…]

### 2023-08-14 paper/supp_figs.tex

@@
 \usepackage{tikz}
+\usepackage{pifont}
 \usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
@@
 \addbibresource{library.bib}
+
+\newcommand{\xmark}{\ding{55}}
 
@@
 
-The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Demorcratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa".
-We excluded 4 countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana.
-These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on circumcision.
+The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa".
+We excluded 4 SSA countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana.
+These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
 
@@
 Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
-\textbf{[Expand on reasons for exclusions]} [Link in your survey figure] Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
+\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} 
+Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
+The surveys which were excluded on the basis of this requirement were the Botswana 2008 BAIS and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys.
+For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.
+Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
+See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.
 
@@
     \centering
-    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
-    \caption{Household surveys detailing circumcision patterns in SSA.
+    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.png}
+    \caption{Household surveys detailing circumcision patterns in sub-Saharan Africa.
 The colour and size of points are determined by the provider and sample size of each respective survey.
@@
       \endfoot
+
       %%%%%%%%%%%%%%%%%%%%%%
@@
 & 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Benin}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Botswana}} \\ 
+& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
+& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Burkina Faso}} \\ 
+& 2003 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
 \multicolumn{2}{l}{\textbf{Burundi}} \\ 
@@
 & 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Cameroon}} \\ 
+& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Central African Republic}} \\ 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Chad}} \\ 
+& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Congo - Kinshasa}} \\ 
+& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Côte d’Ivoire}} \\ 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Eswatini}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
+& 2010 (MICS) & \checkmark & \checkmark & \xmark & \xmark \\ 
+& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Ethiopia}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Gabon}} \\ 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Gambia}} \\ 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Ghana}} \\ 
+& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Guinea}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Guinea-Bissau}} \\ 
+& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Kenya}} \\ 
+& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Lesotho}} \\ 
+& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2009 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
+& 2014 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Liberia}} \\ 
+& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Malawi}} \\ 
+& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2013 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Mali}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Mozambique}} \\ 
+& 2003 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2009 (AIS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Namibia}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Niger}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Nigeria}} \\ 
+& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Repulic of the Congo}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2009 (AIS) & \checkmark & \xmark & \checkmark & \xmark \\ 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Rwanda}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2008 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Senegal}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Sierra Leone}} \\ 
+& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
 \multicolumn{2}{l}{\textbf{South Africa}} \\ 
-      & 2002 (HSRC) &  \\
-      & 2008 (HSRC) &  \\
-      & 2012 (HSRC) &  \\
-      & 2016 (DHS)  &  \\
-      & 2017 (HSRC) &  
+& 2002 (HSRC) & \checkmark & \checkmark & \xmark & \checkmark \\ 
+& 2008 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2012 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Tanzania}} \\ 
+& 2003 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2007 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2012 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Togo}} \\ 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Uganda}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2011 (AIS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Zambia}} \\ 
+& 2007 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+\multicolumn{2}{l}{\textbf{Zimbabwe}} \\ 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt]
+
 \end{longtable}
 }
-% \end{landscape}
 

### 2023-08-14 paper/supp_figs.tex
Caption survey Q table

@@
       \\[-5pt]\hline
-      \caption{Table caption}
+      \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country.
+Surveys which did not include a "Circumcision Status" and "Age at Circumcision" question could not be used, while circumcision type could not be inferred from surveys which did not have a "Who performed the circumcision" and/or "Where was the circumcision performed" question.}
       \endfoot

### 2023-08-14 paper/scripts/032_results.R
Update map plot with better text size

@@ -417,7 +417,7 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       na.value = "grey",
       breaks = seq(0, 1, by = 0.1),
       limits = c(0, 1),
-      label = scales::label_percent(accuracy = 1), 
+      label = scales::label_percent(accuracy = 1, trim = FALSE), 
       guide = guide_colourbar(
         direction = "horizontal",
         label = TRUE,
@@ -426,12 +426,11 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
         frame.colour = "black",
         ticks = TRUE,
         barheight = 1,
-        # barwidth = 20,
-        barwidth = 22,
+        # barwidth = 17, # may want this?
+        barwidth = 18,
         title.position = "bottom"
       )
     ) +
-    # guides(fill = guide_colourbar(title.position = "right")) +
     ggnewscale::new_scale_fill() +
     # colour percentage change differently
     geom_sf(
@@ -446,7 +445,7 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       na.value = "grey",
       breaks = seq(-0.2, 0.5, by = 0.1),
       limits = c(-0.2, 0.5),
-      label = scales::label_percent(accuracy = 1),
+      label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
       guide = guide_colourbar(
         direction = "horizontal", 
         label = TRUE, 
@@ -455,20 +454,16 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
         frame.colour = "black", 
         ticks = TRUE, 
         barheight = 1,
-        # barwidth = 20,
-        barwidth = 15,
+        # barwidth = 10,
+        barwidth = 10.5,
         title.position = "bottom"
       )
     ) +
-    # guides(fill = guide_colourbar(title.position = "right")) +
     facet_grid(type ~ year) + 
-    theme_minimal() +
+    theme_minimal(base_size = 9) +
     theme(
       axis.text       = element_blank(),
       axis.ticks      = element_blank(),
-      strip.text      = element_text(size = 20), #  face = "bold"),
-      legend.text     = element_text(size = 12),
[…]

### 2023-08-15 paper/scripts/032_results.R
Update map plot

@@ -244,15 +244,6 @@ iso_df <- iso_df %>%
 #### Figure 2: Map of MC Coverage across SSA 20-2020 15-29 year olds ####
 
 ## Map Plot ##
-main_title <- paste0(
-  # "MC Coverage, ",
-  "Circumcision Coverage ", 
-  paste0(spec_years[1], "-", spec_years[2]),
-  ", age ",
-  spec_age_group,
-  " years"
-)
-# Plot all types & with facets 
 
 # additions: 
 # - Have single faceted R plot, with tag in corner (done, no tags though ..)
@@ -263,7 +254,6 @@ main_title <- paste0(
 
 # Qs: 
 # - How do we want colour bars displayed? Like Tristan, on the side of his plot? 
-# 
 
 country_area_level = 0
 results_area_level = NULL
@@ -272,12 +262,14 @@ spec_main_title    = main_title
 
 main_title <- paste0(
   # "MC Coverage, ",
-  "Male circumcision coverage, ",
+  "Circumcision coverage ", 
   paste0(spec_years[1], "-", spec_years[2]),
-  ", age ",
+  ", ",
   spec_age_group,
-  " years"
+  " year olds"
 )
+# Plot all types & with facets 
+
 
 results_agegroup1 <- results_agegroup
 areas1 <- areas
@@ -494,22 +486,28 @@ p2final <- map_plot(tmp, areas_plot, colourPalette2, colourPalette) +
 #   units = "in"
 # )
 
-# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
-pdf(
-# png(
-  "paper_poster_plots/paper/plots/02_map_plot_facet.pdf", 
-  # "paper_poster_plots/paper/plots/02_map_plot_facet2.png", 
-  width = 6.3, 
-  height = 6.5
-)
-p2final + 
+p2final <- p2final + 
   theme(
-    plot.title    = element_text(size = rel(1.8), hjust = 0.5), 
+    # plot.title    = element_text(size = rel(1.8), hjust = 0.5), 
+    plot.title    = element_text(size = rel(1.6), hjust = 0.5), 
     strip.text    = element_text(size = rel(1.5)), 
     # probably too small, but so annoying to fix!!
-    legend.text   = element_text(size = rel(0.8))
+    # legend.text   = element_text(size = rel(0.8))
[…]

### 2023-08-15 paper/scripts/032_results.R
Update change plot with NEJM colours, sensible text sizes

@@ -981,44 +981,61 @@ p5 <- tmp_long %>%
     labels = country_pos_df$country,
     expand = expansion(add = 0.6)
   ) +
-  scale_y_continuous(
-    label = scales::label_percent(),
-    limits = c(0, 1),
-    breaks = seq(0, 1, by = 0.2)
-  ) +
   labs(
     x        = "Country",
     y        = "Change in Coverage (%)",
     colour   = "Year",
-    title    = "Absolute change in male circumcision coverage between 2000 and 2020 (15-29 year olds)",
+    # title    = "Absolute change in male circumcision coverage between 2000 and 2020 (15-29 year olds)",
+    title    = "Change in male circumcision coverage, 2000 - 2020, 15-29 year olds",
     subtitle = ""
   ) +
   facet_wrap(type ~ .) + # , scales = "free") +
-  theme_minimal() +
+  theme_bw(base_size = 8) +
   # Altering plot text size
   theme(
-    axis.text.x      = element_text(size = 14),
-    axis.text.y      = element_text(size = 16),
-    strip.text       = element_text(size = 16),
-    legend.text      = element_text(size = 18),
-    legend.title     = element_text(size = 18),
-    axis.title       = element_text(size = 18),
-    plot.title       = element_text(size = 22, hjust = 0.5),
     legend.position  = "bottom",
     strip.background = element_rect(fill = NA, colour = "white"),
-    plot.tag         = element_text(size = 16, face = "bold"),
-    panel.background = element_rect(fill = NA, color = "black")
+    panel.background = element_rect(fill = NA, color = "black"),
+    panel.border = element_blank()    
   ) +
-  coord_flip(clip = "off")
+  coord_flip(clip = "off", expand = TRUE)
 
-p5
+# dev.new(width = 6.3, height = 6, noRStudioGD = TRUE)
+p5 <- p5 + 
+  # New England Journal of Medicine colourscheme
+  ggsci::scale_colour_nejm() +
+  # scale_x_continuous(expand = c(0, 1), limits = c(0, 1)) + 
+  scale_y_continuous(
+    expand = c(0, 0), 
+    limits = c(0, 1), 
+    label = scales::label_percent(),
+    breaks = seq(0, 1, by = 0.2), 
+    n.breaks = 5, 
+    minor_breaks = NULL
+  ) + 
+  theme(
+    plot.title          = element_text(
[…]

### 2023-08-15 paper/scripts/032_results.R
Update change plot with annotations for VMMC and non-VMMC

@@ -927,9 +927,10 @@ tmp <- tmp %>%
 annotate_df <- data.frame(
   country_idx = c(
     c(length(plot_order) + 1),
-    c(length(plot_order) - (country_positions1 + 4))
+    c(length(plot_order) - (country_positions1 + 3.5))
   ),
-  value = c(-0.12, -0.15), 
+  # value = c(-0.12, -0.15), 
+  value = c(0.22, 0.12), 
   type  = factor(c("MC", "MC"), levels = c("MC", "MMC", "TMC")),
   label = c("Non-VMMC", "VMMC")
 )
@@ -970,7 +971,7 @@ p5 <- tmp_long %>%
     data = annotate_df, 
     # aes(label = label),
     aes(x = country_idx,  y = value, label = label), 
-    size = 5, 
+    size = 3, 
     fontface = "bold"
   ) +
   # label countries, with space for vline splitting VMMC & non-VMMC
@@ -1000,7 +1001,6 @@ p5 <- tmp_long %>%
   ) +
   coord_flip(clip = "off", expand = TRUE)
 
-# dev.new(width = 6.3, height = 6, noRStudioGD = TRUE)
 p5 <- p5 + 
   # New England Journal of Medicine colourscheme
   ggsci::scale_colour_nejm() +
@@ -1028,6 +1028,9 @@ p5 <- p5 +
     panel.spacing       = unit(0.65, units = "cm"), 
     plot.margin         = unit(c(0, 0.5, 0, 0), "cm") 
   )
+
+# dev.new(width = 6.3, height = 6, noRStudioGD = TRUE)
+# p5
 # dev.off()
 
 saveRDS(p5, "paper_poster_plots/paper/plots/05_change_00_20.RDS")

### 2023-08-15 paper/paper.tex

@@
 
-TODO: Finish this write up!
-TODO: Add results! Also add ternary plot
+\todo{Finish this write up!}
+\todo{Add results! Also add ternary plot}
 
@@
     \centering
-    \includegraphics[width=.9\linewidth]
-    {plots/02_map_plot_facet.png}
+    % \includegraphics[width=.9\linewidth]
+    \includegraphics[width=1\linewidth]
+    % {plots/02_map_plot_facet.png}
+    {paper/plots/02_map_plot_facet.png}
     \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years.
@@
 \end{figure}
+\todo{
+  - Use divergent colour palette for "% change", and different one for coverage
+- Need to position colour bars under corresponding facets, rather than to the side
+- Grey out countries with no type (done)
+- reevaluate text size
+}
 
@@
     {plots/05_change_00_20.png}
-    \caption{\emph{Absolute difference, with associated errors, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region.
+    % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region.
 Plots are split by circumcision type.
@@
 }}
+    \caption{\emph{Absolute change in circumcision coverage between 2000 and 2020 for 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type.
+The countries below the horizontal black line are VMMC priority countries}}
 \end{figure}

### 2023-08-17 paper/scripts/032_results.R
Update map plot so colour bar text doesn't touch

@@ -67,7 +67,7 @@ target_iso3 <- c(
 # Colour palette for map plot
 colourPalette <- rev(colorRampPalette(
   c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
-    "#e6f598", "#abdda4", "#66c2a5", "#3288bd", 
+    "#e6f598", "#abdda4", "#66c2a5", "#3288bd", "#13699e",
     "#5e4fa2")
 )(100))
 # change mint green as it's awful looking in % Change facets of map plot
@@ -255,11 +255,6 @@ iso_df <- iso_df %>%
 # Qs: 
 # - How do we want colour bars displayed? Like Tristan, on the side of his plot? 
 
-country_area_level = 0
-results_area_level = NULL
-spec_model <- "No program data"
-spec_main_title    = main_title
-
 main_title <- paste0(
   # "MC Coverage, ",
   "Circumcision coverage ", 
@@ -268,8 +263,11 @@ main_title <- paste0(
   spec_age_group,
   " year olds"
 )
-# Plot all types & with facets 
 
+country_area_level = 0
+results_area_level = NULL
+spec_model <- "No program data"
+spec_main_title    = main_title
 
 results_agegroup1 <- results_agegroup
 areas1 <- areas
@@ -382,6 +380,8 @@ rm(results_agegroup1, areas1); gc()
    
 map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
 
+  # spec_results$mean <- 100 * spec_results$mean
+  
   spec_results$type <- factor(
     spec_results$type, 
     levels = c("Total", "Medical", "Traditional")
@@ -437,7 +437,8 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       na.value = "grey",
       breaks = seq(-0.2, 0.5, by = 0.1),
       limits = c(-0.2, 0.5),
-      label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
+      # label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
+      label = scales::label_percent(accuracy = 1, trim = TRUE, prefix = "\t"),
       guide = guide_colourbar(
         direction = "horizontal", 
         label = TRUE, 
@@ -454,6 +455,11 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
[…]

### 2023-08-17 paper/scripts/032_results.R
Update change plot to use red for 2020 (to match subnat plot)

@@ -912,8 +912,8 @@ annotate_df <- data.frame(
     c(length(plot_order) + 1),
     c(length(plot_order) - (country_positions1 + 3.5))
   ),
-  # value = c(-0.12, -0.15), 
-  value = c(0.22, 0.12), 
+  # value = c(0.22, 0.12), 
+  value = c(0.24, 0.14), 
   type  = factor(c("MC", "MC"), levels = c("MC", "MMC", "TMC")),
   label = c("Non-VMMC", "VMMC")
 )
@@ -940,14 +940,8 @@ p5 <- tmp_long %>%
       # colour = factor(year)
     ), 
     arrow = arrow(length = unit(0.3, "cm")), 
-    size = 1
+    size = 0.6
   ) +
-  # horizontal line at 0% 
-  # geom_hline(
-  #   yintercept = 0,
-  #   size = 0.8,
-  #   colour = "grey50"
-  # ) +
   # add vline for VMMC - non-VMMC split
   geom_vline(xintercept = country_positions1) +
   geom_text(
@@ -965,6 +959,14 @@ p5 <- tmp_long %>%
     labels = country_pos_df$country,
     expand = expansion(add = 0.6)
   ) +
+  scale_y_continuous(
+    expand = c(0, 0), 
+    limits = c(0, 1), 
+    label = scales::label_percent(),
+    breaks = seq(0, 1, by = 0.2), 
+    n.breaks = 5 # , 
+    # minor_breaks = NULL
+  ) + 
   labs(
     x        = "Country",
     y        = "Change in Coverage (%)",
@@ -975,31 +977,11 @@ p5 <- tmp_long %>%
   ) +
   facet_wrap(type ~ .) + # , scales = "free") +
   theme_bw(base_size = 8) +
+  # use NEJM colours (want 2020 in red though)
+  scale_colour_manual(values = c("#0072B5", "#BC3C29")) + 
+  # pal_nejm("default")(2)[2:1] + 
   # Altering plot text size
   theme(
-    legend.position  = "bottom",
-    strip.background = element_rect(fill = NA, colour = "white"),
-    panel.background = element_rect(fill = NA, color = "black"),
-    panel.border = element_blank()    
-  ) +
-  coord_flip(clip = "off", expand = TRUE)
-
-p5 <- p5 + 
-  # New England Journal of Medicine colourscheme
-  ggsci::scale_colour_nejm() +
-  # scale_x_continuous(expand = c(0, 1), limits = c(0, 1)) + 
-  scale_y_continuous(
[…]

### 2023-08-17 paper/supp_figs.tex

@@
 
+% bibliography
 \renewcommand\Affilfont{\itshape\footnotesize}
@@
 We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
-These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \textbf{[Citations]}.
+These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs} \cite{ais} \cite{phia} \cite{hsrc2002} \cite{hsrc2008} \cite{hsrc2012} \cite{hsrc2017} \todo{include MICS reference}.
 Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
-\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} 
+\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} \todo{done, what do you mean by "link in survey figure?"}
 Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
-The surveys which were excluded on the basis of this requirement were the Botswana 2008 BAIS and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys.
+The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008} \cite{bais2013}.
 For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.
 Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
+See figure 1 for a visual representation of the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information. 
 See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.
@@
     \centering
-    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.png}
+    \includegraphics[width=.9\linewidth]{paper/plots/01_survey_table.png}
     \caption{Household surveys detailing circumcision patterns in sub-Saharan Africa.
@@
 
-Circumcisions were classed as a medical male circumcision (MMC) and traditional male circumcision (TMC) sing responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
-Respondents that did not have any information related to the type of circumcision were classified as having an “unknown” male circumcision (MC).
+Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
+Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type.
 
@@
 \textbf{[Participation rates table]}
+\todo{Get Matt to make dummy table for me based on this info for 2-3 countries, then I can fill in}
 
@@
 [Add in information about the boundaries] 
+\todo{Section for Jeff}
 
@@
 Distributed (?) to single-year of age according to ??? 
+\todo{Section for Jeff}
 
@@
 
+\todo{Fix links to HSRC surveys, no longer working!}
+\todo{Get reference for MICS surveys!}
+\todo{May have to reference every survey, as in Cork paper!}
+
+\printbibliography
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{appendix}

### 2023-08-17 paper/scripts/032_results.R
Fix x-axis, text size and colour in subnational plot

@@ -567,6 +567,8 @@ plt_data <- plt_data %>%
   ) %>% 
   left_join(country_pos_df)
 
+# 
+set.seed(123)
 p3 <- plt_data %>% 
   # take max area level for each country
   group_by(iso3) %>% 
@@ -574,8 +576,6 @@ p3 <- plt_data %>%
   ggplot(
     aes(
       # countries on the x-axis, in specified order
-      # x = forcats::fct_rev(forcats::fct_relevel(iso3, levels = plot_order)), 
-      # x = factor(iso3, levels = rev(plot_order)),
       x = country_idx, 
       # median MC Coverage on the y-axis
       y = median
@@ -583,20 +583,22 @@ p3 <- plt_data %>%
   ) +
   # add points coloured by region with weighted populations determining size
   geom_jitter(
-    # aes(color = region, size = population), 
     aes(size = population), 
-    colour = wesanderson::wes_palette("Zissou1")[1],
+    colour = "#BC3C29", # red, to match coverage change plot below
     shape = 20, 
-    width = 0.1, 
+    width = 0.1, # width of jitter, not points!
     alpha = 0.5
+  ) +
+  scale_size_continuous(
+    breaks = c(1, 10, 20), 
+    # limits = c(10, 50), 
+    # breaks = c(100, 200, 300), 
+    labels = paste0(c(1, 10, 20), "x")
   ) +
   # add median national level to plot as white dots
   geom_point(
     data = filter(plt_data, area_level == 0),
     size = 5, 
-    # fill = "white", 
-    # fill = "#DCDCDC",
-    # fill = "#F5F5F5",
     fill = "#F1F1F1",
     col = "black", 
     alpha = 1, 
@@ -615,38 +617,21 @@ p3 <- plt_data %>%
   # annotate plot with regional labels
   annotate(
     geom = "text",
-    # x = zoo::rollmean(c(country_positions1, 0), 2),
-    x = c(length(plot_order) + 1), # , length(plot_order) - (country_positions1 + 4)),
-    y = 0.04,
-    # label = c("non-VMMC", "VMMC"),
+    x = c(length(plot_order) + 1),
+    y = 0.12,
     label = "non-VMMC",
-    # angle = 270,
     fontface = "bold",
-    size = 5
+    size = 4.5
   ) +
   annotate(
     geom = "text",
-    # x = zoo::rollmean(c(country_positions1, 0), 2),
[…]

### 2023-08-17 paper/scripts/032_results.R
Try make text not touch in map plot

@@ -379,6 +379,15 @@ spec_areas <- areas_plot
 rm(results_agegroup1, areas1); gc()
    
 map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
+  
+  n <- 0
+  hor_push <- function(x) {
+    print(x)
+    n <<- n + 1
+    if (count %% 2 == 1) return(0) else return(0.5)
+  }
+  
+  rm(n)
 
   # spec_results$mean <- 100 * spec_results$mean
   
@@ -435,10 +444,9 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
     scale_fill_gradientn(
       colours = colourPalette2,
       na.value = "grey",
-      breaks = seq(-0.2, 0.5, by = 0.1),
+      breaks = seq(-0.2, 0.5, by = 0.1), 
       limits = c(-0.2, 0.5),
-      # label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
-      label = scales::label_percent(accuracy = 1, trim = TRUE, prefix = "\t"),
+      label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
       guide = guide_colourbar(
         direction = "horizontal", 
         label = TRUE, 
@@ -459,7 +467,8 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       strip.text    = element_text(size = rel(1.5)), 
       # probably too small, but so annoying to fix!!
       # legend.text   = element_text(size = rel(0.75)) # 0.70 too small
-      legend.text   = element_text(size = rel(0.72), vjust = 0.5),
+      # legend.text   = element_text(size = rel(0.72), hjust = 0.1),
+      legend.text   = element_text(size = rel(0.71)),
       axis.text       = element_blank(),
       axis.ticks      = element_blank(),
       legend.position = "bottom",
@@ -472,10 +481,10 @@ p2final <- map_plot(tmp, areas_plot, colourPalette2, colourPalette) +
   ggtitle(main_title)
 
 # save object for org-mode paper draft
-saveRDS(
-  p2final,
-  "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
-)
+# saveRDS(
+#   p2final,
+#   "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
+# )
 
 # dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
 # p2final

### 2023-08-17 paper/supp_figs.tex
Updates from Overleaf

@@
 {\linespread{1}
-\small
-\begin{longtable}[c]{ll ccc ccc ccc ccc}
+  \footnotesize 
+\begin{longtable}[c]{ll ccc c}
       %%%%%%%%%%%%%%%%%%%%
@@
       \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
-      \cmidrule(lr){5-7}
+      \cmidrule(lr){5-6}
        & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
@@
       \hline
-      \vspace{-5pt}
+      \vspace{-3pt}
       \endhead
@@
       %%%%%%%%%%%%%%%%%%%%
-      \\[-5pt]\hline
+      \\[-3pt] \hline
       \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country.
@@
       \endfoot
-
       %%%%%%%%%%%%%%%%%%%%%%
@@
       \multicolumn{2}{l}{\textbf{Angola}} \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Benin}} \\ 
@@
 & 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Botswana}} \\ 
 & 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
-& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[5pt] 
+& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Burkina Faso}} \\ 
 & 2003 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Burundi}} \\ 
 & 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Cameroon}} \\ 
@@
 & 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Central African Republic}} \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Chad}} \\ 
@@
 & 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Congo - Kinshasa}} \\ 
-& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Côte d’Ivoire}} \\ 
 & 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Eswatini}} \\ 
@@
 & 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Ethiopia}} \\ 
@@
 & 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Gabon}} \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Gambia}} \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Ghana}} \\ 
@@
 & 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Guinea}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Guinea-Bissau}} \\ 
 & 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Kenya}} \\ 
@@
 & 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Lesotho}} \\ 
@@
 & 2014 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Liberia}} \\ 
 & 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Malawi}} \\ 
@@
 & 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Mali}} \\ 
@@
 & 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Mozambique}} \\ 
@@
 & 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Namibia}} \\ 
@@
 & 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Niger}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Nigeria}} \\ 
@@
 & 2016 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Repulic of the Congo}} \\ 
@@
 & 2009 (AIS) & \checkmark & \xmark & \checkmark & \xmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Rwanda}} \\ 
@@
 & 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Senegal}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 
+& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Sierra Leone}} \\ 
@@
 & 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{South Africa}} \\ 
@@
 & 2016 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Tanzania}} \\ 
@@
 & 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Togo}} \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Uganda}} \\ 
@@
 & 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Zambia}} \\ 
@@
 & 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 
+& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
 \multicolumn{2}{l}{\textbf{Zimbabwe}} \\ 
@@
 & 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt]
-
+& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark 
 \end{longtable}
@@
 {\linespread{1}
-\small
 \begin{table}[htbp]
 	\centering
+    \footnotesize
 	\caption{Criteria used to classify circumcisions from the survey data as MMC or TMC.}

### 2023-08-18 paper/scripts/032_results.R
Have negative values in blue in map plot

@@ -64,26 +64,29 @@ target_iso3 <- c(
 )
 
 
-# Colour palette for map plot
-colourPalette <- rev(colorRampPalette(
-  c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
-    "#e6f598", "#abdda4", "#66c2a5", "#3288bd", "#13699e",
-    "#5e4fa2")
-)(100))
-# change mint green as it's awful looking in % Change facets of map plot
+# Colour palette for "% change" facets in map plot
 # colourPalette <- rev(colorRampPalette(
 #   c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
-#     "#e6f598", 
-#     # "#66c2a5", 
-#     "#54bb9a",
-#     "#46af8e",  
-#     "#3288bd", "#5e4fa2")
+#     "#e6f598", "#abdda4", "#66c2a5", "#3288bd", "#13699e",
+#     "#5e4fa2")
 # )(100))
 
+# Breaks are between -0.2 and -0.5 => 7 breaks overall
+# Want everything negative to be blue (so 2 / 7 of colours)
+# Change to 14 colours in scale, with first 4 as blue, then each "break" 
+# constitutes one colour, and negative values will be in blue
+colourPalette <- rev(colorRampPalette(
+  c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
+    "#e6f598", "#abdda4", "#8CD1A4", "#66C2A4", "#3D94B7", "#2C82B7", "#13699e",
+    "#5e4fa2")
+)(140))
 
-# colourPalette for % changeR
-# colourPalette2 <- rev(heat.colors(100))
-# colourPalette2 <- viridis::viridis(100)
+# change region changing from blue to grean to only blue
+colourPalette[30:40] <- colourPalette[30]
+# change greenish-blue to be more green
+# colourPalette[41:45] <- colourPalette[45]
+
+# Colour Palette for years in map plot
 colourPalette2 <- viridis::plasma(100)
 
 
@@ -380,17 +383,6 @@ rm(results_agegroup1, areas1); gc()
    
 map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
   
-  n <- 0
-  hor_push <- function(x) {
-    print(x)
-    n <<- n + 1
-    if (count %% 2 == 1) return(0) else return(0.5)
-  }
-  
[…]

### 2023-08-18 paper/scripts/032_results.R
Have negative values in blue in map plot

@@ -489,9 +489,9 @@ p2final <- map_plot(tmp, areas_plot, colourPalette2, colourPalette) +
 #   "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
 # )
 
-dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
-p2final
-dev.off()
+# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
+# p2final
+# dev.off()
 
 # save plots
 ggsave(

### 2023-08-18 paper/supp_figs.tex
Updates from Overleaf

@@
 We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
-These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs} \cite{ais} \cite{phia} \cite{hsrc2002} \cite{hsrc2008} \cite{hsrc2012} \cite{hsrc2017} \todo{include MICS reference}.
+These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs, ais, phia, hsrc2002, hsrc2008, hsrc2012, hsrc2017} \todo{include MICS reference}.
 Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
@@
 Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
-The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008} \cite{bais2013}.
+The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008, bais2013}.
 For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.

### 2023-08-18 paper/scripts/032_results.R
Clean up geofaceted age plot

@@ -741,11 +741,14 @@ ssa_grid <- geofacet::africa_countries_grid1 %>%
       name == "Democratic Republic of the Congo" ~ "DR Congo",
       name == "Republic of the Congo"            ~ "Congo",
       name == "Equatorial Guinea"                ~ "Eq. Guinea",
-      name == "Central African Republic"          ~ "Cent. Af. Rep.",
+      name == "Guinea-Bissau"                    ~ "Gin. Bissau",
+      name == "Central African Republic"         ~ "Cent. Af. Rep.",
       TRUE                                       ~ name
     )
   ) %>%
-  filter(name %in% c(ssa_countries, "Eq. Guinea", "Cent. Af. Rep."))
+  filter(
+    name %in% c(ssa_countries, "Gin. Bissau", "Eq. Guinea", "Cent. Af. Rep.")
+  )
 
 # remove missing rows and columns (only looking at SSA, not all of Africa)
 min_row <- min(ssa_grid$row)
@@ -762,41 +765,34 @@ if (min_col > 1) {
 p4_geo <- p4 +
   # geofacet based on SSA shape
   geofacet::facet_geo(~ area_name, grid = ssa_grid) +
-  # make x-axis text smaller to fit all of map
-  # ggtitle(
-  #   paste0("MMC & TMC Coverage, 2010-2020, ", spec_age_group, " year olds")
-  # ) +
-  ggtitle(paste0("MMC & TMC Coverage vs Age, 2020")) +
+  ggtitle(paste0("Medical & traditional male circumcision by age, 2020")) +
+  # set theme and base size for text
+  theme_minimal(base_size = 9) + 
+  # reduce x-axis ticks, too crowded
+  scale_x_continuous(breaks = seq(0, 60, by = 20)) + 
+  # remove x-axis
+  labs(y = "") +  
   theme(
-    strip.text = element_text(size = 20, face = "bold"),
-    legend.position = "none", # remove legend, add with crop
-    plot.title = element_text(hjust = 0.5, face = "bold", family = "Arial"),
-    axis.text.x = element_text(size = 14, face = "bold", angle = 0, hjust = 1, vjust = 1)
-  ) +
-  labs(y = "") # remove x-axis
-  # scale_x_continuous(
-  #   # breaks = seq(spec_years[1], last(spec_years), by = 2),
[…]

### 2023-08-18 paper/scripts/032_results.R
Add white background to plots with

@@ -421,7 +421,8 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
         barheight = 1,
         # barwidth = 17, # may want this?
         barwidth = 18,
-        title.position = "bottom"
+        title.position = "bottom", 
+        plot.background = element_rect(fill = "white", colour = "white")
       )
     ) +
     ggnewscale::new_scale_fill() +
@@ -475,7 +476,8 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
       axis.ticks      = element_blank(),
       legend.position = "bottom",
       panel.grid      = element_blank(),
-      panel.spacing   = unit(0.01, "lines") # make plot as "dense" as possible
+      panel.spacing   = unit(0.01, "lines"), # make plot as "dense" as possible
+      plot.background = element_rect(fill = "white", colour = "white")
     )
 }
 
@@ -700,7 +702,7 @@ p3$plot_order <- plot_order
 # p3
 # dev.off()
 
-saveRDS(p3, "paper_poster_plots/paper/plots/03_subnat_plot.png")
+# saveRDS(p3, "paper_poster_plots/paper/plots/03_subnat_plot.RDS")
 ggplot2::ggsave(
   "paper_poster_plots/paper/plots/03_subnat_plot.png", 
   p3, 

### 2023-08-22 paper/scripts/032_results.R
Use blue-white-red colour scheme for map plot change

@@ -75,19 +75,24 @@ target_iso3 <- c(
 # Want everything negative to be blue (so 2 / 7 of colours)
 # Change to 14 colours in scale, with first 4 as blue, then each "break" 
 # constitutes one colour, and negative values will be in blue
-colourPalette <- rev(colorRampPalette(
+# colourPalette <- rev(colorRampPalette(
+colourPalette2 <- rev(colorRampPalette(
   c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
     "#e6f598", "#abdda4", "#8CD1A4", "#66C2A4", "#3D94B7", "#2C82B7", "#13699e",
     "#5e4fa2")
-)(140))
+)(100))
 
 # change region changing from blue to grean to only blue
-colourPalette[30:40] <- colourPalette[30]
+# colourPalette[30:40] <- colourPalette[30]
 # change greenish-blue to be more green
 # colourPalette[41:45] <- colourPalette[45]
 
 # Colour Palette for years in map plot
-colourPalette2 <- viridis::plasma(100)
+# colourPalette <- viridis::plasma(100)
+colourPalette <- c(
+  grDevices::colorRampPalette(c("blue","white"))(40), 
+  grDevices::colorRampPalette(c("white", "red"))(100)
+)
 
 
 #### Load Data ####

### 2023-08-22 paper/supp_figs.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item Aggregated areas
     \item Model calibration
@@
 Following a similar approach to \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type.
-
-We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
+We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).
 
 In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
-In countries that did not have a survey that contained information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type.
-Therefore, we consider a used survey data to estimates the probabilities and coverage of circumcision of any or (unknown) type (MC).
+Some countries did not have any surveys that collected information on the type of circumcision (see above), so we were unable to conduct an analysis of the probabilities of circumcision by type.
+For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.
 
@@
 
-We used survey data to model the probabilities of receiving a TMC, MMC or MC for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
+In countries where suitable survey information was collected on circumcision type, we used survey data to model the probabilities of receiving a TMC, MMC or MC for individuals residing in district $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
 
@@
 
-\noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in region $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
+\noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in district $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
 \begin{equation} 
@@
 \end{equation}
-A key assumption of \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa but an assumption of a constant probability of TMC might not be feasible everywhere.
-For example, in some countries the level and practices of TMC has changed through time due to demographic shifts.
+A key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere.
+For example, in some countries the level and practices of TMC have changed through time due to demographic shifts.
 There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
@@
 varying over time).
+
 The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function, 
@@
 \end{equation*}
-where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC across regions.
+where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a district random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-district interaction term to allow different age patterns of TMC across districts.
 The {\it time-variant} probability of TMC was also modelled using a piece-wise logit-linear function,
@@
 \end{equation*}
-where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, $\theta_i$ is a temporal random effect,  $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC  across regions and $\hat{\delta}_{at}$ is an age-time interaction term to allow for different age patterns of TMCs over time.
-We did not include a space-time interaction into due to computational reasons.
+where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a district random effect, $\hat{\phi}_a$ is an age random effect, $\theta_i$ is a temporal random effect,  $\hat{\gamma}_{ia}$ is an age-district interaction term to allow different age patterns of TMC across districts and $\hat{\delta}_{at}$ is an age-time interaction term to allow for different age patterns of TMCs over time.
+We did not include a district-time interaction into due to computational constraints.
 
@@
 
-\noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
+\noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in district $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
 \begin{equation*}
@@
 To ensure $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the TMC prior to MMC in each time step.
-Therefore, we condition on this and practically model the probability an individual in region $i$ received an MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
+Therefore, we condition on this and practically model the probability an individual in district $i$ received an MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
 \begin{equation*}
@@
 
-The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed  since 2008 in countries that have programmes to scale-up MMC for HIV prevention.
+The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention.
 VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
@@
 \cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
-This ensured that any increase in MMC for those aged 10 and over did not affect the probability of MMC in those under 10 in South Africa.
+This ensured that any increase in MMC for those aged 10 and over did not bias the probability of MMC in those under 10 in South Africa.
 However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage.
-Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) [Need a name] and (ii) [Need a name].
-
-We modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:
-
+Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) no cut-off and (ii) paediatric cut off.
+
+We modelled the probability of MMC {\it with no cut-off} using a piece-wise logit-linear function, 
 \begin{equation*}
@@
 \end{equation*}
-where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MMCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions.
-
-Therefore, we modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:
+where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MMCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MMCs over time across districts.
+We also modelled the probability of MMC {\it with a paediatric cut-off} using a piece-wise logit-linear function,
 \begin{equation*}
@@
 \end{equation*}
-where $\bar{\alpha}$ and $\alpha$ are intercepts, $\bar{\psi}_i$ and $\psi_i$ are regional random effects, $\theta_i$ are temporal random effects, $\bar{\phi}_a$ and $\phi_a$ are age random effects, $\bar{\gamma}_{ia}$ and $\gamma_{ia}$ are age-space interaction terms to allow for different age patterns of MMCs between regions, for paediatric circumcision and adolescent and adult circumcision respectively.
-The $\delta_{at}$ is an age-time interaction term to allow for different age patterns of MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions, in adolescent and adult men.
-We assume that the probabilities of MMC among those aged 0--9 were constant over time, (i.e.
+where $\bar{\alpha}$ and $\alpha$ are intercepts, $\bar{\psi}_i$ and $\psi_i$ are district random effects, $\theta_i$ are temporal random effects, $\bar{\phi}_a$ and $\phi_a$ are age random effects, $\bar{\gamma}_{ia}$ and $\gamma_{ia}$ are age-district interaction terms for paediatric circumcision and adolescent and adult circumcision respectively.
+The $\delta_{at}$ is an age-time interaction term to allow for different age patterns of MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across districts in adolescent and adult men.
+We assume that the probability of MMC among those aged 0--9 were constant over time, (i.e.
 $\lambda^{\text{MMC}}_{iat} \equiv \lambda^{\text{MMC}}_{ia}$ when $0\leq a \leq 9$), as paediatric medical circumcision practices are unrelated to VMMC for HIV prevention and are relatively stable.
 
-The choice of whether a country used a {\color{red}\bf[Need a name]} or {\color{red}\bf[Need a name]} probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
+The choice of whether a country used a paediatric cut-off or no cut-off in the probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
 
@@
 
-Some countries did not have a survey that collected information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type.
-In this case, we use survey data to model the probabilities of receiving a MC of any type for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
-
-We defined $\lambda^{\text{MC}}_{iat}$ as the probability an individual in region $i$ received a circumcision  at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
+In countries that did not have a survey that contained information on the type of circumcision, we used survey data to model the probabilities of receiving a MC of any (or unknown) type for individuals residing in district $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.
+
+\noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability that an individual in district $i$ received a circumcision (either a TMC or MMC) at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
 \begin{equation} 
-		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
-	\label{eqn::mc}
+		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
+	\label{eqn::MC}
 \end{equation}
-Here, we model $\lambda^{\text{MC}}_{iat}$ using a piece-wise logit-linear function:
+We modelled the probability of MC using a piece-wise logit-linear function:
 \begin{equation*}
@@
 \end{equation*}
-where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MCs over time across regions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Including aggregated estimates}
-\label{sec::aggregated}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{equation*}
-	\lambda^{\text{MC}}_{Rat} = \frac{\sum_{i\in R}P_{iat}\lambda^{\text{MC}}_{iat}}{\sum_{i\in R}P_{iat}}
-\end{equation*}
+where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MCs over time across districts.
 
@@
 
-The probability $S_{iat}$ of remaining uncircumcised up to age $a$ and time $t$,  typically referred to as the survivor function, is expressed as
-\begin{equation}
+We define the probability of remaining uncircumcised, $S_{iat}$, in district $i$, at age $a$ and time $t$ (often called the survivor function), is estimated using, 
+\begin{equation*}
 	\begin{split}
@@
 	\label{eqn::survfunc}
-\end{equation}
-where $\lambda^{\text{UC}}_{iat}$ is the probability an individual in region $i$ remained uncircumcised at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$, was
+\end{equation*}
+where $\lambda^{\text{UC}}_{iat}$ is the probability an individual in district $i$ remained uncircumcised at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
 \begin{equation*}
@@
 
-The cumulative incidence function (CIF) defines the marginal probability (or coverage/proportion) of individuals who received a TMC, a MMC or a MC of any type by age $a$ and time $t$, accounting for the competing risk of other circumcision types.
+The cumulative incidence function (CIF) defines the marginal probability (or coverage/proportion) of individuals residing in district $i$ who received a TMC, MMC or MC of any (or unknown) type by age $a$ and time $t$, accounting for the competing risk of other circumcision types.
 This was calculated as the sum of incidence of circumcision by type $k$ at each age up to $a$:
@@
 
-In space, we assigned the random effects $\hat{\psi}_i$, $\bar{\psi}_i$, $\psi_i$, $\hat{\gamma}_{ia}$, $\gamma_{ia}$ and $\zeta_{it}$, intrinsic conditional autoregressive (ICAR) priors in space \cite{besag1995conditional}.
-An ICAR model allows us to encodes spatial dependence between neighbouring regions which allows information on the probability and coverage of circumcision in areas where data is sparse or non-existent to be borrowed.
+In space, we assigned the random effects $\hat{\psi}_i$, $\bar{\psi}_i$, $\psi_i$, $\hat{\gamma}_{ia}$, $\gamma_{ia}$ and $\zeta_{it}$, intrinsic conditional autoregressive (ICAR) priors \cite{besag1995conditional}.
+An ICAR model allows us to encode spatial dependence between neighbouring regions which allows information on the probability and coverage of circumcision in areas where data is sparse or non-existent to be borrowed.
 For a generic parameter $\beta_i$, an ICAR model assumes that the mean of $\beta_i$ is a weighted average its neighbours,
@@
 Here, $j \sim i$ refers to the neighbours of region $i$, $n_i$ is the number of neighbours and $\tau_{\beta}$ is the marginal precision \cite{rue2005gaussian}.
+The joint distribution may be equivalently expressed as $\boldsymbol{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{I})$ where $Q_{I}$ is the precision matrix encoding the adjacency structure of the neighbourhoods.
+The precision matrix $Q_{I}$ is rank deficient and consequently the prior is improper \cite{rue2005gaussian}.
 
 In age, we modelled the random effects ($\hat{\phi}_a$, $\bar{\phi}_a$, $\phi_a$, $\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$ and $\delta_{at}$) using penalised B-splines.
+This allows us to smooth across the age of circumcision profile and also allows information on the probability and coverage of circumcision for ages to be borrowed where the data is sparse or non-existent (i.e.
+older age groups).
 For a generic parameter $\beta_a$, penalised B-splines assumes that $\beta_a$ is a sum of basis functions,
@@
 \end{align*} 
-where $b_{aj}$ are B-spline basis functions {\color{red}[CITE]} with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $\omega_{j}$ are the spline weight parameters to be estimated.
-The weights $w_{j}$ are penalised using an AR1 process
+where $b_{aj}$ are B-spline basis functions {\color{red}[CITE]} with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $w_{j}$ are the spline weight parameters to be estimated.
+The weights $w_{j}$ are penalised using an AR1 process,
 \begin{align*} 
@@
 \end{align*}
-where $|\rho_{w}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{w}$ is the precision.
-
-In time, we consider three possible prior distirbution choices: an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2).
-{\color{red} \bf [Need more information]}
-% \noindent In time, we assigned the random effects $\theta_t$, $\delta_{at}$ and $\zeta_{it}$ an autoregressive process of order 1 (AR1) priors,
+where $|\rho_{w}| < 1$ is an autocorrelation parameter controlling the correlation of the effect of the current age on the previous age and $\tau_{w}$ is the precision.
+The joint distribution is given by $\boldsymbol{w}\; | \; \rho_{w}, \tau_{w} \sim N(\boldsymbol{0}, \tau_{w}^{-1}Q^{-1}_{J}(\rho_{w}))$ where $Q_{J}$ is the precision matrix as defined by the basis functions and the autocorrelation parameter.
+Then defining $\boldsymbol{\beta} = W_{\beta}\cdot \boldsymbol{w}$ where $W_{\beta}$ is a design matrix evaluating the basis functions $b_{aj}$ at each age of interest, the joint distribution is given by, $\boldsymbol{\beta}\; | \;\boldsymbol{\omega}, \; W_{\beta}, \; \rho_{w}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{A})$ where Q^{-1}_{A} = W_{\beta}\cdot Q^{-1}_{J}(\rho_{w})\cdot W_{\beta}^T.
+
+In time, we consider three possible prior distribution choices for the random effects ($\hat{\theta}_t$, $\hat{\delta}_{at}$, $\theta_t$, $\delta_{at}$ and $\zeta_{it}$): an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2).
+AR and RW processes allows us to encode temporal dependence between survey information on the probability and coverage of circumcision and project this into the future.
+For a generic parameter $\beta_t$, an AR1 process assumes that,
 \begin{align*} 
@@
 \end{align*}
-
+where $|\rho_{\beta}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{\beta}$ is the precision.
+The joint distribution may be equivalently expressed as $\boldsymbol{\beta}\; | \; \rho_{\beta}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{T}(\rho_{\beta}))$ where $Q_{T}$ is the precision matrix and encodes the first order dependency in time controlled by the autocorrelation parameter $\rho_{\beta}$.
+A RW1 process assumes that,
 \begin{align*} 
@@
 \end{align*}
-
+and a RW2 process assumes that,
 \begin{align*} 
@@
 \end{align*}
-
-% where $|\rho_{\phi}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{\beta}$ is the precision.
-
-Moreover, age-space, age-time, and space-time interaction terms ($\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$, $\delta_{at}$ and $\zeta_{it}$) are modelled using a Type IV interactions as defined by Knorr-Held and Leonard \cite{knorr2000bayesian},
-
-We assigned Gaussian priors to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$.
-Exponential priors were placed on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$.
-Gaussian priors were set for all correlation parameters on the logit scale, such that
+where $\tau_{\beta}$ is the precision.
+For both RW1 and RW2, the joint distribution may be equivalently expressed as $\boldsymbol{\beta}\; | \; \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{T})$ where $Q_{T}$ is the precision matrix and encodes the dependency in time of the process and will be rank deficient and consequently the prior would be improper \cite{rue2005gaussian}.
+The choice of whether a country uses a AR1, RW1 and RW2 as a temporal prior was chosen depending on which produced the best out-of-sample model fit during model calibration (see Section \ref{sec::modelcheck} for further details).
+
+Moreover, age-space, age-time, and space-time interaction terms ($\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$, $\hat{\delta}_{at}$, $\delta_{at}$, and $\zeta_{it}$) are modelled using a Type IV interaction as defined by Knorr-Held and Leonard \cite{knorr2000bayesian},
+\begin{align*} 
+  \hat{\boldsymbol{\gamma}} \; | \; \rho_{\boldsymbol{\hat{\gamma}}}, \tau_{\boldsymbol{\hat{\gamma}}} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\hat{\gamma}} Q^{-1}_{\hat{\gamma}}) \\
+  \bar{\boldsymbol{\gamma}} \; | \; \rho_{\boldsymbol{\bar{\gamma}}}, \tau_{\boldsymbol{\bar{\gamma}}} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\bar{\gamma}} Q^{-1}_{\bar{\gamma}}) \\
+  \boldsymbol{\gamma} \; | \; \rho_{\gamma}, \tau_{\gamma} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\gamma} Q^{-1}_{\gamma})\\
+  \boldsymbol{\hat{\delta}} \; | \; \tau_{\hat{\delta}} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\hat{\delta}} Q^{-1}_{\hat{\delta}})\\
+  \boldsymbol{\delta} \; | \; \tau_{\delta} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\delta} Q^{-1}_{\delta})\\
+  \boldsymbol{\zeta} \; | \; \rho_{\zeta}, \tau_{\zeta} &\sim N(\boldsymbol{0}, \;\tau^{-1}_{\zeta} Q^{-1}_{\zeta})
+\end{align*}
+where the precision matrices constructed using Kronecker products 
+\begin{align*} 
+	Q_{\hat{\gamma}} = Q_{\bar{\gamma}} = Q_{\gamma} &= Q_A \otimes Q_I\\
+	Q_{\hat{\delta}} = Q_{\delta} &= Q_A \otimes Q_T\\
+	Q_{\zeta} &=Q_I \otimes Q_T
+\end{align*}
+Here, $Q_I$, $Q_A$ and $Q_T$ are precision matrices discussed above.
+
+Gaussian priors were assigned to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$. Gaussian priors were set for all correlation parameters on the logit scale, such that 
 \begin{align*} 
@@
 corresponding to 95\% CI prior weight that the autocorrelation parameters are between 0.48 and 0.99 on the real scale.
+For the age, district and age-district random effects, we assigned exponential priors on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$ on each of these processes.
+For the temporal, age-time and space-time random effects, the hyperpriors on the standard deviations $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}}$ were decided as part of the model calibration process (see Section \ref{sec::modelcheck} for further details).
 
@@
 
-Survey data consists of individual observations of self-reported age at circumcision, date of birth, and circumcision type (medical or traditional) from male survey respondents.
-Circumcision status observations were right censored if the respondent reported not being circumcised at the time of the survey or left censored if the individual reported being circumcised at the time of survey but did not report their age at circumcision.
-
-\noindent Each survey $s \in S = \{1, 2, \ldots, N_S\}$ consists of sampled individuals $j \in J_s = \{0, 1, 2, \ldots, N_{J_s}\}$ residing in region $i \in I = \{1, 2, \ldots, N_I\}$.
-Surveyed individuals were followed from their year of birth until their year of circumcision or their year of censoring.
+The extracted survey data consisted of individual observations of self-reported age at circumcision, date of birth, and circumcision type (medical or traditional) from male survey respondents (see above).
+Each survey $s \in S = \{1, 2, \ldots, N_S\}$ consists of sampled individuals $j \in J_s = \{0, 1, 2, \ldots, N_{J_s}\}$ residing in region $i \in I = \{1, 2, \ldots, N_I\}$.
+Individuals were followed from their year of birth to either their year of circumcision or their year of censoring.
 For circumcised individuals, the year of circumcision was calculated as the year of birth plus the age at circumcision.
-It was assumed that no circumcisions occurred after age 59, so for uncircumcised individuals, censoring occurred either in the survey year or when they were 59.
-Individuals who self-reported they were circumcised but have a missing age at circumcision were included in the analysis through left censoring.
+It was assumed that no circumcisions occurred after age 59, so for uncircumcised individuals, right censoring occurred either in the survey year or when they were 59.
+Individuals who self-reported they were circumcised but did not report an age at circumcision were included in the analysis through left censoring.
 
@@
 	\item[(7)] \textbf{MC left censored (MCLC)}: Individuals in region $i$ reporting a circumcision, of unknown type at an unknown age and time, between birth at time $t-a$ and age $a$ at time $t$.
-The likelihood of this outcome was the probability of being circumcised in region $i$ before age $a$ at time $t$, $(1-S_{iat}) = \text{CIF}^{\text{MMC}}_{iat}$
+The likelihood of this outcome was the probability of being circumcised in region $i$ before age $a$ at time $t$, $(1-S_{iat}) = \text{CIF}^{\text{MC}}_{iat}$
 \end{itemize}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Accounting for survey design}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \noindent Survey data are collected through a complex two-stage cluster sampling design with unequal sampling probabilities.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Model checking}
+
+\subsubsection{Accounting for regional aggregates}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Wherever possible, we matched survey data to clusters with accompanying geo-coordinates in order to assign the PSNU unit.
+However, geo-cordinates were not available in some surveys (e.g.
+MICS, see above) and therefore we were unable to allocate the PSNU unit directly.
+In this case, we matched survey data to the least granular areal unit declared by the survey.
+In some instances, these areal units represented PSNU unit, however in many cases, these are on higher administrative boundaries (e.g.
+national/admin-0).
+
+In order to include survey data on district as well as other administrative aggregates levels into the model, we estimate a population-weighted regional estimate of the probabilities of TMC, MMC and/or MC.
+We define the probability that an individual in region $ R \subset I = \{1, 2, \ldots, N_I\}$ received a circumcision of type $k$ at age $a$ and time step $t$ as
+\begin{equation*}
+	\lambda^{k}_{Rat} = \frac{\sum_{i\in R}P_{iat}\lambda^{k}_{iat}}{\sum_{i\in R}P_{iat}}
+\end{equation*}
+where $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, and $P_{iat}$ is an estimate of the male population at age $a$ and time step $t$ in district $i$.
+The district level probabilities of TMC, MMC and MC are then replaced with regional equivalents in the likelihood.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Final model selection}
 \label{sec::modelcheck}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The choice of the final model to use in each country was decided in a two stage process.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Model specification}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the first stage of selecting the final model in each country, we performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC.
+For each of the 12 model combinations,
+
+We sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
+We compared the mean predictions against the empirical survey estimates, aggregated to calculate predictive distributions by five year age groups (from 0-4 through 55-59) to avoid to many zeroes.
+
+To measure within-sample model fit we estimated the continuous ranked probability scores (CRPS), the mean absolute error (MAE) and root mean square error (RMSE).
+We also evaluated the coverage the posterior predictive distributions by calculating the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles of the posterior predictive distribution.
+The best performing models
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Model calibration}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-08-22 paper/old/model_spec_ppc_table.tex
Move old model spec analysis

\documentclass{article}

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{todonotes}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}
\usepackage{pifont}
\newcommand{\xmark}{\ding{55}}

\begin{document}

\section{Model Specification}
\label{sec:org8802288}

\subsection{non-VMMC countries}
\label{sec:org09db5e8}

Table 1 contains the results of our within-sample posterior predictive analysis of each possible model specification for all non-VMMC countries. We have calculated the CRPS, ELPD and RMSE of our posterior predictions versus our survey estimates, and totaled the number of countries for which each model is deemed "best" by each of these metrics. This was done for all possible temporal prior choices, not to choose a best temporal prior (a task better left to out-of-sample posterior checks, as in our model calibration section below), but rather to determine whether there is an interaction between temporal prior choice and model specification.
\todo{Add section about how averages are messed up by outliers? Need to investigate!}

\vspace{10 mm}

% Table of PPCs for model specification
% Need two tables; one for VMMC, one for non-VMMC
% Columns: Temporal Prior, Circumcision Type (with total as well), Metric, and then column for each model type, which will have another header saying something like "# of times model spec best"
% Caption?

{\linespread{1}
  \footnotesize 
% \begin{longtable}[c]{ll ccc c}
\begin{longtable}[c]{llllllll}
        \hline
        & & & & \multicolumn{3}{c}{\bf Number of countries where model specification is best}\\
        \cmidrule{5-8} \\
        & {\bf Temporal Prior} & {\bf Circumcision Type} & {\bf Metric}  & {\bf Neither} & {\bf Time TMC} & {\bf Paediatric Cutoff} & {\bf Both} \\[5pt]
        % & {\bf Prior} & {\bf Type} \\[5pt]
        \midrule
        & AR1 & MC & CRPS & 1 & 2 & \bf{6} & \bf{6} \\ 
        & AR1 & MC & ELPD & 3 & \bf{6} & 4 & 2 \\ 
        & AR1 & MC & RMSE & 1 & \bf{7} & 3 & 4 \\ 
        \hline 
        & AR1 & MC & Total & 5 & \bf{15} & 13 & 12 \\ 
        \hline \\ 
        & AR1 & MMC & CRPS & 4 & \bf{8} & 1 & 2 \\ 
        & AR1 & MMC & ELPD & 2 & 2 & 4 & \bf{7} \\ 
        & AR1 & MMC & RMSE & 0 & \bf{9} & 4 & 2 \\ 
        \hline 
        & AR1 & MMC & Total & 6 & \bf{19} & 9 & 11 \\ 
        \hline \\ 
        & AR1 & TMC & CRPS & 5 & \bf{7} & 2 & 1 \\ 
        & AR1 & TMC & ELPD & 1 & \bf{9} & 4 & 1 \\ 
        & AR1 & TMC & RMSE & 1 & \bf{7} & 4 & 3 \\ 
        \hline 
        & AR1 & TMC & Total & 7 & \bf{23} & 10 & 5 \\ 
        \hline \\ 
        & RW1 & MC & CRPS & 3 & 2 & 4 & \bf{6} \\ 
        & RW1 & MC & ELPD & 2 & \bf{9} & 2 & 2 \\ 
        & RW1 & MC & RMSE & 3 & 5 & 1 & \bf{6} \\ 
        \hline 
        & RW1 & MC & Total & 8 & \bf{16} & 7 & 14 \\ 
        \hline \\ 
        & RW1 & MMC & CRPS & 2 & \bf{10} & 1 & 2 \\ 
        & RW1 & MMC & ELPD & 4 & 2 & 4 & \bf{5} \\ 
        & RW1 & MMC & RMSE & 1 & \bf{10} & 2 & 2 \\ 
        \hline 
        & RW1 & MMC & Total & 7 & \bf{22} & 7 & 9 \\ 
        \hline \\ 
        & RW1 & TMC & CRPS & 2 & \bf{9} & 2 & 2 \\ 
        & RW1 & TMC & ELPD & 2 & \bf{8} & 4 & 1 \\ 
        & RW1 & TMC & RMSE & 2 & \bf{8} & 2 & 3 \\ 
        \hline 
        & RW1 & TMC & Total & 6 & \bf{25} & 8 & 6 \\ 
        \hline \\ 
        & RW2 & MC & CRPS & 1 & 1 & \bf{7} & 6 \\ 
        & RW2 & MC & ELPD & \bf{5} & 4 & 2 & 4 \\ 
        & RW2 & MC & RMSE & 0 & \bf{6} & 3 & \bf{6} \\ 
        \hline 
        & RW2 & MC & Total & 6 & 11 & 12 & \bf{16} \\ 
        \hline \\ 
        & RW2 & MMC & CRPS & 3 & \bf{12} & 0 & 0 \\ 
        & RW2 & MMC & ELPD & 5 & 1 & 3 & \bf{6} \\ 
        & RW2 & MMC & RMSE & 1 & \bf{9} & 3 & 2 \\ 
        \hline 
        & RW2 & MMC & Total & 9 & \bf{22} & 6 & 8 \\ 
        \hline \\ 
        & RW2 & TMC & CRPS & 2 & \bf{9} & 1 & 3 \\ 
        & RW2 & TMC & ELPD & 2 & \bf{11} & 2 & 0 \\ 
        & RW2 & TMC & RMSE & 1 & \bf{9} & 2 & 3 \\ 
        \hline 
        & RW2 & TMC & Total & 5 & \bf{29} & 5 & 6 \\ 
        \bottomrule
    % \end{tabular}
    \caption{Table of Posterior Predictive Check results for model specification analysis of non-VMMC countries. 
    % For each temporal prior and circumcision type
    Each numeric column shows the number of times a given model specification is deemed "best" according to the metric in question, for each temporal prior and circumcision type. The four model specifications are: \textbf{"Neither"}: Neither a time effect for TMC, nor a peadiatric age cutoff for MMC are incorporated, \textbf{"Time TMC"}: a time effect for TMC is included in the model, \textbf{"Paediatric Cutoff"}: a peadiatric age cutoff for MMC is included in the model and \textbf{"Both"}: both a time effect for TMC and a paediatric age cutoff for MMC are included in the model. MC = Male circumcision, MMC = Medical male circumcision, TMC = traditional male circumcision.
    }
% \end{table}
\end{longtable}
}

\todo{come up with better names for model specs}

\vspace{10 mm}

% non-VMMC, rw_order 0
For the AR1 temporal prior and MC, the best model for both ELPD and RMSE was "Time TMC", while for CRPS, "Both" and "Paediatric Cutoff" tied as best.
Totalling across all metrics, the best model was "Time TMC", although it was only marginally favoured over "Paediatric Cutoff" and "Both" (in 15 countries vs 13 and 12, respectively).  
For MMC, "Time TMC" is deemed to be the best for CRPS and RMSE, while "Both" is chosen by the ELPD. Totalling across metrics, "Time TMC" was by far the favoured model. 
For TMC, "Time TMC" was again determined to be the best model, this time by all metrics. This is unsurprising, particularly for non-VMMC countries, as the alternative model specifications include a very strong assumption of constant TMC.

Therefore, "Time TMC" was the most chosen model specification here across all circumcision types, as the model that produces the "best" fit for the most countries, by consensus of our three metrics.
% It was interesting that this contrasts with our analysis of the mean fit  statistics across all countries, perhaps suggesting that there are several outlier countries that skew our mean values. 
% \todo{Investigate these outliers!}
It was interesting to note that there was some disagreement between our three metrics for MC and MMC, while for TMC all agreed.

% non-VMMC, rw_order 1: 
For the RW1 temporal prior and MC, the best model for ELPD was "Time TMC", while for CRPS and RMSE it was "Both". However, totalling across metrics, the best model overall, albeit narrowly (16 vs 14 for both) was "Time TMC".
For MMC, "Time TMC" was the best for CRPS and RMSE, while "Both" was the best for ELPD. Totalling all metrics, "Time TMC" was by far the favoured model. 
For TMC, "Time TMC" was determined to be the best model for all model fits. 
Here, in contrast to the AR1 temporal prior, another model specification, "Both", was determined to be the best model for MC for two of our three metrics. 
However, it was important to note here that in almost all non-VMMC countries, MC coverage was very high, often over 90\%, and had been that way for many years, due to high historical TMC. Therefore, each model specification gave similar and very accurate estimates of MC, meaning we decided to prioritise the more difficult task of more accurately predicting MMC and TMC coverage, and how that has changed over time. 
In light of this, the model which performed best for MMC and TMC was chosen, meaning "Time TMC" was also deemed the best model specification for the RW1 temporal prior.

% non-VMMC, rw_order 2:
For the RW2 temporal prior and MC, it was interesting to note that "Time TMC" was not the sole choice of model for any of  our three metrics, tying for the best RMSE with "Both". 
Totalled across all metrics, "Both" was selected as the model which produced the best fit in the most countries. 
For MMC, in contrast to MC, CRPS and RMSE determined "Time TMC" to be the best  model, while ELPD chose "Both" as the best model. 
Totalling across metrics, "Time TMC" was by far chosen as the best model in the most countries. 
Again for TMC, all metrics were in agreement in selecting "Time TMC" as the best model.

In conclusion, for non-VMMC coutries "Time TMC" was determined to be the best model for all temporal priors, and seven out of nine temporal prior - circumcision type combinations, of which the two not in agreement were for MC, which was less of a priority than accurately estimating MMC and TMC. 
% It was interesting that the results here (i.e. when looking at the number of  times a model performs "best" in each country) for AR1 was in contrast to when we looked at mean fit statistics across all countries, perhaps suggesting there were some outliers for "Time TMC" model results which should be explored.

\subsection{non-VMMC countries}
\label{sec:org09db5e8}

The results of the same analysis performed on VMMC countries are shown in Table 2.

\vspace{10 mm}

% Table 2: Same but for VMMC countries
{\linespread{1}
  \footnotesize 
% \begin{longtable}[c]{ll ccc c}
\begin{longtable}[c]{llllllll}
        \hline
        & & & & \multicolumn{3}{c}{\bf Number of countries where model specification is best}\\
        \cmidrule{5-8} \\
        & {\bf Temporal Prior} & {\bf Circumcision Type} & {\bf Metric}  & {\bf Neither} & {\bf Time TMC} & {\bf Paediatric Cutoff} & {\bf Both} \\[5pt]
        % & {\bf Prior} & {\bf Type} \\[5pt]
        \midrule
        & AR1 & MC & CRPS & 3 & 1 & \bf{6} & 3 \\ 
        & AR1 & MC & ELPD & \bf{4} & \bf{4} & 2 & 3 \\ 
        & AR1 & MC & RMSE & 3 & 2 & \bf{5} & 3 \\ 
        \hline 
        & AR1 & MC & Total & 10 & 7 & \bf{13} & 9 \\ 
        \hline \\ 
        & AR1 & MMC & CRPS & 1 & \bf{6} & 2 & 4 \\ 
        & AR1 & MMC & ELPD & 5 & 2 & \bf{6} & 0 \\ 
        & AR1 & MMC & RMSE & 0 & \bf{7} & 1 & 5 \\ 
        \hline 
        & AR1 & MMC & Total & 6 & \bf{15} & 9 & 9 \\ 
        \hline \\ 
        & AR1 & TMC & CRPS & 1 & \bf{7} & 2 & 3 \\ 
        & AR1 & TMC & ELPD & 2 & \bf{7} & 1 & 3 \\ 
        & AR1 & TMC & RMSE & 0 & \bf{6} & 4 & 3 \\ 
        \hline 
        & AR1 & TMC & Total & 3 & \bf{20} & 7 & 9 \\ 
        \hline \\ 
        & RW1 & MC & CRPS & \bf{5} & 1 & 2 & \bf{5} \\ 
        & RW1 & MC & ELPD & 3 & \bf{5} & 3 & 2 \\ 
        & RW1 & MC & RMSE & 4 & 1 & 2 & \bf{6} \\ 
        \hline 
        & RW1 & MC & Total & 12 & 7 & 7 & \bf{13} \\ 
        \hline \\ 
        & RW1 & MMC & CRPS & 1 & \bf{7} & 2 & 3 \\ 
        & RW1 & MMC & ELPD & 2 & 3 & \bf{6} & 2 \\ 
        & RW1 & MMC & RMSE & 2 & \bf{6} & 1 & 4 \\ 
        \hline 
        & RW1 & MMC & Total & 5 & \bf{16} & 9 & 9 \\ 
        \hline \\ 
        & RW1 & TMC & CRPS & 1 & \bf{7} & 2 & 3 \\ 
        & RW1 & TMC & ELPD & 3 & \bf{7} & 1 & 2 \\ 
        & RW1 & TMC & RMSE & 1 & \bf{6} & 3 & 3 \\ 
        \hline 
        & RW1 & TMC & Total & 5 & \bf{20} & 6 & 8 \\ 
        \hline \\ 
        & RW2 & MC & CRPS & 3 & 1 & 3 & \bf{6} \\ 
        & RW2 & MC & ELPD & 2 & 4 & \bf{7} & 0 \\ 
        & RW2 & MC & RMSE & 4 & 4 & 0 & \bf{5} \\ 
        \hline 
        & RW2 & MC & Total & 9 & 9 & 10 & \bf{11} \\ 
        \hline \\ 
        & RW2 & MMC & CRPS & 2 & \bf{7} & 1 & 3 \\ 
        & RW2 & MMC & ELPD & 3 & 1 & \bf{7} & 2 \\ 
        & RW2 & MMC & RMSE & 1 & \bf{9} & 1 & 2 \\ 
        \hline 
        & RW2 & MMC & Total & 6 & \bf{17} & 9 & 7 \\ 
        \hline \\ 
        & RW2 & TMC & CRPS & 3 & \bf{5} & 2 & 3 \\ 
        & RW2 & TMC & ELPD & 2 & \bf{7} & 1 & 3 \\ 
        & RW2 & TMC & RMSE & 2 & \bf{5} & 3 & 3 \\ 
        \hline 
        & RW2 & TMC & Total & 7 & \bf{17} & 6 & 9 \\ 
        % \hline \\ 
        \bottomrule
    % \end{tabular}
    \caption{Table of Posterior Predictive Check results for model specification analysis of VMMC countries. 
    % For each temporal prior and circumcision type
    Each numeric column shows the number of times a given model specification is deemed "best" according to the metric in question, for each temporal prior and circumcision type. The four model specifications are: \textbf{"Neither"}: Neither a time effect for TMC, nor a peadiatric age cutoff for MMC are incorporated, \textbf{"Time TMC"}: a time effect for TMC is included in the model, \textbf{"Paediatric Cutoff"}: a peadiatric age cutoff for MMC is included in the model and \textbf{"Both"}: both a time effect for TMC and a paediatric age cutoff for MMC are included in the model. MC = Male circumcision, MMC = Medical male circumcision, TMC = traditional male circumcision.
    }
% \end{table}
\end{longtable}
}

% VMMC, rw_order 0: 
For MC, CRPS and RMSE determined "Paed Cutoff" to be the best model, while 
ELPD chose the "Neither" model. 
Totalling across metrics, "Paed Cutoff" was chosen as the best model. However, all four models perform reasonably well. 
For MMC the best model according to CRPS and RMSE was "Time TMC", while for ELPD it was Paed Cutoff. 
Over all metrics, "Time TMC" was by far the best model. 
For TMC, as was the case for non-VMMC countries, "Time TMC" was chosen as the best model by all three metrics.

There were several interesting observations to make from these results. 
There was an even greater contrast for VMMC countries between what model performs best in the most countries when estimating MC ("Paed Cutoff"), and for MMC and TMC, i.e. type specific estimates ("Time TMC"). 
Here, however, the decision to favour accuracy in predicting MC over MMC and TMC, or vice versa, was less clear. 
MC coverage varied considerably both between and within VMMC countries, and if we decide that estimates of total rather than type-specific circumcision are to be prioritised, then accurate MC estimation could be considered more important than accurate predictions of MMC and TMC patterns. 
This constrasted with non-VMMC countries, where MC was almost universally high and homogeneous, and so estimates of MC were similar for all model specifications.

However, it was interesting to note that, totalling across each circumcision type and metric, "Time TMC" was by far the most favoured model (57 vs the next best mode, "Paed Cutoff", which had 32 "votes"), so perhaps in a consensus between all circumcision types and metrics, "Time TMC" was the best model for VMMC countries, for the AR1 temporal prior. 
Another important observation was that the "Both" model, which combines both the time effect for TMC and the paediatric age cutoff for MMC seen in the "Time TMC" and "Paed Cutoff" models, did not appear to perform better than either of these. 
However, it was only narrowly chosen less than "Paed Cutoff" (27 vs 29).

It was also very important to take into consideration that these fit metrics were based on comparisons to survey estimates for 15-29 year olds, as those younger than 15 were not surveyed. 
Therefore, we were unable to determine whether the "Paed Cutoff" and/or "Both" models performed better for these younger ages in VMMC countries, where it could be argued that they would, since we have knowledge of the fact that VMMC programme policy prohibits performing MMCs on those younger than 10. This fact further obscures our quantitative choice of the best model specification for VMMC countries based on these metrics. 
Finally, model choice across all types was less clear than for Non-VMMC  countries, highlighting lesser differences between model specifications for VMMC countries, perhaps not so suprising given low TMC in these areas, and the lack of survey estimates for those aged under 15 to properly evaluate models with a peadiatric age cutoff for MMC. 
\todo{May also be a good idea to remove KEN and ETH, both high circumcising VMMC countries, to determine if they were influential here in model choice.}
\todo{Also for ETH look into Gambella province.}

% VMMC, rw_order 1: 
For the RW1 temporal prior and MC, the "Neither" and "Both" models tied as the best model as chosen by CRPS, while for ELPD "Time TMC" was the best model, and for RMSE "Both" was preferred. 
Totalling across metrics, the "Both" model was narrowly best. 
It was interesting to see a lot of disagreement between metrics here, and a less clear choice of the best model specification when totalling across metrics. 
For MMC, the "Time TMC" model was favoured by CRPS and RMSE, while for ELPD the "Paed Age Cutoff model was the best. 
Again, for TMC the "Time TMC" model was chosen as best by all three metrics.

In conclusion, we can again see a difference in the best model for total circumcision/MC and for type-specific circumcision (MMC and TMC). 
The "Time TMC" model was the best when totalling across all metrics and types, but this distinction was much less clear than for non-VMMC countries.

% VMMC, rw_order 2:
For the RW2 temporal prior and MC, the "Both" model was best for CRPS and RMSE, while the "Paed Cutoff" was best for ELPD.
Totalling across metrics, all models performed similarly well, ranging from 9 to 11, with the "Both" model narrowly favoured over the "Paed Cutoff" model. 
FOr MMC, "Time TMC" was best for CRPS and RMSE, while the "Paed Cutoff" model was best for ELPD. 
The "Time TMC" was deemed the best when totalling across all metrics. 
Finally, once more for TMC, the "Time TMC" model was best across all metrics.

In conclusion for VMMC countries, the "Time TMC" model was chosen as best for 6 out of  9 temporal prior-curcumcision type combinations. 
However, this choice was much less "clear cut" than for non-VMMC countries, and there was a stark constrast between the best model for MC and for MMC and TMC, as detailed in our conclusions from the results for the AR1 temporal prior above. 
The models with a paediatric age cutoff for MMC performed reasonably well here, even including the caveat that their perform was evaluated through comparisons to survey estimates of the 15-29 age group, rather than an unavailable younger/wider age group of, say, 10-29, where it could be argued that their performance and the relative effect of model selection on fit could be better ascertained. 
Indeed, as we have prior knowledge that that VMMC programmes do not perform paediatric MMCs, we could prioritise our qualitative investigation and knowledge of MMC and VMMC practises in VMMC prioirity countries to decide 
to go with the "Both" model. 
\todo{Discuss with Matt and Jeff the best model to use here!!}

\end{document}

### 2023-08-22 paper/supp_figs.tex
Updates from Overleaf

@@
 national/admin-0).
+\todo{Not entirely convinced that }
 
@@
 where $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, and $P_{iat}$ is an estimate of the male population at age $a$ and time step $t$ in district $i$.
-The district level probabilities of TMC, MMC and MC are then replaced with regional equivalents in the likelihood.
+The regional probabilities of TMC, MMC and MC
+
+for surveys not at the
+
+with regional equivalents in the likelihood above in order to include higher level aggregates.
 
@@
 
-In the first stage of selecting the final model in each country, we performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC.
-For each of the 12 model combinations,
-
-We sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
+In the first stage of selecting the final model, we performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC.
+
+In each country,
+
+For each of the 12 model combinations, we sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
 We compared the mean predictions against the empirical survey estimates, aggregated to calculate predictive distributions by five year age groups (from 0-4 through 55-59) to avoid to many zeroes.
-
 To measure within-sample model fit we estimated the continuous ranked probability scores (CRPS), the mean absolute error (MAE) and root mean square error (RMSE).

### 2023-08-23 paper/scripts/032_results.R
Add SSD, grey out all NA countries, add blue Lake Victoria

@@ -248,6 +248,43 @@ iso_df <- iso_df %>%
   ) %>%
   mutate(region = ifelse(region == "", "Other", region))
 
+# areas for SSD (want to add to map plot)
+dat_loc <- "paper_poster_plots/aids_2022_poster/data/"
+ 
+ssn_areas <- sf::read_sf(file.path(
+  dat_loc, 
+  "ssd_admbnda_imwg_nbs_shp/ssd_admbnda_adm0_imwg_nbs_20180817.shp"
+)) %>% 
+  select(CNTRY_NAME = ADM0_EN) %>% 
+  group_split(CNTRY_NAME) %>% 
+  purrr::map(function(x) {
+    cntry <- unique(x$CNTRY_NAME)
+    x <- sf::st_union(x) # may need sf::st_combine?
+    df <- data.frame("CNTRY_NAME" = cntry)
+    sf::st_geometry(df) <- x
+    return(df)
+  }) %>%  
+  bind_rows() %>% 
+  mutate(
+    iso3 = countrycode::countrycode(CNTRY_NAME, "country.name", "iso3c"),
+    area_id = iso3,
+    area_name = CNTRY_NAME,
+    area_level = 0
+  ) %>% 
+  filter(!is.na(iso3)) %>% 
+  select(iso3, area_id, area_name, area_level)
+
+# add to areas 
+areas_map <- bind_rows(areas, ssn_areas) %>% 
+  filter(!is.na(iso3))
+
+# Also add Lake Victoria for blue in map plot
+lake_vic <- rnaturalearth::ne_download(
+  scale = 110, type = "lakes", category = "physical") %>% 
+  sf::st_as_sf(lakes110, crs = 4269) %>% 
+  filter(name == "Lake Victoria") %>% 
+  select(name)
+
 
 #### Figure 2: Map of MC Coverage across SSA 20-2020 15-29 year olds ####
 
@@ -278,7 +315,7 @@ spec_model <- "No program data"
 spec_main_title    = main_title
 
 results_agegroup1 <- results_agegroup
-areas1 <- areas
+areas1 <- areas_map
 
 ## Plot ##
 
@@ -310,10 +347,24 @@ tmp <- results_agegroup1 %>%
         type %in%       c("MC coverage", "MMC coverage", "TMC coverage")
     )
 
+# Create dummy rows of NAs for missing countries - want them grey in map
+missing_iso3 <- unique(
+  areas_join$iso3[!areas_join$iso3 %in% results_agegroup$iso3]
+)
+
[…]

### 2023-08-23 paper/scripts/032_results.R
Subnat plot: make dots smaller, move title to x-axis, increase VMMC label verbosity

@@ -651,10 +651,8 @@ p3 <- plt_data %>%
   filter(area_level == max(area_level)) %>% 
   ggplot(
     aes(
-      # countries on the x-axis, in specified order
-      x = country_idx, 
-      # median MC Coverage on the y-axis
-      y = median
+     x = country_idx,  # countries on the x-axis, in specified order
+     y = median # median MC Coverage on the y-axis
     )
   ) +
   # add points coloured by region with weighted populations determining size
@@ -674,7 +672,7 @@ p3 <- plt_data %>%
   # add median national level to plot as white dots
   geom_point(
     data = filter(plt_data, area_level == 0),
-    size = 5, 
+    size = 4.5, 
     fill = "#F1F1F1",
     col = "black", 
     alpha = 1, 
@@ -694,18 +692,21 @@ p3 <- plt_data %>%
   annotate(
     geom = "text",
     x = c(length(plot_order) + 1),
-    y = 0.12,
-    label = "non-VMMC",
+    # y = 0.12,
+    y = 0.21,
+    label = "non-VMMC Priority Countries",
     fontface = "bold",
-    size = 4.5
+    size = 3.5
   ) +
   annotate(
     geom = "text",
-    x = c(length(plot_order) - (country_positions1 + 4)),
-    y = 0.075,
-    label = "VMMC",
+    # x = c(length(plot_order) - (country_positions1 + 4)),
+    x = c(length(plot_order) - (country_positions1 + 5)),
+    # y = 0.075,
+    y = 0.175,
+    label = "VMMC Priority Countries",
     fontface = "bold",
-    size = 4.5
+    size = 3.5
   ) +
   theme_bw(base_size = 8) + 
   scale_x_continuous(
@@ -731,25 +732,26 @@ p3 <- plt_data %>%
     # labels = paste0(c(1, 50), "x")
   ) +
   labs(
-    y = "Median Male Circumcision Coverage", 
+    # y = "Median Male Circumcision Coverage", 
+    y = paste0("Male Circumcision Coverage, ", spec_years[2], ", ", spec_age_group, " year olds"),
     x = element_blank(), 
-    # size = "District pop. relative\nto median district size", 
     size = "District pop. relative to\n median district size", 
     color = "Region"
   ) +
-  ggtitle(paste0(
-    # "District-Level MC Coverage, ", spec_years[2], " ages ", spec_age_group, " years old"
[…]

### 2023-08-23 paper/scripts/032_results.R
Geofaceted plot: Add boxes and grids, more verbose legend moved to bottom left

@@ -762,9 +762,9 @@ p3 <- plt_data %>%
 
 p3$plot_order <- plot_order
 
-dev.new(width = 6.3, height = 8, noRStudioGD = TRUE)
-p3
-dev.off()
+# dev.new(width = 6.3, height = 8, noRStudioGD = TRUE)
+# p3
+# dev.off()
 
 # saveRDS(p3, "paper_poster_plots/paper/plots/03_subnat_plot.RDS")
 ggplot2::ggsave(
@@ -807,7 +807,7 @@ ssa_grid <- geofacet::africa_countries_grid1 %>%
       name == "Democratic Republic of the Congo" ~ "DR Congo",
       name == "Republic of the Congo"            ~ "Congo",
       name == "Equatorial Guinea"                ~ "Eq. Guinea",
-      name == "Guinea-Bissau"                    ~ "Gin. Bissau",
+      # name == "Guinea-Bissau"                    ~ "Gin. Bissau",
       name == "Central African Republic"         ~ "Cent. Af. Rep.",
       TRUE                                       ~ name
     )
@@ -833,23 +833,31 @@ p4_geo <- p4 +
   geofacet::facet_geo(~ area_name, grid = ssa_grid) +
   ggtitle(paste0("Medical & traditional male circumcision by age, 2020")) +
   # set theme and base size for text
-  theme_minimal(base_size = 9) + 
+  theme_bw(base_size = 9) + 
   # reduce x-axis ticks, too crowded
   scale_x_continuous(breaks = seq(0, 60, by = 20)) + 
   # remove x-axis
-  labs(y = "") +  
+  # labs(y = "") +  
+  # labs(title = "",
+  #   y = "Circumcision coverage by age, 2020"
+  # ) + 
   theme(
     axis.text.x     = element_text(size = rel(1.1)),
-    axis.text.y     = element_blank(),
+    axis.text.y     = element_text(size = rel(1.1)),
+    axis.title.y    = element_text(size = rel(1.5)),
     legend.text     = element_text(size = rel(1.2)),
-    strip.text      = element_text(size = 8.5),
-    plot.title      = element_text(size = rel(1.5),  hjust = 0.5),
-    panel.grid      = element_blank(),
-    plot.background = element_rect(fill = "white", colour = "white"),
-    legend.position = "bottom"
+    legend.direction = "vertical",
+    # legend.position = "bottom",
[…]

### 2023-08-24 paper/scripts/032_results.R
Change plot: add closed arrows, move legend, improve text size

@@ -63,6 +63,20 @@ target_iso3 <- c(
   "RWA", "ZAF", "SWZ", "UGA", "TZA", "ZMB", "ZWE"
 )
 
+# VMMC countries  
+vmmc_iso3 <- c(
+  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF" # LSO, SWZ ran already
+)
+vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
+
+# countries with no type information
+no_type_iso3 <- c("LBR", "SEN", "NER", "GIN", "COD")
+
+# remaining countries
+iso3 <- ssa_iso3[!ssa_iso3 %in% c(vmmc_iso3, no_type_iso3)]
+
+
 
 # Colour palette for "% change" facets in map plot
 # colourPalette <- rev(colorRampPalette(
@@ -95,19 +109,22 @@ colourPalette <- c(
 )
 
 
+# plot order for countries, first non-VMMC & then VMMC countries
+plot_order <- c(
+  "BEN", "BFA", "CIV", "GHA", "GIN", "GNB", "LBR", "MLI", "NER", 
+  "NGA", "SEN", "SLE", "GMB", "TGO", "AGO", "CMR", "CAF", "TCD", 
+  "COG", "COD", "GAB", "BDI", "ETH", "KEN", "MWI", "MOZ", "RWA", 
+  "TZA", "UGA", "ZMB", "ZWE", "BWA", "SWZ", "LSO", "NAM", "ZAF"
+)
+
+# where to add horizontal line for VMMC vs non-VMMC
+country_positions1 <- length(vmmc_iso3) + 1
+
+
 #### Load Data ####
 
 # orderly archives
 archives <- orderly::orderly_list_archive()
-
-# VMMC countries  
-vmmc_iso3 <- c(
-  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
-  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF" # LSO, SWZ ran already
-)
-no_type_iso3 <- c("LBR", "SEN", "NER", "GIN", "COD")
-
-iso3 <- ssa_iso3[!ssa_iso3 %in% c(vmmc_iso3, no_type_iso3)]
 
 pars_df <- bind_rows(
   # parameters for VMMC countries 
[…]

### 2023-08-24 paper/scripts/032_results.R
Subnat plot: move VMMC label to look okay in png

@@ -683,22 +683,26 @@ p3 <- plt_data %>%
   # annotate plot with regional labels
   annotate(
     geom = "text",
-    x = c(length(plot_order) + 1),
+    x = c(length(plot_order) + 0.5),
     # y = 0.12,
-    y = 0.21,
-    label = "non-VMMC Priority Countries",
+    # y = 0.21,
+    y = 0.01,
+    label = "non-VMMC \n Priority Countries",
     fontface = "bold",
-    size = 3.5
+    size = 3.5, 
+    hjust = 0
   ) +
   annotate(
     geom = "text",
     # x = c(length(plot_order) - (country_positions1 + 4)),
-    x = c(length(plot_order) - (country_positions1 + 5)),
+    x = c(length(plot_order) - (country_positions1 + 4.5)),
     # y = 0.075,
-    y = 0.175,
-    label = "VMMC Priority Countries",
+    # y = 0.175,
+    y = 0.01,
+    label = "VMMC \n Priority Countries",
     fontface = "bold",
-    size = 3.5
+    size = 3.5, 
+    hjust = 0
   ) +
   theme_bw(base_size = 8) + 
   scale_x_continuous(

### 2023-08-24 paper/scripts/031_results_data.R
Update survey plot

@@ -259,8 +259,14 @@ plot_surveys <- survey_tbl %>%
   ) %>%
   # arrange by region (as a factor) and country (alphabetically)
   arrange(region, country) %>%
-  # convert country to factor
-  mutate(country = fct_inorder(country))
+  # change long country name, severely affecting plot width
+  mutate(
+    country = ifelse(
+      country == "Central African Republic", "Cent. Af. Rep.", country
+    ),
+    # convert country to factor
+    country = fct_inorder(country)
+  )
 
 
 fig1data <- plot_surveys %>%
@@ -301,15 +307,15 @@ p1 <- fig1data %>%
   # annotate plot with (vertical) regional labels
   annotate(
     "text",
-    2020,
+    2020.2,
     # have labels in between horizontal lines
     zoo::rollmean(c(country_positions, 0), 2),
     label = c("Western", "Central", "Eastern", "Southern"),
     angle = 270,
     fontface = "bold",
-    size = 6
+    size = 4
   ) +
-  geom_point(stroke = 3) +
+  geom_point(stroke = 2) +
   # specify x and y labels, subbing country name for country_idx
   scale_x_continuous(
     "Survey Year", 
@@ -334,14 +340,15 @@ p1 <- fig1data %>%
     size = guide_legend(order = 3)
   ) +
   labs(
-    colour = "Survey Type",
+    colour = "Survey type",
     # shape = "Type Distinction",
-    shape = "Information on Circumcision Type",
-    size = "Sample Size"
+    shape = "Info on circumcision type",
+    size = "Sample size"
   ) +
+  theme_bw() + 
   theme(
     axis.title.x = element_text(size = 12, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1.0, size = 14, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 14, face = "bold"),
     axis.text.y = element_text(size = 12, face = "bold"),
     legend.text = element_text(size = 15, face= "bold"),
     legend.title = element_text(size = 14, face = "bold"),
@@ -356,6 +363,11 @@ p1 <- fig1data %>%
   ) +
   coord_cartesian(xlim = c(2002, 2018.75), clip = "off")
 # p1
+
+# dev.new(width = 6.3, height = 10.5, noRStudioGD = TRUE)
+# p1
+# dev.off()
+
[…]

### 2023-08-24 paper/paper.tex
Updates from Overleaf
Change captions

--- 2023-08-15 paper/paper.tex
@@
 % Surveys Plot (may be moved to supp. figs)
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
 The colour and size of points are determined by the provider and sample size of each respective survey.
-Triangular points have no information on circumcision type.}}
+Triangular points have no information on circumcision type.
+Cent.
+Af.
+Rep.
+= Central African Republic}}
 \end{figure}
@@
 % Map Plot
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
     {paper/plots/02_map_plot_facet.png}
-    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years.
-Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively.
-Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
+    \caption{\emph{Estimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years.
+Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively.
+Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all.}}
 \end{figure}
-\todo{
-  - Use divergent colour palette for "% change", and different one for coverage
-- Need to position colour bars under corresponding facets, rather than to the side
-- Grey out countries with no type (done)
-- reevaluate text size
-}
 
@@
 % Subnational coverage plot
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
     {plots/03_subnat_plot.png}
-    \caption{\emph{District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.
-    Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).
-    Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}}
+    \caption{\emph{District-level median percentage of men aged 15-29 years who were circumcised in 2020 in 33 SSA countries.
+    Each point is a district, sized by district population relative to average district size.
+    Each white dot represents the national median. 
+    A vertical dotted line signifies the UNAIDS target of 90\% national male circumcision amongst 15-29 year olds.
+The countries below the horizontal black line are VMMC priority countries.
+VMMC = Voluntary Medical Male Circumcision.}}
 \end{figure}
+
+\todo{
+ - Check UNAIDS target for 15-29 year olds, may be 80\%? May want to remove this line altogether?
+}
 
@@
 % Geofaceted plot of 2020 coverage by age
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
 The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy.
-Purple areas represent countries where circumcision type could not be ascertained from surveys.}}
+Purple areas represent countries where circumcision type could not be ascertained from surveys, and so shows total male circumcision.
+Cent.
+Af.
+Rep.
+= Central African Republic, Eq.
+Guinea = Equatorial Guinea.}}
 \end{figure}
@@
 % todo: Rewrite caption
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \includegraphics[width=.9\linewidth]
-    {plots/05_change_00_20.png}
+    \includegraphics[width=1\linewidth]
+    {plots/06_change_00_20.png}
     % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region.
@@
 }}
-    \caption{\emph{Absolute change in circumcision coverage between 2000 and 2020 for 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type.
-The countries below the horizontal black line are VMMC priority countries}}
+    \caption{\emph{Circumcision coverage in 2000 and 2020 amongst 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type.
+The countries below the horizontal black line are VMMC priority countries.}}
 \end{figure}

### 2023-08-24 paper/scripts/031_results_data.R
Survey plot: improve font size

@@ -345,13 +345,15 @@ p1 <- fig1data %>%
     shape = "Info on circumcision type",
     size = "Sample size"
   ) +
-  theme_bw() + 
+  theme_bw(base_size = 9) + 
   theme(
-    axis.title.x = element_text(size = 12, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 14, face = "bold"),
-    axis.text.y = element_text(size = 12, face = "bold"),
-    legend.text = element_text(size = 15, face= "bold"),
-    legend.title = element_text(size = 14, face = "bold"),
+    axis.title.x = element_text(size = rel(1.5), colour = "black"),
+    axis.text.x = element_text(
+      size = rel(1.5), angle = 45, hjust = 1, colour = "black"
+    ),
+    axis.text.y = element_text(size = rel(1.5), colour = "black"),
+    legend.text = element_text(size = rel(1.5), colour = "black"),
+    legend.title = element_text(size = rel(1.5), colour = "black"),
     legend.position = "bottom",
     legend.box = "vertical",
     legend.spacing = unit(0, "cm"),
@@ -362,7 +364,7 @@ p1 <- fig1data %>%
     plot.margin = margin(0.25, 1, 0, 0, "cm") 
   ) +
   coord_cartesian(xlim = c(2002, 2018.75), clip = "off")
-# p1
+p1
 
 # dev.new(width = 6.3, height = 10.5, noRStudioGD = TRUE)
 # p1

### 2023-08-24 paper/scripts/020_methods_data.R
Change suvrey table slightly

@@ -235,13 +235,15 @@ sample_sizes <- survey_circumcision %>%
 
 # find original sample; this will give participation
 n_orig <- survey_circumcision_orig %>% 
-  group_by(survey_id) %>% 
-  summarise(n_orig = n(), .groups = "drop") %>% 
-  select(-survey_id)
+  count(survey_id) %>% 
+  # select(-survey_id)
+  identity()
 
-sample_sizes <- cbind(sample_sizes, n_orig) %>% 
+# sample_sizes <- cbind(sample_sizes, n_orig) %>% 
+sample_sizes <- left_join(sample_sizes, n_orig) %>% 
+  relocate(n_orig = n, .before = everything()) %>% 
   # calculate participation rates
-  mutate(part_rates = N / n_orig) %>% 
+  # mutate(part_rates = N / n_orig) %>% 
   select(-survey_id)
 
 # find level of left and right censoring occuring
@@ -260,6 +262,7 @@ cens <- survey_circumcision %>%
   
 # finally, find number of known circumcision types
 types <- survey_circumcision %>% 
+  mutate(type = ifelse(type == "Missing", NA, type)) %>% 
   group_by(survey_id) %>% 
   summarise(
     across(all_of(c("circ_who", "circ_where", "type")),
@@ -270,21 +273,27 @@ types <- survey_circumcision %>%
 
 # now join together!
 table3 <- cbind(survey_names, sample_sizes, cens, types) %>% 
-  select(-c(survey_id, n_orig)) %>% 
-  mutate(part_rates = paste(round(100 * part_rates, 3), "%", sep = "")) %>% 
-  rename(
+  # select(-c(survey_id, n_orig)) %>% 
+  select(-survey_id) %>% 
+  # remove questions about circ type; unneeded
+  select(-c(known_who, known_where)) %>% 
+  # mutate(part_rates = paste(round(100 * part_rates, 3), "%", sep = "")) %>% 
+  select(
     "Country"                      = country, 
     "Year"                         = year, 
     "Series"                       = series, 
-    "Sample Size"                  = N, 
+    # "Sample Size"                  = N, 
+    "Sample Size"                  = n_orig,
     "Effective Sample Size"        = Neff, 
-    "Participation Rates"          = part_rates, 
+    # "Participation Rates"          = part_rates, 
+    "Number Participated"          = N, 
     "Left Censored"                = left_censored, 
     "Right Censored/Uncircumcised" = right_censored, 
[…]

### 2023-08-24 paper/paper.tex
Updates from Overleaf

@@
 
-Several major survey series included questions on male circumcision status, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys.
+The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
+We excluded Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
+
+{\color{red} Several major survey series included questions on male circumcision status, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys.
 
@@
 
-Sub-national populations from WorldPop were used to calculate circumcision coverage from circumcision rates. (reference)
+Sub-national populations from WorldPop were used to calculate circumcision coverage from circumcision rates. (reference)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{sec:org681dda6}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-08-24 paper/supp_figs.tex
Updates from Overleaf

@@
 
-The study consisted of 33 sub-Saharan countries, which in approximate order from North to South and then West to East are: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa".
-We excluded 4 SSA countries: Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana.
-These were excluded because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
-
-We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
+The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
+We excluded Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
+In total, we identified 109 nationally representative household surveys conducted the study region between 2002 and 2019.
 These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs, ais, phia, hsrc2002, hsrc2008, hsrc2012, hsrc2017} \todo{include MICS reference}.
@@
 
+\begin{landscape}
+    {\linespread{1}
+  \footnotesize 
+\begin{longtable}[c]{ll cccc ccc ccc}
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table header %%%
+      %%%%%%%%%%%%%%%%%%%%
+      % Upper layer of table header
+      \hline
+      % Lines inside the header
+      \multicolumn{1}{l}{} & & \multicolumn{4}{c}{\bf Survey questions} & \multicolumn{2}{c}{\bf Sample size} & \multicolumn{2}{c}{\bf Circumcision status} & \multicolumn{2}{c}{\bf Circumcision metadata} \\
+      \cmidrule(lr){3-6} \cmidrule(lr){7-8}\cmidrule(lr){9-10} \cmidrule(lr){11-12}
+       & & {\bf Circ.} & {\bf Age at} & {\bf Who} & {\bf Where } & \multirow{2}{*}{\bf Total} & \multirow{2}{*}{\bf Included (\%)} & \multirow{2}{*}{\bf Uncircumcised (\%)} & \multirow{2}{*}{\bf Circumcised (\%)} & {\bf Known age} & {\bf Known type}
+       \\
+       & & {\bf Status} & {\bf Circ.} & {\bf performed?} & {\bf performed?}  & & & & & {\bf at circ. (\%)} & {\bf of circ. (\%)} \\[5pt]
+      % Lower lines
+      \hline
+      \vspace{-3pt}
+      \endhead
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table footer %%%
+      %%%%%%%%%%%%%%%%%%%%
+      \\[-3pt] \hline
+      \endfoot
+      %%%%%%%%%%%%%%%%%%%%%%
+      %%% Table contents %%%
+      %%%%%%%%%%%%%%%%%%%%%%
+      \multicolumn{2}{l}{\textbf{Angola}} \\ 
+& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark & 5684 & 5660 (99.58\%) & 207 (3.66\%) & 5453 (96.34\%) & 4106 (75.30\%) & 4767 (75.30\%) \\[3pt]
+\multicolumn{2}{l}{\textbf{Benin}} \\ 
+& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark & 5321 & 5317 (99.92\%) & 234 (4.40\%) & 5083 (95.60\%) & 0 (0.00\%) & 0 (0.00\%) \\ 
+& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark & 5153 & 5129 (99.53\%) & 354 (6.90\%) & 4775 (93.10\%) & 2709 (56.73\%) & 4328 (56.73\%) \\  
+& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark & 4577 & 4370 (95.48\%) & 124 (2.84\%) & 4246 (97.16\%) & 4141 (97.53\%) & 4210 (97.53\%) \\  
+& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark & 7595 & 7569 (99.66\%) & 401 (5.30\%) & 7168 (94.70\%) & 2514 (35.07\%) & 7063 (35.07\%) \\[3pt]
+\end{longtable}
+
+\begin{longtable}[c]{ll ccc ccc}
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table header %%%
+      %%%%%%%%%%%%%%%%%%%%
+      % Upper layer of table header
+      \hline
+      % Lines inside the header
+      \multicolumn{1}{l}{} & & \multicolumn{2}{c}{\bf Sample size} & \multicolumn{2}{c}{\bf Circumcision status} & \multicolumn{2}{c}{\bf Circumcision metadata} \\ 
+      \cmidrule(lr){3-4} \cmidrule(lr){5-6}\cmidrule(lr){7-8} 
+       & & \multirow{2}{*}{\bf Total} & \multirow{2}{*}{\bf Included (\%)} & \multirow{2}{*}{\bf Uncircumcised (\%)} & \multirow{2}{*}{\bf Circumcised (\%)} & {\bf Known age at} & {\bf Known type of}
+       \\
+       & & & & & & {\bf circumcision (\%)} & {\bf circumcision (\%)} \\[5pt]
+      % Lower lines
+      \hline
+      \vspace{-3pt}
+      \endhead
+      %%%%%%%%%%%%%%%%%%%%
+      %%% Table footer %%%
+      %%%%%%%%%%%%%%%%%%%%
+      \\[-3pt] \hline
+      \endfoot
+      %%%%%%%%%%%%%%%%%%%%%%
+      %%% Table contents %%%
+      %%%%%%%%%%%%%%%%%%%%%%
+\multicolumn{2}{l}{\textbf{Angola}} \\ 
+& 2015 (DHS) & 5684 & 5660 (99.58\%) & 207 (3.66\%) & 5453 (96.34\%) & 4106 (75.30\%) & 4767 (75.30\%) \\[3pt]
+\multicolumn{2}{l}{\textbf{Benin}} \\ 
+& 2006 (DHS) & 5321 & 5317 (99.92\%) & 234 (4.40\%) & 5083 (95.60\%) & 0 (0.00\%) & 0 (0.00\%) \\ 
+& 2012 (DHS) & 5153 & 5129 (99.53\%) & 354 (6.90\%) & 4775 (93.10\%) & 2709 (56.73\%) & 4328 (56.73\%) \\ 
+& 2014 (MICS) & 4577 & 4370 (95.48\%) & 124 (2.84\%) & 4246 (97.16\%) & 4141 (97.53\%) & 4210 (97.53\%) \\ 
+& 2017 (DHS) & 7595 & 7569 (99.66\%) & 401 (5.30\%) & 7168 (94.70\%) & 2514 (35.07\%) & 7063 (35.07\%) \\[3pt]
+\end{longtable}
+}
+\end{landscape}
+
 The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates. 
@@
 The joint distribution is given by $\boldsymbol{w}\; | \; \rho_{w}, \tau_{w} \sim N(\boldsymbol{0}, \tau_{w}^{-1}Q^{-1}_{J}(\rho_{w}))$ where $Q_{J}$ is the precision matrix as defined by the basis functions and the autocorrelation parameter.
-Then defining $\boldsymbol{\beta} = W_{\beta}\cdot \boldsymbol{w}$ where $W_{\beta}$ is a design matrix evaluating the basis functions $b_{aj}$ at each age of interest, the joint distribution is given by, $\boldsymbol{\beta}\; | \;\boldsymbol{\omega}, \; W_{\beta}, \; \rho_{w}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{A})$ where Q^{-1}_{A} = W_{\beta}\cdot Q^{-1}_{J}(\rho_{w})\cdot W_{\beta}^T.
+Then defining $\boldsymbol{\beta} = W_{\beta}\cdot \boldsymbol{w}$ where $W_{\beta}$ is a design matrix evaluating the basis functions $b_{aj}$ at each age of interest, the joint distribution is given by, $\boldsymbol{\beta}\; | \;\boldsymbol{\omega}, \; W_{\beta}, \; \rho_{w}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{A})$ where $Q^{-1}_{A} = W_{\beta}\cdot Q^{-1}_{J}(\rho_{w})\cdot W_{\beta}^T$.
 

### 2023-08-25 paper/scripts/032_results.R
Plot updates, as suggested by Matt 24/08/23

@@ -467,7 +467,9 @@ spec_areas <- areas_plot
 
 rm(results_agegroup1, areas1); gc()
    
-map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
+map_plot <- function(
+    spec_results, spec_areas, lake_vic, colourPalette, colourPalette2
+  ) {
   
   spec_results$type <- factor(
     spec_results$type, 
@@ -527,19 +529,9 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
     ) + 
     labs(fill = "") +
     scale_fill_gradientn(
-    # scale_fill_gradient2(
       colours = colourPalette2,
-      # colours = c(colourPalette_blue, colourPalette_other),
-      #colours = c(
-      #  colourPalette_blue, 
-      #  colourPalette_green, 
-      #  colourPalette_yellow, 
-      #  colourPalette_red_orange
-      #),
       na.value = "grey",
-      # breaks = seq(-0.2, 0.5, by = 0.1), 
       breaks = seq(-0.2, 0.5, by = 0.1), 
-      # limits = c(-0.2, 0.5),
       limits = c(-0.2, 0.5),
       label = scales::label_percent(accuracy = 1, trim = TRUE), #  prefix = " "),
       guide = guide_colourbar(
@@ -573,7 +565,7 @@ map_plot <- function(spec_results, spec_areas, colourPalette, colourPalette2) {
     )
 }
 
-p2final <- map_plot(tmp, areas_plot, colourPalette2, colourPalette) + 
+p2final <- map_plot(tmp, areas_plot, lake_vic, colourPalette2, colourPalette) + 
   ggtitle(main_title)
 
 
@@ -687,7 +679,7 @@ p3 <- plt_data %>%
     # y = 0.12,
     # y = 0.21,
     y = 0.01,
-    label = "non-VMMC \n Priority Countries",
+    label = "non-VMMC \nPriority Countries",
     fontface = "bold",
     size = 3.5, 
     hjust = 0
@@ -699,7 +691,7 @@ p3 <- plt_data %>%
     # y = 0.075,
     # y = 0.175,
     y = 0.01,
-    label = "VMMC \n Priority Countries",
+    label = "VMMC \nPriority Countries",
     fontface = "bold",
     size = 3.5, 
     hjust = 0
@@ -729,7 +721,7 @@ p3 <- plt_data %>%
   ) +
   labs(
[…]

### 2023-08-25 paper/paper.tex

@@
 
-"threemc" (Matt's model for male circumcision) (or "Multi-level model for male circumcision"?) is
-a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). We have extended
-this model from its initial application in South Africa to
-33
-countries within the SSA region.
+Following a similar approach to Thomas {\it et al.} \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision which uses a competing risk discrete time-to-event process stratified by region, age, time, and type.
+We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).
+
+In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+Some countries did not have any surveys that collected information on the type of circumcision (see Supplementary Material for more detail), so we were unable to conduct an analysis of the probabilities of circumcision by type.
+For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.
+
+% "threemc" (Matt's model for male circumcision) (or "Multi-level model for male circumcision"?) is
+% a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). We have extended
+% this model from its initial application in South Africa to
+% 33
+% countries within the SSA region.
 The model produces estimates of circumcision rates, incidence and coverage (i.e.
@@
 Circumcision rates are projected after their most recent household survey
-assuming continuation of estimated age-specific rates, with probabilistic uncertainty. Estimates
-for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
+% assuming continuation of estimated age-specific rates, with probabilistic uncertainty. Estimates
+% for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
 
-A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practises and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
+% A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practises and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
 MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the  main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
 
-Countries were modelled at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
+% Countries were modelled at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
 Model estimates were weighted by population and post-stratified to produce estimates for their "parent" regions.
 
-Some additional features were added to threemc during the course of this analysis: 
-\begin{itemize}
-\item Where no information on circumcision type was available for every survey in a given country, a type-agnostic version of the model was used,
-\item Survey estimates for less granular areas were used to inform likelihood estimation for their "child" areas, where previously they were ignored,
-\item optional addition of a temporal effect for TMC, due to the suggestion of survey estimates that TMC practices may be changing, even in non-VMMC target countries, over time, and
-\item an optional random walk (RW) temporal prior was implemented, where previously only an auto-regressive (AR1) temporal prior was available.
-\end{itemize}
+% Some additional features were added to threemc during the course of this analysis: 
+% \begin{itemize}
+% \item Where no information on circumcision type was available for every survey in a given country, a type-agnostic version of the model was used,
+% \item Survey estimates for less granular areas were used to inform likelihood estimation for their "child" areas, where previously they were ignored,
+% \item optional addition of a temporal effect for TMC, due to the suggestion of survey estimates that TMC practices may be changing, even in non-VMMC target countries, over time, and
+% \item an optional random walk (RW) temporal prior was implemented, where previously only an auto-regressive (AR1) temporal prior was available.
+% \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In our choice of model specification, we were interested in two main assumptions/features of the
-model:
-\begin{itemize}
-\item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
-\item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-If possible, we hoped to use the same model for every country, or failing that, come up with a
-satisfactory choice of model specification which would make sense both qualitatively and
-quantitatively.
+% In our choice of model specification, we were interested in two main assumptions/features of the
+% model:
+% \begin{itemize}
+% \item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
+% \item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
+% \end{itemize}
 
-Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
-In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
-Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
+% If possible, we hoped to use the same model for every country, or failing that, come up with a
+% satisfactory choice of model specification which would make sense both qualitatively and
+% quantitatively.
+
+% Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
+% In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
+% Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
 This suggests that MMCs in these countries are likely to be on paediatric individuals in traditional settings, so the assumption of constant and
-negligible paedaitric MMC could be a poor one. 
-Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
-It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
-patterns in non-VMMC countries.
+% negligible paedaitric MMC could be a poor one. 
+% Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
+% It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
+% patterns in non-VMMC countries.
 
-Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
-As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
-It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
-Historical TMC patterns in these countries, differ significantly, even subnationally.
-It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
-In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
-We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
+% Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
+% As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
+% It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
+% Historical TMC patterns in these countries, differ significantly, even subnationally.
+% It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
+% In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
+% We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
 
-We have also performed a quantitative analysis of the different model specifications available
-to us. A more detailed treatment of this can be found in section x of the appendix.
+% We have also performed a quantitative analysis of the different model specifications available
+% to us. A more detailed treatment of this can be found in section x of the appendix.
 
-For each country, we fit a model for each possible model specification for threemc, that is:
-\begin{itemize}
-\item for each choice of temporal prior, namely AR1, RW1 and RW2,
-\item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
-\item a choice of whether to include a temporal effect for TMC.
-\end{itemize}
-Thus totalling 12 possible models for each country.
-These models were fit to all of the survey data available, rather than a subset of the data.
-This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
-As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
+% For each country, we fit a model for each possible model specification for threemc, that is:
+% \begin{itemize}
+% \item for each choice of temporal prior, namely AR1, RW1 and RW2,
+% \item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
+% \item a choice of whether to include a temporal effect for TMC.
+% \end{itemize}
+% Thus totalling 12 possible models for each country.
+% These models were fit to all of the survey data available, rather than a subset of the data.
+% This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
+% As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
 
-The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
-Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
+% The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
+% Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
 
-Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
-Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
-This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
+% Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
+% Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
+% This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
 A "good" calibration was regarded as one in which roughly 50\% of survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range.
-Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
+% Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
 
-Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
+% Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
 
-For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
-The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
-This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
-It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
-Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
-These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
+% For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
+% The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
+% This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
+% It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
+% Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
+% These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
 
-In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
-This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
-However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
-As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
+% In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
+% This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
+% However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
+% As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
 
-Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
-In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
+% Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
+% In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
 For completeness, we decided to include a temporal effect for TMC in the model specification for VMMC priority countries.
 
-It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
-A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
+% It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
+% A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-For some VMMC priority countries, we did not have access to more recent survey data. 
-One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
-In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
-VMMC programme data was an available source of more recent circumcision data.
-The DMPPT2 model explicitly used this data to estimate MMC. 
-The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
-This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
-Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
-A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The two main drivers of uncertainty over time in threemc were:
-\begin{itemize}
-\item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
-\item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
-\end{itemize}
-The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
+% For some VMMC priority countries, we did not have access to more recent survey data. 
+% One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
+% In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
+% VMMC programme data was an available source of more recent circumcision data.
+% The DMPPT2 model explicitly used this data to estimate MMC. 
+% The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
+% This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
+% Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
+% A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
 
-Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
-One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
-To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
-A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
-For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
+% The two main drivers of uncertainty over time in threemc were:
+% \begin{itemize}
+% \item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
+% \item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
+% \end{itemize}
+% The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
 
-\todo{Finish this write up!}
-\todo{Add results! Also add ternary plot}
+% Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
+% One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
+% To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
+% A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
+% For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
+
+% \todo{Finish this write up!}
+% \todo{Add results! Also add ternary plot}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \label{sec:orgfc68fc8}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Our data consisted of 109 nationally representative household surveys conducted in 33 SSA countries between 2002 and 2019.
@@
 
-In addition to Botswana, Guinea-Bissau, Equitorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit threemc in these countries either.
+In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit threemc in these countries either.
 

### 2023-08-25 paper/scripts/032_results.R
Subnat plot: non-VMMC -> Non-VMMC, decrease point size, remove 90% x axis break

@@ -649,14 +649,12 @@ p3 <- plt_data %>%
   ) +
   scale_size_continuous(
     breaks = c(1, 10, 20), 
-    # limits = c(10, 50), 
-    # breaks = c(100, 200, 300), 
     labels = paste0(c(1, 10, 20), "x")
   ) +
   # add median national level to plot as white dots
   geom_point(
     data = filter(plt_data, area_level == 0),
-    size = 4.5, 
+    size = 4, 
     fill = "#F1F1F1",
     col = "black", 
     alpha = 1, 
@@ -675,21 +673,16 @@ p3 <- plt_data %>%
   # annotate plot with regional labels
   annotate(
     geom = "text",
-    x = c(length(plot_order) + 0.5),
-    # y = 0.12,
-    # y = 0.21,
+    x = c(length(plot_order) + 0.85),
     y = 0.01,
-    label = "non-VMMC \nPriority Countries",
+    label = "Non-VMMC \nPriority Countries",
     fontface = "bold",
     size = 3.5, 
     hjust = 0
   ) +
   annotate(
     geom = "text",
-    # x = c(length(plot_order) - (country_positions1 + 4)),
-    x = c(length(plot_order) - (country_positions1 + 4.5)),
-    # y = 0.075,
-    # y = 0.175,
+    x = c(length(plot_order) - (country_positions1 + 3.9)),
     y = 0.01,
     label = "VMMC \nPriority Countries",
     fontface = "bold",
@@ -706,12 +699,12 @@ p3 <- plt_data %>%
     expand = expansion(add = 0.6)
   ) +
   scale_y_continuous(
-    n.breaks = 6, 
-    breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1),
     expand = c(0, 0), 
     limits = c(0, 1), 
-    labels = scales::percent
-  ) +
+    label = scales::label_percent(),
+    breaks = seq(0, 1, by = 0.25), 
+    n.breaks = 5 
+  ) + 
   scale_size_continuous(
     breaks = c(1, 10, 20), 
     range = c(1, 12),
@@ -732,8 +725,8 @@ p3 <- plt_data %>%
   # )) + 
   scale_color_manual(values = wesanderson::wes_palette("Zissou1")[c(1, 4)]) +
   theme(
-    # axis.text.x = element_text(size = c(rep(12, 3), 15, 12)),
-    axis.text.x = element_text(size = c(rep(12, 4), 15, 12), colour = "black"),
[…]

### 2023-08-25 paper/scripts/032_results.R
Change plot: centre facet labels, make arrows smaller, make x-axis title bold

@@ -767,6 +767,9 @@ rm(p3); gc()
 
 #### Figure 4: Geofaceted plot for single ages ####
 
+# results_age <- readr::read_csv(
+#   "paper_poster_plots/paper/data/results_age.csv.gz"
+# )
 p4 <- plt_coverage_year_national_single_age(
   results_age  = results_age,
   areas        = areas,
@@ -1029,7 +1032,7 @@ p6 <- tmp_long %>%
       xend   = tmp_long_upper$country_idx,
       yend   = tmp_long_upper$value
     ), 
-    arrow = arrow(length = unit(0.2, "cm"), type = "closed"), 
+    arrow = arrow(length = unit(0.15, "cm"), type = "closed"), 
     size = 0.6
   ) +
   # add vline for VMMC - non-VMMC split
@@ -1074,11 +1077,13 @@ p6 <- tmp_long %>%
   # Altering plot text size
   theme(
     axis.text.x         = element_text(size = rel(1.2), colour = "black"),
-    axis.title.x        = element_text(size = rel(1.2), colour = "black"),
+    axis.title.x        = element_text(
+      size = rel(0.9), face = "bold", colour = "black", vjust = -1
+    ),
     axis.text.y         = element_text(size = rel(1.2), colour = "black"),
     axis.ticks.length.y = unit(5, "pt"), 
     strip.text          = element_text(
-      size = rel(0.9), face = "bold", colour = "black", hjust = 0
+      size = rel(0.9), face = "bold", colour = "black" #  , hjust = 0
     ),
     legend.text         = element_text(size = rel(1.2), colour = "black"),
     legend.position     = c(0.062, 0.9),

### 2023-08-25 paper/scripts/032_results.R
Map plot: fix borders not showing in % change facets of map plot

@@ -479,10 +479,40 @@ map_plot <- function(
   spec_results_change <- filter(spec_results, year == "% Change")
   spec_results_year <- filter(spec_results, year != "% Change")
   
-  p <- ggplot() +
+  ggplot() +
     geom_sf(
       data = spec_results_year,
       aes(fill = mean), 
+      size = 0.5,
+      colour = NA
+    ) +
+    labs(fill = "") +
+    scale_fill_gradientn(
+      colours = colourPalette,
+      na.value = "grey",
+      breaks = seq(0, 1, by = 0.1),
+      limits = c(0, 1),
+      label = scales::label_percent(accuracy = 1, trim = FALSE), 
+      guide = guide_colourbar(
+        # title = " Percent circumcised, 15–29 years",
+        title = paste0(" Percent circumcised, ", spec_age_group, " years"),
+        direction = "horizontal",
+        label = TRUE,
+        draw.ulim = TRUE,
+        draw.llim = TRUE,
+        frame.colour = "black",
+        ticks = TRUE,
+        barheight = 1,
+        barwidth = 17,
+        title.position = "bottom", 
+        plot.background = element_rect(fill = "white", colour = "white")
+      )
+    ) +
+    ggnewscale::new_scale_fill() +
+    # colour percentage change differently
+    geom_sf(
+      data = spec_results_change,
+      aes(fill = mean),
       size = 0.5,
       colour = NA
     ) +
@@ -499,43 +529,17 @@ map_plot <- function(
       size   = 0.5
     ) + 
     labs(fill = "") +
-    scale_fill_gradientn(
-      colours = colourPalette,
-      na.value = "grey",
-      breaks = seq(0, 1, by = 0.1),
-      limits = c(0, 1),
-      label = scales::label_percent(accuracy = 1, trim = FALSE), 
-      guide = guide_colourbar(
-        direction = "horizontal",
-        label = TRUE,
-        draw.ulim = TRUE,
-        draw.llim = TRUE,
-        frame.colour = "black",
-        ticks = TRUE,
-        barheight = 1,
-        # barwidth = 17, # may want this?
-        barwidth = 18,
-        title.position = "bottom", 
-        plot.background = element_rect(fill = "white", colour = "white")
-      )
-    ) +
-    ggnewscale::new_scale_fill() +
-    # colour percentage change differently
-    geom_sf(
-      data = spec_results_change,
[…]

### 2023-08-25 paper/scripts/032_results.R
Map plot: fix borders not showing in % change facets of map plot

@@ -94,7 +94,7 @@ colourPalette2 <- rev(colorRampPalette(
   c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#ffffbf",
     "#e6f598", "#abdda4", "#8CD1A4", "#66C2A4", "#3D94B7", "#2C82B7", "#13699e",
     "#5e4fa2")
-)(100))
+)(50))
 
 # change region changing from blue to grean to only blue
 # colourPalette[30:40] <- colourPalette[30]
@@ -104,8 +104,8 @@ colourPalette2 <- rev(colorRampPalette(
 # Colour Palette for years in map plot
 # colourPalette <- viridis::plasma(100)
 colourPalette <- c(
-  grDevices::colorRampPalette(c("blue","white"))(40), 
-  grDevices::colorRampPalette(c("white", "red"))(100)
+  grDevices::colorRampPalette(c("blue","white"))(20), 
+  grDevices::colorRampPalette(c("white", "red"))(50)
 )
 
 
@@ -555,7 +555,7 @@ map_plot <- function(
     theme_minimal(base_size = 9) +
     theme(
       strip.text    = element_text(size = rel(1.1), face = "bold"), 
-      legend.text   = element_text(size = rel(0.8)),
+      legend.text   = element_text(size = rel(0.75)),
       legend.title = element_text(size = rel(1.0), face = "bold", hjust = 0.5),
       axis.text       = element_blank(),
       axis.ticks      = element_blank(),

### 2023-08-25 paper/scripts/032_results.R
Geofaceted plot: ONly keep major x grids, add grey for missing countries

@@ -770,17 +770,6 @@ rm(p3); gc()
 # results_age <- readr::read_csv(
 #   "paper_poster_plots/paper/data/results_age.csv.gz"
 # )
-p4 <- plt_coverage_year_national_single_age(
-  results_age  = results_age,
-  areas        = areas,
-  last_surveys = last_surveys,
-  spec_ages    = 0:60,
-  spec_year    = last(spec_years),
-  spec_model   = "No program data",
-  main         = "",
-  # n_plots      = length(unique(results_agegroup$iso3))
-  n_plots      = length(unique(results_age$iso3))
-)[[1]]
 
 # grid for geofaceting, standardise country names
 ssa_grid <- geofacet::africa_countries_grid1 %>%
@@ -799,6 +788,20 @@ ssa_grid <- geofacet::africa_countries_grid1 %>%
   filter(
     name %in% c(ssa_countries, "Gin. Bissau", "Eq. Guinea", "Cent. Af. Rep.")
   )
+
+p4 <- plt_coverage_year_national_single_age(
+  results_age  = results_age,
+  areas        = areas,
+  last_surveys = last_surveys,
+  spec_ages    = 0:60,
+  spec_year    = last(spec_years),
+  spec_model   = "No program data",
+  main         = "", 
+  ssa_grid     = ssa_grid,
+  # n_plots      = length(unique(results_agegroup$iso3))
+  n_plots      = length(unique(results_age$iso3))
+)[[1]]
+
 
 # remove missing rows and columns (only looking at SSA, not all of Africa)
 min_row <- min(ssa_grid$row)
@@ -819,7 +822,9 @@ p4_geo <- p4 +
   # set theme and base size for text
   theme_bw(base_size = 9) + 
   # reduce x-axis ticks, too crowded
-  scale_x_continuous(breaks = seq(0, 60, by = 20)) + 
+  scale_x_continuous(
+    breaks = seq(0, 60, by = 20), limits = c(0, 60), expand = c(0, 0)
+  ) + 
   # remove x-axis
   # labs(y = "") +  
   labs(
@@ -839,10 +844,14 @@ p4_geo <- p4 +
     # legend.position = "bottom",
     legend.position = c(0.15, 0.2),
     # legend.justification = "left",
-    strip.text      = element_text(size = 7.5), # , hjust = -0.1),
+    # strip.text      = element_text(size = 7.5), # , hjust = -0.1),
+    strip.text      = element_text(size = 6.8, face = "bold"), # , hjust = -0.1),
[…]

### 2023-08-30 paper/scripts/032_results.R
Add age at circumcision plot

@@ -170,22 +170,42 @@ results_agegroup <- load_orderly_data(
   bind_rows()
 gc()
 
-# # most recent results for single ages
+# most recent results for single ages
 # results_age <- load_orderly_data(
 #   task = "02final_aggregations", 
 #   dirs = results_dirs[!is.na(results_dirs)],
-#   filenames = "Results_Age_Prevalence.csv.gz"
+#   # filenames = "Results_Age_Prevalence.csv.gz"
 # )$output %>% 
 #   bind_rows() %>% 
 #   filter(type %in% paste(c("MC", "MMC", "TMC"), "coverage"))
+# results_age <- readr::read_csv(
+#   "paper_poster_plots/paper/data/results_age.csv.gz"
+# )
 # gc()
-# 
+
+# incidence for age specific results
+# results_age_n_performed <- load_orderly_data(
+#   task = "02final_aggregations", 
+#   dirs = results_dirs[!is.na(results_dirs)],
+#   filenames = "Results_Age_Incidence.csv.gz"
+# )$output %>% 
+#   bind_rows() %>% 
+#   filter(type %in% paste0(c("MC", "MMC", "TMC"), "s performed"))
+# results_age_n_performed <- readr::read_csv(
+#   "paper_poster_plots/paper/data/results_age_n_performed.csv.gz"
+# )
+# gc()
+#  
 if (!"iso3" %in% names(results_agegroup)) {
   results_agegroup$iso3 <- substr(results_agegroup$area_id, 0, 3)
 }
-# 
 # if (!"iso3" %in% names(results_age)) {
 #   results_age$iso3 <- substr(results_age$area_id, 0, 3)
+# }
+# if (!"iso3" %in% names(results_age_n_performed)) {
+#   results_age_n_performed$iso3 <- substr(
+#     results_age_n_performed$area_id, 0, 3
+#   )
 # }
 
 # results_agegroup_n_circ <- readr::read_csv(file.path(
@@ -230,9 +250,9 @@ if (!"iso3" %in% names(results_agegroup)) {
 
 
 # VMMC iso3s not in results
-missing_iso3 <- target_iso3[!target_iso3 %in% results_agegroup$area_id]
+# missing_iso3 <- target_iso3[!target_iso3 %in% results_agegroup$area_id]
 # missing_iso3 <- target_iso3[!target_iso3 %in% results_age$area_id]
[…]

### 2023-08-30 paper/paper.tex
Updates from Overleaf

@@
 
-Following a similar approach to Thomas {\it et al.} \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision which uses a competing risk discrete time-to-event process stratified by region, age, time, and type.
+Following a similar approach to Thomas {\it et al.} \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision stratified by region, age, time, and type.
 We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).
@@
 In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+
+For the probability of TMC, a key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere.
+For example, in some countries the level and practices of TMC have changed through time due to demographic shifts.
+There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
+Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
+Here, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e.
+constant over time) and (ii) time variant (i.e.
+varying over time).
+The {\it time invariant} probability of TMC was modelled by a logit-linear function with random effects for age, district, as well as an age-district interaction, to allow for different patterns in the age at circumcision across districts.
+The {\it time variant} was also modelled by a logit-linear function with random effects for age, district, time, as well as age-district and age-time interaction, to allow for different patterns in the age at circumcision across space and time.
+We did not include a district-time interaction into due to computational constraints.
+
+The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention.
+VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
+Due to this, Thomas et al.
+\cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
+This ensured that any increase in MMC for those aged 10 and over did not bias the probability of MMC in those under 10 in South Africa.
+However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage.
+Therefore, we consider two models for the probability of MMC in each country: (i) no cut-off and (ii) paediatric cut off.
+
+We modelled probability of MMC with {\it no paediatric cut-off} was modelled using logit-linear function with random effects for age, time, and district, and interactions for district-time, age-time, and age-district, to allow for inter-district/time/age variation in circumcision rates.
+For the probability of MMC with {\it a paediatric cut-off}, the probability of paediatric MMC-nT was modelled using a logit-linear function with random effects for age, district, an age-district interaction, to allow for different practices of paediatric circumcision observed across districts.
+We assumed that the probability of paediatric MMC-nT was constant over time.
+The probability of adolescent and adult MMC-nT was also modelled using logit-linear function with random effects for age, time, and district, as well as all the associated two-way interactions to allow for inter-district/time/age variation in circumcision rates.
+To ensure the probability of MC (i.e.
+the sum of the probabilities of MMC and TMC) was not larger than one, we applied the probability of TMC before MMC in each time step.
+
+Whether a country used (i) a time-invariant or time-variant probability of TMC and (i) a paediatric cut-off or no cut-off in the probability of MMC, was decided based on which produced the best within-sample model fit (see Section XX for further details).
+
 Some countries did not have any surveys that collected information on the type of circumcision (see Supplementary Material for more detail), so we were unable to conduct an analysis of the probabilities of circumcision by type.
 For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.
+We used survey data to model the probability of MC directly, using a discrete time-to-event process.
+We modelled probability of MC using logit-linear function with random effects for age, time, and district, as well as the associated two-way interactions to allow for inter-district/time/age variation in MC rates.
 
-% "threemc" (Matt's model for male circumcision) (or "Multi-level model for male circumcision"?) is
-% a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). We have extended
-% this model from its initial application in South Africa to
-% 33
-% countries within the SSA region.
-The model produces estimates of circumcision rates, incidence and coverage (i.e.
-cumulative indidence), with associated uncertainty bounds, stratified by type, year, age and location.
-Circumcision rates are projected after their most recent household survey
-% assuming continuation of estimated age-specific rates, with probabilistic uncertainty. Estimates
-% for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
+We calculated the estimated circumcision coverage by type (MMC/TMC/MC) within each cohort using the cumulative incidence function, which defines the marginal probability (or proportion/coverage of) individuals who were received an MMC, TMC, or MC by district, age and time, whilst accounting for the competing risk of other circumcision type.
 
-% A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practises and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
-MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the  main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
+Prior distributions were specified on all model parameters and were specified to allow areas, with little to no data, to borrow district-age-time information on circumcision.
+Furthermore, we wanted to ensure any correlation in circumcision practices across district, age and time was modelled.
+We assigned intrinsic conditional autoregressive (ICAR) priors to the district random effects, and penalised B-spline functions on the age random effects.
+The temporal random effects were assigned one of three potential priors in each country: an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2).
+The choice of whether a country uses a AR1, RW1 and RW2 as a temporal prior was chosen depending on which produced the best out-of-sample model fit during model calibration (see Section XX for further details).
+The age-space, age-time, and space-time interaction terms were modelled as Type IV interactions as defined by Knorr-Held and Leonard, where precision matrices were constructed through Kronecker products.
+Vague Gaussian priors were assigned to each of the intercepts, and Gaussian priors were specified for all correlation parameters on the logit scale, such that a priori there was 95\% probability that the autocorrelation parameters on AR1 processes were between 0.48 and 0.99 on the real scale.
+We assigned exponential priors on standard deviations parameters, with the same hyperparameters for the age, district and age-district random effects.
+For the time, age-time and space-time random effects, the hyperparameters on the exponential priors were decided during model calibration (see Section XX for further details).
 
-% Countries were modelled at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.
-Model estimates were weighted by population and post-stratified to produce estimates for their "parent" regions.
-
-% Some additional features were added to threemc during the course of this analysis: 
-% \begin{itemize}
-% \item Where no information on circumcision type was available for every survey in a given country, a type-agnostic version of the model was used,
-% \item Survey estimates for less granular areas were used to inform likelihood estimation for their "child" areas, where previously they were ignored,
-% \item optional addition of a temporal effect for TMC, due to the suggestion of survey estimates that TMC practices may be changing, even in non-VMMC target countries, over time, and
-% \item an optional random walk (RW) temporal prior was implemented, where previously only an auto-regressive (AR1) temporal prior was available.
-% \end{itemize}
+Technical details of the model are in Supplementary Materials.
 
@@
 
-\subsection{Comparison to results of DMPPT2 model}
-\label{sec:orge0178ca}
-
-TODO: Write this section!
+% \subsection{Comparison to results of DMPPT2 model}
+% \label{sec:orge0178ca}
+% 
+% TODO: Write this section!
 
@@
 
-In the majority of VMMC countries, the results of threemc and DMPPT2 largely agree. 
-However, for several countries, namely Tanzania, Zimbabwe and parts of Kenya, we can see that DMPPT2 estimates far exceed empirical survey and threemc estimates, and indeed the population of many districts, suggesting that they may be adversely affected by
-\begin{enumerate}
-\item people travelling from their home districts to others to avail of VMMC programmes, and
-\item ii) possible misreporting occurring in programmatic data due to incentives to report higher numbers of circumcisions for VMMC clinics.
-\end{enumerate}
-Where it is desired to incorporate VMMC programme data in estimates of MC coverage, threemc may provide a useful "baseline" circumcision estimate for DMPPT2 up until the last household survey was performed, with programme data taking over as the main data source thereafter.
-threemc may also complement DMPPT2 in it's inclusion of estimates for TMC, since DMPPT2 and the programme data only concern MMC.
+% In the majority of VMMC countries, the results of threemc and DMPPT2 largely agree. 
+% However, for several countries, namely Tanzania, Zimbabwe and parts of Kenya, we can see that DMPPT2 estimates far exceed empirical survey and threemc estimates, and indeed the population of many districts, suggesting that they may be adversely affected by
+% \begin{enumerate}
+% \item people travelling from their home districts to others to avail of VMMC programmes, and
+% \item ii) possible misreporting occurring in programmatic data due to incentives to report higher numbers of circumcisions for VMMC clinics.
+% \end{enumerate}
+% Where it is desired to incorporate VMMC programme data in estimates of MC coverage, threemc may provide a useful "baseline" circumcision estimate for DMPPT2 up until the last household survey was performed, with programme data taking over as the main data source thereafter.
+% threemc may also complement DMPPT2 in it's inclusion of estimates for TMC, since DMPPT2 and the programme data only concern MMC.
 
-There were several limitations inherint in the threemc model, and in this analysis. 
+There were several limitations inherent in the threemc model, and in this analysis. 
 TODO: Write these out!

### 2023-08-30 paper/supp_figs.tex

--- 2023-08-22 paper/supp_figs.tex
@@
       \\[-3pt] \hline
-      \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country.
-Surveys which did not include a "Circumcision Status" and "Age at Circumcision" question could not be used, while circumcision type could not be inferred from surveys which did not have a "Who performed the circumcision" and/or "Where was the circumcision performed" question.}
       \endfoot
@@
 & 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Burkina Faso}} \\ 
-& 2003 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Burundi}} \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Cameroon}} \\ 
-& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Central African Republic}} \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Chad}} \\ 
-& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Congo - Kinshasa}} \\ 
-& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Côte d’Ivoire}} \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Eswatini}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
-& 2010 (MICS) & \checkmark & \checkmark & \xmark & \xmark \\ 
-& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Ethiopia}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Gabon}} \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Gambia}} \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Ghana}} \\ 
-& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Guinea}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Guinea-Bissau}} \\ 
-& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Kenya}} \\ 
-& 2003 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2014 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Lesotho}} \\ 
-& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2009 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
-& 2014 (DHS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Liberia}} \\ 
-& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Malawi}} \\ 
-& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2013 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Mali}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Mozambique}} \\ 
-& 2003 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2009 (AIS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Namibia}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \checkmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Niger}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Nigeria}} \\ 
-& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Repulic of the Congo}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2009 (AIS) & \checkmark & \xmark & \checkmark & \xmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Rwanda}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2008 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Senegal}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Sierra Leone}} \\ 
-& 2008 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{South Africa}} \\ 
-& 2002 (HSRC) & \checkmark & \checkmark & \xmark & \checkmark \\ 
-& 2008 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2012 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Tanzania}} \\ 
-& 2003 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2004 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2007 (AIS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2012 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Togo}} \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Uganda}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2011 (AIS) & \checkmark & \checkmark & \xmark & \checkmark \\ 
-& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Zambia}} \\ 
-& 2007 (DHS) & \checkmark & \checkmark & \xmark & \xmark \\ 
-& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\ 
-& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Zimbabwe}} \\ 
-& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark 
 \end{longtable}
 }
+
+\begin{landscape}
+\include{paper/figures/supp_figs/Survey_Table}
+\end{landscape}
 
@@
 
-Gaussian priors were assigned to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$. Gaussian priors were set for all correlation parameters on the logit scale, such that 
+Gaussian priors were assigned to each of the intercepts, $\alpha, \;\hat{\alpha}, \;\bar{\alpha} \sim N(0, 5^2)$. Gaussian priors were set for any correlation parameters on the logit scale, such that 
 \begin{align*} 

### 2023-08-31 paper/scripts/032_results.R
Add scatter plot to map plot of age at circ

@@ -902,6 +902,7 @@ mean_circ_age <- calc_circ_age_ridge(
   results_age_n_performed,
   areas,
   spec_years = spec_years[[2]],
+  # spec_years = 2000,
   area_levels = unique(results_age_n_performed$area_level),
   spec_model = "No program data",
   spec_ages = 0:60, 
@@ -1003,51 +1004,47 @@ tmp <- tmp %>%
 spec_results <- tmp
 spec_areas <- areas_plot
 
-rm(mean_circ_age, areas1); gc()
+# rm(mean_circ_age, areas1); gc()
    
 map_plot_circ_age <- function(
-    spec_results, spec_areas, lake_vic, colourPalette
+    spec_results, spec_areas, lake_vic, colourPalette, n_breaks = 3
   ) {
   
   levs = c("Total", "Medical", "Traditional")
   levs <- levs[levs %in% spec_results$type]
   
+  stopifnot(n_breaks %in% c(3, 6))
+  
   spec_results$type <- factor(spec_results$type, levels = levs)
   
-  # spec_results_change <- filter(spec_results, year == "% Change")
-  # spec_results_year <- filter(spec_results, year != "% Change")
+  spec_results$mean_f <- cut(spec_results$mean, n_breaks)
+  if (n_breaks == 3) {
+    levels(spec_results$mean_f) <- c("0-10", "11-20", "> 20")
+  } else {
+    levels(spec_results$mean_f) <- c(
+      "0-5", "6-10", "11-15", "16-20", "21-25", "> 25"
+    )
+  }
+  
+  if (is.function(colourPalette)) {
+    cols <- colourPalette(n_breaks)
+  } else cols <- colourPalette
+  names(cols) = levels(spec_results$mean_f)
   
   ggplot() +
     geom_sf(
       data = spec_results, # spec_results_year,
-      aes(fill = mean), 
+      aes(fill = mean_f), 
       size = 0.5,
       colour = NA
     ) +
     labs(fill = "") +
-    scale_fill_gradientn(
-      colours = colourPalette,
-      na.value = "grey",
-      # breaks = seq(0, 60, by = 10),
-      breaks = seq(0, 30, by = 5), # average age at circ < 30
-      # limits = c(0, 60),
-      limits = c(0, 30),
-      # label = scales::label_percent(accuracy = 1, trim = FALSE), 
-      guide = guide_colourbar(
[…]

### 2023-08-31 paper/scripts/032_results.R
Make circ age plot taller

@@ -19,6 +19,7 @@ library(ggsci)
 library(geofacet)
 library(glue)
 library(ggtext)
+library(cowplot)
 source("Shiny/src/functions.R") # plotting functions
 source("paper_poster_plots/paper/scripts/00_funs.R")
 
@@ -1165,7 +1166,7 @@ p5_scatter <- sf::st_drop_geometry(tmp) %>%
 ggsave(
   "paper_poster_plots/paper/plots/05_map_plot_mean_circ_age.png", 
   # p5,
-  cowplot::plot_grid(plotlist = list(p5, p5_scatter), ncol = 1),
+  plot_grid(plotlist = list(p5, p5_scatter), ncol = 1),
   width = 6.3, 
   height = 9, 
   units = "in"

### 2023-08-31 paper/paper.tex
Add section on age at circumcision, still to be filled in
Updates from Overleaf

@@
 
+\subsection{Subnational Heterogeneity in Age at Medical and Traditional Circumcision}
+\label{sec:org92e0f37}
+
+Fill in! Take some of the last section and put it here.
+
+% Geofaceted plot of 2020 coverage by age
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=.9\linewidth]
+    {plots/05_map_plot_mean_circ_age.png}
+    \caption{\emph{(A) Estimated distinct-level age at circumcision in 2020 in 33 sub-Saharan African countries.
+Maps show mean medical male circumcision (MMC) and mean traditional male circumcision (TMC) age.
+Countries without estimates are in grey.
+Mean circumcision ages are binned into three distinct groups: 0-10, 11-20 and over 20.
+(B) Scatterplot of district-level mean traditional male circumcision age versus mean medical male circumcision age.
+A diagonal dashed line passes through the origin and (30, 30).
+Points representing each district are coloured by whether their country is a Voluntary Male Medical Circumcision (VMMC) priority country.}}
+\end{figure}
+
+% stimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years.
+Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively.
+Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all
+
 \subsection{Decrease in TMC in SSA region Over Time}

### 2023-08-31 paper/scripts/032_results.R
Change circ age plot

@@ -1166,9 +1166,10 @@ p5_scatter <- sf::st_drop_geometry(tmp) %>%
 ggsave(
   "paper_poster_plots/paper/plots/05_map_plot_mean_circ_age.png", 
   # p5,
-  plot_grid(plotlist = list(p5, p5_scatter), ncol = 1),
+  plot_grid(plotlist = list(p5, p5_scatter), ncol = 1, rel_heights = c(1.2, 1)),
   width = 6.3, 
-  height = 9, 
+  # height = 10, 
+  height = 8, 
   units = "in"
 )
 

### 2023-08-31 paper/scripts/032_results.R
Change circ age plot

@@ -1113,7 +1113,7 @@ p5_scatter <- sf::st_drop_geometry(tmp) %>%
   # scale_colour_tron() + 
   labs(
     x = "Mean medical circumcision age, 2020",
-    y = "Mean traditional circumcision age, 2020", 
+    y = "Mean traditional circumcision age", 
     colour = "", 
     tag = "B"
   ) + 
@@ -1129,9 +1129,9 @@ p5_scatter <- sf::st_drop_geometry(tmp) %>%
   theme_bw(base_size = 9) + 
   theme(
     axis.text.x       = element_text(size = rel(1.6), colour = "black"),
-    axis.title.x      = element_text(size = rel(1.4), face = "bold"),
+    axis.title.x      = element_text(size = rel(1.3), face = "bold"),
     axis.text.y       = element_text(size = rel(1.6), colour = "black"), 
-    axis.title.y      = element_text(size = rel(1.4), face = "bold"),
+    axis.title.y      = element_text(size = rel(1.3), face = "bold"),
     legend.text       = element_text(size = rel(1.5), colour = "black"),
     legend.position   = c(0.15, 0.8),
     # remove white box behind legend
@@ -1166,7 +1166,7 @@ p5_scatter <- sf::st_drop_geometry(tmp) %>%
 ggsave(
   "paper_poster_plots/paper/plots/05_map_plot_mean_circ_age.png", 
   # p5,
-  plot_grid(plotlist = list(p5, p5_scatter), ncol = 1, rel_heights = c(1.2, 1)),
+  plot_grid(plotlist = list(p5, p5_scatter), ncol = 1, rel_heights = c(1.3, 1)),
   width = 6.3, 
   # height = 10, 
   height = 8, 

### 2023-08-31 paper/scripts/032_results.R
Change circ age plot; move legend of map closer

@@ -1075,7 +1075,9 @@ map_plot_circ_age <- function(
       plot.tag          = element_text(size = rel(2), face = "bold"),
       plot.tag.position = c(0.1, 1),
       # add margin to remove grey spaces in combined plots
-      plot.margin     = unit(c(1.1, 0, 1.1, 0), "cm")
+      plot.margin     = unit(c(1.1, 0, 1.1, 0), "cm"),
+      # move legend items closer together
+      legend.spacing.x = unit(0.1, "cm")
     )
 }
 
@@ -1085,10 +1087,11 @@ p5 <- map_plot_circ_age(
   rev(wesanderson::wes_palette("Darjeeling1", 3)),
   3
 )
-
-# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
 # p5
-# dev.off()
+
+dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
+p5
+dev.off()
 
 # save object for org-mode paper draft
 # saveRDS(

### 2023-09-01 paper/scripts/031_results_data.R
Update surey table plot to be stratified by VMMC status, rather than SSA region

@@ -51,6 +51,13 @@ ssa_iso3 <- sort(c(
   "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
 ))
 
+# VMMC countries  
+vmmc_iso3 <- c(
+  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA"
+)
+vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
+
 # countries for which we have no results
 no_mod_iso3 <- c("BWA", "CAF", "GNB")
 
@@ -65,6 +72,18 @@ country_name_convention <- function(x) {
   )
 }
 ssa_countries <- country_name_convention(ssa_countries)
+
+# order to plot countries in; first non-VMMC, then VMMC
+# Note: This includes countries not modelled as well 
+plot_order <- c(
+  "BEN", "BFA", "CIV", "GHA", "GIN", "GNB", "LBR", "MLI", "NER", 
+  "NGA", "SEN", "SLE", "GMB", "TGO", "AGO", "CMR", "CAF", "TCD", 
+  "COG", "COD", "GAB", "BDI", "ETH", "KEN", "MWI", "MOZ", "RWA", 
+  "TZA", "UGA", "ZMB", "ZWE", "BWA", "SWZ", "LSO", "NAM", "ZAF"
+)
+
+# where to add horizontal line for VMMC vs non-VMMC
+country_positions <- length(vmmc_iso3) + 1
 
 
 #### Load Data ####
@@ -105,7 +124,7 @@ populations <- load_archive(
 last_surveys <- readr::read_csv("global/most_recent_surveys.csv")
 
 # Prepare circ data, normalise survey weights and apply Kish coefficients.
-survey_circumcision <- prepare_survey_data(
+survey_circumcision <- bind_rows(prepare_survey_data(
   areas               = areas,
   survey_circumcision = select(survey_circumcision, -matches("area_level")),
   area_lev            = threemc::datapack_psnu_area_level,
@@ -114,9 +133,27 @@ survey_circumcision <- prepare_survey_data(
   cens_age            = cens_age,
   rm_missing_type     = rm_missing_type,
   norm_kisk_weights   = TRUE
-)
+))
 
-survey_circumcision <- data.table::rbindlist(survey_circumcision)
[…]

### 2023-09-01 paper/scripts/032_results.R
Tidy up code

@@ -592,10 +592,10 @@ p2final <- map_plot(tmp, areas_plot, lake_vic, colourPalette2, colourPalette)
 
 
 # save object for org-mode paper draft
-# saveRDS(
-#   p2final,
-#   "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
-# )
+saveRDS(
+  p2final,
+  "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
+)
 
 # dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
 # p2final
@@ -769,7 +769,7 @@ p3 <- plt_data %>%
 # p3
 # dev.off()
 
-# saveRDS(p3, "paper_poster_plots/paper/plots/03_subnat_plot.RDS")
+saveRDS(p3, "paper_poster_plots/paper/plots/03_subnat_plot.RDS")
 ggplot2::ggsave(
   "paper_poster_plots/paper/plots/03_subnat_plot.png", 
   p3, 
@@ -876,12 +876,11 @@ p4_geo <- p4 +
     panel.grid.major.y = element_blank()
   )
 
-# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
 # dev.new(width = 6.3, height = 8,  noRStudioGD = TRUE)
 # p4_geo
 # dev.off()
 
-# saveRDS(p4_geo, "paper_poster_plots/paper/plots/04_geo_age.RDS")
+saveRDS(p4_geo, "paper_poster_plots/paper/plots/04_geo_age.RDS")
 ggplot2::ggsave(
   "paper_poster_plots/paper/plots/04_geo_age.png", 
   p4_geo, 
@@ -1089,15 +1088,9 @@ p5 <- map_plot_circ_age(
 )
 # p5
 
-dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
-p5
-dev.off()
-
-# save object for org-mode paper draft
-# saveRDS(
-#   p5,
-#   "paper_poster_plots/paper/plots/05_map_plot_mean_circ_age.RDS"
-# )
+# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
+# p5
+# dev.off()
 
 # scatter plot of TMC vs MMC for districts
 p5_scatter <- sf::st_drop_geometry(tmp) %>% 
[…]

### 2023-09-01 paper/scripts/020_methods_data.R
Add logicals, as per Matt's request

@@ -273,6 +273,7 @@ types <- survey_circumcision %>%
 
 # now join together!
 table3 <- cbind(survey_names, sample_sizes, cens, types) %>% 
+  # arrange(survey_id) %>% 
   # select(-c(survey_id, n_orig)) %>% 
   select(-survey_id) %>% 
   # remove questions about circ type; unneeded
@@ -295,5 +296,21 @@ table3 <- cbind(survey_names, sample_sizes, cens, types) %>%
     "Known Circumcision Type"      = known_type
   )
 
+# add logicals in
+table3 <- table3 %>% 
+  bind_cols(
+    table1 %>% 
+      arrange(survey_id) %>% 
+      select(-survey_id) %>% 
+      mutate(across(contains("circ"), ~ ifelse(. == "[/]xmark", FALSE, TRUE)))
+  ) %>% 
+  relocate(contains("circ_"), .after = "Series") %>% 
+  rename(
+    "Circumcision Status" = circ_status,
+    "Age at Circumcision" = circ_age,
+    "Who performed?"      = circ_who, 
+    "Where performed?"    = circ_where
+  )
+
 # tabulate and export to Latex (to do!)
-readr::write_csv(table3)
+readr::write_csv(table3, "circ_table.csv")

### 2023-09-01 paper/scripts/031_results_data.R
Survey table: Move VMMC labels down slightly

@@ -364,7 +364,7 @@ p1 <- fig1data %>%
   annotate(
     geom = "text",
     x = 1999.2,
-    y = c(length(plot_order) - 0.07),
+    y = c(length(plot_order) - 0.2),
     # y = c(length(plot_order) + ),
     label = "Non-VMMC \nPriority \nCountries",
     fontface = "bold",
@@ -375,7 +375,7 @@ p1 <- fig1data %>%
     geom = "text",
     x = 1999.2,
     # y =  c(length(plot_order) - (country_positions + 3.9)),
-    y =  c(length(plot_order) - (country_positions + 7.7)),
+    y =  c(length(plot_order) - (country_positions + 7.9)),
     label = "VMMC \nPriority \nCountries",
     # angle = 270,
     fontface = "bold",

### 2023-09-01 paper/scripts/032_results.R
Add GHA and COD to plots

@@ -173,16 +173,16 @@ gc()
 
 # most recent results for single ages
 # results_age <- load_orderly_data(
-#   task = "02final_aggregations", 
+#   task = "02final_aggregations",
 #   dirs = results_dirs[!is.na(results_dirs)],
-#   # filenames = "Results_Age_Prevalence.csv.gz"
-# )$output %>% 
-#   bind_rows() %>% 
+#   filenames = "Results_Age_Prevalence.csv.gz"
+# )$output %>%
+#   bind_rows() %>%
 #   filter(type %in% paste(c("MC", "MMC", "TMC"), "coverage"))
 # results_age <- readr::read_csv(
 #   "paper_poster_plots/paper/data/results_age.csv.gz"
 # )
-# gc()
+gc()
 
 # incidence for age specific results
 # results_age_n_performed <- load_orderly_data(
@@ -196,7 +196,7 @@ gc()
 #   "paper_poster_plots/paper/data/results_age_n_performed.csv.gz"
 # )
 # gc()
-#  
+  
 if (!"iso3" %in% names(results_agegroup)) {
   results_agegroup$iso3 <- substr(results_agegroup$area_id, 0, 3)
 }
@@ -590,16 +590,15 @@ map_plot <- function(
 
 p2final <- map_plot(tmp, areas_plot, lake_vic, colourPalette2, colourPalette)
 
+# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
+# p2final
+# dev.off()
 
 # save object for org-mode paper draft
 saveRDS(
   p2final,
   "paper_poster_plots/paper/plots/02_map_plot_facet.RDS"
 )
-
-# dev.new(width = 6.3, height = 6.5,  noRStudioGD = TRUE)
-# p2final
-# dev.off()
 
 # save plots
 ggsave(
@@ -696,15 +695,17 @@ p3 <- plt_data %>%
   annotate(
     geom = "text",
     x = c(length(plot_order) + 0.85),
+    # x = c(length(plot_order) + 0.3),
     y = 0.01,
-    label = "Non-VMMC \nPriority Countries",
+    label = "Non-VMMC Priority \nCountries",
     fontface = "bold",
     size = 3.5, 
     hjust = 0
   ) +
   annotate(
     geom = "text",
-    x = c(length(plot_order) - (country_positions1 + 3.9)),
+    # x = c(length(plot_order) - (country_positions1 + 3.9)),
[…]

### 2023-09-01 paper/scripts/033_results_rerender_plots.R
Script to re-render plots on Windows

@@ -1,0 +1,77 @@
+#### Load RDS files, create plots ####
+
+# This avoids issues with linux rendering of plots
+
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+
+# Figure 1: Survey table
+p1 <- readRDS("paper_poster_plots/paper/plots/01_survey_table.png")
+ggplot2::ggsave(
+  "paper_poster_plots/paper/plots/01_survey_table.png", 
+  p1, 
+  width = 6.3, 
+  height = 8,
+  units = "in"
+)
+
+# Figure 2: Coverage Map 
+p2final <- readRDS("paper_poster_plots/paper/plots/02_map_plot_facet.RDS")
+ggsave(
+  "paper_poster_plots/paper/plots/02_map_plot_facet.png", 
+  p2final,
+  width = 6.3, 
+  height = 6.5, 
+  units = "in"
+)
+
+# Figure 3: Subnational coverage variation
+p3 <- readRDS("paper_poster_plots/paper/plots/03_subnat_plot.RDS")
+ggplot2::ggsave(
+  "paper_poster_plots/paper/plots/03_subnat_plot.png", 
+  p3, 
+  width = 6.3, 
+  height = 8,
+  units = "in"
+)
+
+# Figure 4: Geofacet of coverage by age
+p4_geo <- readRDS("paper_poster_plots/paper/plots/04_geo_age.RDS")
+ggplot2::ggsave(
+  "paper_poster_plots/paper/plots/04_geo_age.png", 
+  p4_geo, 
+  width = 6.3, 
+  height = 8,
+  units = "in"
+)
+
+# Figure 5: Map & scatter of mean age at circumcision
+p5 <- readRDS(
+  "paper_poster_plots/paper/plots/051_map_plot_mean_circ_age_map.RDS"
+)
+p5_scatter <- saveRDS(
+  "paper_poster_plots/paper/plots/052_map_plot_mean_circ_age_scatter.RDS"
+)
+ggsave(
+  "paper_poster_plots/paper/plots/05_map_plot_mean_circ_age.png", 
+  # p5,
+  plot_grid(
+    plotlist = list(p5, p5_scatter), ncol = 1, rel_heights = c(1.3, 1)
+  ),
+  width = 6.3, 
+  height = 8, 
+  units = "in"
+)
+
+# Figure 6: 
+p6 <- readRDS("paper_poster_plots/paper/plots/06_change_00_20.RDS")
[…]

### 2023-09-01 paper/scripts/032_results.R
Add GHA and COD to plots

@@ -1289,8 +1289,9 @@ tmp <- tmp %>%
 
 annotate_df <- data.frame(
   country_idx = c(
-    c(length(plot_order) + 0.5),
-    c(length(plot_order) - (country_positions1 + 4))
+    c(length(plot_order) + 0.6),
+    # c(length(plot_order) - (country_positions1 + 4))
+    c(length(plot_order) - (country_positions1 + 6))
   ),
   # value = c(0.24, 0.14), 
   value = c(0.05, 0.04), 

### 2023-09-26 paper/model_spec_ppcs_tables.tex

\documentclass{article}

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{array}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

\begin{document}

\section{Model Specification}
\label{sec:org8802288}

\subsection{non-VMMC countries}
\label{sec:org09db5e8}

%% Notes on Table

Some very rough notes on results of table below:

Nomenclature:
Time-invariant, No cut-off model: Neither
Time-invariant, paed cut-off model: Paed cut-off
Time-variant, No cut-off model: Time TMC
Time-variant, paed cut-off model: Both

\textbf{AR1}
\begin{itemize}
    \item MC: CPRS lowest for Both, RMSE lowest for Time TMC, 50\% CI closest to 50\% for Time TMC, 80\% CI closest for Neither, and 95\% CI closest for Both.
    \item MMC: CRPS and RMSE lowest for Neither, 50\% CI closest for Neither, 80\% & 95\% CI closest for time TMC
    \item TMC: Same as MMC, but 50\% CI best for Paed Cutoff 
    \item Conclusions:
    \begin{itemize}
        \item MC: Fairly inconclusive, but for most summary statistics (except 80\% CI, fairly narrowly) a model which includes a time TMC component is preferred. Choosing between "Both" and "Time TMC", it appears that Time TMC has noticeably worse CRPS, 80\% and 95\% coverage, and only marginally better RMSE and 50\% coverage, so the best model for MC appears to be "Both".
        \item MMC (\& TMC): "Neither" model seems to be narrowly favoured for MMC and tied for TMC with Time TMC for type-specific circumcision, particularly for mean fit statistics. Strange in that this seems to only be the case for the AR1 temporal prior. Comparing values, mean fit statistics were certainly better for "Neither". While we would like our model to be well calibrated, having the best 95\% CI is probably most important in terms of coverage, and the "Time TMC" model has much better 95\% coverage (85.45 vs 89.95 for MMC, 85.49 vs 91.38 for TMC) (and 80\% covergae, at 71.77 vs 78.35 for MMC and 72.50 vs 80.30 for TMC), so Time TMC is the much better model here in terms of the overall coverage of the model. 
    \end{itemize}
    \item Final Choice: As Time TMC is one of or the most favoured model for all circumcision types for the AR1 temporal prior, it appears to be the best choice of model across all types. 
\end{itemize}

\vspace{\bigskipamount}

\textbf{RW1}

\begin{itemize}
    \item MC: CRPS and RMSE lowest for Both (but very narrowly better than Time TMC model), 50\% coverage best for Time TMC, 80\% coverage best for Both, 95\% coverage best for Paed cutoff (by quite a bit!)
    \item MMC \& TMC: CRPS and RMSE lowest for Both (again, narrowly better than Time TMC), 50\% coverage best for Neither, 80\% and 95\% coverage best for Time TMC. 
    \item Conclusions:
    \begin{itemize}
        \item MC: Also inconclusive, mean fit statistics narrowly best and 90\% coverage considerably better for "Both" model than "Time TMC", so best model here is "Both". 
        \item MMC \& TMC: Similar to AR1 temporal prior, Both model narrowly better for mean fit statistics than Time TMC, but Time TMC has far better coverage (95\% coverage is 90.66 vs 80.87 for MMC and 92.17 vs 81.59 for TMC, so much better), and so Time TMC is the best model here.
    \end{itemize}
    \item Final Choice: "Both" is narrowly favoured for MC over Time TMC, while Time TMC is better for MMC and TMC, so best model choice here across all types is "Time TMC". 
\end{itemize}

\vspace{\bigskipamount}

\textbf{RW2}
\begin{itemize}
    \item MC: CRPS, RMSE, 50\% CI best for Time TMC, 80\% covreage best for Neither (very well calibrated at 79.77), 95\% coverage best for Both (although all models have pretty good coverage here, with the lowest being Time TMC at 86.79). 
    \item MMC \& TMC: CPRS \& RMSE best for Time TMC (as in MC as well), 50\% coverage best for "Neither", 80\% and 95\% coverage best for Time TMC.
    \item Conclusions:
      \begin{itemize}
          \item MC: Fit statistics best for Time TMC, with CRPS in particular being by far the lowest (53.68 vs the next lowest 74.41 for "Both") (may be a mistake?). Although other models have higher 80\% and 95\% coverage, there is not enough of a difference in coverage to ignore this glaring difference in CRPS, so the "Time TMC" model is probably best here. 
          \item MMC \& TMC: Time TMC model best for all but 50\% coverage, so Time TMC is clearly the preferred model.
      \end{itemize}
    \item Final Choice: Time TMC clearly the best model. Interesting that for the RW2 temporal prior we get the behaviour that perhaps we most expected to get for all models, with the "Time TMC" model giving both better mean fit statistics and also posterior predictive coverage, across all circumcision types. 
\end{itemize}

\vspace{\bigskipamount}

\textbf{So seems the best model across all temporal priors and circumcision types is the model which has time-variant TMC and no paediatric cut-off for TMC (i.e. the "Time TMC" model)}

\vspace{\bigskipamount}

\textbf{Other Notes on non-VMMC}:
\begin{itemize}
    \item Seems to be a pattern emerging whereby including a peadiatric age cutoff vs not improves mean fit statistics (i.e. CRPS \& RMSE), at the loss of posterior predictive coverage (this is bucked for RW2 temporal prior, however, where we see more "expected" behaviour, with the "Time TMC" model having lower CRPS and RMSE than "Both"). 
    \item However, the inclusion of a Time TMC component is routinely preferred, in agreement with our qualitative analysis of the different model specifications 
    \item Again, important to note that we don't have survey data on < 15 year olds, so perhaps the value of including a paediatric age cutoff for MMC isn't identifiable here?
    \item Wanted to choose these models based mainly on mean fit statistics and not posterior predictive coverage, but the choice of model via CRPS and RMSE, usually "Both", doesn't necessarily agree with our qualitative choice of "Time TMC", while the choice of model via coverage is Time TMC (again, this is for AR1 and RW1, not the RW2 temporal prior). Not sure if I'm being very biased in choosing the model I think makes the most sense qualitatively (and also "looked" the best in graphical comparisons of model fit to survey points) in this supposedly quantitative analysis of the different model specifications!!

\end{itemize}

%% Model Specification Table 1: Non-VMMC countries %%
\begin{landscape}

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.75cm} 
     >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-15} 
  & & & \multicolumn{6}{c}{\bf Time invariant} & 
      \multicolumn{6}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-9} 
  \cmidrule(lr){10-15} 
  & {\bf MMC Model} & {\bf Type} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
  \hline 
AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
 RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
 RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total 
             male circumcision (MC), medical male circumcision (MMC) and 
             traditional male circumcision (TMC) from fitting the 12 candidate 
             models and taking the median value across all Non-VMMC countries. Combinations include 
             (i) Time invariant or Time variant TMC, 
             (ii) No cut off vs. Paediatric cut-off in MMC, and 
             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
             Random Walk 2 (RW2) temporal prior. 
             For all combinations, the within-sample continuous ranked 
             probability scores (CRPS), mean absolute error (MAE) , 
             root mean squared error (RMSE), and the proportion of empirical 
             observations that fell within the 50\%, 80\%, and 95\% 
             quantiles are shown.} 
  \label{tab::PPC1Non-VMMC} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{VMMC countries}
\label{sec:org09db5e8}

%% Notes on Table %% 
\textbf{AR1}

\begin{itemize}
    \item MC: CRPS best for Time TMC, but all similar (2202.10 vs highest at 220.73 for Neither), RMSE best for Both (but rounded to two decimal places is 021 for all!), 50\% coverage best for Time TMC, 80\% Coverage narrowly best for Neither (78.47 vs lowest at 78.18 for Both), 95\% coverage best for Paed Cut-off, but similarly very high everywhere (88.89 vs lowest at 88.56 for Time TMC). 
    \item MMC \& TMC: Very similar to MC (need to expand on this), little difference between models, both in terms of mean fit statistics and posterior predictive coverage.
    \item Conclusions: 
    \begin{itemize}
        \item MC: Models provide very similar fit, with very little difference in both mean fit statistics and coverage between them. Therefore, it is best to go with the model that makes the most sense qualitatively (see below).
        \item MMC & TMC: Similar Conclusion. 
    \end{itemize}
    \item \textbf{Final Choice}: 
    \begin{itemize}
      \item Qualitatively, the inclusion of a Time TMC component, while computationally expensive, will not harm model fit (but excluding it may harm VMMC countries with high TMC, like Kenya and Ethiopia).
      \item Also, it is simplest to have a similar treatment of time TMC for both the VMMC and non-VMMC models, unless we have a good reason not to.
      \item The inclusion of a paedaitric age cutoff for MMC makes sense as we know that VMMC programmes do not perform paediatric circumcisions on policy
      \item Therefore, the choice of the "Both" model makes the most sense here, in light of the fact that there is little quantitative difference between model fits. 
    \end{itemize}
\end{itemize}

\textbf{RW1 \& RW2}
- Need to expand on writing for RW1 and RW2 temporal priors, but essentially we're seeing the same thing, in that both mean fit statistics and posterior predictive coverages differ very little between models, so we should revert back to our qualitative choice of using a Time TMC component, and a paediatric age cutoff for MMC (i.e. the "Both" model).

%% Model Specification Table 1: Non-VMMC countries %%

\begin{landscape}

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.75cm} 
     >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-15} 
  & & & \multicolumn{6}{c}{\bf Time invariant} & 
      \multicolumn{6}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-9} 
  \cmidrule(lr){10-15} 
  & {\bf MMC Model} & {\bf Type} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
  \hline 
AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
 RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
 RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total 
             male circumcision (MC), medical male circumcision (MMC) and 
             traditional male circumcision (TMC) from fitting the 12 candidate 
             models and taking the median value across all Non-VMMC countries. Combinations include 
             (i) Time invariant or Time variant TMC, 
             (ii) No cut off vs. Paediatric cut-off in MMC, and 
             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
             Random Walk 2 (RW2) temporal prior. 
             For all combinations, the within-sample continuous ranked 
             probability scores (CRPS), mean absolute error (MAE) , 
             root mean squared error (RMSE), and the proportion of empirical 
             observations that fell within the 50\%, 80\%, and 95\% 
             quantiles are shown.} 
  \label{tab::PPC1Non-VMMC} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{landscape}

\end{document}

### 2023-09-26 paper/supp_figs.tex

@@
 Lycias Zembe\textsuperscript{5},
-Jeffrey W. Eaton\textsuperscript{1,6} \\
+Jeffrey W. Imai-Eaton\textsuperscript{1,6} \\
 \smallskip
@@
 
-The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
-We excluded Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
-In total, we identified 109 nationally representative household surveys conducted the study region between 2002 and 2019.
-These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs, ais, phia, hsrc2002, hsrc2008, hsrc2012, hsrc2017} \todo{include MICS reference}.
-Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
-\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} \todo{done, what do you mean by "link in survey figure?"}
-Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
-The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008, bais2013}.
-For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.
+We identified 109 nationally representative household surveys across sub-Saharan Africa between 2002 and 2019 that contained information on self-reported circumcision status (see Table 1).
+These included several major survey series, namely the Demographic and Health Surveys (DHS) \cite{dhs}, AIDS Indicator Surveys (AIS) \cite{ais}, Population-based HIV Impact Assessment (PHIA) surveys \cite{phia}, Multiple Indicator Cluster Surveys (MICS) \cite{mics}, and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{hsrc2002, hsrc2008, hsrc2012, hsrc2017}.
+{\color{red}We excluded 2008 and 2013 Botswana AIDS Impact Surveys (BAIS) \cite{bais2008, bais2013}, the Central African Republic 2018 MICS survey, and the 2014 and 2018 Guinea-Bissau MICS surveys, as these surveys did not contain the information on age at circumcision required for modelling.}
+
+In total, we extracted data from 104 surveys conducted in 33 sub-Saharan countries: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, and South Africa.
+{\color{red}Equatorial Guinea, Guinea-Bissau, the Central African Republic and Botswana were not included as they either had no surveys conducted, or, where no surveys were available.} Figure 1 shows all available surveys, by the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information.
+
+We extracted variables such as age, cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
+The age of the respondents was calculated using both the century-month-code (CMC) of birth and interview dates.
+When calculating the residence of the respondents e matched survey data to clusters with accompanying (masked) geo-coordinates in order to assign the primary sub-national unit (PSNU) for modelling purposes.
+However, geo-cordinates were not available in some surveys and therefore we were unable to allocate their PSNU directly.
+Instead, we matched survey data to the least granular areal unit declared by the survey (most often level 1 administrative boundaries).
+Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’.
+Table 2 shows how the classification of circumcision type follows from these responses.
+Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type.
+Survey respondents were excluded if they were missing any demographic information or had a missing circumcision status.
+Table 1 shows a summary of the circumcision-related information from each surveys, and includes the availability of the circumcision related questions from the survey as well as the sample sizes in each survey.
+% For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.
 Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
-See figure 1 for a visual representation of the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information. 
-See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.
 
-\begin{figure}[H]
+\begin{figure}[!hbtp]
     \centering
-    \includegraphics[width=.9\linewidth]{paper/plots/01_survey_table.png}
+    \includegraphics[width=0.8\linewidth]{paper/plots/01_survey_table.png}
     \caption{Household surveys detailing circumcision patterns in sub-Saharan Africa.
@@
 
-Demographic variables such as age, residence and survey sampling weight were extracted from all surveys, alongside information related to circumcision: self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
-\textbf{[Write and link in survey table].}
-
-% \begin{landscape}
-{\linespread{1}
-  \footnotesize 
-\begin{longtable}[c]{ll ccc c}
-      %%%%%%%%%%%%%%%%%%%%
-      %%% Table header %%%
-      %%%%%%%%%%%%%%%%%%%%
-      % Upper layer of table header
-      \hline
-      % Lines inside the header
-      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
-      \cmidrule(lr){5-6}
-       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
-       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
-      % Lower lines
-      \hline
-      \vspace{-3pt}
-      \endhead
-      %%%%%%%%%%%%%%%%%%%%
-      %%% Table footer %%%
-      %%%%%%%%%%%%%%%%%%%%
-      \\[-3pt] \hline
-      \endfoot
-      %%%%%%%%%%%%%%%%%%%%%%
-      %%% Table contents %%%
-      %%%%%%%%%%%%%%%%%%%%%%
-      \multicolumn{2}{l}{\textbf{Angola}} \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Benin}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Botswana}} \\ 
-& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
-& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
-\end{longtable}
-}
-
 \begin{landscape}
@@
 \end{landscape}
-
-The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates. 
-Survey respondents were located to their districts using masked cluster geocoordinates. 
-Where these coordinates were unavailable (as in several MICS surveys) respondents were located to their level 1 administrative boundaries, most often corresponding to a province.
-
-Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
-Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type.
 
@@
 }
-
-In total, information was extracted from XXX, XXX respondents from all surveys.
-\textbf{[Participation rates table]}
-\todo{Get Matt to make dummy table for me based on this info for 2-3 countries, then I can fill in}
 
@@
     \item Model calibration
-    \item Prior choice
     \item Citations
@@
 national/admin-0).
-\todo{Not entirely convinced that }
+\todo{Not entirely convinced that this is true...}
 
@@
 where $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, and $P_{iat}$ is an estimate of the male population at age $a$ and time step $t$ in district $i$.
-The regional probabilities of TMC, MMC and MC
-
-for surveys not at the
-
-with regional equivalents in the likelihood above in order to include higher level aggregates.
+The district probabilities of TMC, MMC and MC were replaced with the higher level aggregates in the likelihood above for surveys that did not collect information on the district level.
 
@@
 
-\subsection{Final model selection}
+\subsection{Model specification, calibration and choice of temporal priors}
 \label{sec::modelcheck}
@@
 
-The choice of the final model to use in each country was decided in a two stage process.
+Using a combination of both within-sample and out-of-sample model fit, we considered whether a country should have
+\begin{enumerate}
+    \item a time-invariant or time-variant probability of TMC 
+    \item a paediatric cut-off or no cut-off in the probability of MMC 
+    \item an AR1, RW1 or RW2 as the temporal prior, along with appropriate hyperpriors
+\end{enumerate}
+and was decided in a two stage process.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The first stage involved choosing the model specification within each country.
+We performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC (i.e.
+1.
+and 2.
+above).
+We only used within-sample model fit here as we were most interested here in which model specification would produce the best model fit in each country, rather than in any relative short-term forecasting ability.
+For example, in VMMC priority countries, changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation and it might be more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy and therefore the model may need a paediatric cut-off.
+Conversely, in non-VMMC priority countries any changes in MMC is likely to be at the cost of TMC, which might be done at the paediatric level and therefore may mot need a paediatric cut-off.
 
-\subsubsection{Model specification}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the first stage of selecting the final model, we performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC.
-
-In each country,
-
+In each country, we ran a total of 12 model combinations (1., 2.
+and 3.
+above) on all available survey data.
+The choice of temporal prior is done after the model specification (see below), so but regardless we fit for each temporal prior for completeness.
 For each of the 12 model combinations, we sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
@@
 We also evaluated the coverage the posterior predictive distributions by calculating the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles of the posterior predictive distribution.
-The best performing models
+These were used to decide the best performing models (i.e.
+lowest CRPS/MAE/RMSE) in each country for the final model prediction.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+After the model specification was chosen, the second stage involved model calibration.
+We performed posterior predictive checking to assess the out-of-sample model fit to decide whether a country used an AR1, RW1, or RW2 temporal prior and appropriate hyperpriors for the corresponding hyperparameters (3.
+above).
+We considered out-of-sample model fit here as in some cases, we did not have access to recent survey data and we wanted to select a model that produces the most accurate forecast of circumcision coverage.
+For example, the most recent survey in Tanzania took place in 2016 (see above).
+However as Tanzania is an VMMC priority country, it is likely there has been a significant increase in MMC coverage since then that will not be captured and therefore we want to choose the temporal prior that produces the best forecasts in year proceeding the surveys.
 
-\subsubsection{Model calibration}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{\color{red} FINAL PARAGRAPH ABOUT HOW WE PERFORM MODEL CALIBRATION...}
 
@@
 
-\newpage
-\section{Model Selection}
-\label{sec::PPC2}
+% \newpage
+% \section{Model Selection}
+% \label{sec::PPC2}
 
@@
 
+\section{Model specification, calibration and choice of temporal priors}
+\label{sec::modelcheck}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Using a combination of both within-sample and out-of-sample model fit, we considered whether a country should have
+\begin{enumerate}
+    \item a time-invariant or time-variant probability of TMC 
+    \item a paediatric cut-off or no cut-off in the probability of MMC 
+    \item an AR1, RW1 or RW2 as the temporal prior, along with appropriate hyperpriors
+\end{enumerate}
+and was decided in a two stage process.
+
+The first stage involved choosing the model specification within each country.
+We performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC (i.e.
+1.
+and 2.
+above).
+We only used within-sample model fit here as we were most interested here in which model specification would produce the best model fit in each country, rather than in any relative short-term forecasting ability.
+For example, in VMMC priority countries, changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation and it might be more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy and therefore the model may need a paediatric cut-off.
+Conversely, in non-VMMC priority countries any changes in MMC is likely to be at the cost of TMC, which might be done at the paediatric level and therefore may mot need a paediatric cut-off.
+
+In each country, we ran a total of 12 model combinations (1., 2.
+and 3.
+above) on all available survey data.
+The choice of temporal prior is done after the model specification (see below), so but regardless we fit for each temporal prior for completeness.
+For each of the 12 model combinations, we sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
+We compared the mean predictions against the empirical survey estimates, aggregated to calculate predictive distributions by five year age groups (from 0-4 through 55-59) to avoid to many zeroes.
+To measure within-sample model fit we estimated the continuous ranked probability scores (CRPS), the mean absolute error (MAE) and root mean square error (RMSE).
+We also evaluated the coverage the posterior predictive distributions by calculating the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles of the posterior predictive distribution.
+These were used to decide the best performing models (i.e.
+lowest CRPS/MAE/RMSE) in each country for the final model prediction.
+
+After the model specification was chosen, the second stage involved model calibration.
+We performed posterior predictive checking to assess the out-of-sample model fit to decide whether a country used an AR1, RW1, or RW2 temporal prior and appropriate hyperpriors for the corresponding hyperparameters (3.
+above).
+We considered out-of-sample model fit here as in some cases, we did not have access to recent survey data and we wanted to select a model that produces the most accurate forecast of circumcision coverage.
+For example, the most recent survey in Tanzania took place in 2016 (see above).
+However as Tanzania is an VMMC priority country, it is likely there has been a significant increase in MMC coverage since then that will not be captured and therefore we want to choose the temporal prior that produces the best forecasts in year proceeding the surveys.
+
+{\color{red} FINAL PARAGRAPH ABOUT HOW WE PERFORM MODEL CALIBRATION...}
+
+%%%%%%%%%%%%%%%%%%
+%%% References %%%
+%%%%%%%%%%%%%%%%%%
 
@@
 \printbibliography
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2023-09-26 paper/model_spec_ppcs_tables.tex
New model specification tables added

@@
 %% Model Specification Table 1: Non-VMMC countries %%
+
 \begin{landscape}
@@
   \footnotesize 
-  \begin{tabular}{>{\bfseries}p{0.75cm} 
-     >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
-     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
-     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
   \hline  
-  & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
-  \cmidrule(lr){4-15} 
-  & & & \multicolumn{6}{c}{\bf Time invariant} & 
-      \multicolumn{6}{c}{\bf Time variant} \\ 
-  \cmidrule(lr){4-9} 
-  \cmidrule(lr){10-15} 
-  & {\bf MMC Model} & {\bf Type} & 
-      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
-      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
+  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\
+  \cmidrule(lr){4-5} 
+  \cmidrule(lr){6-7} 
+  \cmidrule(lr){8-9} 
+  \cmidrule(lr){10-11} 
+  \cmidrule(lr){12-13} 
+  \cmidrule(lr){14-15} 
+  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
   \hline 
-AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
-  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
-  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
-  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
-  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
-  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
- RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
-  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
-  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
-  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
-  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
-  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
- RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
-  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
-  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
-  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
-  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
-  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
+    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
+ & \bf MC & \bf NC &  75.81 &  79.00 &   0.11 &   0.11 &   0.14 & \bf  0.13 &  69.56 & \bf 67.22 & \bf 79.51 &  76.71 &  88.42 &  83.81 & \\ 
+  &  & \bf PC &  74.99 & \bf 74.65 &   0.11 & \bf  0.11 &   0.14 &   0.14 &  70.30 &  68.93 &  80.58 &  80.55 & \bf 88.84 &  88.60 & \\[3pt] 
+  & \bf MMC & \bf NC & \bf123.68 & 133.31 & \bf  0.21 &   0.24 & \bf  0.26 &   0.30 & \bf 50.23 &  59.02 &  71.77 & \bf 78.35 &  85.45 & \bf 89.95 & \\ 
+  &  & \bf PC & 132.86 & 127.44 &   0.23 &   0.21 &   0.28 &   0.26 &  46.35 &  45.78 &  67.48 &  66.67 &  81.95 &  80.84 & \\[3pt] 
+  & \bf TMC & \bf NC & \bf112.09 & 119.62 & \bf  0.20 &   0.22 & \bf  0.25 &   0.28 &  52.20 &  61.76 &  72.50 & \bf 80.30 &  85.49 & \bf 91.37 & \\ 
+  &  & \bf PC & 118.05 & 115.27 &   0.21 &   0.20 &   0.27 &   0.25 & \bf 48.84 &  47.16 &  68.48 &  67.66 &  82.26 &  81.16 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
+ & \bf MC & \bf NC &  77.22 &  77.86 &   0.12 &   0.12 &   0.14 &   0.14 &  68.59 & \bf 66.54 &  78.83 &  75.30 &  87.28 &  82.52 & \\ 
+  &  & \bf PC &  76.06 & \bf 75.66 &   0.12 & \bf  0.11 &   0.14 & \bf  0.14 &  69.44 &  68.76 &  79.79 & \bf 79.83 & \bf 88.14 &  87.33 & \\[3pt] 
+  & \bf MMC & \bf NC & 124.16 & \bf120.06 &   0.21 &   0.22 &   0.27 &   0.28 & \bf 49.28 &  58.79 &  69.78 & \bf 79.64 &  84.24 & \bf 90.66 & \\ 
+  &  & \bf PC & 128.45 & 127.44 &   0.22 & \bf  0.21 &   0.27 & \bf  0.26 &  46.65 &  46.26 &  66.77 &  67.68 &  80.68 &  80.87 & \\[3pt] 
+  & \bf TMC & \bf NC & 112.48 & \bf106.09 &   0.20 &   0.21 &   0.26 &   0.27 & \bf 51.56 &  61.07 &  71.27 & \bf 81.80 &  85.06 & \bf 92.17 & \\ 
+  &  & \bf PC & 115.99 & 114.87 &   0.20 & \bf  0.20 &   0.26 & \bf  0.25 &  48.24 &  47.82 &  67.33 &  68.31 &  81.56 &  81.59 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
+ & \bf MC & \bf NC &  77.22 & \bf 53.68 &   0.12 & \bf  0.11 &   0.15 & \bf  0.13 &  68.77 & \bf 68.00 & \bf 79.77 &  78.64 &  88.08 &  86.79 & \\ 
+  &  & \bf PC &  74.80 &  74.41 &   0.11 &   0.11 &   0.14 &   0.14 &  70.68 &  69.77 &  81.56 &  80.99 & \bf 90.31 &  89.70 & \\[3pt] 
+  & \bf MMC & \bf NC & 124.69 & \bf 96.50 &   0.22 & \bf  0.19 &   0.27 & \bf  0.24 & \bf 48.90 &  52.66 &  69.03 & \bf 76.51 &  83.23 & \bf 89.90 & \\ 
+  &  & \bf PC & 128.19 & 126.95 &   0.21 &   0.21 &   0.26 &   0.26 &  46.48 &  46.22 &  66.46 &  66.78 &  80.77 &  80.57 & \\[3pt] 
+  & \bf TMC & \bf NC & 112.85 & \bf 89.62 &   0.20 & \bf  0.18 &   0.26 & \bf  0.23 & \bf 50.95 &  55.51 &  70.36 & \bf 78.36 &  83.36 & \bf 90.72 & \\ 
+  &  & \bf PC & 115.88 & 115.32 &   0.20 &   0.20 &   0.25 &   0.25 &  48.08 &  47.41 &  67.29 &  67.46 &  80.84 &  81.06 & \\[3pt] 
   \hline 
   \end{tabular} 
-  \caption{Results of the posterior predictive checking in total 
-             male circumcision (MC), medical male circumcision (MMC) and 
-             traditional male circumcision (TMC) from fitting the 12 candidate 
-             models and taking the median value across all Non-VMMC countries. Combinations include 
-             (i) Time invariant or Time variant TMC, 
-             (ii) No cut off vs. Paediatric cut-off in MMC, and 
-             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
-             Random Walk 2 (RW2) temporal prior. 
-             For all combinations, the within-sample continuous ranked 
-             probability scores (CRPS), mean absolute error (MAE) , 
-             root mean squared error (RMSE), and the proportion of empirical 
-             observations that fell within the 50\%, 80\%, and 95\% 
-             quantiles are shown.} 
-  \label{tab::PPC1Non-VMMC} 
+  \caption{Results of the posterior predictive checking in total male 
+    circumcision (MC), medical male circumcision (MMC) and traditional male 
+    circumcision (TMC) from fitting the 12 candidate models in Non-VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
+    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
+    temporal prior. For all combinations, the within-sample continuous ranked 
+    probability scores (CRPS), mean absolute error (MAE), root mean square 
+    error (RMSE), and the proportion of empirical observations that fell within 
+    the 50\%, 80\%, and 95\% quantiles are shown.} 
+  \label{tab::PPC2Non-VMMC} 
 \end{table}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{landscape}
+
+% \begin{landscape}
+% 
+% {\linespread{1} 
+%   \begin{table}[H] 
+%   \centering 
+%   \footnotesize 
+%   \begin{tabular}{>{\bfseries}p{0.75cm} 
+%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+%   \hline  
+%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
+%   \cmidrule(lr){4-15} 
+%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
+%       \multicolumn{6}{c}{\bf Time variant} \\ 
+%   \cmidrule(lr){4-9} 
+%   \cmidrule(lr){10-15} 
+%   & {\bf MMC Model} & {\bf Type} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
+%   \hline 
+% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
+%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
+%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
+%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
+%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
+%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
+%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
+%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
+%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
+%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
+%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
+%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
+%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
+%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
+%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
+%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
+%   \hline 
+%   \end{tabular} 
+%   \caption{Results of the posterior predictive checking in total 
+%              male circumcision (MC), medical male circumcision (MMC) and 
+%              traditional male circumcision (TMC) from fitting the 12 candidate 
+%              models and taking the median value across all Non-VMMC countries. Combinations include 
+%              (i) Time invariant or Time variant TMC, 
+%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
+%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
+%              Random Walk 2 (RW2) temporal prior. 
+%              For all combinations, the within-sample continuous ranked 
+%              probability scores (CRPS), mean absolute error (MAE) , 
+%              root mean squared error (RMSE), and the proportion of empirical 
+%              observations that fell within the 50\%, 80\%, and 95\% 
+%              quantiles are shown.} 
+%   \label{tab::PPC1Non-VMMC} 
+% \end{table}} 
+% 
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+% \end{landscape}
 
@@
   \footnotesize 
-  \begin{tabular}{>{\bfseries}p{0.75cm} 
-     >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
-     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
-     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
   \hline  
-  & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
-  \cmidrule(lr){4-15} 
-  & & & \multicolumn{6}{c}{\bf Time invariant} & 
-      \multicolumn{6}{c}{\bf Time variant} \\ 
-  \cmidrule(lr){4-9} 
-  \cmidrule(lr){10-15} 
-  & {\bf MMC Model} & {\bf Type} & 
-      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
-      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
+  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\
+  \cmidrule(lr){4-5} 
+  \cmidrule(lr){6-7} 
+  \cmidrule(lr){8-9} 
+  \cmidrule(lr){10-11} 
+  \cmidrule(lr){12-13} 
+  \cmidrule(lr){14-15} 
+  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
   \hline 
-AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
-  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
-  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
-  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
-  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
-  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
- RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
-  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
-  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
-  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
-  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
-  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
- RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
-  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
-  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
-  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
-  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
-  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
+    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
+ & \bf MC & \bf NC & 220.73 & \bf220.10 &   0.16 &   0.16 &   0.21 &   0.21 &  60.51 & \bf 60.23 & \bf 78.47 &  78.32 &  88.84 &  88.56 & \\ 
+  &  & \bf PC & 220.70 & 220.11 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 &  60.48 &  60.37 &  78.37 &  78.18 & \bf 88.89 &  88.77 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.43 & \bf163.95 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.40 &  84.69 &  85.11 &  93.21 & \bf 93.99 & \\ 
+  &  & \bf PC & 168.45 & 165.81 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.13 &  69.12 & \bf 84.40 &  84.71 &  92.89 &  93.64 & \\[3pt] 
+  & \bf TMC & \bf NC & 189.20 & \bf185.47 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.74 &  64.23 &  82.30 &  82.45 &  92.02 & \bf 92.25 & \\ 
+  &  & \bf PC & 191.07 & 188.56 &   0.14 &   0.14 &   0.19 &   0.19 & \bf 63.41 &  63.60 &  82.01 & \bf 81.81 &  91.85 &  91.98 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
+ & \bf MC & \bf NC & 220.08 & 240.11 &   0.17 &   0.18 &   0.22 &   0.23 &  60.81 & \bf 58.56 & \bf 78.89 &  77.33 & \bf 89.06 &  88.16 & \\ 
+  &  & \bf PC & 220.29 & \bf218.79 &   0.17 & \bf  0.16 &   0.22 & \bf  0.21 &  60.90 &  60.51 &  78.79 &  78.83 &  89.04 &  88.97 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.60 & 167.02 &   0.13 &   0.13 &   0.18 &   0.19 &  68.34 &  69.26 &  84.54 &  85.35 &  93.22 & \bf 94.08 & \\ 
+  &  & \bf PC & 168.66 & \bf165.65 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 & \bf 68.24 &  69.42 & \bf 84.39 &  84.80 &  93.19 &  93.83 & \\[3pt] 
+  & \bf TMC & \bf NC & 188.94 & 195.44 &   0.14 &   0.15 &   0.20 &   0.21 &  64.08 &  64.40 &  83.05 &  83.21 &  92.49 & \bf 92.59 & \\ 
+  &  & \bf PC & 190.81 & \bf187.53 &   0.14 & \bf  0.14 &   0.20 & \bf  0.19 & \bf 63.77 &  64.04 &  82.58 & \bf 82.53 &  92.13 &  92.23 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
+ & \bf MC & \bf NC & 220.19 & 219.09 &   0.16 &   0.16 &   0.21 &   0.21 &  60.55 &  60.45 &  78.14 &  78.49 &  88.69 &  88.68 & \\ 
+  &  & \bf PC & 221.05 & \bf218.97 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 & \bf 60.19 &  60.47 &  78.27 & \bf 78.59 &  88.76 & \bf 88.78 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.84 & \bf164.16 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.59 &  84.51 &  85.14 &  93.20 & \bf 94.01 & \\ 
+  &  & \bf PC & 168.58 & 165.97 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.33 &  69.13 & \bf 84.33 &  84.60 &  92.93 &  93.63 & \\[3pt] 
+  & \bf TMC & \bf NC & 188.93 & \bf184.27 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.64 &  64.73 &  82.42 &  82.86 &  91.99 & \bf 92.25 & \\ 
+  &  & \bf PC & 191.49 & 187.82 &   0.14 &   0.14 &   0.20 &   0.19 & \bf 63.23 &  63.78 & \bf 81.74 &  82.34 &  91.71 &  92.00 & \\[3pt] 
   \hline 
   \end{tabular} 
-  \caption{Results of the posterior predictive checking in total 
-             male circumcision (MC), medical male circumcision (MMC) and 
-             traditional male circumcision (TMC) from fitting the 12 candidate 
-             models and taking the median value across all Non-VMMC countries. Combinations include 
-             (i) Time invariant or Time variant TMC, 
-             (ii) No cut off vs. Paediatric cut-off in MMC, and 
-             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
-             Random Walk 2 (RW2) temporal prior. 
-             For all combinations, the within-sample continuous ranked 
-             probability scores (CRPS), mean absolute error (MAE) , 
-             root mean squared error (RMSE), and the proportion of empirical 
-             observations that fell within the 50\%, 80\%, and 95\% 
-             quantiles are shown.} 
-  \label{tab::PPC1Non-VMMC} 
+  \caption{Results of the posterior predictive checking in total male 
+    circumcision (MC), medical male circumcision (MMC) and traditional male 
+    circumcision (TMC) from fitting the 12 candidate models in VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
+    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
+    temporal prior. For all combinations, the within-sample continuous ranked 
+    probability scores (CRPS), mean absolute error (MAE), root mean square 
+    error (RMSE), and the proportion of empirical observations that fell within 
+    the 50\%, 80\%, and 95\% quantiles are shown.} 
+  \label{tab::PPC1VMMC} 
 \end{table}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+% \begin{landscape}
+% 
+% {\linespread{1} 
+%   \begin{table}[H] 
+%   \centering 
+%   \footnotesize 
+%   \begin{tabular}{>{\bfseries}p{0.75cm} 
+%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+%   \hline  
+%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
+%   \cmidrule(lr){4-15} 
+%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
+%       \multicolumn{6}{c}{\bf Time variant} \\ 
+%   \cmidrule(lr){4-9} 
+%   \cmidrule(lr){10-15} 
+%   & {\bf MMC Model} & {\bf Type} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
+%   \hline 
+% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
+%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
+%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
+%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
+%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
+%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
+%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
+%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
+%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
+%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
+%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
+%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
+%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
+%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
+%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
+%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
+%   \hline 
+%   \end{tabular} 
+%   \caption{Results of the posterior predictive checking in total 
+%              male circumcision (MC), medical male circumcision (MMC) and 
+%              traditional male circumcision (TMC) from fitting the 12 candidate 
+%              models and taking the median value across all Non-VMMC countries. Combinations include 
+%              (i) Time invariant or Time variant TMC, 
+%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
+%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
+%              Random Walk 2 (RW2) temporal prior. 
+%              For all combinations, the within-sample continuous ranked 
+%              probability scores (CRPS), mean absolute error (MAE) , 
+%              root mean squared error (RMSE), and the proportion of empirical 
+%              observations that fell within the 50\%, 80\%, and 95\% 
+%              quantiles are shown.} 
+%   \label{tab::PPC1Non-VMMC} 
+% \end{table}}
+%  
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+% 
+% \end{landscape}
+
 \end{document}

### 2023-09-26 paper/supp_figs.tex
New model specification tables added

@@
 
-We extracted variables such as age, cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
+We extracted variables such as age, cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practitioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
 The age of the respondents was calculated using both the century-month-code (CMC) of birth and interview dates.

### 2023-11-15 paper/paper.tex
Updates from Overleaf
Paper as it stands on overleaf 08/11/23 14:35
Update directory name in script

@@
 For example, in some countries the level and practices of TMC have changed through time due to demographic shifts.
-There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
+There has also been a sment of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
 Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.

### 2023-11-15 paper/scripts/00_funs.R

@@ -74,13 +74,26 @@ load_orderly_data <- function(
   dirs <- dirs[!is.na(dirs)]
   # return dirs if filenames unspecified
   if (is.null(filenames)) return(list("dirs" = dirs_return))
-  files <- file.path(
-    "archive", 
-    task,
-    dirs, 
-    "artefacts/", # prob don't need this? I just structure my tasks this way
-    filenames
-  )
+  if (all(grepl("archive", dirs)) && all(grepl("artefacts", dirs))) {
+    files <- file.path(dirs, filenames)
+  # } else if (!grepl("archive", filenames)) {
+  #   files <- file.path(
+  #     "archive", 
+  #     task,
+  #     dirs, 
+  #     # dirname(dirs),
+  #     # "artefacts/", # prob don't need this? I just structure my tasks this way
+  #     filenames
+  #   )
+  } else {
+    files <- file.path(
+      "archive", 
+      task,
+      dirs, 
+      "artefacts/", # prob don't need this? I just structure my tasks this way
+      filenames
+    )
+  }
   # return filenames if load_fun isn't specified
   if (!is.null(load_fun) == FALSE) {
     return(list("dirs"  = dirs_return, "files" = files))

### 2023-11-15 paper/scripts/01_abstract_imports.R

@@ -1,0 +1,1 @@
+#### Pull through figures for abstract results, etc ####

### 2023-11-15 paper/scripts/020_methods_data.R

@@ -16,7 +16,7 @@ library(geofacet)
 library(glue)
 library(ggtext)
 # source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots/paper/scripts/00_funs.R") # shared functions
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
 
 ### Metadata ###
 
@@ -183,12 +183,12 @@ for (i in seq_len(nrow(table1))) {
 
 # sink to text file
 sink(
-  "paper_poster_plots/paper/figures/supp_figs/table_1_survey_questions.txt", 
+  "paper_poster_plots_threemc/paper/figures/supp_figs/table_1_survey_questions.txt", 
   append = FALSE
 )
 for (i in seq_along(text)) cat(text[i], "\n")
 sink()
-# TODO: When pasting into TeX table, must search and replace [/] with \
+# TODO: When pasting into TeX table, must search and s [/] with \
 
 
 #### Table 2: Circumcision Type Definitions ####

### 2023-11-15 paper/scripts/031_results_data.R

@@ -25,7 +25,7 @@ library(geofacet)
 library(glue)
 library(ggtext)
 source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots/paper/scripts/00_funs.R") # shared functions
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
 
 #### Metadata ####
 
@@ -694,9 +694,9 @@ data_inlines <- c(
 #### Saving ####
 
 # save plot
-saveRDS(p1, "paper_poster_plots/paper/plots/01_survey_table.RDS")
+saveRDS(p1, "paper_poster_plots_threemc/paper/plots/01_survey_table.RDS")
 ggplot2::ggsave(
-  "paper_poster_plots/paper/plots/01_survey_table.png", 
+  "paper_poster_plots_threemc/paper/plots/01_survey_table.png", 
   p1, 
   width = 6.3, 
   height = 8,
@@ -704,4 +704,4 @@ ggplot2::ggsave(
 )
 
 # save data for inlines
-saveRDS(data_inlines, "paper_poster_plots/paper/data/01_data_inlines.RDS")
+saveRDS(data_inlines, "paper_poster_plots_threemc/paper/data/01_data_inlines.RDS")

### 2023-11-15 paper/scripts/032_results.R

@@ -19,9 +19,11 @@ library(ggsci)
 library(geofacet)
 library(glue)
 library(ggtext)
-library(cowplot)
+# library(cowplot)
+library(patchwork)
+library(gridExtra)
 source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots/paper/scripts/00_funs.R")
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
 
 #### Metadata ####
 
@@ -143,13 +145,33 @@ results_dirs <- load_orderly_data(
     )"
 )$dirs
 
-results_agegroup <- load_orderly_data(
-  task = "02final_aggregations",
-  dirs = results_dirs[!is.na(results_dirs)],
-  filenames = "Results_AgeGroup_Prevalence.csv.gz"
-)$output %>%
-  bind_rows()
-gc()
+# function to add iso3 column to dataframe from area id, if not already present
+add_iso3 <- function(df) {
+  stopifnot("area_id" %in% names(df))
+  if (!"iso3" %in% names(df)) {
+    df$iso3 <- substr(df$area_id, 0, 3)
+    df <- df %>% 
+      relocate(iso3, .before = area_id)
+  }
+  return(df)
+}
+
+# results_agegroup <- load_orderly_data(
+#   task = "02final_aggregations",
+#   dirs = results_dirs[!is.na(results_dirs)],
+#   filenames = "Results_AgeGroup_Prevalence.csv.gz"
+# )$output %>%
+#   bind_rows()
+# gc()
+results_agegroup <- readr::read_csv(
+  "paper_poster_plots_threemc/paper/data/results_agegroup.csv.gz"
+)
+results_agegroup <- add_iso3(results_agegroup)
+# save results for use later
+# readr::write_csv(
+#   results_agegroup, 
+#   "paper_poster_plots_threemc/paper/data/results_agegroup.csv.gz"
+# )
 
 # most recent results for single ages
 # results_age <- load_orderly_data(
@@ -160,34 +182,31 @@ gc()
 #   bind_rows() %>%
 #   filter(type %in% paste(c("MC", "MMC", "TMC"), "coverage"))
 # results_age <- readr::read_csv(
-#   "paper_poster_plots/paper/data/results_age.csv.gz"
+#   "paper_poster_plots_threemc/paper/data/results_age.csv.gz"
+# )
+# results_age <- add_iso3(results_age)
[…]

### 2023-11-15 paper/scripts/033_results_rerender_plots.R

@@ -8,11 +8,12 @@ library(cowplot)
 library(sf)
 library(ggsci)
 library(geofacet)
+library(patchwork)
 
 # Figure 1: Survey table
-p1 <- readRDS("paper_poster_plots/paper/plots/01_survey_table.RDS")
+p1 <- readRDS("paper_poster_plots_threemc/paper/plots/01_survey_table.RDS")
 ggplot2::ggsave(
-  "paper_poster_plots/paper/plots/01_survey_table.png", 
+  "paper_poster_plots_threemc/paper/plots/01_survey_table.png", 
   p1, 
   width = 6.3, 
   height = 8,
@@ -21,9 +22,9 @@ ggplot2::ggsave(
 rm(p1); gc()
 
 # Figure 2: Coverage Map 
-p2final <- readRDS("paper_poster_plots/paper/plots/02_map_plot_facet.RDS")
+p2final <- readRDS("paper_poster_plots_threemc/paper/plots/02_map_plot_facet.RDS")
 ggsave(
-  "paper_poster_plots/paper/plots/02_map_plot_facet.png", 
+  "paper_poster_plots_threemc/paper/plots/02_map_plot_facet.png", 
   p2final,
   width = 6.3, 
   height = 6.5, 
@@ -32,9 +33,9 @@ ggsave(
 rm(p2final); gc()
 
 # Figure 3: Subnational coverage variation
-p3 <- readRDS("paper_poster_plots/paper/plots/03_subnat_plot.RDS")
+p3 <- readRDS("paper_poster_plots_threemc/paper/plots/03_subnat_plot.RDS")
 ggplot2::ggsave(
-  "paper_poster_plots/paper/plots/03_subnat_plot.png", 
+  "paper_poster_plots_threemc/paper/plots/03_subnat_plot.png", 
   p3, 
   width = 6.3, 
   height = 8,
@@ -43,9 +44,9 @@ ggplot2::ggsave(
 rm(p3); gc()
 
 # Figure 4: Geofacet of coverage by age
-p4_geo <- readRDS("paper_poster_plots/paper/plots/04_geo_age.RDS")
+p4_geo <- readRDS("paper_poster_plots_threemc/paper/plots/04_geo_age.RDS")
 ggplot2::ggsave(
-  "paper_poster_plots/paper/plots/04_geo_age.png", 
+  "paper_poster_plots_threemc/paper/plots/04_geo_age.png", 
   p4_geo, 
[…]

### 2023-11-15 paper/scripts/ind_supp_figs.R

@@ -1,7 +1,7 @@
 #### Individual Country Supplementary figures of final results ####
 
 # Must be run inside `threemc_orderly` repo, with this repo in top level of 
-# this directory, and called `paper_poster_plots`
+# this directory, and called `paper_poster_plots_threemc`
 
 #### Libs ####
 
@@ -18,7 +18,7 @@ library(scales)
 library(ggridges)
 library(threemc)
 source("Shiny/src/functions.R")
-source("paper_poster_plots/paper/scripts/00_funs.R")
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
 
 
 #### Metadata ####
@@ -28,10 +28,10 @@ orderly_root <- here::here()
 # save width for plots == width of page on paper
 save_width <- 6.3
 
-save_loc <- "paper_poster_plots/paper/plots/supp_figs/"
+save_loc <- "paper_poster_plots_threemc/paper/plots/supp_figs/"
 if (!dir.exists(save_loc)) create_dirs_r(save_loc)
 
-cntry <- "ZAF" # temp, run for one country, might loop thereafter
+# cntry <- "ZAF" # temp, run for one country, might loop thereafter
 
 spec_age_group <- "15-29"
 spec_age_group_double <- c(spec_age_group, "30-49")
@@ -157,21 +157,25 @@ results_dir <- file.path(
 )
 results_agegroup <- results_reader(type = "age groups", dir_path = results_dir)
 
-# results_age <- load_orderly_data(
-#   task = "02final_aggregations", 
-#   dirs = results_dirs[!is.na(results_dirs)],
-#   filenames = "Results_Age_Prevalence.csv.gz"
-# )$output %>% 
-#   bind_rows() %>% 
-#   # filter(type %in% paste(c("MC", "MMC", "TMC"), "coverage")) %>% 
-#   identity()
+results_age <- load_orderly_data(
+  task = "02final_aggregations", 
+  dirs = results_dir[!is.na(results_dir)],
+  filenames = "Results_Age_Prevalence.csv.gz"
+)$output %>% 
+  bind_rows() %>% 
+  filter(type %in% paste(c("MC", "MMC", "TMC"), "coverage")) %>% 
+  identity()
+
 results_age <- results_reader(type = "age", dir_path = results_dir)
+
 gc()
 
-areas <- load_orderly_data("00a2_areas_join", 
-                           query = "latest", 
-                           file = "areas.geojson", 
[…]

### 2023-11-15 poster_plots_no_shiny_consolidation.R

@@ -164,7 +164,7 @@ last_surveys <- readr::read_csv("global/most_recent_surveys.csv")
 
 # Additional areas from Oli, so map plot can be for all of SSA
 # dat_loc <- "poster/data/"
-dat_loc <- "paper_poster_plots/aids_2022_poster/data/"
+dat_loc <- "paper_poster_plots_threemc/aids_2022_poster/data/"
 non_ssa_afr_areas <- sf::read_sf(
   file.path(
     dat_loc, 

### 2023-11-16 paper/scripts/plots_ind/02_age_at_circ.R
Directory with plotting code for single plots

@@ -1,0 +1,195 @@
+#### Figure 5: Map + scatter plot of age at circumcision ####
+
+stopifnot(basename(getwd()) == "paper_poster_plots_threemc")
+
+#### Libraries ####
+
+library(ggplot2)
+library(dplyr)
+library(sf)
+# devtools::install_github("thomasp85/patchwork")
+library(patchwork)
+
+#### Setup ####
+
+plt_data5 <- read_sf("paper/data/plots_ind/05_age_at_circ.geojson")
+areas <- read_sf("paper/data/plots_ind/05_areas.geojson") %>% 
+  filter(area_level == 0)
+# Add Lake Victoria for blue in map plot
+lake_vic <- rnaturalearth::ne_download(
+  scale = 110, type = "lakes", category = "physical") %>% 
+  sf::st_as_sf(lakes110, crs = 4269) %>% 
+  filter(name == "Lake Victoria") %>% 
+  select(name)
+
+# number of discrete age groups to group plot into
+n_breaks <- 7
+
+vmmc_iso3 <- c(
+  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF"
+)
+
+#### Plot & Save ####
+
+map_plot_circ_age <- function(
+    spec_results, spec_areas, lake_vic, colourPalette, n_breaks = 4
+  ) {
+  
+  levs = c("Total", "Medical", "Traditional")
+  levs <- levs[levs %in% spec_results$type]
+  
+  stopifnot(n_breaks %in% c(4, 7, 10))
+  
+  spec_results$type <- factor(spec_results$type, levels = levs)
+  
+  # functionalise this
+  # create discrete age bands, depending on the number of "breaks" specified
+  cut_breaks <- c(seq(0, 30, length.out = n_breaks), Inf)
+  if (n_breaks == 4) {
+    cut_breaks <- cut_breaks + 1
+    break_labels <- c("0-10", "11-20", "21-30", "30+")
+  } else if (n_breaks == 7) {
+    break_labels <- c("0-4", "5-9", "10-14", "15-19", "20-24", "25-29", "30+")
+  } else if (n_breaks == 10) {
+    cut_breaks <- cut_breaks + 1
+    break_labels <- c(
+      "0-3",   "4-6",   "7-10", "11-13", "14-16", 
[…]

### 2023-11-16 paper/scripts/plots_ind/functions.R

@@ -1,0 +1,1 @@
+/home/paddy7wb/imperial_repos/threemc-orderly/Shiny/src/functions.R

### 2023-11-16 paper/scripts/plots_ind/functions.R
Change functions to not be symbolinked in, Overleaf does not allow this (annoying!)

@@ -1,1 +1,4439 @@
-/home/paddy7wb/imperial_repos/threemc-orderly/Shiny/src/functions.R
+#### common functions amongst plots
+
+#### reads in results ####
+results_reader <- function(cntry = NULL, type, dir_path, pattern = NULL,
+                           model_type = NULL, ...) {
+  # do we want results for discrete ages or "binned" age groups?
+  if (type == "age") ages <- "_Age_" else ages <- "AgeGroup"
+  # list files, and pull names for desired country and type
+  # (maybe shouldn't hard code this path into the function?)
+  f <- list.files(dir_path, full.names = TRUE)
+  f <- f[grepl(ages, f)]
+  if (!is.null(cntry)) f <- f[grepl(cntry, f)]
+  if (!is.null(pattern)) f <- f[grepl(pattern, f)]
+
+  if (length(f) < 3) message("some data is missing!")
+  if (length(f) > 3) message("some unexpected data may be present!")
+
+  # load files and append them together. Return this appended df
+  results_age <- as.data.frame(data.table::rbindlist(
+    lapply(f, data.table::fread, ...), use.names = TRUE
+  ))
+  if (!is.null(model_type)) {
+    results_age <- results_age %>%
+      filter(model %in% model_type)
+  }
+  # Avoid annoying error with model type created when aggregating
+  if (sum(grepl("programme", results_age$model)) != 0) {
+    results_age <- results_age %>%
+      mutate(model = stringr::str_replace(model, "programme", "program"))
+  }
+  return(results_age)
+}
+
+#### Function to Add "Light" Column to Data ####
+add_last_surveys <- function(.data, last_surveys, add_rows = TRUE, join_cols = c("iso3", "area_id")) {
+    # join data with last_surveys
+    if (!"iso3" %in% names(.data)) {
+        .data$iso3 <- substr(.data$area_id, 0, 3)
+    }
+    .data <- .data %>%
+        # add last surveys for each country
+        # left_join(last_surveys, by = c("iso3", "area_id")) %>%
+        left_join(last_surveys, by = join_cols) %>%
+        # assume missing survey years are max for that country
+        group_by(iso3) %>%
+        mutate(survey_year = ifelse(
+            is.na(survey_year),  max(survey_year, na.rm = TRUE), survey_year
+        )) %>%
+        ungroup() %>%
[…]

### 2023-11-16 paper/paper.tex
Updates from Overleaf

--- 2023-08-31 paper/paper.tex
@@
   \noindent \textbf{Methods} \\
-  \noindent We analysed self-reported data on male circumcision from x nationally representative household
-  surveys conducted in x SSA countries between 2006-2020. A spatio-temporal Bayesian
-  competing-risks time-to-event model was used to estimate rates of traditional and medical
-  circumcision by age, location, and time. Circumcision coverage in 2020 was projected assuming
-  continuation of estimated age-specific rates, with probabilistic uncertainty.
+  \noindent We analysed self-reported data on male circumcision from x nationally representative household surveys conducted in x SSA countries between 2006-2020.
+  A spatio-temporal Bayesian competing-risks time-to-event model was used to estimate rates of traditional and medical circumcision by age, location, and time.
+  Circumcision coverage in 2020 was projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty.
 
@@
 
-HIV epidemic continues to to be a problem. Many interventions available etc. VMMC has been proven to be an effective way of doing this.
+The HIV epidemic continues to be a public health priority, with the Joint United Nations Programme on HIV/AIDS (UNAIDS) estimating that over 25 million people live with HIV across sub-Saharan Africa in 2022, with over 650,000 new infections that year \cite{UNAIDSStats}.
+To achieve the the global community's ambitious goals of ending the AIDS public health crisis by 2030, more work will need to be done \cite{UNAIDSStrategy}.
+Among the numerous interventions available, voluntary medical male circumcision (VMMC) has emerged as a powerful and cost-effective intervention to reduce HIV incidence \cite{bansi2023cost} with it is estimated to reduce male-to-female transition of HIV by nearly 60\% \cite{gray2007male, bailey2007male, auvert2005randomized, gray2012effectiveness, grund2017association}.
+Furthermore, other research has shown that VMMC can decrease the risk of male-to-male transmission of HIV \cite{pintye2019benefits}, and reduce the transmission of other sexually transmitted infections \cite{tobian2009male}.
 
-The World Health Organization (WHO) and the Joint United Nations Programme on HIV/AIDS (UNAIDS) have identified fifteen countries in sub-Saharan Africa that have a high HIV prevalence and low male circumcision (MC) coverage as priority countries which should scale-up VMMC for HIV prevention: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \todo{Check this and the citations} \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
-Since 2007, there have been XX\todo{Find this number and cite} million VMMCs conducted in these countries with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR) and the Global Fund to Fight AIDS, Tuberculosis and Malaria.
-Targets were set by UNAIDS to reach 80\% circumcision coverage among men aged 15--49 years in priority countries by 2015 which have since been updated to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework}.
+In light of this evidence, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
+Ambitious targets were set by UNAIDS to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 in these priority countries \cite{WHOFramework}.
+As such, over XX\todo{Find this number and cite} million VMMCs have been conducted in these countries between 2007 and 2022 with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR).
 

### 2024-01-28 paper/paper.tex
Overleaf changes

@@
 
-In light of this evidence, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
-Ambitious targets were set by UNAIDS to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 in these priority countries \cite{WHOFramework}.
-As such, over XX\todo{Find this number and cite} million VMMCs have been conducted in these countries between 2007 and 2022 with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR).
+There is a need to provide comprehensive estimates of male circumcision coverage by age,  time and type across sub-Saharan Africa, however, the landscape is complex and highly heterogeneous for numerous reasons.
+\todo{Need to expand this and add citations}
 
-The landscape of male circumcision in sub-Saharan Africa is complex and highly heterogeneous.
-Despite the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries.
+Firstly, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
+Ambitious targets were set by UNAIDS to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework} and as a result, over XX\todo{Find this number and cite} million VMMCs have been conducted in these priority countries between 2007 and 2022 with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR).
+
+Secondly, while the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries.
 The provision of traditional male circumcision (TMC), such as the typical age at circumcision and what it entails, can vary considerably and is influenced by community, religious, ethnic and cultural led values.
@@
 TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training.
-The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, due to TMC may not involve a complete circumcision and instead be only partial removal of the foreskin or a simple incision in the prepuce in some populations.
+The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, as TMC may not involve a complete circumcision and instead be only partial removal of the foreskin or a simple incision in the prepuce in some populations.
 \todo{Cite this paragraph.}
 
-Why is understanding this important? DMPPT2 and Cork et al. and Thomas et al. have been approaches
+Cork et al.
+provided the first set of comprehensive estimates of circumcision coverage in sub-Saharan Africa.
+They used survey data within a Bayesian geo-statistical model to produce annual estimates of total male circumcision coverage subnationally in sub-Saharan Africa between 2000 and 2017.
+Their approach focused on predicting circumcision coverage among only the aggregate age range 15–49 years, did not distinguish between circumcision type, and did not track the structured dynamics of circumcision coverage by type within cohorts.
 
-In this paper,...
+Thomas et al.
+aimed to address these issues by producing a model that synthesises both survey and programmatic data to generate region-age-time-type specific probabilities and coverage of male circumcision.
+The model extended a competing risks time-to-event model which enabled ...
+However, this study only focused on South Africa....
+
+Here, we take a similar approach to Thomas et al.
+in order to model estimate the probabilities and coverage of medical and traditional male circumcision by subnational area, single-year age, and time with probabilistic uncertainty.
+Here
 
@@
 Countries without estimates are in grey.
-Mean circumcision ages are binned into three distinct groups: 0-10, 11-20 and over 20.
+Mean circumcision ages are binned into five-year age groups and over 30s.
 (B) Scatterplot of district-level mean traditional male circumcision age versus mean medical male circumcision age.
-A diagonal dashed line passes through the origin and (30, 30).
+A diagonal dashed line passes through the origin and (25, 25).
 Points representing each district are coloured by whether their country is a Voluntary Male Medical Circumcision (VMMC) priority country.}}

### 2024-02-07 paper/paper.tex
Add numbers to 1st section (still median differences within countries to do)

@@
 
-% For each country, we fit a model for each possible model specification for threemc, that is:
+% For each country, we fit a model for each possible model specification for \verb|threemc|, that is:
 % \begin{itemize}
@@
 % The DMPPT2 model explicitly used this data to estimate MMC. 
-% The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
+% The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by \verb|threemc| where only these older surveys are available.
 % This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
-% Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
+% Hence, it was felt that \verb|threemc| likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
 % A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
 
-% The two main drivers of uncertainty over time in threemc were:
+% The two main drivers of uncertainty over time in \verb|threemc| were:
 % \begin{itemize}
 % \item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
-% \item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
+% \item The choice of temporal prior, for which \verb|threemc| supports the use of an AR1, RW1 or RW2 prior.
 % \end{itemize}
@@
 % To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
-% A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
+% A grid search over sensible variance hyperparameter values from the "naive" \verb|threemc| fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice.
 % For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
@@
 No information on age at circumcision was present in the 2004 and 2008 Botswana Aids Impact Surveys.
-This complete left censoring of circumcised individuals meant that threemc could not be fit to Botswana.
+This complete left censoring of circumcised individuals meant that \verb|threemc| could not be fit to Botswana.
 Right censoring of circumcision status, indicating as of yet uncircumcised individuals, averaged 35.299\% across all surveys, ranging from 0.399\% in the The Gambia 2018 MICS survey to 91.432\% in the Eswatini 2006 DHS survey.
@@
 
-In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit threemc in these countries either.
+In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit \verb|threemc| in these countries either.
 
@@
 
-Between 2007, the year VMMC programme implementation began, and 2020, an estimated x million men(95\% CI: x - x million) were newly circumcised. 
-Of these, x million (x - x million) were MMCS, along with x million (x - x million) TMCS. 
-This translated to an increase in MC for the SSA region of x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in  2020. 
-MC in 2020 ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x, while MMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x and TMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x.
-The largest percentage increase in MC coverage from 2010 to 2020 was x\% (x\% - x\%) in x, from x\% (x\% - x\%) to x (x\% - x\%), while for MMC it was x\% (x\% - x\%) in x. 
-The number of annual MCs performed increased from x (x to x) in 2006 to x (x to x) in 2020, a growth of x (x to x) annually. 
-Amongst these, x (x to x) were MMCs in 2006, while in 2020 x (x to x) MMCs were performed, representing an increase in x (x to x) in MMCs performed annually. 
-TMC did not increase anywhere,  and actually decreased in several countries from 2010 to 2020. 
-This is the focus of a later section of our results.
+% Between 2007, the year VMMC programme implementation began, and 2020, an estimated x million men(95\% CI: x - x million) were newly circumcised. 
+% Of these, x million (x - x million) were MMCS, along with x million (x - x million) TMCS. 
+% This translated to an increase in MC for the SSA region of x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in  2020. 
+% MC in 2020 ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x, while MMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x and TMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x.
+% The largest percentage increase in MC coverage from 2010 to 2020 was x\% (x\% - x\%) in x, from x\% (x\% - x\%) to x (x\% - x\%), while for MMC it was x\% (x\% - x\%) in x. 
+% The number of annual MCs performed increased from x (x to x) in 2006 to x (x to x) in 2020, a growth of x (x to x) annually. 
+% Amongst these, x (x to x) were MMCs in 2006, while in 2020 x (x to x) MMCs were performed, representing an increase in x (x to x) in MMCs performed annually. 
+% TMC did not increase anywhere,  and actually decreased in several countries from 2010 to 2020. 
+% This is the focus of a later section of our results. 
+In 2006, the year before VMMC programme implementation began, an estimated 217.236 million men (95\%
+CI: 211.079 - 222.008 million) were circumcised in the 33 countries in SSA for which we have valid circumcision
+data. 
+Of these, 67.021 million (62.554 - 73.259 million) were MMCS, and 102.286 million (95.718 - 106.665
+million) were TMCS. 
+This contrasts with 2020, where an estimated 337.913 million males (316.265 - 362.898
+million) were circumcised in these same countries, of which 125.738 million (106.081 - 157.406 million) were
+performed as MMCS, and 136.555 million (124.189 - 144.146 million) as TMCS. 
+This constituted an increase
+of 120.677 million (105.185 - 140.89 million) newly circumcised males between 2006 and 2020, with 58.717
+million (43.528 - 84.147 million) new MMCs performed, and 34.269 million (28.471 - 37.481 million) new
+TMCs performed. 
+The disparity between the number of MCs performed and the number of MMCs performed
+can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic
+Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or
+TMC. 
+This translated to a change in mean MC coverage for the SSA region from 57.62\% (59.13\% - 55.55\%
+) in 2006 to 63.2\% (66.94\% - 59.71\%) in 2020, or an increase of 5.58\% (4.16\% - 7.81\%). 
+MMC coverage increased from 18.75\% (17.75\% - 19.9\%  in 2006 to 26.09\% (23.11\% - 30.04\%) in 2020, an increase of 7.33\%
+(5.36\% - 10.14\%). 
+TMC changed from 24.64\% (23.57\% - 25.58\%) in 2006 to 22.75\% (21.34\% - 24.06\%) in 2020, a decrease of 1.89\% (1.51\% - 2.23\%).
 
-For VMMC countries, MC increased from x\% (x\% - x\%) to x\% (x\% - x\%), largely driven by an increase in MMC from x\% (x\% to x\%)  to x\% (x\% - x\%). 
-In constrast, for the non-VMMC countries, MC increased from x\% (x\% - x\%) to x\% (x\% - x\%), with MMC going from x\% (x\% to x\%)  to x\% (x\% - x\%). 
-TMC in 2020 for VMMC countries averaged x\% (x\% - x\%), compared to x\% (x\% - x\%) in non-VMMC countries.
+MC coverage in each country in 2006 ranged from 4.97\% (4.78\% - 5.16\%) in Zimbabwe to 95.99\% (86.43\% -
+(99.72\%) in Guinea, while MMC in 2006 ranged from 1.63\% (1.47\% - (1.76\%) in Zimbabwe to 60.05\% (56.56\%
+- (64.15\%) in Congo and TMC ranged from 0.93\% (0.75\% - (1.12\%) in Eswatini to 65.19\% (63.41\% - (66.94\%)
+in Benin. In contrast, in 2020 MC coverage was estimated to have ranged from 13.77\% (10.51\% - 18.87\%) in
+Zimbabwe to 96.95\% (89.74\% - (99.91\%) in Senegal, while MMC ranged from 11.55\% (8.24\% - (16.68\%) in
+Zimbabwe to 64.08\% (61.16\% - (67.11\%) in Sierra Leone and TMC ranged from 0.69\% (0.56\% - (0.84\%) in
+Eswatini to 63.02\% (59.34\% - (66.65\%) in Benin.
 
-Increases in MC coverage from 2010 to 2020 were very heterogeneous, with VMMC programmes generally targeting subnational regions where HIV burden is high and where VMMC as a HIV prevention method is better acknowledged (ref.
-42 in Matt's paper)
-In ESA countries, MC in 2010 averaged x\% (x\% - x\%). 
-This increased to x\% (x\% - x\%) in 2020. MMC increased from x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in 2020. 
-In constant, in WCA MC in 2010 averaged x\% (x\% - x\%), while in 2020 it averaged x\% (x\% - x\%).
-MMC in WCA increased from x\% (x\% - x\%)
-2020 TMC in ESA countries averaged x\% (x\% - x\%), compared to x\% (x\% - x\%) in WCA countries.
+The largest percentage increase in MC coverage from 2006 to 2020 was in Lesotho at 21.7\% (18.66\% - 25.93\%),
+from 30.06\% (29.53\% - 30.7\%) in 2006 to 51.76\% (48.19\% - 56.63\%) in 2020, while the highest percentage
+increase in MMC was also in Lesotho at 21.49\% (18.14\% - 26.13\%), from 6.37\% (5.93\% - 6.88\%) in 2006 to
+27.86\% (24.08\% - 33.01\%) in 2020. For TMC, the largest percentage decrease between 2006 and 2020 was in
+Ghana at 8.76\% (6.09\% - 9.61\%), from 58.2\% (55.2\% - 60.8\%) in 2006 to 49.44\% (45.58\% - 54.71\%) in 2020.
+
+The number of annual MCs performed increased from 0.29 million (0.23 - 0.38 million) in 2006 to 0.29 million
+(0.23 - 0.38 million) in 2020, a growth of 0.1 million (0.056 - 0.127 million) annually, averaged across all
+interceding years. Amongst these, 0.29 million (0.23 - 0.38 million) were MMCs in 2006, while in 2020 0.391
+million (0.287 - 0.506 million) MMCs were performed, representing an increase in million (0.012 - 0.166
+million) in MMCs performed annually. The number of TMCs performed annually did increase slightly from
+2006, from 0.12 million (0.115 - 0.125 million) to 0.128 million ( 0.085 - 0.159 million) in 2020. However,
+TMC prevalence actually decreased in many countries from 2006 to 2020. This is the focus of a later results
+section.
 
@@
 
-Within countries, the median difference in MC coverage between the districts with lowest and highest coverage in 2020 was x\% (x\% - x\%).
-For ESA countries, this was x\% (x\% - x\%), in contrast to WCA countries, where it was x\% (x\% - x\%).
-The largest variation overall (and ESA) was in x, from x\% in x to x\% in x, while the largest variation for WCA countries was x, from x\% in x to x\% in x. 
-In total, the mean percentage of districts in each country with greater than 90\% MC coverage amongst those aged 10-29 was x\%. In ESA, this was x\%, while in WCA, this was x\%.
+% Within countries, the median difference in MC coverage between the districts with lowest and highest coverage in 2020 was x\% (x\% - x\%).
+% For ESA countries, this was x\% (x\% - x\%), in contrast to WCA countries, where it was x\% (x\% - x\%).
+% The largest variation overall (and ESA) was in x, from x\% in x to x\% in x, while the largest variation for WCA countries was x, from x\% in x to x\% in x. 
+% In total, the mean percentage of districts in each country with greater than 90\% MC coverage amongst those aged 10-29 was x\%. In ESA, this was x\%, while in WCA, this was x\%.
 
@@
 However, this has resulted in just x country, x, expected to have realised this goal.
-Granular district and age-stratified estimates for MC, as provided by threemc, provide a key source of information for focusing further programme implementation in these VMMC priority countries, in addition to subnational HIV burden estimates which identify the areas most in need of HIV prevention interventions such as VMMC.
+Granular district and age-stratified estimates for MC, as provided by \verb|threemc|, provide a key source of information for focusing further programme implementation in these VMMC priority countries, in addition to subnational HIV burden estimates which identify the areas most in need of HIV prevention interventions such as VMMC.
 
-% In the majority of VMMC countries, the results of threemc and DMPPT2 largely agree. 
-% However, for several countries, namely Tanzania, Zimbabwe and parts of Kenya, we can see that DMPPT2 estimates far exceed empirical survey and threemc estimates, and indeed the population of many districts, suggesting that they may be adversely affected by
+% In the majority of VMMC countries, the results of \verb|threemc| and DMPPT2 largely agree. 
+% However, for several countries, namely Tanzania, Zimbabwe and parts of Kenya, we can see that DMPPT2 estimates far exceed empirical survey and \verb|threemc| estimates, and indeed the population of many districts, suggesting that they may be adversely affected by
 % \begin{enumerate}
@@
 % \end{enumerate}
-% Where it is desired to incorporate VMMC programme data in estimates of MC coverage, threemc may provide a useful "baseline" circumcision estimate for DMPPT2 up until the last household survey was performed, with programme data taking over as the main data source thereafter.
-% threemc may also complement DMPPT2 in it's inclusion of estimates for TMC, since DMPPT2 and the programme data only concern MMC.
+% Where it is desired to incorporate VMMC programme data in estimates of MC coverage, \verb|threemc| may provide a useful "baseline" circumcision estimate for DMPPT2 up until the last household survey was performed, with programme data taking over as the main data source thereafter.
+% \verb|threemc| may also complement DMPPT2 in it's inclusion of estimates for TMC, since DMPPT2 and the programme data only concern MMC.
 
-There were several limitations inherent in the threemc model, and in this analysis. 
+There were several limitations inherent in the \verb|threemc| model, and in this analysis. 
 TODO: Write these out!
 There is much scope for further developments from this analysis. 
-One obvious, though difficult possibility is the incorporation of programme data within threemc. 
-Efforts to do so in South Africa were successful in the original threemc paper, but further implementation of the model including programme data in Malawi has struggled to ?
+One obvious, though difficult possibility is the incorporation of programme data within \verb|threemc|. 
+Efforts to do so in South Africa were successful in the original \verb|threemc| paper, but further implementation of the model including programme data in Malawi has struggled to ?
 survey and programme data.
-In the face of these difficulties, a viable compromise may be to use threemc to provide baseline MC and estimates for TMC to the DMPPT2 tool, as described above. 
+In the face of these difficulties, a viable compromise may be to use \verb|threemc| to provide baseline MC and estimates for TMC to the DMPPT2 tool, as described above. 
 The results of this analysis can also provide circumcision coverage covariates to eligible models which seek to estimate and predict HIV incidence and prevalence, such as Naomi. 
-Finally, we hope that threemc can continue to incorporate new household surveys as they become available, which will be useful for both providing new circumcision estimates, and validating current predictions.
+Finally, we hope that \verb|threemc| can continue to incorporate new household surveys as they become available, which will be useful for both providing new circumcision estimates, and validating current predictions.
 In particular, a new DHS survey is expected for Botswana in ?, a welcome development which will allow the model to be extended to this VMMC priority country.
@@
 \label{sec:org2a96da6}
-threemc is implemented in an R package, which can be found on Github at \url{https://github.com/mrc-ide/threemc}.
-The code used to generate the results of this paper is located at \url{https://github.com/mrc-ide/threemc-orderly}, and makes heavy use of the orderly R package [include reference!].
+\verb|threemc| is implemented in an R package, which can be found on Github at \url{https://github.com/mrc-ide/threemc}.
+The code used to generate the results of this paper is located at \url{https://github.com/mrc-ide/threemc-orderly}, and makes heavy use of the \verb|orderly| R package [include reference!].
 \end{document}

### 2024-04-05 paper/paper_cals.Rmd
First section draft done

---
title: "Circumcision Paper Text"
author: "Paddy O'Toole"
date: "2023-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- TODO: Change year from 2020 to 2023 -->

```{r, echo = FALSE}
# libraries
library(dplyr, warn.conflicts = FALSE)

# Metadata 
spec_agegroup <- "15-29"
spec_years <- c(2006, 2020)

ssa_iso3 <- sort(c(
  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
))
```

```{r, echo = FALSE}
# Functions

# change numbers to be expressed in "millions"
to_mill <- \(x) round(x / 1e6, 3)

# change decimal to percentage
to_percentage <- \(x) paste0(round(x * 100, 2), "%")

# translate iso3 to country name
to_cntry_name <- function(x) {
  x_cntry = countrycode::countrycode(x, "iso3c", "country.name")
  # special cases
  case_when(
      x_cntry == "Congo - Brazzaville" ~ "Congo",
      x_cntry == "Congo - Kinshasa"    ~ "DR Congo",
      TRUE                             ~ x_cntry
  )
}

# simplify type
simplify_type <- function(dat) {
  dat %>% 
    mutate(type = case_when(
      grepl("MMC", type) ~ "MMC", 
      grepl("TMC", type) ~ "TMC", 
      TRUE               ~ "MC"
    ))
}
```

# Results

## Subnational Variation in Total, Medical \& Traditional Circumcision over time

```{r, echo = FALSE}
x1 <- readRDS("data/inlines/01_inlines.RDS")
for (i in seq_along(x1)) {
  assign(names(x1)[i], x1[[i]])
}
iso3_lowest_highest_cov <- simplify_type(iso3_lowest_highest_cov)
iso3_cov_diffs <- simplify_type(iso3_cov_diffs)
```

<!-- I surely need to add something about 10-29/15-29 year olds here? -->
<!-- Plot is of 15-29 year olds, but then I talk only about whole pop here -->
In 2006, the year before VMMC programme implementation began, an estimated 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_mill()` 
million men (95\% CI: 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_mill()` 
-
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in the 33 countries in SSA for which we have valid 
circumcision data. 
Of these, 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were MMCS, and 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) were TMCS. 
This contrasts with 2020, where an estimated 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_mill()` 
million males 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in these same countries, of which 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were performed as MMCS, and 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) as TMCS. 
This constituted an increase of 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) newly circumcised males between 2006 and 2020, with 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) new MMCs performed, and 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(upper) %>% to_mill()` 
million) new TMCs performed. 
The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
This translated to a change in mean MC coverage for the SSA region from 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`)
in 2020, or an increase of
`r covs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`).
MMC coverage increased from 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`) 
in 2020, an increase of 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`).
while TMC changed from 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2020, a decrease of
`r covs[[2]] %>% filter(type == "TMC") %>% mutate(mean = mean * -1) %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "TMC") %>% mutate(upper = upper * -1) %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "TMC") %>%  mutate(lower = lower * -1) %>%  pull(lower) %>% to_percentage()`).

<!-- TODO: Need to change this to be filtered by year as well!! -->
MC coverage in each country in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
In contrast, in 2020 MC coverage was estimated to have ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
<!-- Anything else to be said about this? -->

The largest percentage increase in MC coverage from 2006 to 2020 was 
in 
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020,
while the highest percentage increase in MMC was also in 
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020. 
For TMC, the largest percentage decrease between 2006 and 2020 was in 
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020.

The number of annual MCs performed increased from 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2006 to 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2020, a growth of 
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million (
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(lower) %>% to_mill()`
-
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) annually, averaged across all interceding years. 
Amongst these, 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) were MMCs in 2006, while in 2020 
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_mill()` 
million) MMCs were performed, representing an increase in 
million 
(`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) in MMCs performed annually. 
The number of TMCs performed annually did increase slightly from 2006, from 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_mill()` 
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) to 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_mill()`
million
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_mill()`
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_mill()`
million) in 2020. However, 
TMC coverage actually decreased in many countries from 2006 to 2020. 
<!-- Should I give a number here? -->
This is the focus of section \ref{sec:org5fb5e18}.

<!-- *Second Plot* -->
<!-- Want to show here how ??? -->
Within countries, the median difference in MC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(area_name)`
,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(area_name)`.
The median difference within countries in MMC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(area_name)`,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(area_name)`.
For TMC coverage, the median difference between districts in 2020 was 
`r district_diffs_vmmc$median_cov_diffs %>% filter(type == "TMC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(area_name)`,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(area_name)`.
<!-- Anything else? --->

### 2024-04-05 paper/paper.tex

@@
 
-Patrick O'Toole\textsuperscript{1},
-Matthew L. Thomas\textsuperscript{1,2},
+Patrick O'Toole\textsuperscript{1,2},
+Matthew L. Thomas\textsuperscript{1,3,4},
 Oliver Stevens\textsuperscript{1},
-Kevin Lam\textsuperscript{1,3},
-Katharine Kripke\textsuperscript{4},
+Kevin Lam\textsuperscript{1,5},
+Katharine Kripke\textsuperscript{6},
 Rachel Esra\textsuperscript{1},
-Ian Wanyeki\textsuperscript{5},
-Lycias Zembe\textsuperscript{5},
-Jeffrey W. Imai-Eaton\textsuperscript{1,6} \\
+Ian Wanyeki\textsuperscript{7},
+Lycias Zembe\textsuperscript{7},
+Jeffrey W. Imai-Eaton\textsuperscript{1,8} \\
 \smallskip
 
-\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial Colleg  e London, London, United Kingdom\\
-\textbf{2} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
-\textbf{3} Department of Statistics, University of British Columbia, Vancouver, Canada\\
-\textbf{4} Avenir Health, Washington, District of Columbia, United States of America\\
-\textbf{5} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
-\textbf{6} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
+\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London, London, United Kingdom\\
+\textbf{2} Department of Mathematical Sciences, University of Bath, Bath, United Kingdom\\
+\textbf{3} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{4} National Centre for Atmospheric Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{5} Department of Statistics, University of British Columbia, Vancouver, Canada\\
+\textbf{6} Avenir Health, Washington, District of Columbia, United States of America\\
+\textbf{7} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
+\textbf{8} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
 
@@
 To achieve the the global community's ambitious goals of ending the AIDS public health crisis by 2030, more work will need to be done \cite{UNAIDSStrategy}.
-Among the numerous interventions available, voluntary medical male circumcision (VMMC) has emerged as a powerful and cost-effective intervention to reduce HIV incidence \cite{bansi2023cost} with it is estimated to reduce male-to-female transition of HIV by nearly 60\% \cite{gray2007male, bailey2007male, auvert2005randomized, gray2012effectiveness, grund2017association}.
+Among the numerous interventions available, voluntary medical male circumcision (VMMC) has emerged as a powerful and cost-effective intervention to reduce HIV incidence \cite{bansi2023cost} with it estimated to reduce male-to-female transition of HIV by 60\% \cite{gray2007male, bailey2007male, auvert2005randomized, gray2012effectiveness, grund2017association}.
 Furthermore, other research has shown that VMMC can decrease the risk of male-to-male transmission of HIV \cite{pintye2019benefits}, and reduce the transmission of other sexually transmitted infections \cite{tobian2009male}.
 
-There is a need to provide comprehensive estimates of male circumcision coverage by age,  time and type across sub-Saharan Africa, however, the landscape is complex and highly heterogeneous for numerous reasons.
-\todo{Need to expand this and add citations}
+In 2007, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
+UNAIDS' aim was to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework}.
+As a result, over XX\todo{Find this number and cite} million VMMCs have been conducted in these priority countries between 2007 and 2022 with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR).
 
-Firstly, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}.
-Ambitious targets were set by UNAIDS to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework} and as a result, over XX\todo{Find this number and cite} million VMMCs have been conducted in these priority countries between 2007 and 2022 with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR).
+There is a need to provide comprehensive \todo{Want to make point that TMC is decreasing in this para, but don't have a reference.
+Paddy said there was, check with him.} and accurate estimates of male circumcision coverage across all ages, over time, across sub-Saharan Africa to (i) aid VMMC programmes planning, delivery, target setting and checking target attainment and (ii) to evaluate the impacts of VMMC campaigns on HIV incidence.
+However, this is complex task, as despite the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries.
+The coverage and provision of traditional male circumcision (TMC) can vary considerably and is mainly influenced by community, religious, ethnic and cultural led values.
+For example, in South Africa, TMC coverage ranged from 5.3\% in KwaZulu-Natal to 48.9\% in Eastern Cape among 15-49 year olds, with the average age of circumcision varying from 12.2 years in Limpopo to 20.4 in Western Cape \cite{thomas2024substantial}.
+\todo{Should I add a national comparison from the results?} TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training \cite{drain2006male, wilcken2010traditional, weiss2000male}.
+The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, as TMC may not involve a complete circumcision in some populations \cite{WHOTraditional, shaffer2007protective, bailey2008male}.
 
-Secondly, while the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries.
-The provision of traditional male circumcision (TMC), such as the typical age at circumcision and what it entails, can vary considerably and is influenced by community, religious, ethnic and cultural led values.
-There is substantial sub-national heterogeneity in the proportion and average of men receiving TMC between at a district level in South Africa.
-Even on a national level TMC is universally practiced in {\color{red}\bf XXX} and is barely conducted in {\color{red}\bf XXX}.
-TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training.
-The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, as TMC may not involve a complete circumcision and instead be only partial removal of the foreskin or a simple incision in the prepuce in some populations.
-\todo{Cite this paragraph.}
-
+There have been a number of recent approaches to estimate coverage of circumcision in sub-Saharan Africa \cite{cork2020mapping, kripke2016age, kripke2016cost, thomas2024substantial}.
 Cork et al.
-provided the first set of comprehensive estimates of circumcision coverage in sub-Saharan Africa.
-They used survey data within a Bayesian geo-statistical model to produce annual estimates of total male circumcision coverage subnationally in sub-Saharan Africa between 2000 and 2017.
-Their approach focused on predicting circumcision coverage among only the aggregate age range 15–49 years, did not distinguish between circumcision type, and did not track the structured dynamics of circumcision coverage by type within cohorts.
+\cite{cork2020mapping} developed a Bayesian geo-statistical model, which utilizes survey data, to produce annual estimates of total male circumcision coverage sub-nationally in sub-Saharan Africa between 2000 and 2017.
+This approach is limited cannot provide a full picture of the coverage and provisions of circumcision alone, as the model only produced estimates at the aggregate age range 15–49 years, does not distinguish between circumcision type, and does not track the structured dynamics of circumcision coverage by type within cohorts.
+Kripke et al.
+\cite{kripke2016age, kripke2016cost} developed The Decision Makers’ Program Planning Toolkit, Version 2 (DMPPT2), a compartmental model that combines estimates of circumcision coverage from survey data prior to the VMMC scale-up, with information on the reported numbers of VMMCs, to estimate circumcision coverage and unmet need across sub-Saharan Africa in 5-year age groups at a subnational level over time.
+This approach is also limited as the model does not incorporate data from more recent household surveys (since intervention implementation), does not estimate any uncertainty associated with the circumcision coverage estimates and also does not distinguish by circumcision type.
 
 Thomas et al.
-aimed to address these issues by producing a model that synthesises both survey and programmatic data to generate region-age-time-type specific probabilities and coverage of male circumcision.
-The model extended a competing risks time-to-event model which enabled ...
-However, this study only focused on South Africa....
-
-Here, we take a similar approach to Thomas et al.
-in order to model estimate the probabilities and coverage of medical and traditional male circumcision by subnational area, single-year age, and time with probabilistic uncertainty.
-Here
+\cite{thomas2024substantial} aimed to address the issues of both models by producing a model to generate region-age-time-type specific probabilities and coverage of male circumcision.
+The model extended a competing risks time-to-event model which enabled the synthesising of both survey data and programmatic data from VMMC providers.
+However, this study focused only on South Africa and the model was developed with many local dynamics in the provision to synthesise both data sources.
+\todo{Jeff - Feel like I need to expand this but not sure how much detaul to give here.}Here, we take a similar approach to Thomas et al.
+and develop a discrete-time competing risks time-to-event model only using survey data in order to estimate the probabilities and coverage of medical and traditional male circumcision by sub-national area, single-year age, and time along with probabilistic uncertainty.
+We applied the model to estimate annual probabilities and coverage of circumcision by district in XXX countries across sub-Saharan Africa between 2008 and 2023 in order to quantify gaps in attainment of VMMC targets within priority age groups.
 
@@
 The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
-We excluded Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
+We excluded Equitorial Guinea, Guinea-Bissau and the Central African Republic because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
 
@@
 17 surveys had more than 90\% left censoring of circumcision age, with 42 surveys having less than 10\% left censoring.
+\todo{Rewrite now BWA has surveys!}
 No information on age at circumcision was present in the 2004 and 2008 Botswana Aids Impact Surveys.
@@
 
+\todo{Rewrite as BWA now has surveys}
 In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit \verb|threemc| in these countries either.
@@
 2006, from 0.12 million (0.115 - 0.125 million) to 0.128 million ( 0.085 - 0.159 million) in 2020. However,
-TMC prevalence actually decreased in many countries from 2006 to 2020. This is the focus of a later results
-section.
+TMC coverage actually decreased in many countries from 2006 to 2020. This is the focus of section \ref{sec:org5fb5e18}.
 
@@
 \end{figure}
+
+Within countries, the median difference in MC coverage between districts with lowest and highest coverage in 2020 was 56.01\% The smallest variation was in Lesotho, at 48.97\% in Qacha’s Nek to 55.26\% in Berea, while the largest variation was in Mozambique, at 5.35\% in Chifunde to 77.9\% in Homoíne.
+The median difference within countries in MMC coverage between districts with lowest and highest coverage in 2020 was 38.69\% The smallest variation was in Eswatini, at 16.94\% \% in Shiselweni to 24.69\% \% in Manzini, while the largest variation was in Tanzania, at 7.81\% \% in Tandahimba DC to 74.87\% \% in Iringa MC.
+For TMC coverage, the median difference between districts in 2020 was 55.54\% The smallest variation was in Eswatini, at 0.97\% in Eenhana to 79.51\% in Okakarara, while the largest variation was in Namibia, at 0.45\% in Lubombo to 100\% in Manzin.
+
+\todo{Anything else to add here?}
 
@@
 
-\section{Availability of data and materials}
-\label{sec:orgd999c87}
-\subsection{Data Availability}
-\label{sec:org953a659}
-\subsection{Code Availability}
-\label{sec:org2a96da6}
-\verb|threemc| is implemented in an R package, which can be found on Github at \url{https://github.com/mrc-ide/threemc}.
-The code used to generate the results of this paper is located at \url{https://github.com/mrc-ide/threemc-orderly}, and makes heavy use of the \verb|orderly| R package [include reference!].
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Acknowledgments}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+{\color{red}(Ask Jeff for funding information.)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Author contributions}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+{\color{red}(Ask Jeff to help with this.)} P.O.T, M.L.T., and J.W.I.-E.
+conceived the study.
+P.O.T, J.W.I.-E., O.S.
+and R.E.
+collated data sources.
+P.O.T.
+led the data management and conducted the analysis.
+P.O.T.
+and M.L.T developed the statistical model.
+K.K., I.W.
+and L.Z.
+gave expert input on circumcision on the models and interpretation of data and results.
+P.O.T.
+and M.L.T.
+wrote the first draft of the manuscript with input from J.W.I.-E.
+All authors revised the manuscript for content and approved the final version for submission.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Code Availability}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The code used to implement the models and produce the results presented in this manuscript is available from {\color{red}(Add link)}.
+We have also archived the code on Zenodo and this is available from {\color{red}(Add Link)}.
+An R package implementing an updated and extended version of the methods from this manuscript is currently being constructed and is available from https://github.com/mrc-ide/threemc.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Data Availability}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Household survey data are available by request to and The Demographic and Health Survey (DHS) Program (https://dhsprogram.com/ methodology/survey/survey-display-390.cfm) the South Africa Human Science Research Council (HSRC; http://datacuration.hsrc.ac.za/content/view/access-to-data), Population-based HIV Impact Assessment Project (PHIA; <Link>), and Botswana AIDS Impact Survey (BAIS, <Link>).
+Estimates of population were obtained from {\color{red}(Ask Jeff)}.
+Administrative boundaries and hierarchies were obtained from {\color{red}(Ask Jeff)}.
+The source data underpinning the results presented in this manuscript can be found in Supplementary Data {\color{red}(Add This.)}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Competing Interests}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The authors declare no competing interests.
+
 \end{document}

### 2024-04-10 paper/paper_cals.Rmd
Add text from other sections, to be filled in

@@
 <!-- Anything else? --->
+
+## Subnational Variation in Total, Medical \& Traditional Circumcision across different ages
+
+Age at circumcision differed greatly by circumcision type and location. 
+The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was x, reflecting VMMC focus on these ages. 
+The age group with the highest MC coverage in 2020 was x, in contrast to 2006, where this age group was x. 
+The age group with the highest MMC coverage in 2020 was x, while for TMC coverage this age group was x. 
+The average age of MC in 2020 in SSA was x, compared to x in 2006. 
+For MMC, the average age at circumcision in 2020 was x, compared to x in 2006, while for TMC the average age was x in 2020, compared to x in 2006. 
+The average age of MC in 2020 for ESA was x, while in WCA it was x.
+
+## Subnational Heterogeneity in Age at Medical and Traditional Circumcision
+
+Fill in!
+
+## Decrease in TMC in SSA region Over Time
+
+The average TMC coverage in SSA in 2006 was x\% (x\% to x\%). 
+This fell to x\% (x\% to x\%) in 2020, representing a decrease of x\% (x\% to x\%). 
+In ESA, TMC coverage was x\% (x\% to x\%) in 2006, compared to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) decrease.
+In constrast, TMC coverage in WCA was x\% (x\% to x\%) versus x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) fall.
+In 2006, x (x to x) TMCs were performed, while in 2020 this was reduced to x (x to x), representing a x (x to x) decrease in annual TMCs.
+In ESA, the annual number of TMCs performed dropped from x (x to x) in 2006 to x (x to x) in 2020, a x (x to x) drop. 
+In WSA, this number fell from x (x to x) in 2006 to x (x to x) in 2020, a fall of x (x to x).
+For the 10-29 age group, TMC coverage was reduced from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a drop of x\% (x\% to x\%).
+In VMMC countries, this was reduced from x\% (x\% to x\%) to x\% (x\% to x\%) from 2006 to 2020, while even in non-VMMC countries this decreased from x\% (x\% to x\%) to x\% (x\% to x\%). 
+The largest decrease in TMC coverage from 2006 to 2020 was in x, from x\% (x\% to x\%) to x\% (x\% to x\%). 
+[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from x\% (x\% to x\%) to x\% (x\% to x\%) in x.
+
+## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries
+
+Amongst the 13 VMMC priority countries modelled, just x countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, x and x. 
+MC coverage across these countries increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020. 
+X (x to x) circumcisions were performed between 2007 and 2020 in these countries. 
+Of these, x (x to x) were MMCs. 
+No countries were expected to have reached this goal in all districts. 
+The number of annual MCs increased from x (x to x) in 2006 to x (x to x) in 2020. 
+x (x to x) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, x (x to x) times the projected number of MCs for 2020. 
+The largest increase in MC coverage amongst VMMC priority countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase. 
+In contrast, the lowest increase in MC coverage in these countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.
+
+However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries. 
+x/x districts in these countries were expected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from x/x in 2006, before VMMC programmes began. 
+Even in x, where MC was projected to be lowest in 2020, x/x districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
+MC coverage there increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.

### 2024-04-10 paper/paper_cals.Rmd
Put xs on their own lines

--- 2024-04-05 paper/paper_cals.Rmd
@@
 <!-- Anything else? --->
+
+## Subnational Variation in Total, Medical \& Traditional Circumcision across different ages
+
+<!-- TODO: Replace WCA/ECA with VMMC/Non-VMMC -->
+
+Age at circumcision differed greatly by circumcision type and location. 
+The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was 
+x, 
+reflecting VMMC focus on these ages. 
+The age group with the highest MC coverage in 2020 was 
+x, 
+in contrast to 2006, where this age group was 
+x. 
+The age group with the highest MMC coverage in 2020 was 
+x, 
+while for TMC coverage this age group was 
+x. 
+The average age of MC in 2020 in SSA was 
+x, 
+compared to 
+x 
+in 2006. 
+For MMC, the average age at circumcision in 2020 was 
+x, 
+compared to 
+x 
+in 2006, while for TMC the average age was 
+x 
+in 2020, compared to 
+x 
+in 2006. 
+The average age of MC in 2020 for ESA was 
+x, 
+while in WCA it was 
+x.
+
+## Subnational Heterogeneity in Age at Medical and Traditional Circumcision
+
+Fill in!
+
+## Decrease in TMC in SSA region Over Time
+
+The average TMC coverage in SSA in 2006 was 
+x
+\% (
+x
+\% to 
+x
+\%). 
+This fell to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, representing a decrease of 
+x
+\% (
+x
+\% to 
+x
+\%). 
+In ESA, TMC coverage was 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006, compared to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a 
+x
+\% (
+x
+\% to 
+x
+\%) decrease. 
+In constrast, TMC coverage in WCA was 
+x
+\% (
+x
+\% to 
+x
+\%) versus 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a 
+x
+\% (
+x
+\% to 
+x
+\%) fall. 
+In 2006, 
+x 
+(
+x 
+to 
+x
+) TMCs were performed, while in 2020 this was reduced to 
+x 
+(
+x to 
+x
+), representing a 
+x (
+x
+to
+x
+) decrease in annual TMCs.
+In ESA, the annual number of TMCs performed dropped from 
+x
+(
+x
+to 
+x
+) in 2006 to 
+x
+(
+x
+to 
+x
+) in 2020, a 
+x 
+(
+x
+to 
+x
+) drop. 
+In WSA, this number fell from 
+x 
+(
+x 
+to 
+x
+) in 2006 to 
+x 
+(
+x
+to 
+x
+) in 2020, a fall of 
+x
+(
+x
+to 
+x
+).
+<!-- TODO: Change to 15-29, right? -->
+For the 10-29 age group, TMC coverage was reduced from 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006 to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a drop of 
+x
+\% 
+(
+x
+\% to 
+x
+\%).
+In VMMC countries, this was reduced from 
+x
+\% (
+x
+\% to 
+x
+\%) to 
+x
+\% (
+x
+\% to 
+x
+\%) from 2006 to 2020, while even in non-VMMC countries this decreased from 
+x
+\% (
+x
+\% to 
+x
+\%) to 
+x
+\% (
+x
+\% to 
+x
+\%). 
+The largest decrease in TMC coverage from 2006 to 2020 was in 
+x
+, from 
+x
+\% (
+x
+\% to 
+x
+\%) to 
+x
+\% (
+ x 
+\% to 
+ x 
+\%). 
+[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from 
+x 
+\% (
+x 
+\% to 
+x 
+\%) to 
+x 
+\% (
+x 
+\% to 
+x 
+\%) in 
+x 
+.
+
+## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries
+
+Amongst the 13 VMMC priority countries modelled, just 
+x
+ countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
+x
+ and 
+x
+. 
+MC coverage across these countries increased from 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006 to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020.
+
+x
+ (
+x
+ to 
+x
+) circumcisions were performed between 2007 and 2020 in these countries. 
+Of these, 
+x
+ (
+x
+ to 
+x
+) were MMCs. 
+No countries were e
+x
+pected to have reached this goal in all districts. 
+The number of annual MCs increased from 
+x
+ (
+x
+ to 
+x
+) in 2006 to 
+x
+ (
+x
+ to 
+x
+) in 2020.
+
+x
+ (
+x
+ to 
+x
+) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, 
+x
+ (
+x
+ to 
+x
+) times the projected number of MCs for 2020. 
+The largest increase in MC coverage amongst VMMC priority countries was in 
+x
+, from 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006 to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a 
+x
+\% (
+x
+\% to 
+x
+\%) increase. 
+In contrast, the lowest increase in MC coverage in these countries was in 
+x
+, from 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006 to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a 
+x
+\% (
+x
+\% to 
+x
+\%) increase.
+
+However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries.
+
+x
+/
+x
+ districts in these countries were e
+x
+pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
+x
+/
+x
+ in 2006, before VMMC programmes began. 
+Even in 
+x
+, where MC was projected to be lowest in 2020, 
+x
+/
+x
+ districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
+MC coverage there increased from 
+x
+\% (
+x
+\% to 
+x
+\%) in 2006 to 
+x
+\% (
+x
+\% to 
+x
+\%) in 2020, a 
+x
+\% (
+x
+\% to 
+x
+\%) increase.

### 2024-04-11 paper/paper_cals.Rmd
Add five year age group comparisons for VMMC countries

@@
 
-## Subnational Variation in Total, Medical \& Traditional Circumcision across different ages
+## Subnational Variation in total, medical \& traditional circumcision across different ages
+
+```{r, echo = FALSE}
+x2 <- readRDS("data/inlines/02_inlines.RDS")
+for (i in seq_along(x2)) {
+  assign(names(x2)[i], x2[[i]])
+}
+age_group_cov <- sapply(
+  age_group_cov, simplify_type, simplify = FALSE, USE.NAMES = TRUE
+)
+age_group_cov_non_vmmc <- sapply(
+  age_group_cov_non_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
+)
+age_group_cov_vmmc <- sapply(
+  age_group_cov_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
+)
+```
 
@@
 Age at circumcision differed greatly by circumcision type and location. 
-The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was 
-x, 
-reflecting VMMC focus on these ages. 
-The age group with the highest MC coverage in 2020 was 
-x, 
-in contrast to 2006, where this age group was 
-x. 
-The age group with the highest MMC coverage in 2020 was 
-x, 
-while for TMC coverage this age group was 
-x. 
-The average age of MC in 2020 in SSA was 
-x, 
-compared to 
+The five-year age group in 2006, the year before VMMC programme implementation began, 
+which had the highest MC coverage across the SSA region was
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(age_group)`, 
+at 
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`
+)
+. 
+In contrast, the age group with the highest MC coverage in 2020 was 
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(age_group)`,
+at
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`
+).
+The five-year age group in 2006 which had the highest MMC coverage was
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(age_group)`, 
+at 
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`
+)
+. 
+The age group with the highest MMC coverage in 2020 was also
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(age_group)`,
+, now at
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`
+).
+The five-year age group in 2006 which had the highest TMC coverage was
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(age_group)`, 
+at 
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`
+)
+. 
+The age group with the highest TMC coverage in 2020 was
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(age_group)`,
+,
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
+-
+`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`
+).
+This decrease in the five-year age group with the highest MC coverage, increase in the 
+age group for TMC with the highest coverage (as well as a decrease in coverage for 
+the highest five-year age group), and increase in overall MMC coverage across the SSA region is 
+indicative of the effect of VMMC programme implementation on the region.
+
+<!-- TODO Still: 
+- 15-29 year olds increase in MC/TMC/MMC (already written about?)
+- Contrast to 30-49 year olds somehow, showing different patterns of circ
+(increasing more for MC/MMC, decreasing more for TMC)
+- Compare differences in VMMC and non-VMMC, in terms of the above
+-->
+We may compare changes in circumcision amongst two age groups; 15-29 year olds, which 
+are a particular focus for VMMC implementation, and 30-49 year olds, which are not. 
+MC coverage amongst 15-29 year olds increased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+In contrast, MC coverage amongst 30-49 year olds only increased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Therefore, MC coverage across SSA saw greater increases in this younger age group than in this older one, in line 
+with VMMC programme age focus. 
+Similarly, MMC coverage amongst 15-29 year olds increased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while MMC coverage amongst 30-49 year olds increased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Therefore, MMC coverage across SSA also saw greater increases amongst 15-29 year olds 
+than amongst 30-49 year olds. 
+The changes seen in TMC, however, contrast to these larger increases in MC and MMC coverage for 15-29 year olds. 
+TMC coverage amongst 15-29 year olds decreased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Thus, TMC coverage decreased less in absolute terms amongst 30-49 year olds than amongst 
+15-29 year olds, which is line with the greater focus on performing MMCs amongst this 
+younger age group.
+
+Finally, we can contrast patterns in circumcision pattern for different age groups
+amongst VMMC and non-VMMC priority countries, where differences in 2006 and 2020 
+levels and patterns of circumcision seem to be more pronounced.
+
+<!-- For VMMC countries, five year age group MC, MMC, TMC -->
+For VMMC priority countries, five-year age group MC coverage in both 2006 and 2020 was highest amongst 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
+) and 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
+), respectively. 
+However, in 2006 MMC coverage was highest amongst 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
+ year olds, at 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
+). 
+This contrasts with 2020, where MMC coverage was highest amongst 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
+ year olds, at
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
+ (
 x
-in 2006. 
-For MMC, the average age at circumcision in 2020 was 
-x, 
-compared to 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
+ - 
 x
-in 2006, while for TMC the average age was 
-x 
-in 2020, compared to 
-x 
-in 2006. 
-The average age of MC in 2020 for ESA was 
-x, 
-while in WCA it was 
-x.
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
+), showing a shift upwards in age for MMCs in VMMC priority countries, as a result of VMMC focus on young adults. 
+In 2006, TMC coverage was greatest in 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
+). while in 2020 it was most prevalent in
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`, highlighting a shift upwards in TMCs in VMMC priority countries, 
+likely resulting from previously TMCs being performed as TMCs.
+
+For non-VMMC countries, five year age group MC, MMC, TMC
+
+Similarly, we can compare the 2006 and 2020 circumcision levels amongst 15-29 and 30-49 year olds
+in both VMMC and non-VMMC countries, respectively.
 
@@
 Fill in! 
+- Talk mainly about average age at which MCs/MMCs/TMCs performed in 2006 and 2020
+- Also compare VMMC and non-VMMC
+
+The mean age at circumcision for MC in 2006 was 
+x
+(
+x
+- 
+x
+), while in 2020 it was
+x 
+(
+x
+-
+x
+).
+Similarly, the mean age at circumcision for MMC in 2006 was 
+x
+(
+x
+- 
+x
+), while in 2020 it was
+x 
+(
+x
+-
+x
+).
+Finally, the mean age at circumcision in 2006 for TMC was 
+x
+(
+x
+- 
+x
+), while in 2020 it was
+x 
+(
+x
+-
+x
+).
+So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
+However, it is important to note that the uncertainty ranges in our credible intervals 
+overlap, so this increase is ?. 
+In constant, the mean age at circumcision for TMC decreased. 
+This may suggest that VMMC implementation amongst 15-29 year olds has 
+corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
+replaced some circumcisions which would previously have been performed as TMCs, 
+which may explain the observed decrease in mean age of TMC.
+
+What is the narrative here?
+- For SSA, MC and MMC age goes up, TMC goes down
+- For VMMC, average age for all substantially higher, but follows same pattern. 
+  Could be argued that this is because people previously receiving TMCs are now receiving MMCs, 
+  pushing mean age of TMC down further. 
+- For non-VMMC, ages substantially lower. 
+  MMC age actually decreases, suggesting MMC-nT occuring, replacing TMC!
 
@@
 x
-\% (
+(
 x
-\% to 
+to 
 x
-\%) in 2006 to 
+) in 2006 to 
 x
-\% (
+(
 x
-\% to 
+to 
 x
-\%) in 2020, a 
+) in 2020, a 
 x
-\% (
+(
 x
-\% to 
-x
-\%) increase.
+to 
+x) increase.

### 2024-04-11 paper/paper_cals.Rmd
Add five- and fifteen-year age group comparisons for VMMC vs non-VMMC

@@
 <!-- For VMMC countries, five year age group MC, MMC, TMC -->
-For VMMC priority countries, five-year age group MC coverage in both 2006 and 2020 was highest amongst 
+For VMMC priority countries, five-year age group MC coverage 2006 was highest amongst 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
+), but in 2020 was highest amongst
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(age_group)`
+year olds, at
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
+), respectively. 
+This highlights both the increased prevalence of MC in VMMC priority countries, and the
+downward shift in age profile of those who are circumcised, since VMMC programme 
+implementation began. 
+In 2006 MMC coverage was highest amongst 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
+ year olds, at 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
+). 
+This contrasts with 2020, where MMC coverage was highest amongst 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
+ year olds, at
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
+ (
+x
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
+ - 
+x
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
+).
+This shows that much of the downward shift in age profile of circumcised individuals since 2006 
+has been "driven" by an increase in the number of MMCs performed amongst younger individuals. 
+In 2006, TMC coverage was greatest in 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
+). while in 2020 it was most prevalent in
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
+year olds, at 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
+ (
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
+ - 
+`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`.
+This perhaps highlights that VMMC implementation has been focused on areas where 
+TMC has not historically been widely prevalent, and so seems to have had little effect on patterns of TMC in 
+VMMC priority countries, both in terms of its age profile and prevalence.
+
+We can constrast this for the non-VMMC priority countries in SSA.
+The five-year age group MC coverage in both 2006 and 2020 was highest amongst 
 `r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
@@
 ), respectively. 
+This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) hasn't noticably changed. 
 However, in 2006 MMC coverage was highest amongst 
@@
 `r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
-), showing a shift upwards in age for MMCs in VMMC priority countries, as a result of VMMC focus on young adults. 
+), showing an interesting shift upwards in age for MMCs in non-VMMC priority countries, as a result of VMMC focus on young adults, as well as a general increase in MMC coverage in these countries. 
 In 2006, TMC coverage was greatest in 
@@
 
-For non-VMMC countries, five year age group MC, MMC, TMC
-
 Similarly, we can compare the 2006 and 2020 circumcision levels amongst 15-29 and 30-49 year olds
 in both VMMC and non-VMMC countries, respectively.
+
+In VMMC priority countries, MC coverage amongst 15-29 year olds increased from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+In contrast, MC coverage in 30-49 year olds went from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Therefore, MC coverage in VMMC priority countries increased amongst 15-29 year olds at a higher rate than amongst 30-49 year olds, and indeed greater than in SSA as a whole, highlighting the effects of VMMC implementation in these countries since 2006.
+Similarly, MMC coverage amongst 15-29 year olds increased from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while MMC coverage amongst 30-49 year olds increased from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Therefore, MMC coverage in VMMC priority countries also saw greater increases amongst 15-29 year olds 
+than amongst 30-49 year olds, and greater increases than for SSA as a whole. 
+Again, TMC coverage amongst both fifteen year age groups constrast to these increases for MC and MMC. 
+TMC coverage amongst 15-29 year olds decreased from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+This decrease in TMC coverage can partly be attributed to a combination of increased population in non-TMC practising areas, but TMC coverage also decreased less in absolute terms amongst 30-49 year olds than amongst
+15-29 year olds, which is line with the greater focus on performing MMCs, and hence replacing TMCs, amongst this 
+younger age group.
+
+In contrast, for non-VMMC priority countries, MC coverage in 15-29 year olds increased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, staying relatively stagnant. 
+MC coverage in 30-49 year olds also increased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, so again, when taking our credible intervals into account, there was little 
+increase amongst this age group in non-VMMC priority countries. 
+It is interesting that MC seems to have increased more amongst 30-49 year olds 
+than amongst 15-29, defying the trend amongst VMMC priority countries and SSA as a whole. 
+MMC coverage amongst 15-29 year olds increased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while MMC coverage amongst 30-49 year olds increased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Hence, MMC coverage in non-VMMC countries also saw greater increases amongst 30-49 year olds 
+than in 15-29 year olds, but not much change overall when factoring in our uncertainty. 
+TMC coverage amongst 15-29 year olds decreased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
+) in 2006
+to
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
+- 
+`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020. 
+Thus, TMC coverage decreased less in absolute terms amongst 30-49 year olds than amongst 
+15-29 year olds, which is line with the greater focus on performing MMCs amongst this 
+younger age group.
 

### 2024-04-11 paper/paper_cals.Rmd
Finish section 2

@@
 
+<!-- What else could we add to this section? Section 2 is very large!!!
+- Could talk about non-VMMC vs VMMC more anyway -->
+
 ```{r, echo = FALSE}
@@
 million) new TMCs performed. 
-The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
+The disparity between the number of MCs performed and the number of MMCs performed can be partly explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
 This translated to a change in mean MC coverage for the SSA region from 
@@
 `r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, staying relatively stagnant. 
+) in 2020, staying relatively similar. 
 MC coverage in 30-49 year olds also increased from 
@@
 younger age group. 
+TMC coverage decreased more amongst non-VMMC countries for both age groups, suggesting 
+likely replacement of historical TMC with MMC.
 
 ## Subnational Heterogeneity in Age at Medical and Traditional Circumcision
+
+```{r}
+
+```
 
@@
 x
+
 (

### 2024-04-12 paper/paper_cals.Rmd
Finish section 4

@@
----
+ub
 title: "Circumcision Paper Text"
@@
 
-# simplify type
+# simplify type for faster filtering
 simplify_type <- function(dat) {
@@
     ))
+}
+
+# tidy up aggregated age data
+tidy_age <- function(dat, sig_fig = 2) {
+  dat %>% 
+    mutate(across(contains("average_age"), \(x) round(x, sig_fig))) %>% 
+    rename(
+      mean = average_age, lower = average_age_lower, upper = average_age_upper
+    ) %>% 
+    simplify_type()
 }
@@
 ```{r}
-
+x3 <- readRDS("data/inlines/03_inlines.RDS")
+for (i in seq_along(x3)) {
+  assign(names(x3)[i], x3[[i]])
+}
+aggr_mean_circ_age <- tidy_age(aggr_mean_circ_age)
+aggr_mean_circ_age_non_vmmc <- tidy_age(aggr_mean_circ_age_non_vmmc)
+aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
 ```
@@
 The mean age at circumcision for MC in 2006 was 
-x
-
-(
-x
-- 
-x
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(upper)`
 ), while in 2020 it was
-x 
-(
-x
--
-x
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(upper)`
 ).
+<!-- Therefore, factoring in uncertainty there doesn't seem to have been a 
+significant drop in mean age at MC from 2006 to 2020. -->
 Similarly, the mean age at circumcision for MMC in 2006 was 
-x
-(
-x
-- 
-x
-), while in 2020 it was
-x 
-(
-x
--
-x
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
+), and in 2020 it was
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
 ).
+<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
 Finally, the mean age at circumcision in 2006 for TMC was 
-x
-(
-x
-- 
-x
-), while in 2020 it was
-x 
-(
-x
--
-x
-).
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
+), and in 2020 it was
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
 So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
 However, it is important to note that the uncertainty ranges in our credible intervals 
-overlap, so this increase is ?. 
-In constant, the mean age at circumcision for TMC decreased. 
+overlap, so this increase could be seen as "non-significant", in some sense. 
+In contrast, the mean age at circumcision for TMC was seen to decrease, altough again, 
+not in a manor that exceeds our uncertainty bounds. 
 This may suggest that VMMC implementation amongst 15-29 year olds has 
@@
 
-What is the narrative here?
-- For SSA, MC and MMC age goes up, TMC goes down
+As in the previous section, we can also compare how the mean age of circumcision differs 
+amongst VMMC priority countries, versus their non-VMMC prority counterparts in SSA.
+
+For VMMC priority countries, the mean age at circumcision for MC in 2006 was 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(upper)`
+), while in 2020 it was
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(upper)`
+).
+Similarly, for MMC in 2006 the mean age at circumcision was
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
+), while in 2020 it was
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
+).
+<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
+Lastly, the mean age at circumcision in 2006 for TMC was 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
+), and in 2020 it was
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
+So the mean age at circumcision for all circumcision types is higher in VMMC 
+priority countries than overall in SSA, highlighting the historically low levels of MC and
+TMC in these countries. 
+Like in SSA overall, the mean age at circumcision for MC and MMC went up slightly, albeit not 
+significantly when factoring in uncertainty bounds. 
+Again, mean age at TMC also decreased in VMMC priority countries.
+
+For non-VMMC priority countries, the mean age at MC in 2006 was 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(upper)`
+), while in 2020 it was
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(upper)`
+).
+Similarly, the mean age at MMC in 2006 was 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
+), and in 2020 it was
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
+).
+<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
+Finally, the mean age at TMC in 2006 for TMC was 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
+), and in 2020 it was
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
+(
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
+- 
+`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
+In contrast to our VMMC priority countries, these countries have a lower mean at 
+circumcision for all circumcision types, largely driven by high TMC levels historically. 
+It is interesting that the age at circumcision for MC and MMC actually increased for
+non-VMMC priority countries, in contrast to SSA as a whole and the priority countries. 
+Likewise, the mean age at TMC increased. 
+This can perhaps be explained by a possible replacement of TMC with MMC in a 
+traditional setting, so at generally younger ages than MMCs performed as part of 
+VMMC programmes. 
+This caused a natural shift upwards of the mean age at TMC, as younger individuals 
+are now more likely to receive MMCs.
+
+<!-- What is the narrative here?
+- For SSA, MC and MMC age goes up, TMC goes down (done)
 - For VMMC, average age for all substantially higher, but follows same pattern. 
@@
 - For non-VMMC, ages substantially lower. 
-  MMC age actually decreases, suggesting MMC-nT occuring, replacing TMC!
+  MMC age actually decreases, suggesting MMC-nT occuring, replacing TMC! -->
 
@@
 
+```{r}
+x4 <- readRDS("data/inlines/04_inlines.RDS")
+for (i in seq_along(x4)) {
+  assign(names(x4)[i], x4[[i]])
+}
+
+```
+
+Narrative here:
+<!-- TMC coverage difference 2006 - 2020, SSA, VMMC, non-VMMC
+- Decrease much more pronounced for non-VMMC
+Number of TMCs performed in 2006 vs 2020, VMMC, non-VMMC
+- Number increased more for VMMC countries (?)
+Change for 15-29 vs 30-49
+- Change relatively similar for non-VMMC, but 15-29 sees much greater change for 
+  VMMC countries
+Country with largest drop (CIV and ? in VMMC)
+- Comment on population of CIV (28 mil) (?) -->
+
 The average TMC coverage in SSA in 2006 was 
-x
-\% (
-x
-\% to 
-x
-\%). 
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
+). 
 This fell to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, representing a decrease of 
-x
-\% (
-x
-\% to 
-x
-\%). 
-In ESA, TMC coverage was 
-x
-\% (
-x
-\% to 
-x
-\%) in 2006, compared to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, a 
-x
-\% (
-x
-\% to 
-x
-\%) decrease. 
-In constrast, TMC coverage in WCA was 
-x
-\% (
-x
-\% to 
-x
-\%) versus 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, a 
-x
-\% (
-x
-\% to 
-x
-\%) fall. 
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, a decrease of 
+`r to_percentage(tmc_cov$mean_tmc_cov_diff$mean)`. 
+In non-VMMC priority countries, TMC coverage was 
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
+). 
+This fell to 
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, representing a decrease of 
+`r to_percentage(tmc_cov_non_vmmc$mean_tmc_cov_diff$mean)`
+.
+In contrast, TMC coverage in VMMC priority countries was 
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
+). 
+This fell to 
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
+to 
+x
+`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
+) in 2020, representing a decrease of 
+`r to_percentage(tmc_cov_vmmc$mean_tmc_cov_diff$mean)`.
+Therefore, the decrease in TMC found throughout SSA is much more pronounced for 
+non-VMMC countries.
+
 In 2006, 
-x 
-(
-x 
-to 
-x
-) TMCs were performed, while in 2020 this was reduced to 
-x 
-(
-x to 
-x
+`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
+- 
+`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
+) TMCs were performed, while in 2020 this increased to 
+`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(lower) %>% round(0)`
+-
+`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(upper) %>% round(0)`
 ), representing a 
-x (
-x
-to
-x
-) decrease in annual TMCs.
-In ESA, the annual number of TMCs performed dropped from 
-x
-(
-x
-to 
-x
+`r round(-tmcs_performed$tmcs_performed_diff$mean, 0)`
+increase in annual TMCs.
+However, this increase must be taken within the context of a large increase
+in population in SSA over this period, from 1.23 billion in 2006 to 1.80 billion in 2020, 
+and as seen in our coverage estimates above, constitutes a decrease in the 
+number of TMCs performed per capita in the region (need to calculate this?!)
+<!-- populations %>% filter(age_group == "0+", year %in% spec_years) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
+<!-- populations %>% filter(age_group == "0+", year %in% spec_years, iso3 %in% vmmc_iso3) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
+<!-- populations %>% filter(age_group == "0+", year %in% spec_years, !(iso3 %in% vmmc_iso3)) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
+In non-VMMC priority countries, the annual number of TMCs performed changed from 
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
+- 
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
 ) in 2006 to 
-x
-(
-x
-to 
-x
-) in 2020, a 
-x 
-(
-x
-to 
-x
-) drop. 
-In WSA, this number fell from 
-x 
-(
-x 
-to 
-x
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(lower) %>% round(0)`
+- 
+`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(upper) %>% round(0)`
+) in 2020, or by 
+`r round(-tmcs_performed_non_vmmc$tmcs_performed_diff$mean, 0)`
+.
+This is within the context of the population of non-VMMC priority countries increasing 
+from 749 million to 1.11 billion from 2006 to 2020. 
+In VMMC priority countries, the number of TMCs performed went from 
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
+- 
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
 ) in 2006 to 
-x 
-(
-x
-to 
-x
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
+(
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
+- 
+`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
 ) in 2020, a fall of 
-x
-(
-x
-to 
-x
-).
+`r round(-tmcs_performed_vmmc$tmcs_performed_diff$mean, 0)`.
+In VMMC priority countries, the population increased from 481 million to 694 million. 
+TODO: Comment on this
+
 <!-- TODO: Change to 15-29, right? -->
-For the 10-29 age group, TMC coverage was reduced from 
-x
-\% (
-x
-\% to 
-x
-\%) in 2006 to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, a drop of 
-x
-\% 
-(
-x
-\% to 
-x
-\%).
-In VMMC countries, this was reduced from 
-x
-\% (
-x
-\% to 
-x
-\%) to 
-x
-\% (
-x
-\% to 
-x
-\%) from 2006 to 2020, while even in non-VMMC countries this decreased from 
-x
-\% (
-x
-\% to 
-x
-\%) to 
-x
-\% (
-x
-\% to 
-x
-\%). 
+We can also compare the differences in TMC coverage change between 15-29 and 
+30-49 year olds, in SSA as a whole and in VMMC and non-VMMC priority countries.
+
+For the 15-29 age group, TMC coverage was reduced from 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2020, a drop of 
+`r tmc_cov_ssa_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+.
+This contrasted with the 30-49 age group, where TMC coverage went from 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2020, a drop of 
+`r tmc_cov_ssa_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+.
+Therefore, in SSA as a whole TMC coverage decreased slightly more amongst 15-29 
+year olds than in 30-49 year olds, likely as a result of VMMC programme focus on 
+this age group.
+
+For the 15-29 year olds in non-VMMC priority countries, TMC coverage was reduced from 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2020, a drop of 
+`r tmc_cov_non_vmmc_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+.
+This contrasted with the 30-49 age group, where TMC coverage went from 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2020, a drop of 
+`r tmc_cov_non_vmmc_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+.
+Therefore in non-VMMC priority countries the decrease in TMC coverage was larger
+for both age groups than in SSA as a whole, but the difference between this decrease
+for 15-29 year olds versus 30-49 year olds is less pronounced.
+
+For VMMC priority countries, the 15-29 age group, TMC coverage was reduced from 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
+) in 2020, representing a fall of 
+`r tmc_cov_vmmc_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
+.
+In the 30-49 age group, TMC coverage in VMMC priority countries dropped from 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+(
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
+to 
+`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
+) in 2020, a drop of 
+`r tmc_cov_vmmc_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
+.
+Therefore, in VMMC priority countries there is a much greater disparity in the 
+drop in TMC coverage between 15-29 and 30-49 year olds. 15-29 year olds saw 
+a much greater drop in TMC coverage, likely resulting from VMMC programme focus on 
+these ages.
+
 The largest decrease in TMC coverage from 2006 to 2020 was in 
-x
-, from 
-x
-\% (
-x
-\% to 
-x
-\%) to 
-x
-\% (
- x 
-\% to 
- x 
-\%). 
-[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from 
-x 
-\% (
-x 
-\% to 
-x 
-\%) to 
-x 
-\% (
-x 
-\% to 
-x 
-\%) in 
-x 
+`r to_cntry_name(spec_country_tmc_decrease$mean_tmc_cov_diff$iso3)`, where TMC coverage
+fell from 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
+ to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
+) to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
+ to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`, a 
+decrease of 
+`r to_percentage(spec_country_tmc_decrease[[2]]$mean)`
 .
 
+The largest decrease in TMC coverage amongst VMMC countries was from 
+`r to_cntry_name(spec_country_tmc_decrease$mean_tmc_cov_diff$iso3)`, where TMC coverage
+fell from 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
+(
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
+ to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
+) to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
+(
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
+ to 
+`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`, a 
+decrease of 
+`r to_percentage(spec_country_tmc_decrease[[2]]$mean)`
+.
+
+TODO: Could possibly add smallest decrease here? Would be more interesting for 
+non-VMMC countries, could show where MMC has not begun to replace TMC
+Could also have number of countries in both regions which have experienced a 
+drop in TMC coverage?? Might be interesting for non-VMMC
+
 ## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries
+
+```{r}
+# x5 <- readRDS("data/inlines/05_inlines.RDS")
+# for (i in seq_along(x5)) {
+#   assign(names(x5)[i], x5[[i]])
+# }
+# aggr_mean_circ_age <- tidy_age(aggr_mean_circ_age)
+# aggr_mean_circ_age_non_vmmc <- tidy_age(aggr_mean_circ_age_non_vmmc)
+# aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
+```
 

### 2024-04-12 paper/paper_cals.Rmd
Correct typos

@@
 
-<!-- TODO: Change year from 2020 to 2023 -->
+<!-- TODO: Change year from 2020 to 2023 (once preprint is out) -->
+<!-- TODO: Add survey stuff here -->
+<!-- TODO: Add paragraph breaks (although that's not copying over from PDF) -->
 
@@
  (
-x
 `r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
  - 
-x
 `r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
@@
 
-We can constrast this for the non-VMMC priority countries in SSA.
+We can contrast this for the non-VMMC priority countries in SSA.
 The five-year age group MC coverage in both 2006 and 2020 was highest amongst 
@@
 ), respectively. 
-This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) hasn't noticably changed. 
+This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) has not noticeably changed. 
 However, in 2006 MMC coverage was highest amongst 
@@
  (
-x
 `r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
  - 
-x
 `r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
@@
 than amongst 30-49 year olds, and greater increases than for SSA as a whole. 
-Again, TMC coverage amongst both fifteen year age groups constrast to these increases for MC and MMC. 
+Again, TMC coverage amongst both fifteen year age groups contrast to these increases for MC and MMC. 
 TMC coverage amongst 15-29 year olds decreased from 
@@
 - 
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
-So the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
+`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`
+).
+Therefore, the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
 However, it is important to note that the uncertainty ranges in our credible intervals 
@@
 to 
-x
 `r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
@@
 to 
-x
 `r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
@@
 to 
-x
 `r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
@@
 to 
-x
 `r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
@@
 to 
-x
 `r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
@@
 to 
-x
 `r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
@@
 
-Amongst the 13 VMMC priority countries modelled, just 
+As a reminder, in 2010 the WHO and UNAIDS set a 80\% MC target for 
+15-49 year olds in the VMMC priority countries by 2018.
+This target was expanded in 2016 to the new target of 90\% MC amongst 10-29 year olds 
+in VMMC priority countries by 2021.
+
+Amongst the 14 VMMC priority countries modelled, just 
 x
@@
 ) were MMCs. 
-No countries were e
-x
-pected to have reached this goal in all districts. 
+No countries were expected to have reached this goal in all districts. 
 The number of annual MCs increased from 
@@
 
-However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries.
+However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries.
 

### 2024-04-14 paper/paper_cals.Rmd
Do many of section 5 calculationsvasjdlkfs

@@
 
+# recursively simplify type 
+simplify_type_rec <- function(x) {
+  # for e.g. vector
+  if (!is.list(x)) {
+    return(x)
+  # simplify type in dataframes
+  } else if (is.data.frame(x)) {
+    if ("type" %in% names(x)) simplify_type(x)
+  # traverse list
+  } else simplify_type_rec(x[[1]])
+  return(x)
+}
+
 # tidy up aggregated age data
@@
 x1 <- readRDS("data/inlines/01_inlines.RDS")
+# x1 <- simplify_type_rec(x1)
 for (i in seq_along(x1)) {
@@
 x2 <- readRDS("data/inlines/02_inlines.RDS")
+# x2 <- simplify_type_rec(x2)
 for (i in seq_along(x2)) {
@@
 ```{r}
-# x5 <- readRDS("data/inlines/05_inlines.RDS")
-# for (i in seq_along(x5)) {
-#   assign(names(x5)[i], x5[[i]])
-# }
-# aggr_mean_circ_age <- tidy_age(aggr_mean_circ_age)
-# aggr_mean_circ_age_non_vmmc <- tidy_age(aggr_mean_circ_age_non_vmmc)
+x5 <- readRDS("data/inlines/05_inlines.RDS")
+# x5 <- simplify_type_rec(x5)
+
+for (i in seq_along(x5)) {
+  assign(names(x5)[i], x5[[i]])
+}
+
 # aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
+n_required_vmmc       <- simplify_type(n_required_vmmc)
+largest_smallest_vmmc <- simplify_type(largest_smallest_vmmc)
+increase_vmmc         <- simplify_type(increase_vmmc)
+cum_vmmc_circs_performed <- simplify_type(cum_vmmc_circs_performed)
+vmmc_circs_performed <- simplify_type(vmmc_circs_performed)
+
+# countries above threshold
+cntries_thresh <- to_cntry_name(cntry_abv_thresh$iso3[cntry_abv_thresh$age_group == "15-49"])
+
 ```
@@
 
-Amongst the 14 VMMC priority countries modelled, just 
-x
- countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
-x
+Amongst the 14 VMMC priority countries modelled, 
+`r cntry_abv_thresh %>% filter(age_group == "15-49") %>% nrow()`
+countries were projected to have achieved the VMMC target of 
+80\% MC coverage amongst 15-49 year olds by 2020, 
+`r paste(paste(cntries_thresh[-length(cntries_thresh)], collapse = ", "), last(cntries_thresh), sep = " and ")`.
+None were expected to reach the 90\% target for 10-29 year olds. 
+No countries were expected to have reached these goals in all districts.
+
+MC coverage amongst 10-29 year olds across VMMC priority countries increased from 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
+) in 2020, 
+an increase of 
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
+- 
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
+).
+MMC coverage amongst 10-29 year olds across VMMC priority countries increased from 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
+) in 2020, an increase of 
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
+- 
+`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
+).
+MC coverage amongst 15-49 year olds across VMMC priority countries increased from 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
+) in 2020, 
+an increase of 
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
+- 
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
+).
+MMC coverage amongst 15-49 year olds across VMMC priority countries increased from 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
+) in 2006 to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
+to 
+`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
+) in 2020, an increase of 
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
+(
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
+- 
+`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
+).
+
+Between 2006 and 2020 in these countries, 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(mean) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(lower) %>% to_mill()`
+million
+-
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) MCs were performed on 10-29 year olds.
+Of these, 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) were MMCs, and 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) were TMCs. 
+Over the same period, 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(mean) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(lower) %>% to_mill()`
+million
+-
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) MCs were performed on 15-49 year olds,
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) of which were MMCs, and 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) of which were TMCs.
+
+The number of annual MCs amongst 10-29 year olds increased from 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020.
+
+The number of annual MMCs amongst 10-29 increased from 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020, while in constrast, the number of TMCs decreased from 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020.
+
+For 15-49 year olds, the number of annual MCs increased from 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020.
+
+Annual MMCs amongst 15-49 increased from 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020, while in constrast, the number of TMCs decreased from 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2006 to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
+million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
+million
+ to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
+million
+) in 2020.
+
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean) %>% to_mill()`
+ (
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower) %>% to_mill()`
+ to 
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper) %>% to_mill()`
+) additional circumcisions are required to achieve 90\% and 80\% MC coverage targets 
+for 10-29 and 15-49 year olds, respectively, across all VMMC priority countries.
+
+This equates to 
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
+(
+`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
+ to 
+`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
+)
 and 
-x
-. 
-MC coverage across these countries increased from 
-x
-\% (
-x
-\% to 
-x
-\%) in 2006 to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020.
-
-x
- (
-x
- to 
-x
-) circumcisions were performed between 2007 and 2020 in these countries. 
-Of these, 
-x
- (
-x
- to 
-x
-) were MMCs. 
-No countries were expected to have reached this goal in all districts. 
-The number of annual MCs increased from 
-x
- (
-x
- to 
-x
-) in 2006 to 
-x
- (
-x
- to 
-x
-) in 2020.
-
-x
- (
-x
- to 
-x
-) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, 
-x
- (
-x
- to 
-x
-) times the projected number of MCs for 2020. 
+`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
+(
+`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
+to
+`n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
+)
+times the projected number of MCs for 10-29 and 15-49 year olds for 2020. 
 The largest increase in MC coverage amongst VMMC priority countries was in 

### 2024-04-15 paper/paper_cals.Rmd
Section 5 completed!

@@
 
-## Subnational Variation in Total, Medical \& Traditional Circumcision over time
+## Subnational variation in total, medical \& traditional circumcision over time
 
@@
 
-## Subnational Variation in total, medical \& traditional circumcision across different ages
+## Subnational variation in total, medical \& traditional circumcision across different ages
 
@@
 
-## Subnational Heterogeneity in Age at Medical and Traditional Circumcision
+## Subnational heterogeneity in age at medical and traditional circumcision
 
@@
 
-## Decrease in TMC in SSA region Over Time
+## Decrease in traditional male circumcision in SSA region over time
 
@@
 
-## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries
+## UNAIDS goals progress amongst 10-29 year olds in VMMC target countries
 
@@
 (
-`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
- to 
-`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
+ to 
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
 )
 and 
-`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-(
-`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-to
-`n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
+`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
+(
+`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
+to
+`r n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
 )
 times the projected number of MCs for 10-29 and 15-49 year olds for 2020.
-The largest increase in MC coverage amongst VMMC priority countries was in 
-x
-, from 
-x
-\% (
-x
-\% to 
-x
-\%) in 2006 to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, a 
-x
-\% (
-x
-\% to 
-x
-\%) increase. 
+
+MC coverage in 2020 for 10-29 year olds in VMMC priority countries was highest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
+), and lowest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
+.
+For 15-49 year olds, the highest MC coverage was in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
+), and lowest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
+.
+MMC coverage for 10-29 year olds in VMMC priority countries was highest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
+), and lowest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
+.
+For 15-49 year olds, the highest MMC coverage was in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
+), and lowest in 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
+at 
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
+(
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
+-
+`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
+.
+
+The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries was in 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
+from 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
+) in 2006 to 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+) in 2020, a 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
+) increase. 
 In contrast, the lowest increase in MC coverage in these countries was in 
-x
-, from 
-x
-\% (
-x
-\% to 
-x
-\%) in 2006 to 
-x
-\% (
-x
-\% to 
-x
-\%) in 2020, a 
-x
-\% (
-x
-\% to 
-x
-\%) increase.
+from 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
+) in 2006 to 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
+) in 2020, a 
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
+) increase.
 
 However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries. 
-
-x
-/
-x
- districts in these countries were e
-x
-pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
-x
-/
-x
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
+(
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
+-
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
+)
+of
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(n)) %>% pull()`
+districts in these countries were expected to have reached 90\% MC coverage 
+amongst 10-29 year olds in 2020, up from 
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
+(
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
+-
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
+) of
+`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(n)) %>% pull()`
 in 2006, before VMMC programmes began. 
-Even in 
-x
-, where MC was projected to be lowest in 2020, 
-x
-/
-x
- districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
-MC coverage there increased from 
-x
-(
-x
-to 
-x
-) in 2006 to 
-x
-(
-x
-to 
-x
-) in 2020, a 
-x
-(
-x
-to 
-x) increase.
+Similarly, 
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
+(
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
+-
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
+)
+of
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(n)) %>% pull()`
+districts in these countries were expected to have reached 80\% MC coverage for 
+15-49 year olds in 2020, compared to
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
+(
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
+-
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
+) of
+`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(n)) %>% pull()`
+in 2006.
+
+In 2020, 
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(mean)`
+(
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(lower)`
+-
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(upper)`
+)
+of the 14 VMMC priority countries had no districts which satisfied the 90\% MC coverage target for 10-29
+year olds. This was down from 
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(mean)`
+(
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(lower)`
+-
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(upper)`
+)
+in 2006. 
+Similarly, in 2020, 
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(mean)`
+(
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(lower)`
+-
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(upper)`
+)
+countries had no districts which satisfied the 80\% MC coverage target for 15-49
+year olds. This was down from 
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(mean)`
+(
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(lower)`
+-
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(upper)`
+)
+in 2006.

### 2024-04-15 paper/scripts/032_results.R

@@ -8,6 +8,7 @@
 while(basename(getwd()) != "threemc-orderly") setwd("../.")
 
 #### Libs ####
+
 library(dplyr, warn.conflicts = FALSE)
 library(forcats)
 library(ggplot2)
@@ -24,6 +25,20 @@ library(patchwork)
 library(gridExtra)
 source("Shiny/src/functions.R") # plotting functions
 source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
+
+#### Helper Functions ####
+
+# function to add iso3 column to dataframe from area id, if not already present
+add_iso3 <- function(df) {
+  stopifnot("area_id" %in% names(df))
+  if (!"iso3" %in% names(df)) {
+    df$iso3 <- substr(df$area_id, 0, 3)
+    df <- df %>% 
+      relocate(iso3, .before = area_id)
+  }
+  return(df)
+}
+
 
 #### Metadata ####
 
@@ -69,7 +84,7 @@ target_iso3 <- c(
 # VMMC countries  
 vmmc_iso3 <- c(
   "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
-  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF" # LSO, SWZ ran already
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA" 
 )
 vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
 
@@ -144,17 +159,13 @@ results_dirs <- load_orderly_data(
       parameter:inc_time_tmc    == inc_time_tmc
     )"
 )$dirs
+pars_df$id <- results_dirs
 
-# function to add iso3 column to dataframe from area id, if not already present
-add_iso3 <- function(df) {
-  stopifnot("area_id" %in% names(df))
-  if (!"iso3" %in% names(df)) {
-    df$iso3 <- substr(df$area_id, 0, 3)
-    df <- df %>% 
-      relocate(iso3, .before = area_id)
-  }
-  return(df)
-}
+# countries with new runs, don't have to correct populations for these!
+pars_df$date <- as.numeric(substr(pars_df$id, 0, 8))
+new_countries <- pars_df %>% 
+  filter(date > 20231200) %>% 
+  pull(cntry)
 
 # results_agegroup <- load_orderly_data(
 #   task = "02final_aggregations",
[…]

### 2024-04-15 paper/paper_cals.Rmd
successful knit

@@
 ) in 2020, a 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
 ) increase. 
@@
 ) in 2020, a 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
+(
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
+-
+`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
 ) increase.

### 2024-04-15 paper/paper_cals.Rmd
Add abstract and first results section text

@@
-ub
+---
 title: "Circumcision Paper Text"
@@
 
+# Abstract
+## Background}
+In 2016, UNAIDS developed a Fast-Track strategy that targeted 90\% coverage
+male circumcision (MC) among men aged 10-29 years by 2021 in priority countries in sub-Saharan 
+Africa (SSA) to reduce HIV incidence. There is substantial variation across subnational 
+regions within countries in both traditional male circumcision (TMC) practices and progress
+towards implementation of voluntary medical male circumcision (VMMC). Tracking progress and
+remaining gaps towards VMMC HIV prevention targets requires detailed district-level circumcision
+coverage data.
+
+## Methods
+We analysed self-reported data on male circumcision from x nationally representative household surveys conducted in x SSA countries between 2006-2020.
+A spatio-temporal Bayesian competing-risks time-to-event model was used to estimate rates of traditional and medical circumcision by age, location, and time.
+Circumcision coverage in 2020 was projected assuming continuation of estimated age-specific rates, with probabilistic uncertainty.
+
+## Results
+Across 
+x 
+countries, from 2006 to 2020 an estimated 
+x
+million men (x\% CI x-x million)
+were newly circumcised, of whom x million (x-x million) were medically circumcised, and
+x million (x-x million) traditionally circumcised. 
+In 2020, MC coverage among men 10-29 years ranged from x\% (x\%-x\%) in Zimbabwe (?) to x\% (x\%-x\%) in Togo. 
+MMC coverage ranged from x\% (x\%-x\%) in Malawi to x\% (x\%-x\%) in Tanzania, and TMC coverage
+from x\% (x\%-x\%) in Eswatini to x\% (x\%-x\%) in Ethiopia. 
+The largest increase in MMC coverage was in Lesotho from x\% to x\%. 
+Within countries, the median difference in MC coverage between the districts with lowest and highest coverage was x\%, with the smallest variation in Eswatini (x\% to x\%) and largest in Zambia (x\% to x\%).
+x million men aged 10-29 need to be circumcised to reach 90\% coverage in all countries.
+
+## Conclusions
+VMMC programmes have made substantial, but uneven, progress towards male circumcision targets.
+Granular district and age-stratified data provide information for focusing further programme implementation.
+
 # Results
+
+Our data consisted of 109 nationally representative household surveys conducted in 33 SSA countries between 2002 and 2019.
+x sub-national areas amongst these coutries were included in these surveys and modelled.
+Of these 109 surveys, 104 contained sufficent information on circumcision, as outlined in the Methods section of this paper.
+
+These remaining surveys consisted of 711,715 individuals respondents from 108 birth cohorts from 1903 to 2016.
+The sample size per survey ranged from 21,114 in the South Africa 2017 HSRC survey to 1,459 in the Eswatini 2014 MICS survey.
+
+There was significant censoring and missing data even in the remaining surveys. 
+Left censoring of circumcision status, analagous to unknown circumcision age, averaged  34.438\% across all surveys, and ranged from 0\% in the Rwanda 2008 DHS survey to 99.408\% in the Niger 2006 DHS survey.
+17 surveys had more than 90\% left censoring of circumcision age, with 42 surveys having less than 10\% left censoring.
+\todo{Rewrite now BWA has surveys!}
+No information on age at circumcision was present in the 2004 and 2008 Botswana Aids Impact Surveys.
+This complete left censoring of circumcised individuals meant that \verb|threemc| could not be fit to Botswana.
+Right censoring of circumcision status, indicating as of yet uncircumcised individuals, averaged 35.299\% across all surveys, ranging from 0.399\% in the The Gambia 2018 MICS survey to 91.432\% in the Eswatini 2006 DHS survey.
+
+On average across all surveys, 1.788\% of respondents did not respond to either the circumcision location or provider question, and so had unknown circumcision type. 
+This was lowest in the Burundi 2010 DHS survey, at 0\%, and highest in the South Africa 2002 HSRC survey, at 29.545\%.
+5 countries had unknown circumcision type; DR Congo, Guinea, Liberia, Niger and Senegal. 
+Amongst these countries, left censoring averaged 98.457\%. 
+However, the mean survey circumcision coverage amongst these same countries was 98.457\%, which may explain the relative lack of circumcision information available in their surveys.
+
+\todo{Rewrite as BWA now has surveys}
+In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit \verb|threemc| in these countries either.
+
+More information on individual surveys, including participation rates, can be found in section x of the appendix.
 
@@
 
-```{r}
+```{r, echo = FALSE}
 x3 <- readRDS("data/inlines/03_inlines.RDS")
@@
 
-```{r}
+```{r, echo = FALSE}
 x4 <- readRDS("data/inlines/04_inlines.RDS")
@@
 `r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
- to 
+
 `r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
@@
 `r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
- to 
+ - 
 `r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`, a 
@@
 
-```{r}
+```{r, echo = FALSE}
 x5 <- readRDS("data/inlines/05_inlines.RDS")
@@
 Between 2006 and 2020 in these countries, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(mean) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(lower) %>% to_mill()`
-million
--
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(mean) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(lower) %>% to_mill()` million
+-
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(upper) %>% to_mill()` million
 ) MCs were performed on 10-29 year olds.
 Of these, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()` million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) were MMCs, and 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()` million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) were TMCs. 
 Over the same period, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(mean) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(lower) %>% to_mill()`
-million
--
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(mean) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(lower) %>% to_mill()` million
+-
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(upper) %>% to_mill()` million
 ) MCs were performed on 15-49 year olds,
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()` million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) of which were MMCs, and 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()` million
+(
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()` million
+- 
+`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) of which were TMCs.
@@
 The number of annual MCs amongst 10-29 year olds increased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()` million
+ -  
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()` million
 ) in 2020.
@@
 The number of annual MMCs amongst 10-29 increased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) in 2020, while in constrast, the number of TMCs decreased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) in 2020.
@@
 For 15-49 year olds, the number of annual MCs increased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()` million 
+to 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()` million
 ) in 2020.
@@
 Annual MMCs amongst 15-49 increased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()` million
 ) in 2020, while in constrast, the number of TMCs decreased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()` million
+ (
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()` million
+ - 
+`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()` million
 ) in 2020.
@@
 `r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower) %>% to_mill()`
- to 
+ - 
 `r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper) %>% to_mill()`
@@
 
-This equates to 
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
-(
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
- to 
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
+This is equivalent to 
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff) %>% round(1)`
+(
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff) %>% round(1)`
+ - 
+`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff) %>% round(1)`
 )
 and 
-`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-(
-`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-to
-`r n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
-)
+`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff) %>% round(1)`
+(
+`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff) %>% round(1)`
+to
+`r n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff) %>% round(1)`)
 times the projected number of MCs for 10-29 and 15-49 year olds for 2020.
@@
 (
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(upper)`
+-
 `r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(upper)`
 )
@@
 (
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(upper)`
+-
 `r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(upper)`
 )
@@
 (
+`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(upper)`
+-
 `r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(upper)`
 )
@@
 (
+`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(upper)`
+-
 `r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(upper)`
 )

### 2024-04-16 paper/scripts/031_results_data.R
Adapt results scripts to produce inline figures

@@ -6,7 +6,6 @@
 # interest in the appendix
 
 # TODO: Check number of surveys, seems very low
-# TODO: Remove BWA from plot
 
 # stopifnot(dirname(getwd()) == "threemc-orderly")
 while(basename(getwd()) != "threemc-orderly") setwd("../.")
@@ -33,7 +32,7 @@ source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
 orderly_root <- getwd()
 
 spec_age_group <- "10-29" # change? 
-spec_years <- c(2010, 2020)
+spec_years <- c(2010, 2022)
 
 # for tabulating surveys: 
 rm_missing_type <- FALSE # remove circumcisions with missing type?
@@ -59,7 +58,8 @@ vmmc_iso3 <- c(
 vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
 
 # countries for which we have no results
-no_mod_iso3 <- c("BWA", "CAF", "GNB")
+# no_mod_iso3 <- c("BWA", "CAF", "GNB")
+no_mod_iso3 <- c("CAF", "GNB")
 
 ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
 country_name_convention <- function(x) {
@@ -101,11 +101,23 @@ areas <- load_archive(
 )
 
 # pull surveys
-survey_circumcision_orig <- survey_circumcision <- load_archive(
+survey_circumcision <- load_archive(
   "00b3_survey_join", 
   orderly_root, 
   "survey_circumcision.csv.gz", 
   query = "latest(parameter:is_paper == TRUE)"
+)
+
+survey_circumcision_no_paper <- load_archive(
+  "00b3_survey_join", 
+  orderly_root, 
+  "survey_circumcision.csv.gz", 
+  query = "latest(parameter:is_paper == FALSE)"
+) %>% 
+  filter(survey_id %in% c("UGA2020PHIA"))
+
+survey_circumcision_orig <- survey_circumcision <- bind_rows(
+  survey_circumcision, survey_circumcision_no_paper
 )
 
 survey_circumcision <- survey_circumcision %>% 
@@ -164,7 +176,7 @@ provider_key <- tibble::tribble(
   "DHS",     "Demographic and Health Survey",
   "PHIA",    "Population-Based HIV Impact Assessment",
[…]

### 2024-04-16 paper/scripts/032_results.R

@@ -2073,9 +2073,17 @@ rm(list = c(names(section_4_inlines), "section_4_inlines")); gc()
 results_agegroup_n_circ <- readr::read_csv(
   "paper_poster_plots_threemc/paper/data/results_agegroup_n_circ.csv.gz"
 )
-# results_agegroup <- readr::read_csv(
-#   "paper_poster_plots_threemc/paper/data/results_agegroup.csv.gz"
-# )
+
+results_agegroup <- readr::read_csv(
+  "paper_poster_plots_threemc/paper/data/results_agegroup.csv.gz"
+)
+
+populations <- load_orderly_data(
+  "00c4_pops_aggregate", 
+  query = "latest", 
+  file = "population_agegroup_aggr.csv.gz"
+)$output[[1]]
+
 
 results_agegroup_vmmc <- filter(results_agegroup, iso3 %in% vmmc_iso3)
 results_agegroup_n_circ_vmmc <- filter(results_agegroup_n_circ, iso3 %in% vmmc_iso3)
@@ -2201,6 +2209,25 @@ largest_smallest_vmmc <- results_agegroup_vmmc_spec %>%
   select(iso3, age_group, year, type, mean, lower, upper)
 
 # largest and smallest *increase* in VMMC countries, MC and MMC
+# increase_vmmc <- results_agegroup_vmmc_spec %>%
+#   # calculate differences from 2006 to 2020
+#   tidyr::pivot_wider(names_from = year, values_from = population:upper) %>% 
+#   mutate(
+#     diff_mean = mean_2020 - mean_2006, 
+#     diff_lower = lower_2020 - lower_2006, 
+#     diff_upper = upper_2020 - upper_2006
+#   ) %>% 
+#   tidyr::pivot_longer(population_2006:upper_2020) %>% 
+#   tidyr::separate(col = name, sep = "_", into = c("name", "year")) %>% 
+#   tidyr::pivot_wider(names_from = name) %>% 
+#   filter(year == 2020) %>% 
+#   # take largest and smallest for each type and age group
+#   arrange(type, age_group, desc(diff_mean)) %>% 
+#   group_by(type, age_group) %>% 
+#   slice(c(1, n())) %>% 
+#   ungroup() %>% 
+#   select(iso3, age_group, type, mean, lower, upper, contains("diff"), contains("2020"), contains("2016"))
+
 increase_vmmc <- results_agegroup_vmmc_spec %>%
   # calculate differences from 2006 to 2020
[…]

### 2024-04-16 paper/0_outline/old/model_spec_ppcs_tables.tex
Updates from Overleaf

--- 2023-09-26 paper/model_spec_ppcs_tables.tex
@@
 
-Nomenclature:
-Time-invariant, No cut-off model: Neither
-Time-invariant, paed cut-off model: Paed cut-off
-Time-variant, No cut-off model: Time TMC
-Time-variant, paed cut-off model: Both
-
 \textbf{AR1}
 \begin{itemize}
-    \item MC: CPRS lowest for Both, RMSE lowest for Time TMC, 50\% CI closest to 50\% for Time TMC, 80\% CI closest for Neither, and 95\% CI closest for Both.
-    \item MMC: CRPS and RMSE lowest for Neither, 50\% CI closest for Neither, 80\% & 95\% CI closest for time TMC
-    \item TMC: Same as MMC, but 50\% CI best for Paed Cutoff 
+    \item MC: CPRS lowest for TV, PC, MAE lowest for TV, PC, RMSE lowest for TV, NC, 50\% CI closest to 50\% for TV, NC, 80\% CI closest for TI, NC, and 95\% CI closest for TI, PC.
+    \item MMC: CRPS, MAE and RMSE lowest for TI, NC, 50\% CI closest for TI, NC, 80\% & 95\% CI closest for TV, NC.
+    \item TMC: Same as MMC, but 50\% CI best for TI, PC 
     \item Conclusions:
     \begin{itemize}
-        \item MC: Fairly inconclusive, but for most summary statistics (except 80\% CI, fairly narrowly) a model which includes a time TMC component is preferred.
-Choosing between "Both" and "Time TMC", it appears that Time TMC has noticeably worse CRPS, 80\% and 95\% coverage, and only marginally better RMSE and 50\% coverage, so the best model for MC appears to be "Both".
-        \item MMC (\& TMC): "Neither" model seems to be narrowly favoured for MMC and tied for TMC with Time TMC for type-specific circumcision, particularly for mean fit statistics.
+        \item MC: Fairly inconclusive, but for most summary statistics (except 80\% CI, fairly narrowly) a TV model is preferred.
+Choosing between TV, PC and TV, NC, % it appears that TV, NC has noticeably worse CRPS, 80\% and 95\% coverage, and only marginally better RMSE and 50\% coverage, so the best model for MC appears to be TV, PC.
+        it appears that TV, NC has better RMSE and 50\% coverage, while TV, PC has better MAE, 80\% and 95\% coverage, so it appears that the best model for MC is TV, PC.
+        \item MMC (\& TMC): 
+        For MMC, TV, NC noticably has the worst mean fit statistics.
+However, it does have the best 80\% and 95\% coverage.
+It is a choice between the model with the best fit (TI, NC) and the best coverage (TV, NC).
+I believe the quite large increase in 95\% coverage, from 85.45 to 89.95 and from 80.30 to 91.37 justifies the choice of the TV, NC model for MMC and TMC, respectively.
+It would be interesting to investigate whether there are some outliers in mean fit statistics which are skewing these numbers.
+        % TI, NC model seems to be narrowly favoured for MMC and tied for TMC with TV, NC for type-specific circumcision, particularly for mean fit statistics.
 Strange in that this seems to only be the case for the AR1 temporal prior.
-Comparing values, mean fit statistics were certainly better for "Neither".
-While we would like our model to be well calibrated, having the best 95\% CI is probably most important in terms of coverage, and the "Time TMC" model has much better 95\% coverage (85.45 vs 89.95 for MMC, 85.49 vs 91.38 for TMC) (and 80\% covergae, at 71.77 vs 78.35 for MMC and 72.50 vs 80.30 for TMC), so Time TMC is the much better model here in terms of the overall coverage of the model.
+Comparing values, mean fit statistics were certainly better for TI, NC.
+While we would like our model to be well calibrated, having the best 95\% CI is probably most important in terms of coverage, and the TV, NC model has much better 95\% coverage (85.45 vs 89.95 for MMC, 85.49 vs 91.38 for TMC) (and 80\% covergae, at 71.77 vs 78.35 for MMC and 72.50 vs 80.30 for TMC), so TV, NC is the much better model here in terms of the overall coverage of the model.
     \end{itemize}
-    \item Final Choice: As Time TMC is one of or the most favoured model for all circumcision types for the AR1 temporal prior, it appears to be the best choice of model across all types. 
+    \item Final Choice: As TV, NC is one of or the most favoured model for all circumcision types for the AR1 temporal prior, it appears to be the best choice of model considering all circumcision types.
 \end{itemize}
@@
 \begin{itemize}
-    \item MC: CRPS and RMSE lowest for Both (but very narrowly better than Time TMC model), 50\% coverage best for Time TMC, 80\% coverage best for Both, 95\% coverage best for Paed cutoff (by quite a bit!)
-    \item MMC \& TMC: CRPS and RMSE lowest for Both (again, narrowly better than Time TMC), 50\% coverage best for Neither, 80\% and 95\% coverage best for Time TMC. 
+    \item MC: CRPS, MAE and RMSE lowest for TV, PC, but little difference between the models.  50\% coverage best for TI, NC, 80\% coverage best for TV, PC, 95\% coverage best for TI, PC.
+    \item MMC \& TMC: 
+    CRPS lowest for TV, NC, MAE and RMSE narrowly lowest for TV, PC, 50\% coverage best for TI, NC, 80\% and 95\% coverage very noticably better for TV, PC model.
+    % CRPS, MAE and RMSE lowest for TV, PC (again, narrowly better than TV, NC), 50\% coverage best for TI, NC, 80\% and 95\% coverage best for TV, NC. 
     \item Conclusions:
     \begin{itemize}
-        \item MC: Also inconclusive, mean fit statistics narrowly best and 90\% coverage considerably better for "Both" model than "Time TMC", so best model here is "Both". 
-        \item MMC \& TMC: Similar to AR1 temporal prior, Both model narrowly better for mean fit statistics than Time TMC, but Time TMC has far better coverage (95\% coverage is 90.66 vs 80.87 for MMC and 92.17 vs 81.59 for TMC, so much better), and so Time TMC is the best model here.
+        \item MC: Seems that the TV, PC model is favoured for 4 out of our 6 statistics, and has only narrowly worse 95\% coverage, so the TV, PC model is best. 
+        \item MMC \& TMC: Similar to AR1 temporal prior, TV, PC model better for RMSE and MAE than TV, NC, but TV, NC has significatly lower CRPS (120.06 vs 127.44 for MMC and 106.09 vs 114.87 for TMC, respectively) and far better 80\% and 95\% coverage (95\% coverage is 90.66 vs 80.87 for MMC and 92.17 vs 81.59 for TMC), and so TV, NC is the best model here.
+Notice however that the TV, NC model has very high 50\% coverage (58.79), and so could be said to be poorly calibrated at that level.
     \end{itemize}
-    \item Final Choice: "Both" is narrowly favoured for MC over Time TMC, while Time TMC is better for MMC and TMC, so best model choice here across all types is "Time TMC". 
+    \item Final Choice: TV, NC is favoured for MC over TV, NC, while TV, NC is better for MMC and TMC, so best model choice here across all types is TV, NC. 
 \end{itemize}
@@
 \begin{itemize}
-    \item MC: CRPS, RMSE, 50\% CI best for Time TMC, 80\% covreage best for Neither (very well calibrated at 79.77), 95\% coverage best for Both (although all models have pretty good coverage here, with the lowest being Time TMC at 86.79).
-    \item MMC \& TMC: CPRS \& RMSE best for Time TMC (as in MC as well), 50\% coverage best for "Neither", 80\% and 95\% coverage best for Time TMC.
-    \item Conclusions:
-      \begin{itemize}
-          \item MC: Fit statistics best for Time TMC, with CRPS in particular being by far the lowest (53.68 vs the next lowest 74.41 for "Both") (may be a mistake?).
-Although other models have higher 80\% and 95\% coverage, there is not enough of a difference in coverage to ignore this glaring difference in CRPS, so the "Time TMC" model is probably best here.
-          \item MMC \& TMC: Time TMC model best for all but 50\% coverage, so Time TMC is clearly the preferred model.
-      \end{itemize}
-    \item Final Choice: Time TMC clearly the best model.
-Interesting that for the RW2 temporal prior we get the behaviour that perhaps we most expected to get for all models, with the "Time TMC" model giving both better mean fit statistics and also posterior predictive coverage, across all circumcision types.
+    \item TV, NC model hasn't run for GHA for RW order 2, so any comparisons are not entirely fair (and notice that TV, NC model is favoured for all types here, and has considerably better fit for MC, which is very unlike our other temporal priors, and suggests GHA fit may be an outlier.
+    % \item MC: CRPS, RMSE, 50\% CI best for TV, NC, 80\% covreage best for TI, NC (very well calibrated at 79.77), 95\% coverage best for TV, PC (although all models have pretty good coverage here, with the lowest being TV, NC at 86.79).
+    % \item MMC \& TMC: CPRS \& RMSE best for TV, NC (as in MC as well), 50\% coverage best for "TI, NC", 80\% and 95\% coverage best for TV, NC.
+    % \item Conclusions:
+    %   \begin{itemize}
+    %       \item MC: Fit statistics best for TV, NC, with CRPS in particular being by far the lowest (53.68 vs the next lowest 74.41 for "TV, PC") (may be a mistake?).
+Although other models have higher 80\% and 95\% coverage, there is not enough of a difference in coverage to ignore this glaring difference in CRPS, so the "TV, NC" model is probably best here.
+    %       \item MMC \& TMC: TV, NC model best for all but 50\% coverage, so TV, NC is clearly the preferred model.
+    %   \end{itemize}
+    % \item Final Choice: TV, NC clearly the best model.
+Interesting that for the RW2 temporal prior we get the behaviour that perhaps we most expected to get for all models, with the "TV, NC" model giving both better mean fit statistics and also posterior predictive coverage, across all circumcision types.
 \end{itemize}
@@
 
-\textbf{So seems the best model across all temporal priors and circumcision types is the model which has time-variant TMC and no paediatric cut-off for TMC (i.e. the "Time TMC" model)}
+\textbf{So it seems that the best model across all temporal priors and circumcision types is the model which has time-variant TMC and no paediatric cut-off for TMC}
 
@@
 \begin{itemize}
-    \item Seems to be a pattern emerging whereby including a peadiatric age cutoff vs not improves mean fit statistics (i.e.
-CRPS \& RMSE), at the loss of posterior predictive coverage (this is bucked for RW2 temporal prior, however, where we see more "expected" behaviour, with the "Time TMC" model having lower CRPS and RMSE than "Both").
-    \item However, the inclusion of a Time TMC component is routinely preferred, in agreement with our qualitative analysis of the different model specifications 
-    \item Again, important to note that we don't have survey data on < 15 year olds, so perhaps the value of including a paediatric age cutoff for MMC isn't identifiable here?
-    \item Wanted to choose these models based mainly on mean fit statistics and not posterior predictive coverage, but the choice of model via CRPS and RMSE, usually "Both", doesn't necessarily agree with our qualitative choice of "Time TMC", while the choice of model via coverage is Time TMC (again, this is for AR1 and RW1, not the RW2 temporal prior).
+    \item Seems that for non-VMMC countries, a model with a paediatric cutoff is preferred for MC, but not for MMC and TMC.
+Why do we think this is occurring?
+How could a model that has better estimates of MMC and TMC not also have better estimates of MC?
+And which do we prioritise, a better estimate of circumcision overall, or a better idea of the split in circumcision type?
+I would lean more towards the former, with information about MMC/TMC splits merely being an interesting artefact of the model, rather than the main focus..
+    \item Seems to be a pattern emerging in many (though not all) cases whereby including a peadiatric age cutoff vs not improves mean fit statistics (i.e.
+CRPS, MAE \& RMSE), at the loss of posterior predictive coverage.
+% (this is bucked for RW2 temporal prior, however, where we see more "expected" behaviour, with the "TV, NC" model having lower CRPS and RMSE than "TV, PC").
+    \item However, the inclusion of a TV, NC component is routinely preferred for MMC and TMC, in agreement with our qualitative analysis of the different model specifications 
+    \item Again, important to note that we don't have survey data on < 15 year olds, so perhaps the value (or lack thereof) of including a paediatric age cutoff for MMC isn't identifiable here?
+    \item Wanted to choose these models based mainly on mean fit statistics and not posterior predictive coverage, but the choice of model via CRPS and RMSE, usually TV, PC, doesn't necessarily agree with our qualitative choice of TV, NC, while the choice of model via coverage is TV, NC.
 Not sure if I'm being very biased in choosing the model I think makes the most sense qualitatively (and also "looked" the best in graphical comparisons of model fit to survey points) in this supposedly quantitative analysis of the different model specifications!!
@@
     circumcision (MC), medical male circumcision (MMC) and traditional male 
-    circumcision (TMC) from fitting the 12 candidate models in Non-VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    circumcision (TMC) from fitting the 12 candidate models in Non-VMMC countries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
     (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
@@
     the 50\%, 80\%, and 95\% quantiles are shown.} 
-  \label{tab::PPC2Non-VMMC} 
+  \label{tab::PPC2 Non-VMMC} 
+\end{table}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{landscape}
+
+% \begin{landscape}
+% 
+% {\linespread{1} 
+%   \begin{table}[H] 
+%   \centering 
+%   \footnotesize 
+%   \begin{tabular}{>{\bfseries}p{0.75cm} 
+%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
+%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+%   \hline  
+%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
+%   \cmidrule(lr){4-15} 
+%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
+%       \multicolumn{6}{c}{\bf Time variant} \\ 
+%   \cmidrule(lr){4-9} 
+%   \cmidrule(lr){10-15} 
+%   & {\bf MMC Model} & {\bf Type} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
+%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
+%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
+%   \hline 
+% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
+%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
+%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
+%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
+%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
+%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
+%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
+%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
+%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
+%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
+%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
+%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
+%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
+%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
+%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
+%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
+%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
+%   \hline 
+%   \end{tabular} 
+%   \caption{Results of the posterior predictive checking in total 
+%              male circumcision (MC), medical male circumcision (MMC) and 
+%              traditional male circumcision (TMC) from fitting the 12 candidate 
+%              models and taking the median value across all Non-VMMC countries. Combinations include 
+%              (i) Time invariant or Time variant TMC, 
+%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
+%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
+%              Random Walk 2 (RW2) temporal prior. 
+%              For all combinations, the within-sample continuous ranked 
+%              probability scores (CRPS), mean absolute error (MAE) , 
+%              root mean squared error (RMSE), and the proportion of empirical 
+%              observations that fell within the 50\%, 80\%, and 95\% 
+%              quantiles are shown.} 
+%   \label{tab::PPC1Non-VMMC} 
+% \end{table}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+% \end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{VMMC countries}
+\label{sec:org09db5e8}
+
+%% Notes on Table %% 
+\textbf{AR1}
+
+\begin{itemize}
+    \item MC: CRPS best for TV, NC, but all similar (220.10 vs highest at 220.73 for TI, NC), MAE and RMSE narrowly lowest for TV, PC (need to stop rounding these to 2 decimal places), 50\% coverage best for TV, NC, 80\% Coverage narrowly best for TI, NC (78.47 vs lowest at 78.18 for TV, PC), 95\% coverage best for TI, PC, but similarly very high everywhere (88.89 vs lowest at 88.56 for TV, NC).
+    \item MMC \& TMC: CRPS, MAE and RMSE lowest for TV, NC. Coverages very similar across all models for both circumcision types. 
+    \item \textbf{Conclusions}: 
+    \begin{itemize}
+        \item MC: Models provide very similar fit, with very little difference in both mean fit statistics and coverage between them.
+Therefore, it is best to go with the model that makes the most sense qualitatively (see below).
+        \item MMC \& TMC: Models very similar in terms of coverage, with the TV, NC model giving noticeably better CRPS, making this the best model choice for both circumcision types here. 
+    \end{itemize}
+    \item \textbf{Final Choice}: 
+    \begin{itemize}
+      \item Qualitatively, the inclusion of a time variant TMC component, while computationally expensive, will not harm model fit (but excluding it may harm VMMC countries with high TMC, like Kenya and Ethiopia).
+      \item Also, it is simplest to have a similar treatment of time TMC for both the VMMC and non-VMMC models, unless we have a good reason not to.
+      \item The inclusion of a paediatric age cutoff for MMC makes sense as we know that VMMC programmes do not perform paediatric circumcisions on policy
+      \item Therefore, the choice of the "TV, PC" model makes the most sense here, in light of the fact that there is little quantitative difference between model fits. 
+    \end{itemize}
+\end{itemize}
+
+\textbf{RW1}
+
+\begin{itemize}
+    \item MC: CRPS, RMSE and MAE lowest for TV, PC, coverages similar across several models, but interesting to note that 80\% and 95\% are both better for models with a paediatric cutoff than the models without.
+    \item MMC \& TMC: CRPS lowest for TV, NC, MAE and RMSE lowest for TV, PC, 50\% coverage best for TI, PC, but too high for all models at this level, 80\% coverage is best for TI, PC for MMC and TV, PC for TMC, and 95\% coverage is best for TV, NC for both, although 95\% coverage is high across all models.
+    \item \textbf{Conclusions}: 
+    \begin{itemize}
+        \item MC: 
+        Noticeably better fit for TV, PC, while coverages are very similar across all models, so TV, PC seems to be the best model here. 
+        \item MMC \& TMC: As with AR1 temporal prior, models are very similar in terms of coverage, however the the TV, PC model gives noticeably better CRPS, making this the best model choice for both circumcision types here, in addition to MC.
+    \end{itemize}
+    \item \textbf{Final Choice}: 
+    \begin{itemize}
+      \item It seems here that in terms of mean fit, the TV, PC model is best, while all models provide similar levels of coverage.
+This is nicely in agreement with our qualitative choice for VMMC countries.
+    \end{itemize}
+\end{itemize}
+
+\textbf{RW2}
+
+\begin{itemize}
+    \item MC: CRPS, RMSE and MAE lowest for TV, PC, although there is little difference between any of the models. Coverages are similar across models as well.
+    \item MMC \& TMC: CRPS, MAE and RMSE lowest for TV, NC. Coverages are very similar across all models. 
+    \item \textbf{Conclusions}: 
+    \begin{itemize}
+        \item 
+        Little difference in mean fit or coverage between any of the models.
+For MC, model with TV, PC perhaps winning out on mean fit statistics, while for MMC \& TMC TV, NC is best for CRPS, MAE and RMSE.
+    \end{itemize}
+    \item \textbf{Final Choice}: 
+    \begin{itemize}
+      \item There is very little difference between the mean fit and coverages of any of these models, so the model chosen can be our qualitative one, TV, PC. 
+    \end{itemize}
+\end{itemize}
+
+So, across circumcision types and temporal priors, with some small exceptions which agree with our qualitative model choice, there is little difference between model fits for VMMC countries, so we can go with our qualitative choice of the model with time variant TMC and a paediatric age cutoff for MMC.
+Again, it is important to note that we do not have survey observations for under 15s, and so the true value of including a paediatric age cutoff is unobservable here, but we can see that including a paediatric age cutoff for MMC here does not hurt the model fit for older ages.
+
+%% Model Specification Table 1: Non-VMMC countries %%
+
+\begin{landscape}
+
+{\linespread{1} 
+  \begin{table}[H] 
+  \centering 
+  \footnotesize 
+  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+  \hline  
+  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\
+  \cmidrule(lr){4-5} 
+  \cmidrule(lr){6-7} 
+  \cmidrule(lr){8-9} 
+  \cmidrule(lr){10-11} 
+  \cmidrule(lr){12-13} 
+  \cmidrule(lr){14-15} 
+  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
+  \hline 
+    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
+ & \bf MC & \bf NC & 220.73 & \bf220.10 &   0.16 &   0.16 &   0.21 &   0.21 &  60.51 & \bf 60.23 & \bf 78.47 &  78.32 &  88.84 &  88.56 & \\ 
+  &  & \bf PC & 220.70 & 220.11 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 &  60.48 &  60.37 &  78.37 &  78.18 & \bf 88.89 &  88.77 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.43 & \bf163.95 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.40 &  84.69 &  85.11 &  93.21 & \bf 93.99 & \\ 
+  &  & \bf PC & 168.45 & 165.81 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.13 &  69.12 & \bf 84.40 &  84.71 &  92.89 &  93.64 & \\[3pt] 
+  & \bf TMC & \bf NC & 189.20 & \bf185.47 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.74 &  64.23 &  82.30 &  82.45 &  92.02 & \bf 92.25 & \\ 
+  &  & \bf PC & 191.07 & 188.56 &   0.14 &   0.14 &   0.19 &   0.19 & \bf 63.41 &  63.60 &  82.01 & \bf 81.81 &  91.85 &  91.98 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
+ & \bf MC & \bf NC & 220.08 & 240.11 &   0.17 &   0.18 &   0.22 &   0.23 &  60.81 & \bf 58.56 & \bf 78.89 &  77.33 & \bf 89.06 &  88.16 & \\ 
+  &  & \bf PC & 220.29 & \bf218.79 &   0.17 & \bf  0.16 &   0.22 & \bf  0.21 &  60.90 &  60.51 &  78.79 &  78.83 &  89.04 &  88.97 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.60 & 167.02 &   0.13 &   0.13 &   0.18 &   0.19 &  68.34 &  69.26 &  84.54 &  85.35 &  93.22 & \bf 94.08 & \\ 
+  &  & \bf PC & 168.66 & \bf165.65 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 & \bf 68.24 &  69.42 & \bf 84.39 &  84.80 &  93.19 &  93.83 & \\[3pt] 
+  & \bf TMC & \bf NC & 188.94 & 195.44 &   0.14 &   0.15 &   0.20 &   0.21 &  64.08 &  64.40 &  83.05 &  83.21 &  92.49 & \bf 92.59 & \\ 
+  &  & \bf PC & 190.81 & \bf187.53 &   0.14 & \bf  0.14 &   0.20 & \bf  0.19 & \bf 63.77 &  64.04 &  82.58 & \bf 82.53 &  92.13 &  92.23 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
+ & \bf MC & \bf NC & 220.19 & 219.09 &   0.16 &   0.16 &   0.21 &   0.21 &  60.55 &  60.45 &  78.14 &  78.49 &  88.69 &  88.68 & \\ 
+  &  & \bf PC & 221.05 & \bf218.97 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 & \bf 60.19 &  60.47 &  78.27 & \bf 78.59 &  88.76 & \bf 88.78 & \\[3pt] 
+  & \bf MMC & \bf NC & 167.84 & \bf164.16 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.59 &  84.51 &  85.14 &  93.20 & \bf 94.01 & \\ 
+  &  & \bf PC & 168.58 & 165.97 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.33 &  69.13 & \bf 84.33 &  84.60 &  92.93 &  93.63 & \\[3pt] 
+  & \bf TMC & \bf NC & 188.93 & \bf184.27 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.64 &  64.73 &  82.42 &  82.86 &  91.99 & \bf 92.25 & \\ 
+  &  & \bf PC & 191.49 & 187.82 &   0.14 &   0.14 &   0.20 &   0.19 & \bf 63.23 &  63.78 & \bf 81.74 &  82.34 &  91.71 &  92.00 & \\[3pt] 
+  \hline 
+  \end{tabular} 
+  \caption{Results of the posterior predictive checking in total male 
+    circumcision (MC), medical male circumcision (MMC) and traditional male 
+    circumcision (TMC) from fitting the 12 candidate models in VMMC countries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
+    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
+    temporal prior. For all combinations, the within-sample continuous ranked 
+    probability scores (CRPS), mean absolute error (MAE), root mean square 
+    error (RMSE), and the proportion of empirical observations that fell within 
+    the 50\%, 80\%, and 95\% quantiles are shown.} 
+  \label{tab::PPC1VMMC} 
 \end{table}}
@@
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
+% 
 % \end{landscape}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Testing without strange results}
+\label{sec:org8802288}
 
-\subsection{VMMC countries}
-\label{sec:org09db5e8}
+% Non-VMMC
+\begin{landscape}
+{\linespread{1} 
+  \begin{table}[H] 
+  \centering 
+  \footnotesize 
+  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
+  \hline  
+  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\
+  \cmidrule(lr){4-5} 
+  \cmidrule(lr){6-7} 
+  \cmidrule(lr){8-9} 
+  \cmidrule(lr){10-11} 
+  \cmidrule(lr){12-13} 
+  \cmidrule(lr){14-15} 
+  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
+  \hline 
+    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
+ & \bf MC & \bf NC &  80.63 &  84.04 &   0.12 &   0.12 &   0.15 & \bf  0.14 &  69.87 & \bf 67.36 &  80.40 &  77.36 & \bf 89.35 &  84.79 & \\ 
+  &  & \bf PC &  79.78 & \bf 79.41 &   0.12 & \bf  0.12 &   0.14 &   0.14 &  70.14 &  68.64 &  80.31 & \bf 80.14 &  88.69 &  88.43 & \\[3pt] 
+  & \bf MMC & \bf NC & \bf131.02 & 140.62 & \bf  0.21 &   0.23 & \bf  0.26 &   0.29 & \bf 50.27 &  58.02 &  71.17 & \bf 78.13 &  85.01 & \bf 89.87 & \\ 
+  &  & \bf PC & 140.06 & 134.39 &   0.23 &   0.21 &   0.29 &   0.26 &  48.55 &  48.15 &  70.33 &  69.50 &  84.68 &  83.28 & \\[3pt] 
+  & \bf TMC & \bf NC & \bf118.52 & 125.96 & \bf  0.19 &   0.21 & \bf  0.25 &   0.27 &  52.30 &  60.91 &  71.69 & \bf 80.18 &  85.10 & \bf 91.22 & \\ 
+  &  & \bf PC & 124.22 & 121.36 &   0.21 &   0.20 &   0.27 &   0.25 &  51.30 & \bf 49.38 &  71.28 &  70.49 &  84.97 &  83.62 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
+ & \bf MC & \bf NC &  82.20 &  81.89 &   0.10 &   0.10 &   0.13 &   0.13 &  71.89 & \bf 70.77 &  81.81 & \bf 80.20 &  89.69 &  87.83 & \\ 
+  &  & \bf PC & \bf 80.94 &  81.85 &   0.10 & \bf  0.10 &   0.13 & \bf  0.12 &  72.71 &  71.88 &  82.94 &  82.26 & \bf 91.02 &  88.98 & \\[3pt] 
+  & \bf MMC & \bf NC & 137.16 & \bf131.79 &   0.21 & \bf  0.20 &   0.26 & \bf  0.26 & \bf 50.98 &  56.85 &  70.94 & \bf 78.53 &  84.48 & \bf 89.92 & \\ 
+  &  & \bf PC & 141.78 & 141.40 &   0.21 &   0.21 &   0.26 &   0.26 &  47.94 &  47.50 &  68.03 &  68.83 &  81.30 &  81.50 & \\[3pt] 
+  & \bf TMC & \bf NC & 124.88 & \bf116.03 &   0.20 & \bf  0.19 &   0.25 & \bf  0.25 &  52.69 &  58.89 &  71.97 & \bf 80.68 &  85.29 & \bf 91.45 & \\ 
+  &  & \bf PC & 128.62 & 127.61 &   0.20 &   0.20 &   0.25 &   0.25 & \bf 49.43 &  48.97 &  68.44 &  69.96 &  81.96 &  82.38 & \\[3pt] 
+    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
+ & \bf MC & \bf NC &  54.53 &  53.68 &   0.11 &   0.11 &   0.13 &   0.13 &  68.57 & \bf 68.00 & \bf 79.71 &  78.64 &  87.85 &  86.79 & \\ 
+  &  & \bf PC &  52.56 & \bf 52.22 &   0.10 & \bf  0.10 &   0.12 & \bf  0.12 &  70.55 &  69.53 &  81.55 &  80.95 & \bf 90.16 &  89.50 & \\[3pt] 
+  & \bf MMC & \bf NC & 102.76 & \bf 96.50 &   0.20 & \bf  0.19 &   0.25 &   0.24 &  46.93 & \bf 52.66 &  67.31 & \bf 76.51 &  82.14 & \bf 89.90 & \\ 
+  &  & \bf PC & 103.82 & 102.42 &   0.20 &   0.20 &   0.24 & \bf  0.24 &  44.62 &  44.37 &  64.80 &  65.13 &  79.60 &  79.38 & \\[3pt] 
+  & \bf TMC & \bf NC &  98.76 & \bf 89.62 &   0.19 & \bf  0.18 &   0.24 & \bf  0.23 & \bf 48.51 &  55.51 &  68.58 & \bf 78.36 &  82.24 & \bf 90.72 & \\ 
+  &  & \bf PC & 100.18 &  98.77 &   0.19 &   0.19 &   0.24 &   0.23 &  45.75 &  45.06 &  65.50 &  65.73 &  79.62 &  79.86 & \\[3pt] 
+  \hline 
+  \end{tabular} 
+  \caption{Results of the posterior predictive checking in total male 
+    circumcision (MC), medical male circumcision (MMC) and traditional male 
+    circumcision (TMC) from fitting the 12 candidate models in Non-VMMC countries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
+    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
+    temporal prior. For all combinations, the within-sample continuous ranked 
+    probability scores (CRPS), mean absolute error (MAE), root mean square 
+    error (RMSE), and the proportion of empirical observations that fell within 
+    the 50\%, 80\%, and 95\% quantiles are shown.} 
+  \label{tab::PPC2 Non-VMMC} 
+\end{table}}
 
-%% Notes on Table %% 
-\textbf{AR1}
+\end{landscape}
 
-\begin{itemize}
-    \item MC: CRPS best for Time TMC, but all similar (2202.10 vs highest at 220.73 for Neither), RMSE best for Both (but rounded to two decimal places is 021 for all!), 50\% coverage best for Time TMC, 80\% Coverage narrowly best for Neither (78.47 vs lowest at 78.18 for Both), 95\% coverage best for Paed Cut-off, but similarly very high everywhere (88.89 vs lowest at 88.56 for Time TMC).
-    \item MMC \& TMC: Very similar to MC (need to expand on this), little difference between models, both in terms of mean fit statistics and posterior predictive coverage.
-    \item Conclusions: 
-    \begin{itemize}
-        \item MC: Models provide very similar fit, with very little difference in both mean fit statistics and coverage between them.
-Therefore, it is best to go with the model that makes the most sense qualitatively (see below).
-        \item MMC & TMC: Similar Conclusion. 
-    \end{itemize}
-    \item \textbf{Final Choice}: 
-    \begin{itemize}
-      \item Qualitatively, the inclusion of a Time TMC component, while computationally expensive, will not harm model fit (but excluding it may harm VMMC countries with high TMC, like Kenya and Ethiopia).
-      \item Also, it is simplest to have a similar treatment of time TMC for both the VMMC and non-VMMC models, unless we have a good reason not to.
-      \item The inclusion of a paedaitric age cutoff for MMC makes sense as we know that VMMC programmes do not perform paediatric circumcisions on policy
-      \item Therefore, the choice of the "Both" model makes the most sense here, in light of the fact that there is little quantitative difference between model fits. 
-    \end{itemize}
-\end{itemize}
-
-\textbf{RW1 \& RW2}
-- Need to expand on writing for RW1 and RW2 temporal priors, but essentially we're seeing the same thing, in that both mean fit statistics and posterior predictive coverages differ very little between models, so we should revert back to our qualitative choice of using a Time TMC component, and a paediatric age cutoff for MMC (i.e.
-the "Both" model).
-
-%% Model Specification Table 1: Non-VMMC countries %%
-
+% VMMC
 \begin{landscape}
@@
     \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
- & \bf MC & \bf NC & 220.08 & 240.11 &   0.17 &   0.18 &   0.22 &   0.23 &  60.81 & \bf 58.56 & \bf 78.89 &  77.33 & \bf 89.06 &  88.16 & \\ 
-  &  & \bf PC & 220.29 & \bf218.79 &   0.17 & \bf  0.16 &   0.22 & \bf  0.21 &  60.90 &  60.51 &  78.79 &  78.83 &  89.04 &  88.97 & \\[3pt] 
-  & \bf MMC & \bf NC & 167.60 & 167.02 &   0.13 &   0.13 &   0.18 &   0.19 &  68.34 &  69.26 &  84.54 &  85.35 &  93.22 & \bf 94.08 & \\ 
-  &  & \bf PC & 168.66 & \bf165.65 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 & \bf 68.24 &  69.42 & \bf 84.39 &  84.80 &  93.19 &  93.83 & \\[3pt] 
-  & \bf TMC & \bf NC & 188.94 & 195.44 &   0.14 &   0.15 &   0.20 &   0.21 &  64.08 &  64.40 &  83.05 &  83.21 &  92.49 & \bf 92.59 & \\ 
-  &  & \bf PC & 190.81 & \bf187.53 &   0.14 & \bf  0.14 &   0.20 & \bf  0.19 & \bf 63.77 &  64.04 &  82.58 & \bf 82.53 &  92.13 &  92.23 & \\[3pt] 
+ & \bf MC & \bf NC & 229.83 & 228.27 &   0.17 &   0.17 &   0.22 &   0.22 &  59.94 & \bf 59.54 & \bf 77.98 &  77.77 & \bf 88.40 &  87.99 & \\ 
+  &  & \bf PC & 230.01 & \bf228.10 &   0.17 & \bf  0.17 &   0.22 & \bf  0.22 &  60.00 &  59.63 &  77.87 &  77.89 &  88.36 &  88.27 & \\[3pt] 
+  & \bf MMC & \bf NC & 176.29 & \bf171.90 &   0.14 & \bf  0.13 &   0.19 & \bf  0.19 &  67.33 &  68.44 &  83.87 &  84.64 &  92.83 & \bf 93.72 & \\ 
+  &  & \bf PC & 177.43 & 174.02 &   0.14 &   0.14 &   0.19 &   0.19 & \bf 67.22 &  68.21 & \bf 83.70 &  84.08 &  92.80 &  93.47 & \\[3pt] 
+  & \bf TMC & \bf NC & 200.04 & \bf194.60 &   0.15 & \bf  0.14 &   0.20 & \bf  0.20 &  62.62 &  63.41 &  82.16 &  82.28 &  91.99 & \bf 92.09 & \\ 
+  &  & \bf PC & 202.00 & 198.56 &   0.15 &   0.14 &   0.20 &   0.20 & \bf 62.28 &  62.60 &  81.66 & \bf 81.64 &  91.61 &  91.72 & \\[3pt] 
     \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
@@
     circumcision (MC), medical male circumcision (MMC) and traditional male 
-    circumcision (TMC) from fitting the 12 candidate models in VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
+    circumcision (TMC) from fitting the 12 candidate models in VMMC countries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
     (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
@@
     the 50\%, 80\%, and 95\% quantiles are shown.} 
-  \label{tab::PPC1VMMC} 
+  \label{tab::PPC1 VMMC} 
 \end{table}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% \begin{landscape}
-% 
-% {\linespread{1} 
-%   \begin{table}[H] 
-%   \centering 
-%   \footnotesize 
-%   \begin{tabular}{>{\bfseries}p{0.75cm} 
-%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
-%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
-%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
-%   \hline  
-%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
-%   \cmidrule(lr){4-15} 
-%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
-%       \multicolumn{6}{c}{\bf Time variant} \\ 
-%   \cmidrule(lr){4-9} 
-%   \cmidrule(lr){10-15} 
-%   & {\bf MMC Model} & {\bf Type} & 
-%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
-%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
-%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
-%   \hline 
-% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
-%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
-%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
-%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
-%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
-%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
-%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
-%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
-%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
-%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
-%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
-%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
-%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
-%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
-%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
-%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
-%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
-%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
-%   \hline 
-%   \end{tabular} 
-%   \caption{Results of the posterior predictive checking in total 
-%              male circumcision (MC), medical male circumcision (MMC) and 
-%              traditional male circumcision (TMC) from fitting the 12 candidate 
-%              models and taking the median value across all Non-VMMC countries. Combinations include 
-%              (i) Time invariant or Time variant TMC, 
-%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
-%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
-%              Random Walk 2 (RW2) temporal prior. 
-%              For all combinations, the within-sample continuous ranked 
-%              probability scores (CRPS), mean absolute error (MAE) , 
-%              root mean squared error (RMSE), and the proportion of empirical 
-%              observations that fell within the 50\%, 80\%, and 95\% 
-%              quantiles are shown.} 
-%   \label{tab::PPC1Non-VMMC} 
-% \end{table}}
-%  
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
-% 
-% \end{landscape}
-
 \end{document}

### 2024-04-16 paper/0_outline/old/paper_cals2.Rmd
Updates from Overleaf

--- 2024-04-15 paper/paper_cals.Rmd
@@
 ```
-
-<!-- TODO: Change year from 2020 to 2023 (once preprint is out) -->
-<!-- TODO: Add survey stuff here -->
-<!-- TODO: Add paragraph breaks (although that's not copying over from PDF) -->
 
@@
 
-# simplify type for faster filtering
+# simplify type
 simplify_type <- function(dat) {
@@
 }
-
-# recursively simplify type 
-simplify_type_rec <- function(x) {
-  # for e.g. vector
-  if (!is.list(x)) {
-    return(x)
-  # simplify type in dataframes
-  } else if (is.data.frame(x)) {
-    if ("type" %in% names(x)) simplify_type(x)
-  # traverse list
-  } else simplify_type_rec(x[[1]])
-  return(x)
-}
-
-# tidy up aggregated age data
-tidy_age <- function(dat, sig_fig = 2) {
-  dat %>% 
-    mutate(across(contains("average_age"), \(x) round(x, sig_fig))) %>% 
-    rename(
-      mean = average_age, lower = average_age_lower, upper = average_age_upper
-    ) %>% 
-    simplify_type()
-}
 ```
@@
 
-## Subnational variation in total, medical \& traditional circumcision over time
-
-<!-- What else could we add to this section? Section 2 is very large!!!
-- Could talk about non-VMMC vs VMMC more anyway -->
+## Subnational Variation in Total, Medical \& Traditional Circumcision over time
 
@@
 x1 <- readRDS("data/inlines/01_inlines.RDS")
-# x1 <- simplify_type_rec(x1)
 for (i in seq_along(x1)) {
@@
 million) new TMCs performed. 
-The disparity between the number of MCs performed and the number of MMCs performed can be partly explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
+The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
 This translated to a change in mean MC coverage for the SSA region from 
@@
 million) in 2020. However, 
-TMC coverage actually decreased in many countries from 2006 to 2020. 
+TMC prevalence actually decreased in many countries from 2006 to 2020. 
 <!-- Should I give a number here? -->
@@
 
-<!-- *Second Plot* -->
+*Second Plot* \\
 <!-- Want to show here how ??? -->
 Within countries, the median difference in MC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
-The smallest variation was in
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
-at 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(area_name)`
-,
-while the largest variation was in 
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
-at 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(area_name)`.
-The median difference within countries in MMC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
-The smallest variation was in
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
-at
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
-\%
-in
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(area_name)`,
-while the largest variation was in 
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
-at 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(area_name)`.
-For TMC coverage, the median difference between districts in 2020 was 
-`r district_diffs_vmmc$median_cov_diffs %>% filter(type == "TMC") %>% pull(mean) %>% to_percentage()`
-The smallest variation was in
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
-at
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
-\%
-in
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(area_name)`,
-while the largest variation was in 
-`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
-at 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(area_name)`
-to
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
-\%
-in 
-`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(area_name)`.
-<!-- Anything else? --->
-
-## Subnational variation in total, medical \& traditional circumcision across different ages
-
-```{r, echo = FALSE}
-x2 <- readRDS("data/inlines/02_inlines.RDS")
-# x2 <- simplify_type_rec(x2)
-for (i in seq_along(x2)) {
-  assign(names(x2)[i], x2[[i]])
-}
-age_group_cov <- sapply(
-  age_group_cov, simplify_type, simplify = FALSE, USE.NAMES = TRUE
-)
-age_group_cov_non_vmmc <- sapply(
-  age_group_cov_non_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
-)
-age_group_cov_vmmc <- sapply(
-  age_group_cov_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
-)
-```
-
-<!-- TODO: Replace WCA/ECA with VMMC/Non-VMMC -->
-
-Age at circumcision differed greatly by circumcision type and location. 
-The five-year age group in 2006, the year before VMMC programme implementation began, 
-which had the highest MC coverage across the SSA region was
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(age_group)`, 
-at 
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
+\%,
+with the smallest variation in 
+`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% last() %>% to_cntry_name()`
 (
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`
-)
-. 
-In contrast, the age group with the highest MC coverage in 2020 was 
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(age_group)`,
-at
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`
-).
-The five-year age group in 2006 which had the highest MMC coverage was
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(age_group)`, 
-at 
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`
-)
-. 
-The age group with the highest MMC coverage in 2020 was also
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(age_group)`,
-, now at
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`
-).
-The five-year age group in 2006 which had the highest TMC coverage was
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(age_group)`, 
-at 
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`
-)
-. 
-The age group with the highest TMC coverage in 2020 was
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(age_group)`,
-,
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
--
-`r age_group_cov$fyag_highest_covs %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`
-).
-This decrease in the five-year age group with the highest MC coverage, increase in the 
-age group for TMC with the highest coverage (as well as a decrease in coverage for 
-the highest five-year age group), and increase in overall MMC coverage across the SSA region is 
-indicative of the effect of VMMC programme implementation on the region.
-
-<!-- TODO Still: 
-- 15-29 year olds increase in MC/TMC/MMC (already written about?)
-- Contrast to 30-49 year olds somehow, showing different patterns of circ
-(increasing more for MC/MMC, decreasing more for TMC)
-- Compare differences in VMMC and non-VMMC, in terms of the above
--->
-We may compare changes in circumcision amongst two age groups; 15-29 year olds, which 
-are a particular focus for VMMC implementation, and 30-49 year olds, which are not. 
-MC coverage amongst 15-29 year olds increased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-In contrast, MC coverage amongst 30-49 year olds only increased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Therefore, MC coverage across SSA saw greater increases in this younger age group than in this older one, in line 
-with VMMC programme age focus. 
-Similarly, MMC coverage amongst 15-29 year olds increased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while MMC coverage amongst 30-49 year olds increased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Therefore, MMC coverage across SSA also saw greater increases amongst 15-29 year olds 
-than amongst 30-49 year olds. 
-The changes seen in TMC, however, contrast to these larger increases in MC and MMC coverage for 15-29 year olds. 
-TMC coverage amongst 15-29 year olds decreased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Thus, TMC coverage decreased less in absolute terms amongst 30-49 year olds than amongst 
-15-29 year olds, which is line with the greater focus on performing MMCs amongst this 
-younger age group.
-
-Finally, we can contrast patterns in circumcision pattern for different age groups
-amongst VMMC and non-VMMC priority countries, where differences in 2006 and 2020 
-levels and patterns of circumcision seem to be more pronounced.
-
-<!-- For VMMC countries, five year age group MC, MMC, TMC -->
-For VMMC priority countries, five-year age group MC coverage 2006 was highest amongst 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
-), but in 2020 was highest amongst
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(age_group)`
-year olds, at
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
-), respectively. 
-This highlights both the increased prevalence of MC in VMMC priority countries, and the
-downward shift in age profile of those who are circumcised, since VMMC programme 
-implementation began. 
-In 2006 MMC coverage was highest amongst 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
- year olds, at 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
-). 
-This contrasts with 2020, where MMC coverage was highest amongst 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
- year olds, at
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
-).
-This shows that much of the downward shift in age profile of circumcised individuals since 2006 
-has been "driven" by an increase in the number of MMCs performed amongst younger individuals. 
-In 2006, TMC coverage was greatest in 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
-). while in 2020 it was most prevalent in
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`.
-This perhaps highlights that VMMC implementation has been focused on areas where 
-TMC has not historically been widely prevalent, and so seems to have had little effect on patterns of TMC in 
-VMMC priority countries, both in terms of its age profile and prevalence.
-
-We can contrast this for the non-VMMC priority countries in SSA.
-The five-year age group MC coverage in both 2006 and 2020 was highest amongst 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
-) and 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
-), respectively. 
-This indicates that MC has increased slightly in non-VMMC priority countries, but the age profile (in terms of the five-year age group with the highest coverage) has not noticeably changed. 
-However, in 2006 MMC coverage was highest amongst 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(age_group)`
- year olds, at 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
-). 
-This contrasts with 2020, where MMC coverage was highest amongst 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(age_group)`
- year olds, at
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
-), showing an interesting shift upwards in age for MMCs in non-VMMC priority countries, as a result of VMMC focus on young adults, as well as a general increase in MMC coverage in these countries. 
-In 2006, TMC coverage was greatest in 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`
-). while in 2020 it was most prevalent in
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(age_group)`
-year olds, at 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()`
- (
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()`
- - 
-`r age_group_cov_non_vmmc$fyag_highest_covs %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`, highlighting a shift upwards in TMCs in VMMC priority countries, 
-likely resulting from previously TMCs being performed as TMCs.
-
-Similarly, we can compare the 2006 and 2020 circumcision levels amongst 15-29 and 30-49 year olds
-in both VMMC and non-VMMC countries, respectively.
-
-In VMMC priority countries, MC coverage amongst 15-29 year olds increased from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-In contrast, MC coverage in 30-49 year olds went from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Therefore, MC coverage in VMMC priority countries increased amongst 15-29 year olds at a higher rate than amongst 30-49 year olds, and indeed greater than in SSA as a whole, highlighting the effects of VMMC implementation in these countries since 2006.
-Similarly, MMC coverage amongst 15-29 year olds increased from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while MMC coverage amongst 30-49 year olds increased from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Therefore, MMC coverage in VMMC priority countries also saw greater increases amongst 15-29 year olds 
-than amongst 30-49 year olds, and greater increases than for SSA as a whole. 
-Again, TMC coverage amongst both fifteen year age groups contrast to these increases for MC and MMC. 
-TMC coverage amongst 15-29 year olds decreased from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-This decrease in TMC coverage can partly be attributed to a combination of increased population in non-TMC practising areas, but TMC coverage also decreased less in absolute terms amongst 30-49 year olds than amongst
-15-29 year olds, which is line with the greater focus on performing MMCs, and hence replacing TMCs, amongst this 
-younger age group.
-
-In contrast, for non-VMMC priority countries, MC coverage in 15-29 year olds increased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, staying relatively similar. 
-MC coverage in 30-49 year olds also increased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, so again, when taking our credible intervals into account, there was little 
-increase amongst this age group in non-VMMC priority countries. 
-It is interesting that MC seems to have increased more amongst 30-49 year olds 
-than amongst 15-29, defying the trend amongst VMMC priority countries and SSA as a whole. 
-MMC coverage amongst 15-29 year olds increased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while MMC coverage amongst 30-49 year olds increased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "MMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Hence, MMC coverage in non-VMMC countries also saw greater increases amongst 30-49 year olds 
-than in 15-29 year olds, but not much change overall when factoring in our uncertainty.
-TMC coverage amongst 15-29 year olds decreased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "15-29", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, while TMC coverage amongst 30-49 year olds decreased from 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2006) %>% pull(upper) %>% to_percentage()`
-) in 2006
-to
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(lower) %>% to_percentage()`
-- 
-`r age_group_cov_non_vmmc$spec_agegroups_mean_cov %>% filter(type == "TMC", age_group == "30-49", year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020. 
-Thus, TMC coverage decreased less in absolute terms amongst 30-49 year olds than amongst 
-15-29 year olds, which is line with the greater focus on performing MMCs amongst this 
-younger age group. 
-TMC coverage decreased more amongst non-VMMC countries for both age groups, suggesting 
-likely replacement of historical TMC with MMC.
-
-## Subnational heterogeneity in age at medical and traditional circumcision
-
-```{r}
-x3 <- readRDS("data/inlines/03_inlines.RDS")
-for (i in seq_along(x3)) {
-  assign(names(x3)[i], x3[[i]])
-}
-aggr_mean_circ_age <- tidy_age(aggr_mean_circ_age)
-aggr_mean_circ_age_non_vmmc <- tidy_age(aggr_mean_circ_age_non_vmmc)
-aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
-```
-
-Fill in! 
-- Talk mainly about average age at which MCs/MMCs/TMCs performed in 2006 and 2020
-- Also compare VMMC and non-VMMC
-
-The mean age at circumcision for MC in 2006 was 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MC") %>% pull(upper)`
-), while in 2020 it was
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MC") %>% pull(upper)`
-).
-<!-- Therefore, factoring in uncertainty there doesn't seem to have been a 
-significant drop in mean age at MC from 2006 to 2020. -->
-Similarly, the mean age at circumcision for MMC in 2006 was 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
-), and in 2020 it was
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
-).
-<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
-Finally, the mean age at circumcision in 2006 for TMC was 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
-), and in 2020 it was
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age %>% filter(year == 2020, type == "TMC") %>% pull(upper)`
-).
-Therefore, the mean age at circumcision for MC and MMC went up slightly from 2006 to 2020. 
-However, it is important to note that the uncertainty ranges in our credible intervals 
-overlap, so this increase could be seen as "non-significant", in some sense. 
-In contrast, the mean age at circumcision for TMC was seen to decrease, altough again, 
-not in a manor that exceeds our uncertainty bounds. 
-This may suggest that VMMC implementation amongst 15-29 year olds has 
-corresponded to an upward shift of mean age at circumcision for MC and MMC, and 
-replaced some circumcisions which would previously have been performed as TMCs, 
-which may explain the observed decrease in mean age of TMC.
-
-As in the previous section, we can also compare how the mean age of circumcision differs 
-amongst VMMC priority countries, versus their non-VMMC prority counterparts in SSA.
-
-For VMMC priority countries, the mean age at circumcision for MC in 2006 was 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MC") %>% pull(upper)`
-), while in 2020 it was
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MC") %>% pull(upper)`
-).
-Similarly, for MMC in 2006 the mean age at circumcision was
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
-), while in 2020 it was
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
-).
-<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
-Lastly, the mean age at circumcision in 2006 for TMC was 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
-), and in 2020 it was
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
-So the mean age at circumcision for all circumcision types is higher in VMMC 
-priority countries than overall in SSA, highlighting the historically low levels of MC and
-TMC in these countries. 
-Like in SSA overall, the mean age at circumcision for MC and MMC went up slightly, albeit not 
-significantly when factoring in uncertainty bounds. 
-Again, mean age at TMC also decreased in VMMC priority countries.
-
-For non-VMMC priority countries, the mean age at MC in 2006 was 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MC") %>% pull(upper)`
-), while in 2020 it was
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MC") %>% pull(upper)`
-).
-Similarly, the mean age at MMC in 2006 was 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "MMC") %>% pull(upper)`
-), and in 2020 it was
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "MMC") %>% pull(upper)`
-).
-<!-- Therefore, again there wasn't a sizeable change in mean age at MMC. -->
-Finally, the mean age at TMC in 2006 for TMC was 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2006, type == "TMC") %>% pull(upper)`
-), and in 2020 it was
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(mean)`
-(
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(lower)`
-- 
-`r aggr_mean_circ_age_non_vmmc %>% filter(year == 2020, type == "TMC") %>% pull(upper)`.
-In contrast to our VMMC priority countries, these countries have a lower mean at 
-circumcision for all circumcision types, largely driven by high TMC levels historically. 
-It is interesting that the age at circumcision for MC and MMC actually increased for
-non-VMMC priority countries, in contrast to SSA as a whole and the priority countries. 
-Likewise, the mean age at TMC increased. 
-This can perhaps be explained by a possible replacement of TMC with MMC in a 
-traditional setting, so at generally younger ages than MMCs performed as part of 
-VMMC programmes. 
-This caused a natural shift upwards of the mean age at TMC, as younger individuals 
-are now more likely to receive MMCs.
-
-<!-- What is the narrative here?
-- For SSA, MC and MMC age goes up, TMC goes down (done)
-- For VMMC, average age for all substantially higher, but follows same pattern. 
-  Could be argued that this is because people previously receiving TMCs are now receiving MMCs, 
-  pushing mean age of TMC down further. 
-- For non-VMMC, ages substantially lower. 
-  MMC age actually decreases, suggesting MMC-nT occuring, replacing TMC! -->
-
-## Decrease in traditional male circumcision in SSA region over time
-
-```{r}
-x4 <- readRDS("data/inlines/04_inlines.RDS")
-for (i in seq_along(x4)) {
-  assign(names(x4)[i], x4[[i]])
-}
-
-```
-
-Narrative here:
-<!-- TMC coverage difference 2006 - 2020, SSA, VMMC, non-VMMC
-- Decrease much more pronounced for non-VMMC
-Number of TMCs performed in 2006 vs 2020, VMMC, non-VMMC
-- Number increased more for VMMC countries (?)
-Change for 15-29 vs 30-49
-- Change relatively similar for non-VMMC, but 15-29 sees much greater change for 
-  VMMC countries
-Country with largest drop (CIV and ? in VMMC)
-- Comment on population of CIV (28 mil) (?) -->
-
-The average TMC coverage in SSA in 2006 was 
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
-). 
-This fell to 
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, a decrease of 
-`r to_percentage(tmc_cov$mean_tmc_cov_diff$mean)`. 
-In non-VMMC priority countries, TMC coverage was 
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
-). 
-This fell to 
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, representing a decrease of 
-`r to_percentage(tmc_cov_non_vmmc$mean_tmc_cov_diff$mean)`
-.
-In contrast, TMC coverage in VMMC priority countries was 
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
-). 
-This fell to 
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc$mean_tmc_cov %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`
-) in 2020, representing a decrease of 
-`r to_percentage(tmc_cov_vmmc$mean_tmc_cov_diff$mean)`.
-Therefore, the decrease in TMC found throughout SSA is much more pronounced for 
-non-VMMC countries.
-
-In 2006, 
-`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
-- 
-`r tmcs_performed$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
-) TMCs were performed, while in 2020 this increased to 
-`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(lower) %>% round(0)`
--
-`r tmcs_performed$tmcs_performed %>% filter(year == 2020) %>% pull(upper) %>% round(0)`
-), representing a 
-`r round(-tmcs_performed$tmcs_performed_diff$mean, 0)`
-increase in annual TMCs.
-However, this increase must be taken within the context of a large increase
-in population in SSA over this period, from 1.23 billion in 2006 to 1.80 billion in 2020, 
-and as seen in our coverage estimates above, constitutes a decrease in the 
-number of TMCs performed per capita in the region (need to calculate this?!)
-<!-- populations %>% filter(age_group == "0+", year %in% spec_years) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
-<!-- populations %>% filter(age_group == "0+", year %in% spec_years, iso3 %in% vmmc_iso3) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
-<!-- populations %>% filter(age_group == "0+", year %in% spec_years, !(iso3 %in% vmmc_iso3)) %>% group_by(year) %>% summarise(population = sum(population, na.rm = TRUE)) -->
-In non-VMMC priority countries, the annual number of TMCs performed changed from 
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
-- 
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
-) in 2006 to 
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(lower) %>% round(0)`
-- 
-`r tmcs_performed_non_vmmc$tmcs_performed %>% filter(year == 2020) %>% pull(upper) %>% round(0)`
-) in 2020, or by 
-`r round(-tmcs_performed_non_vmmc$tmcs_performed_diff$mean, 0)`
-.
-This is within the context of the population of non-VMMC priority countries increasing 
-from 749 million to 1.11 billion from 2006 to 2020. 
-In VMMC priority countries, the number of TMCs performed went from 
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
-- 
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
-) in 2006 to 
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(mean) %>% round(0)`
-(
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(lower) %>% round(0)`
-- 
-`r tmcs_performed_vmmc$tmcs_performed %>% filter(year == 2006) %>% pull(upper) %>% round(0)`
-) in 2020, a fall of 
-`r round(-tmcs_performed_vmmc$tmcs_performed_diff$mean, 0)`.
-In VMMC priority countries, the population increased from 481 million to 694 million. 
-TODO: Comment on this
-
-<!-- TODO: Change to 15-29, right? -->
-We can also compare the differences in TMC coverage change between 15-29 and 
-30-49 year olds, in SSA as a whole and in VMMC and non-VMMC priority countries.
-
-For the 15-29 age group, TMC coverage was reduced from 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2020, a drop of 
-`r tmc_cov_ssa_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-.
-This contrasted with the 30-49 age group, where TMC coverage went from 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_ssa_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2020, a drop of 
-`r tmc_cov_ssa_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-.
-Therefore, in SSA as a whole TMC coverage decreased slightly more amongst 15-29 
-year olds than in 30-49 year olds, likely as a result of VMMC programme focus on 
-this age group.
-
-For the 15-29 year olds in non-VMMC priority countries, TMC coverage was reduced from 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2020, a drop of 
-`r tmc_cov_non_vmmc_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-.
-This contrasted with the 30-49 age group, where TMC coverage went from 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_non_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2020, a drop of 
-`r tmc_cov_non_vmmc_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-.
-Therefore in non-VMMC priority countries the decrease in TMC coverage was larger
-for both age groups than in SSA as a whole, but the difference between this decrease
-for 15-29 year olds versus 30-49 year olds is less pronounced.
-
-For VMMC priority countries, the 15-29 age group, TMC coverage was reduced from 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "15-29") %>% pull(upper) %>% to_percentage()`
-) in 2020, representing a fall of 
-`r tmc_cov_vmmc_15_29_30_49[[2]] %>% filter(age_group == "15-29") %>% pull(mean) %>% to_percentage()`
-.
-In the 30-49 age group, TMC coverage in VMMC priority countries dropped from 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2006, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-(
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(lower) %>% to_percentage()`
-to 
-`r tmc_cov_vmmc_15_29_30_49[[1]] %>% filter(year == 2020, age_group == "30-49") %>% pull(upper) %>% to_percentage()`
-) in 2020, a drop of 
-`r tmc_cov_vmmc_15_29_30_49[[2]] %>% filter(age_group == "30-49") %>% pull(mean) %>% to_percentage()`
-.
-Therefore, in VMMC priority countries there is a much greater disparity in the 
-drop in TMC coverage between 15-29 and 30-49 year olds. 15-29 year olds saw 
-a much greater drop in TMC coverage, likely resulting from VMMC programme focus on 
-these ages.
-
-The largest decrease in TMC coverage from 2006 to 2020 was in 
-`r to_cntry_name(spec_country_tmc_decrease$mean_tmc_cov_diff$iso3)`, where TMC coverage
-fell from 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
- to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
-) to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
- to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`, a 
-decrease of 
-`r to_percentage(spec_country_tmc_decrease[[2]]$mean)`
-.
-
-The largest decrease in TMC coverage amongst VMMC countries was from 
-`r to_cntry_name(spec_country_tmc_decrease$mean_tmc_cov_diff$iso3)`, where TMC coverage
-fell from 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(mean) %>% to_percentage()`
-(
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(lower) %>% to_percentage()`
- to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2006) %>% pull(upper) %>% to_percentage()`
-) to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(mean) %>% to_percentage()`
-(
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(lower) %>% to_percentage()`
- to 
-`r spec_country_tmc_decrease[[1]] %>% filter(year == 2020) %>% pull(upper) %>% to_percentage()`, a 
-decrease of 
-`r to_percentage(spec_country_tmc_decrease[[2]]$mean)`
-.
-
-TODO: Could possibly add smallest decrease here? Would be more interesting for 
-non-VMMC countries, could show where MMC has not begun to replace TMC
-Could also have number of countries in both regions which have experienced a 
-drop in TMC coverage?? Might be interesting for non-VMMC
-
-## UNAIDS goals progress amongst 10-29 year olds in VMMC target countries
-
-```{r}
-x5 <- readRDS("data/inlines/05_inlines.RDS")
-# x5 <- simplify_type_rec(x5)
-
-for (i in seq_along(x5)) {
-  assign(names(x5)[i], x5[[i]])
-}
-
-# aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
-n_required_vmmc       <- simplify_type(n_required_vmmc)
-largest_smallest_vmmc <- simplify_type(largest_smallest_vmmc)
-increase_vmmc         <- simplify_type(increase_vmmc)
-cum_vmmc_circs_performed <- simplify_type(cum_vmmc_circs_performed)
-vmmc_circs_performed <- simplify_type(vmmc_circs_performed)
-
-# countries above threshold
-cntries_thresh <- to_cntry_name(cntry_abv_thresh$iso3[cntry_abv_thresh$age_group == "15-49"])
-
-```
-
-As a reminder, in 2010 the WHO and UNAIDS set a 80\% MC target for 
-15-49 year olds in the VMMC priority countries by 2018.
-This target was expanded in 2016 to the new target of 90\% MC amongst 10-29 year olds 
-in VMMC priority countries by 2021.
-
-Amongst the 14 VMMC priority countries modelled, 
-`r cntry_abv_thresh %>% filter(age_group == "15-49") %>% nrow()`
-countries were projected to have achieved the VMMC target of 
-80\% MC coverage amongst 15-49 year olds by 2020, 
-`r paste(paste(cntries_thresh[-length(cntries_thresh)], collapse = ", "), last(cntries_thresh), sep = " and ")`.
-None were expected to reach the 90\% target for 10-29 year olds. 
-No countries were expected to have reached these goals in all districts.
-
-MC coverage amongst 10-29 year olds across VMMC priority countries increased from 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
-) in 2020, 
-an increase of 
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
-- 
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
-).
-MMC coverage amongst 10-29 year olds across VMMC priority countries increased from 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
-) in 2020, an increase of 
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
-- 
-`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
-).
-MC coverage amongst 15-49 year olds across VMMC priority countries increased from 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
-) in 2020, 
-an increase of 
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
-- 
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
-).
-MMC coverage amongst 15-49 year olds across VMMC priority countries increased from 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
-) in 2006 to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
-to 
-`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
-) in 2020, an increase of 
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
-(
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
-- 
-`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
-).
-
-Between 2006 and 2020 in these countries, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(mean) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(lower) %>% to_mill()`
-million
--
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) MCs were performed on 10-29 year olds.
-Of these, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) were MMCs, and 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) were TMCs. 
-Over the same period, 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(mean) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(lower) %>% to_mill()`
-million
--
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) MCs were performed on 15-49 year olds,
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) of which were MMCs, and 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-(
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-- 
-`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) of which were TMCs.
-
-The number of annual MCs amongst 10-29 year olds increased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020.
-
-The number of annual MMCs amongst 10-29 increased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020, while in constrast, the number of TMCs decreased from 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020.
-
-For 15-49 year olds, the number of annual MCs increased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020.
-
-Annual MMCs amongst 15-49 increased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020, while in constrast, the number of TMCs decreased from 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2006 to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
-million
- (
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
-million
- to 
-`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
-million
-) in 2020.
-
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean) %>% to_mill()`
- (
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower) %>% to_mill()`
- to 
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper) %>% to_mill()`
-) additional circumcisions are required to achieve 90\% and 80\% MC coverage targets 
-for 10-29 and 15-49 year olds, respectively, across all VMMC priority countries.
-
-This equates to 
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
-(
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
- to 
-`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
-)
-and 
-`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-(
-`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
-to
-`r n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
-)
-times the projected number of MCs for 10-29 and 15-49 year olds for 2020.
-
-MC coverage in 2020 for 10-29 year olds in VMMC priority countries was highest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-), and lowest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
-.
-For 15-49 year olds, the highest MC coverage was in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-), and lowest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
-.
-MMC coverage for 10-29 year olds in VMMC priority countries was highest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-), and lowest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
-.
-For 15-49 year olds, the highest MMC coverage was in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-), and lowest in 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
-at 
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
-(
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
--
-`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
-.
-
-The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries was in 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
-from 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
-) in 2006 to 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-) in 2020, a 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
-) increase. 
-In contrast, the lowest increase in MC coverage in these countries was in 
-from 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
-) in 2006 to 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-) in 2020, a 
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_mean) %>% to_percentage()`
-(
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_lower) %>% to_percentage()`
--
-`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(diff_upper) %>% to_percentage()`
-) increase.
-
-However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries. 
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
-(
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
--
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
-)
-of
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(n)) %>% pull()`
-districts in these countries were expected to have reached 90\% MC coverage 
-amongst 10-29 year olds in 2020, up from 
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
-(
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
--
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
-) of
-`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(n)) %>% pull()`
-in 2006, before VMMC programmes began. 
-Similarly, 
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
-(
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
--
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
-)
-of
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(n)) %>% pull()`
-districts in these countries were expected to have reached 80\% MC coverage for 
-15-49 year olds in 2020, compared to
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
-(
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
--
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
-) of
-`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(n)) %>% pull()`
-in 2006.
-
-In 2020, 
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(mean)`
-(
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(upper)`
-)
-of the 14 VMMC priority countries had no districts which satisfied the 90\% MC coverage target for 10-29
-year olds. This was down from 
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(mean)`
-(
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(upper)`
-)
-in 2006. 
-Similarly, in 2020, 
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(mean)`
-(
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(upper)`
-)
-countries had no districts which satisfied the 80\% MC coverage target for 15-49
-year olds. This was down from 
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(mean)`
-(
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(lower)`
--
-`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(upper)`
-)
-in 2006.
+<!-- `r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% pull(mean) %>% `[[`(2) %>% to_percentage()` -->

### 2024-04-16 paper/1_paper-preprint/paper.tex
Updates from Overleaf

\documentclass{article}

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{todonotes}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

\renewcommand\Affilfont{\itshape\footnotesize}
\def\ci{\perp\!\!\!\perp}

\renewcommand\Affilfont{\itshape\footnotesize}
\linespread{1.5}

% \usepackage{lineno}
% \linenumbers

% Nature Bibliography style
\usepackage[backend=biber,style=nature]{biblatex}
\addbibresource{library.bib}

%%%%%%%%%%%%%
%%% Title %%%
%%%%%%%%%%%%%
\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}

\author{}
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\vspace{-1cm}

Patrick O'Toole\textsuperscript{1,2},
Matthew L. Thomas\textsuperscript{1,3,4},
Oliver Stevens\textsuperscript{1},
Kevin Lam\textsuperscript{1,5},
Katharine Kripke\textsuperscript{6},
Rachel Esra\textsuperscript{1},
Ian Wanyeki\textsuperscript{7},
Lycias Zembe\textsuperscript{7},
Jeffrey W. Imai-Eaton\textsuperscript{1,8} \\
\smallskip

\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London, London, United Kingdom\\
\textbf{2} Department of Mathematical Sciences, University of Bath, Bath, United Kingdom\\
\textbf{3} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
\textbf{4} National Centre for Atmospheric Sciences, University of Manchester, Manchester, United Kingdom\\
\textbf{5} Department of Statistics, University of British Columbia, Vancouver, Canada\\
\textbf{6} Avenir Health, Washington, District of Columbia, United States of America\\
\textbf{7} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
\textbf{8} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\

\smallskip

* Corresponding Author Email

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  \noindent \textbf{Background} \\

  \noindent \textbf{Methods} \\

  \noindent \textbf{Results} \\

  \noindent \textbf{Conclusions} \\

\end{abstract}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The HIV epidemic continues to be a public health priority, with the Joint United Nations Programme on HIV/AIDS (UNAIDS) estimating that over 25 million people live with HIV across sub-Saharan Africa in 2022, with over 650,000 new infections that year \cite{UNAIDSStats}. To achieve the the global community's ambitious goals of ending the AIDS public health crisis by 2030, more work will need to be done \cite{UNAIDSStrategy}. Among the numerous interventions available, voluntary medical male circumcision (VMMC) has emerged as a powerful and cost-effective intervention to reduce HIV incidence \cite{bansi2023cost} with it estimated to reduce male-to-female transition of HIV by 60\% \cite{gray2007male, bailey2007male, auvert2005randomized, gray2012effectiveness, grund2017association}. Furthermore, other research has shown that VMMC can decrease the risk of male-to-male transmission of HIV \cite{pintye2019benefits}, and reduce the transmission of other sexually transmitted infections \cite{tobian2009male}.

In 2007, the World Health Organization (WHO) and UNAIDS recommended a scale-up in male circumcision coverage for HIV prevention in fifteen countries across Central and Western Africa with a high HIV incidence and low circumcision coverage: Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, South Sudan Tanzania, Uganda, Zambia, and Zimbabwe \cite{UNAIDSJoint, davis2018progress, WHOVoluntary2}. UNAIDS' aim was to reach 90\% circumcision coverage among adolescent boys and young men aged 10--29 years by 2021 \cite{WHOFramework}. Since the decision to scale-up in 2007, over 27 million VMMCs have been conducted in these priority countries with the support of national governments as well as international organisations such as US President’s Emergency Plan for AIDS Relief (PEPFAR) \cite{WHOHIVProg}.

There is a need to provide comprehensive and accurate estimates of male circumcision coverage across all ages, over time, across sub-Saharan Africa to (i) aid VMMC programmes planning, delivery, target setting and checking target attainment and (ii) to evaluate the impacts of VMMC campaigns on HIV incidence. However, this is complex task, as despite the upscaling in medical male circumcision (MMC) being a recent phenomenon, it has been long been practised as part of traditional male initiation ceremonies in many African countries. The coverage and provision of traditional male circumcision (TMC) can vary considerably and is mainly influenced by community, religious, ethnic and cultural led values. For example, in South Africa, TMC coverage ranged from 5.3\% in KwaZulu-Natal to 48.9\% in Eastern Cape among 15-49 year olds, with the average age of circumcision varying from 12.2 years in Limpopo to 20.4 in Western Cape \cite{thomas2024substantial}. TMCs conducted during male initiation ceremonies are often performed using non-medical methods non-clinical settings by a traditional practitioner with no formal medical training \cite{drain2006male, wilcken2010traditional, weiss2000male}. The evidence that TMC provides the same HIV prevention benefits as MMC is mixed, as TMC may not involve a complete circumcision in some populations \cite{WHOTraditional, shaffer2007protective, bailey2008male}.

There have been a number of recent approaches to estimate coverage of circumcision in sub-Saharan Africa \cite{cork2020mapping, kripke2016age, kripke2016cost, thomas2024substantial}. Cork {\it et al.} \cite{cork2020mapping} developed a Bayesian geo-statistical model, utilizing survey data, to produce annual estimates of total male circumcision coverage sub-nationally in sub-Saharan Africa between 2000 and 2017. This approach is limited cannot provide a full picture of the coverage and provisions of circumcision alone as it only produced estimates for 15–49 year olds, does not distinguish between circumcision type, and does not track the structured dynamics of circumcision by type within cohorts. Kripke {\it et al.} \cite{kripke2016age, kripke2016cost} developed The Decision Makers’ Program Planning Toolkit, Version 2 (DMPPT2), a compartmental model that combines estimates of circumcision coverage from survey data (prior to the VMMC scale-up) with information on the reported numbers of VMMCs, to estimate sub-national circumcision coverage and unmet need across sub-Saharan Africa, in 5-year age groups over time. This approach is also limited as the model does not incorporate data from more recent household surveys (since intervention implementation), does not estimate any uncertainty associated with the circumcision coverage estimates and also does not distinguish by circumcision type.

Thomas {\it et al.} \cite{thomas2024substantial} aimed to address the issues of both models by producing a model to generate region-age-time-type specific probabilities and coverage of male circumcision. The model extended a competing risks time-to-event model which enabled the synthesising of both survey data and programmatic data from VMMC providers. However, this study focused only on South Africa and the model was developed with many local dynamics in the provision to synthesise both data sources. Here, we take a similar approach to Thomas {\it et al.} and develop a discrete-time competing risks time-to-event model only using survey data in order to estimate the probabilities and coverage of male circumcision by type, sub-national area, single-year age, and time along with probabilistic uncertainty. We applied the model to estimate annual probabilities and coverage of circumcision by district in 34 countries across sub-Saharan Africa between 2008 and 2023 in order to quantify gaps in attainment of VMMC targets within priority age groups.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Methods}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Study Region}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The study consisted of 34 sub-Saharan Africa countries that have conducted surveys that contain information on self-reported circumcision status since 2002: Angola, Benin, Botswana, Burkina Faso, Burundi, Cameroon, Chad, Côte d’Ivoire, The Democratic Republic of the Congo (DR Congo), Eswatini, Ethiopia, Gabon, Gambia, Ghana, Guinea, Kenya, Lesotho, Liberia, Malawi, Mali, Mozambique, Namibia, Niger, Nigeria, The Republic of the Congo (the Congo), Rwanda, Senegal, Sierra Leone, South Africa, Tanzania, Togo, Uganda, Zambia, and Zimbabwe. We did not include Central African Republic, Equatorial Guinea, Guinea-Bissau, and South Sudan in the study as they either had no surveys conducted, or, had no surveys conducted that collected sufficient data on circumcision status for this analysis (see below).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Household surveys}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In total, we identified 120 nationally representative household surveys across sub-Saharan Africa between 2002 and 2023 that contained information on self-reported circumcision status. These included several major survey series, namely the Demographic and Health Surveys (DHS) \cite{dhs}, AIDS Indicator Surveys (AIS) \cite{ais}, Population-based HIV Impact Assessment (PHIA) surveys \cite{phia}, Multiple Indicator Cluster Surveys (MICS) \cite{mics}, and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{hsrc}. We excluded five surveys as they did not contain the information on age at circumcision required for modelling: 2008 and 2013 Botswana AIDS Impact Surveys (BAIS), the Central African Republic 2018 MICS survey, and the 2014 and 2018 Guinea-Bissau MICS surveys. Figure S1 in the Supplementary Material shows all available surveys, by the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information.

We extracted the age (at survey), cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): (i) self-reported circumcision status, (ii) age at circumcision, (iii) who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practitioner, other or unknown) and (iv) where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown). When calculating the residence of the respondents, we matched survey data to clusters with accompanying (masked) geo-coordinates in order to assign the primary sub-national unit (PSNU; hereafter referred to as the district level) for modelling purposes. However, geo-cordinates were not available in some surveys and therefore we were unable to allocate their district directly. Instead, we matched survey data to the least granular areal unit declared by the survey (most often level 1 administrative boundaries). Survey respondents were excluded if they were missing any demographic information or had a missing circumcision status. Supplementary Table 1 contains a summary of the circumcision-related information from each surveys, the availability of the circumcision related questions and the sample sizes in each survey.

Circumcisions were classed as a medical male circumcision (MMC), traditional male circumcision (TMC) or “unknown” male circumcision (MC) based on the responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ using the criteria described in Supplementary Table 2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Administrative boundaries }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A list of districts, the geographic boundaries, and the nesting in higher level administrative areas were obtained from the Combined Geographic Health Boundaries through the UNAIDS AIDS Data Repository \cite{UNAIDSADR}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Population data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We obtained estimates for the male population size in 5-year age group between 2008 through 2023 through WorldPop \cite{worldpop}. The unconstrained individual country datasets at a 100m resolution were overlaid and aggregated using the UNAIDS administrative boundaries \cite{UNAIDSADR}, and scaled to align with the UN Population Division World Population Prospects 2019 \cite{wpp}. Estimates were then distributed to single-year age using Beers ordinary formula \cite{beersmethod, beers}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Model}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Following a similar approach to \cite{thomas2024substantial}, we developed a Bayesian competing risk discrete time-to-event model \cite{putter2006tutorial}, that utilizes survey data to estimate the probabilities and coverage of circumcision stratified by district, age, time, and type. We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints.

In countries where suitable survey information was collected on circumcision type, we consider the following types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC), (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC) and (3) circumcisions of any or (unknown) type (MC). Some countries did not have any surveys that collected information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type. For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only. A full list of the models applied to each of the countries can be seen in Supplementary Table 3.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Probabilities of circumcision (by type)}
\label{sec::bytype}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In countries where suitable survey information was collected on circumcision type, we used survey data to model the probabilities of receiving a TMC, MMC or MC by district, age and time.

For the probablility of TMC, a key assumption of Thomas {\it et al.} \cite{thomas2024substantial} was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible across sub-Saharan Africa. Firstly, in some countries the level and practices of TMC may have changed through time due to demographic shifts. Secondly, there has also been a recent push, particularly in VMMC priority countries, to replace TMCs with using medical methods (i.e. MMCs) to ensure men obtain the full HIV prevention efficacy and/or for safety considerations \cite{thomas2024substantial}. Finally, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high. The probability of TMC was therefore modelled by a logit-linear function with random effects for age, district, time, as well as age-district and age-time interaction, to allow for different patterns in the age at circumcision across space and time. We did not include a district-time interaction into due to computational constraints.

The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2007. In priority countries, VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices and are unrelated to scale-up of VMMC. Due to this, Thomas {\it et al.} \cite{thomas2024substantial} separated the probability of MMC into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over). This ensured that any increase in MMC for those aged 10 and over did not bias the probability of MMC in those under 10 in South Africa. However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage. Therefore, we consider two models for the probability of MMC in each country: (i) paediatric cut-off for VMMC priority countries and (ii) no paediatric cut off for non-priority countries. For the probability of MMC with {\it a paediatric cut-off}, the probability of paediatric MMC was modelled using a logit-linear function with random effects for age, district, an age-district interaction, to allow for different practices of paediatric circumcision observed across districts. We assumed that the probability of paediatric MMC was constant over time. The probability of adolescent and adult MMC was also modelled using logit-linear function with random effects for age, time, and district, as well as all the associated two-way interactions to allow for inter-district/time/age variation in circumcision rates. We modelled probability of MMC with {\it no paediatric cut-off} was modelled using logit-linear function with random effects for age, time, and district, and interactions for district-time, age-time, and age-district, to allow for inter-district/time/age variation in circumcision rates.  To ensure the probability of MC (i.e. the sum of the probabilities of MMC and TMC) was not larger than one, we applied the probability of TMC before MMC in each time step.

We model the probability of circumcision of any (or unknown) type by taking the sum of having either a TMC or MMC in each district, age, time stratum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Probabilities of circumcision (typeless)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In countries that did not have a survey that containing information on the type of circumcision, we used survey data to model the probabilities of receiving MC  by district, age and time. We modelled probability of MC using logit-linear function with random effects for age, time, and district, as well as the associated two-way interactions to allow for inter-district/time/age variation in MC rates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Circumcision coverage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We calculated the estimated circumcision coverage by type (MMC, TMC, or MC) within each cohort using the cumulative incidence function, which defines the marginal probability (or proportion/coverage of) individuals who were received an MMC, TMC, or MC by district, age and time, whilst accounting for the competing risk of other circumcision type.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Model priors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Prior distributions were specified on all model parameters and were specified to allow areas, with little to no data, to borrow district-age-time information on circumcision. Furthermore, we wanted to ensure any correlation in circumcision practices across district, age and time was modelled. We assigned intrinsic conditional autoregressive (ICAR) priors to the district random effects \cite{besag1995conditional}, and penalised B-spline functions on the age random effects \cite{wood2017generalized}, and a an autoregressive process of order 1 (AR1) on the temporal random effects \cite{shumway2000time}. The age-district, age-time, and district-time interaction terms were modelled as Type IV interactions as defined by Knorr-Held and Leonard, where precision matrices were constructed through Kronecker products \cite{knorr2000bayesian}. Vague Gaussian priors were assigned to each of the intercepts, and Gaussian priors were specified for all correlation parameters on the logit scale, such that a priori there was 95\% probability that the autocorrelation parameters on AR1 processes were between 0.48 and 0.99 on the real scale. We assigned exponential priors on standard deviations parameters, with the same hyperparameters for the age, district and age-district random effects. For the time, age-time and space-time random effects, the hyperparameters on the exponential priors were decided during model calibration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Likelihood}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The extracted survey data consisted of individual observations of self-reported age at circumcision, date of birth, and circumcision type (MMC, TMC, or MC) from male survey respondents. Surveyed individuals were followed from their year of birth to either their year of circumcision or their year of censoring. For circumcised individuals, the year of circumcision was calculated as the year of birth plus the age at circumcision. It was assumed that no circumcisions occurred after age 59  uncircumcised individuals were right censored in either the survey year or when they were 59. Individuals who self-reported they were circumcised but did not report an age at circumcision were left censored.

Survey data are collected through a complex two-stage cluster sampling design with unequal sampling probabilities therefore using a standard likelihood may lead to biased estimates of the probabilities of circumcision and the associated coverage. To account for these survey designs, we used a weighted pseudo-likelihood in which we replaced the observed counts of each event with weighted counts, calculated using survey weights \cite{thomas2024substantial}. Individuals sampling weight were standardised using the Kish effective sample size to ensure comparison across surveys \cite{kish1965survey}.

Wherever possible, we matched survey data to clusters with accompanying geo-coordinates in order to assign the district. However, geo-cordinates were not available in some surveys (e.g. MICS, see above) and therefore we were unable to allocate the district directly. In this case, we matched survey data to the least granular areal unit declared by the survey. In most instances, these areal units represented a higher administrative boundaries (e.g. national/admin-0) than the district. For surveys that did not collect information on the district level, we replaced district probabilities of TMC, MMC and MC with a population-weighted regional estimate in the likelihood to include survey data on higher administrative levels into the model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Inference}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All models were implemented and fitted in R \cite{rcore} using Template Model Builder (TMB) \cite{kristensen2016tmb}. TMB is a software package that performs approximate Bayesian inference by uses automatic differentiation and Laplace approximations to estimate posterior distributions for model parameters. Models were optimised using the quasi-newton L-BFGS-B optimisation method \cite{byrd1995limited}.

Using the final models from each country, we estimated full posterior distributions of the annual probabilities of becoming circumcised and the corresponding circumcision coverage between 2000 and 2023, by circumcision type, single-year age group, and the district level. Posterior predictive distributions for aggregates were obtained using Monte Carlo sampling with samples drawn from the joint posterior distributions, conditional on the optimised hyper-parameters \cite{eaton2021naomi}. Joint samples of the annual probabilities of becoming circumcised and the corresponding circumcision coverage in each region-age-time-type stratum were aggregated to produce samples from the posterior distribution of any quantity of interest. For each aggregate, the posterior mean, median, standard deviation, and quantile-based 95\% credible intervals (CI) were computed from the corresponding posterior distribution. Samples were aggregated: (1) from district level to coarser administrative boundaries (e.g. province, national) and (2) from single-year age groups to five-year age group (0--4, 5--9, etc.) and coarser priority age groups (15--49, 15--29, etc.). A full list of model outputs can be found in Supplementary Table 4.

Further technical details on the model used can be found in the Supplementary Materials.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage 
\printbibliography

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2024-04-16 paper/1_paper-preprint/supp_figs.tex
Updates from Overleaf

--- 2023-08-30 paper/supp_figs.tex
@@
 
+%% Label figures and tables Figure SX and Table SX
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplementary Table}
+
+\setcounter{LTchunksize}{8}
 %%%%%%%%%%%%%
@@
 
-Patrick O'Toole\textsuperscript{1},
-Matthew L. Thomas\textsuperscript{1,2},
+Patrick O'Toole\textsuperscript{1,2},
+Matthew L. Thomas\textsuperscript{1,3,4},
 Oliver Stevens\textsuperscript{1},
-Kevin Lam\textsuperscript{1,3},
-Katharine Kripke\textsuperscript{4},
+Kevin Lam\textsuperscript{1,5},
+Katharine Kripke\textsuperscript{6},
 Rachel Esra\textsuperscript{1},
-Ian Wanyeki\textsuperscript{5},
-Lycias Zembe\textsuperscript{5},
-Jeffrey W. Eaton\textsuperscript{1,6} \\
+Ian Wanyeki\textsuperscript{7},
+Lycias Zembe\textsuperscript{7},
+Jeffrey W. Imai-Eaton\textsuperscript{1,8} \\
 \smallskip
 
-\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial Colleg  e London, London, United Kingdom\\
-\textbf{2} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
-\textbf{3} Department of Statistics, University of British Columbia, Vancouver, Canada\\
-\textbf{4} Avenir Health, Washington, District of Columbia, United States of America\\
-\textbf{5} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
-\textbf{6} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
-
-\smallskip
+\textbf{1} MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London, London, United Kingdom\\
+\textbf{2} Department of Mathematical Sciences, University of Bath, Bath, United Kingdom\\
+\textbf{3} Department of Earth and Environmental Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{4} National Centre for Atmospheric Sciences, University of Manchester, Manchester, United Kingdom\\
+\textbf{5} Department of Statistics, University of British Columbia, Vancouver, Canada\\
+\textbf{6} Avenir Health, Washington, District of Columbia, United States of America\\
+\textbf{7} Joint United Nations Programme on HIV/AIDS (UNAIDS), Geneva, Switzerland\\
+\textbf{8} Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, Massachusetts, United States of America\\
 
@@
 \section{Data}
-\label{sec:org8802288}
 
@@
 
-\subsection{Survey Data}
-\label{sec:org09db5e8}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
-We excluded Equitorial Guinea, Guinea-Bissau, the Central African Republic and Botswana because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
-In total, we identified 109 nationally representative household surveys conducted the study region between 2002 and 2019.
-These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs, ais, phia, hsrc2002, hsrc2008, hsrc2012, hsrc2017} \todo{include MICS reference}.
-Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
-\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} \todo{done, what do you mean by "link in survey figure?"}
-Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework.
-The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008, bais2013}.
-For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys.
-Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
-See figure 1 for a visual representation of the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information. 
-See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.
-
-\begin{figure}[H]
+\begin{figure}[!hbtp]
     \centering
-    \includegraphics[width=.9\linewidth]{paper/plots/01_survey_table.png}
+    \includegraphics[width=0.8\linewidth]{figures/supp_figures/01_survey_table.png}
     \caption{Household surveys detailing circumcision patterns in sub-Saharan Africa.
@@
 Triangular points have no information on circumcision type.}
-    \label{fig:enter-label}
+    \label{fig:surveys}
 \end{figure}
 
-Demographic variables such as age, residence and survey sampling weight were extracted from all surveys, alongside information related to circumcision: self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown).
-\textbf{[Write and link in survey table].}
-
-% \begin{landscape}
-{\linespread{1}
-  \footnotesize 
-\begin{longtable}[c]{ll ccc c}
-      %%%%%%%%%%%%%%%%%%%%
-      %%% Table header %%%
-      %%%%%%%%%%%%%%%%%%%%
-      % Upper layer of table header
-      \hline
-      % Lines inside the header
-      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
-      \cmidrule(lr){5-6}
-       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
-       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
-      % Lower lines
-      \hline
-      \vspace{-3pt}
-      \endhead
-      %%%%%%%%%%%%%%%%%%%%
-      %%% Table footer %%%
-      %%%%%%%%%%%%%%%%%%%%
-      \\[-3pt] \hline
-      \endfoot
-      %%%%%%%%%%%%%%%%%%%%%%
-      %%% Table contents %%%
-      %%%%%%%%%%%%%%%%%%%%%%
-      \multicolumn{2}{l}{\textbf{Angola}} \\ 
-& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Benin}} \\ 
-& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\ 
-& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2014 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\ 
-& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 
-\multicolumn{2}{l}{\textbf{Botswana}} \\ 
-& 2008 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\ 
-& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 
-\end{longtable}
-}
-
 \begin{landscape}
-\include{paper/figures/supp_figs/Survey_Table}
+\include{paper/1_paper-preprint/figures/supp_figures/Survey_Table}
 \end{landscape}
-
-The age of respondents was calculated from the century-month-code (CMC) of birth and interview dates. 
-Survey respondents were located to their districts using masked cluster geocoordinates. 
-Where these coordinates were unavailable (as in several MICS surveys) respondents were located to their level 1 administrative boundaries, most often corresponding to a province.
-
-Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’ were classified \textbf{[Link to the table]}.
-Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type.
 
@@
 
-In total, information was extracted from XXX, XXX respondents from all surveys.
-\textbf{[Participation rates table]}
-\todo{Get Matt to make dummy table for me based on this info for 2-3 countries, then I can fill in}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Administrative boundaries}
-\label{sec:org0995c95}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-[Add in information about the boundaries] 
-\todo{Section for Jeff}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Population}
-\label{sec:org0d7d6e9}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Estimates for the male population size by district and five-year age group from 2002 through 2019 were sourced from XXX. 
-Distributed (?) to single-year of age according to ??? 
-\todo{Section for Jeff}
+\section{Model}
 
@@
 
-\section{Model}
-\label{sec:org38d457a}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-{\color{red} \bf
-To do:
-\begin{itemize}
-    \item Model calibration
-    \item Prior choice
-    \item Citations
-\end{itemize}}
-
-Following a similar approach to \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type.
+Following a similar approach to \cite{thomas2024substantial}, we developed a Bayesian hierarchical model along with small area estimation methods that utilizes survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type.
 We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).
@@
 In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
-Some countries did not have any surveys that collected information on the type of circumcision (see above), so we were unable to conduct an analysis of the probabilities of circumcision by type.
+Some countries did not have any surveys that collected information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type.
 For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.
+A list of the models applied to each of the countries can be seen
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{p{0.35\linewidth} p{0.6\linewidth}}
+        \hline
+         \textbf{Model} & \textbf{Countries }  \\
+        \hline
+         By type - Paediatric cut-off & Botswana, Eswatini, Ethiopia, Kenya, Lesotho, Malawi, Mozambique, Namibia, Rwanda, South Africa, Tanzania, Uganda, Zambia, and Zimbabwe. (14) \\
+         By type - No paediatric cut-off & Angola, Benin, Burkina Faso, Burundi, Cameroon, Chad, Côte d’Ivoire, Gabon, Gambia, Ghana, Mali, Nigeria, The Republic of the Congo (the Congo), Sierra Leone, Togo.
+(15) \\
+         Typeless & The Democratic Republic of the Congo (DR Congo), Guinea, Liberia, Niger, Senegal. \\
+         % Excluded                         & Central African Republic, Equatorial Guinea, Guinea-Bissau, South Sudan. \\
+        \hline
+    \end{tabular}
+    \caption{Caption}
+    \label{tab:my_label}
+\end{table}
 
@@
 \noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in district $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
-\begin{equation} 
+\begin{equation*} 
 		\lambda^{\text{TMC}}_{iat} = \mathbb{P}(\text{TMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
 	\label{eqn::TMC}
-\end{equation}
-A key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere.
-For example, in some countries the level and practices of TMC have changed through time due to demographic shifts.
-There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}.
-Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
-Here, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e.
-constant over time) and (ii) time variant (i.e.
-varying over time).
+\end{equation*}
 
-The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function, 
-\begin{equation*} 
-	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\gamma}_{ia}
-\end{equation*}
-where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a district random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-district interaction term to allow different age patterns of TMC across districts.
-The {\it time-variant} probability of TMC was also modelled using a piece-wise logit-linear function,
+A key assumption of Thomas {\it et al.} \cite{thomas2024substantial} was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible across sub-Saharan Africa.
+Firstly, in some countries the level and practices of TMC may have changed through time due to demographic shifts.
+Secondly, there has also been a recent push, particularly in VMMC priority countries, to replace TMCs with using medical methods (i.e.
+MMCs) to ensure men obtain the full HIV prevention efficacy and/or for safety considerations \cite{thomas2024substantial}.
+Finally, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high.
+Therefore, we model the probability of TMC was also modelled using a piece-wise logit-linear function,
 \begin{equation*} 
@@
 We did not include a district-time interaction into due to computational constraints.
-
-Whether a country used a time-invariant or time-variant probability of TMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
 
@@
 
-The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention.
-VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
-Due to this, Thomas et al.
-\cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
+The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2007.
+In priority countries, VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices and are unrelated to scale-up of VMMC.
+Due to this, Thomas {\it et al.} \cite{thomas2024substantial} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over).
 This ensured that any increase in MMC for those aged 10 and over did not bias the probability of MMC in those under 10 in South Africa.
 However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage.
-Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) no cut-off and (ii) paediatric cut off.
+Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$: The probability of MMC was modelled with a paediatric cut-off for VMMC priority countries and without a paediatric cut-off for non-priority countries.
 
-We modelled the probability of MMC {\it with no cut-off} using a piece-wise logit-linear function, 
-\begin{equation*}
-	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
-\end{equation*}
-where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MMCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MMCs over time across districts.
-We also modelled the probability of MMC {\it with a paediatric cut-off} using a piece-wise logit-linear function,
+We modelled the probability of MMC {\it with a paediatric cut-off} using a piece-wise logit-linear function, 
 \begin{equation*}
@@
 $\lambda^{\text{MMC}}_{iat} \equiv \lambda^{\text{MMC}}_{ia}$ when $0\leq a \leq 9$), as paediatric medical circumcision practices are unrelated to VMMC for HIV prevention and are relatively stable.
-
-The choice of whether a country used a paediatric cut-off or no cut-off in the probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).
+We also modelled the probability of MMC {\it with no cut-off} using a piece-wise logit-linear function,
+\begin{equation*}
+	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
+\end{equation*}
+where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MMCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MMCs over time across districts.
 
@@
 \noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability that an individual in district $i$ received a circumcision (either a TMC or MMC) at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
-\begin{equation} 
+\begin{equation*} 
 		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
 	\label{eqn::MC}
-\end{equation}
+\end{equation*}
 We modelled the probability of MC using a piece-wise logit-linear function:
@@
 
-In time, we consider three possible prior distribution choices for the random effects ($\hat{\theta}_t$, $\hat{\delta}_{at}$, $\theta_t$, $\delta_{at}$ and $\zeta_{it}$): an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2).
-AR and RW processes allows us to encode temporal dependence between survey information on the probability and coverage of circumcision and project this into the future.
+In time, we modelled the random effects ($\hat{\theta}_t$, $\hat{\delta}_{at}$, $\theta_t$, $\delta_{at}$ and $\zeta_{it}$) using an autoregressive process of order 1 (AR1) which allows us to encode temporal dependence between survey information on the probability and coverage of circumcision.
 For a generic parameter $\beta_t$, an AR1 process assumes that,
@@
 The joint distribution may be equivalently expressed as $\boldsymbol{\beta}\; | \; \rho_{\beta}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{T}(\rho_{\beta}))$ where $Q_{T}$ is the precision matrix and encodes the first order dependency in time controlled by the autocorrelation parameter $\rho_{\beta}$.
-A RW1 process assumes that,
-\begin{align*} 
-  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 2, 3,\ldots, N_T \\
-  \beta_{1} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1
-\end{align*}
-and a RW2 process assumes that,
-\begin{align*} 
-  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 3, 4,\ldots, N_T \\
-  \beta_{t} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1, 2
-\end{align*}
-where $\tau_{\beta}$ is the precision.
-For both RW1 and RW2, the joint distribution may be equivalently expressed as $\boldsymbol{\beta}\; | \; \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{T})$ where $Q_{T}$ is the precision matrix and encodes the dependency in time of the process and will be rank deficient and consequently the prior would be improper \cite{rue2005gaussian}.
-The choice of whether a country uses a AR1, RW1 and RW2 as a temporal prior was chosen depending on which produced the best out-of-sample model fit during model calibration (see Section \ref{sec::modelcheck} for further details).
 
@@
 corresponding to 95\% CI prior weight that the autocorrelation parameters are between 0.48 and 0.99 on the real scale.
-For the age, district and age-district random effects, we assigned exponential priors on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$ on each of these processes.
-For the temporal, age-time and space-time random effects, the hyperpriors on the standard deviations $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}}$ were decided as part of the model calibration process (see Section \ref{sec::modelcheck} for further details).
+For the age, district, age-district, temporal, age-time and district-time random effects, we assigned exponential priors on standard deviations, $\sigma_{(\cdot)} = \sqrt{\tau^{-1}_{(\cdot)}} \sim \text{Exp}(1)$ on each of these processes.
 
@@
 \noindent Survey data are collected through a complex two-stage cluster sampling design with unequal sampling probabilities.
-Performing model inference using a standard likelihood may lead to biased estimates so to account for these survey designs, the probabilities of circumcision were estimated using a weighted pseudo-likelihood in which we replaced the observed counts $\text{N}^l_{iat}$ with weighted counts $\tilde{\text{N}}^l_{iat}$, calculated using survey weights.
+Performing model inference using a standard likelihood may lead to biased estimates so to account for these survey designs, the probabilities of circumcision were estimated using a weighted pseudo-likelihood in which we sd the observed counts $\text{N}^l_{iat}$ with weighted counts $\tilde{\text{N}}^l_{iat}$, calculated using survey weights.
 Each individual $j$ in survey $s$ residing in region $i$ had sampling weight $\omega_{sji}$ which were normalised using the Kish effective sample size,
@@
 In this case, we matched survey data to the least granular areal unit declared by the survey.
-In some instances, these areal units represented PSNU unit, however in many cases, these are on higher administrative boundaries (e.g.
-national/admin-0).
-\todo{Not entirely convinced that }
-
-In order to include survey data on district as well as other administrative aggregates levels into the model, we estimate a population-weighted regional estimate of the probabilities of TMC, MMC and/or MC.
+In most instances, these areal units represented a higher administrative boundaries (e.g.
+national/admin-0) than the PSNU unit.
+To include survey data on district as well as other administrative aggregates levels into the model, we estimate a population-weighted regional estimate of the probabilities of TMC, MMC and/or MC.
 We define the probability that an individual in region $ R \subset I = \{1, 2, \ldots, N_I\}$ received a circumcision of type $k$ at age $a$ and time step $t$ as
@@
 where $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, and $P_{iat}$ is an estimate of the male population at age $a$ and time step $t$ in district $i$.
-The regional probabilities of TMC, MMC and MC
+The district probabilities of TMC, MMC and MC were sd with the higher level aggregates in the likelihood above for surveys that did not collect information on the district level.
 
-for surveys not at the
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-with regional equivalents in the likelihood above in order to include higher level aggregates.
+% \subsection{Assessing model fit}
+% \label{sec::modelcheck}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Final model selection}
-\label{sec::modelcheck}
+% {\color{red} To assess model fit and check the model specifications are correct for each country, we performed posterior predictive checking for the full models in each country.
+Furthermore, for countries that stratify  whether using a time-varying probability of TMC and whether to use a paediatric cut-off in the probability of MMC for VMMC priority countries and no paediatric cut-off in the probability of MMC for non-priority countries.
+We only used within-sample model fit here as we were most interested here in which model specification would produce the best model fit in each country, rather than in any relative short-term forecasting ability.
+In each country, we ran a total of 4 model combinations: on all available survey data.
+}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The choice of the final model to use in each country was decided in a two stage process.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Model specification}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the first stage of selecting the final model, we performed posterior predictive checking to assess the within-sample model fit to decide whether to use the time-invariant or time-variant probability of TMC and whether to use a paediatric cut-off or not in the probability of MMC.
-
-In each country,
-
-For each of the 12 model combinations, we sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
+% For each of the model combinations, we sampled each respondents circumcision status 1000 times based on predicted TMC, MMC and MC circumcision coverage in each space-age-time strata.
 We compared the mean predictions against the empirical survey estimates, aggregated to calculate predictive distributions by five year age groups (from 0-4 through 55-59) to avoid to many zeroes.
@@
 We also evaluated the coverage the posterior predictive distributions by calculating the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles of the posterior predictive distribution.
-The best performing models
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Model calibration}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+These were used to decide the best performing models (i.e.
+lowest CRPS/MAE/RMSE) in each country for the final model prediction.
 
@@
 TMB is a software package that performs approximate Bayesian inference by uses automatic differentiation and Laplace approximations to estimate posterior distributions for model parameters.
-Models were optimised using the {\color{red}quasi-newton L-BFGS-B} optimisation method \cite{byrd1995limited}.
+Models were optimised using the quasi-newton L-BFGS-B optimisation method \cite{byrd1995limited}.
 
-Using the final models from each country, we estimated full posterior distributions of the annual probabilities of becoming circumcised and the corresponding circumcision coverage {\color{red}between 2008 and 2021}, by circumcision type, single-year age group, and the PSNU level.
+Using the final models from each country, we estimated full posterior distributions of the annual probabilities of becoming circumcised and the corresponding circumcision coverage between 2000 and 2023, by circumcision type, single-year age group, and the PSNU level.
 Posterior predictive distributions for aggregates were obtained using Monte Carlo sampling with samples drawn from the joint posterior distributions, conditional on the optimised hyper-parameters \cite{eaton2021naomi}.
@@
 				\begin{itemize}
-					\item Annual, {\color{red}\bf 2008-2021}
+					\item Annual, {\color{red}\bf 2000-2023}
 				\end{itemize}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\section{Model Calibration}
-\label{sec::PPC1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{landscape}
-
-\include{paper/figures/supp_figs/PPC_P1_Tables.tex}
-
-\end{landscape}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\section{Model Selection}
-\label{sec::PPC2}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \emph{Put a general discussion element for the model giving an overview}
-
-% "threemc"("Multi-level model for male circumcision") is a Bayesian, spatio-temporal, competing-risks, time-to-event model (reference). 
-% We have extended this model from its initial application in South Africa to 33 countries within the SSA region. 
-% The model produces estimates of circumcision rates, incidence and coverage (i.e. cumulative indidence), with associated uncertainty bounds, stratified by type, year, age and location.
-% Circumcision rates are projected after their most recent household survey assuming continuation of estimated age-specific rates, with probabilistic uncertainty. 
-% Estimates for single ages were binned into 5-year age groups from 0-4 to 54-59, and other age groups of interest, such as the VMMC target age group of 10-29 year-olds.
-
-% \emph{Traditional Circumcision}
-
-% A key assumption of the original threemc model was that TMC was constant over time, due to the perceived intransigence in TMC practices and traditional male initiation ceremonies amongst tribal, cultural and religious groups which have developed over time.
-% MMCs amongst paediatric males, defined as those under 10, were also assumed to be constant over time, as VMMC programmes, the main force behind the adoption of MMC in much of SSA, do not targets males below 10 (reference).
-
-% [Technical details]
-
-% Explain the TMC with time and TMC with no time.
-
-% \emph{Medical Circumcision}
-
-% Explain paed cut off and no paed cut off
-
-% \subsection{Model Specification}
-% \label{sec:org40f2f33}
-
-% In our choice of model specification, we were interested in two main assumptions/features of the
-% model:
-% \begin{itemize}
-% \item How we should treat TMC, in terms of whether to continue to assume a constant rate of TMC over time, or to reject that assumption,
-% \item How to model paediatric MMC, which should be minimal in at least the VMMC target countries.
-% \end{itemize}
-
-% If possible, we hoped to use the same model for every country, or failing that, come up with a
-% satisfactory choice of model specification which would make sense both qualitatively and
-% quantitatively.
-
-% Qualitatively, we have made some presumptions about certain countries and their circumcision patterns.
-% In non-VMMC SSA countries, concentrated in Western and Central Africa (WCA), TMC has historically made up the bulk of MCs.
-% Therefore, most MMCs in non-VMMC countries are likely to have superseded TMCs performed as part of traditional male initiation ceremonies.
-This suggests that MMCs in these countries are likely to be on paediatric individuals in traditional settings, so the assumption of constant and
-% negligible paedaitric MMC could be a poor one. 
-% Because any increases in MMC will come at the expense of TMC in our "competing-risks" model, it is also plausible that the assumption that TMC rates in these countries have been relatively constant may be unrealistic.
-% It is therefore likely that the inclusion of a time effect for TMC and not partitioning MMC into adult and time-invariant paediatric rates will be a more realistic reflection of circumcision
-% patterns in non-VMMC countries.
-
-% Conversely, in VMMC priority countries changes in circumcision patterns have largely been driven by the intervention of VMMC programme implementation. 
-% As such, it is more realistic to assume that paediatric MMCs are minimal, in line with UNAIDS VMMC policy.
-% It is more difficult to say whether the rate of TMC will be constant over time in non-VMMC countries.
-% Historical TMC patterns in these countries, differ significantly, even subnationally.
-% It may therefore be more realistic to also allow TMC to vary over time in VMMC countries.
-% In countries where the rate of TMC is stable over time, the model will capture this behaviour, while in countries where TMC varies over time, the inclusion of a time effect for TMC will provide the model with the additional required flexibility to identify this trend.
-% We would also prefer to not have to treat every VMMC priority country separately with regards to their model specification, so including a time effect for TMC in the models for these countries seems like a logical choice.
-
-% We have also performed a quantitative analysis of the different model specifications available
-% to us. A more detailed treatment of this can be found in section x of the appendix.
-
-% For each country, we fit a model for each possible model specification for threemc, that is:
-% \begin{itemize}
-% \item for each choice of temporal prior, namely AR1, RW1 and RW2,
-% \item a choice of whether or not to include a paediatric age cutoff for MMC of ten, and
-% \item a choice of whether to include a temporal effect for TMC.
-% \end{itemize}
-% Thus totalling 12 possible models for each country.
-% These models were fit to all of the survey data available, rather than a subset of the data.
-% This was because we were most interested here in seeing how the inclusion of a peadiatric age cutoff and/or a temporal TMC effect would effect the fit of the model to the data available, rather than in the relative short-term forecasting ability of the different specifications.
-% As the choice of temporal prior was more important when forecasting, we were not especially interested in how each of these performed here, but regardless we fit for each temporal prior, for completeness.
-
-% The survey weighted empirical survey circumcision coverage was compared to a sample of 1000 draws from the posterior predictions of circumcision coverage for each country.
-% Both were aggregated to area level 1 and to five year age groups (from 15-19 through 55-59), to avoid having too many zeros in the survey estimates.
-
-% Comparisons were made of mean predictions, using expected log-posterior density (ELPD) and continuous ranked probability scores (CRPS), as well as error statistics such as the mean error (ME), root mean error (RME) and root mean error squared (RMSE).
-% Also evaluated was the the "calibration" of our model with regards to it's posterior predictive uncertainty.
-% This involved comparing survey estimates of circumcision coverage with the 50\%, 80\% and 95\% credible intervals (CIs) of our posterior predictive distribution.
-A "good" calibration was regarded as one in which roughly 50\% of survey observations fell within the 50\% CI range, 85\% within the 85\% CI range, and 95\% within the 95\% range.
-% Seeing as we were comparing within-sample mean estimates, we were particularly interested in the RMSE of our predictions compared to the survey estimates.
-
-% Just as we distinguished between VMMC and non-VMMC countries when considering the qualitative merits of each model specification, so too did a pattern emerge here when quantitively comparing the model fits for both sets of SSA countries.
-
-% For the non-VMMC countries there was a drastic difference in mean predictive accuracy between the different model specifications.
-% The best model specification was the model which included a temporal TMC effect, but not a paediatric age cutoff for MMC.
-% This specification performed the best for x / y countries, averaging a RMSE of x, CRPS of x and ELPD of x, in comparison to the next best specification, ?, which averaged an RMSE of x, CRPS of x and ELPD of x.
-% It appeared that the inclusion of a temporal TMC effect was very influential in improving the fit of the model for non-VMMC countries, with specifications including this term averaging a RMSE of x versus x for those which did not include this term.
-% Models including an MMC paediatric age cutoff of 10 consistently performed worse than other models, averaging an RMSE of x versus x. 
-% These findings were in line with our previous intuitions on MC patterns in non-VMMC, mainly WCA countries, where TMC was historically high, and increases in MMC are likely within the previously TMC population, and hence MMCs were likely performed on younger individuals than in VMMC countries.
-
-% In contrast, for the VMMC priority countries, the choice of whether to include an MMC paedaitric age cutoff had little effect on model fit.
-% This may be because under fifteens were not surveyed, and so there were no survey estimates for paediatric populations to compare to our model predictions.
-% However, the inclusion of this MMC paediatic age cutoff did have a negative effect to the fit for the models to adults for non-VMMC countries, so the fact that it's inclusion here did not hurt model fit suggests it was a more accurate representation of MMC patterns in VMMC priority countries.
-% As we were aware of VMMC programme policy in not currently circumcising under fifteens, and since it did not seem to negatively effect model fit to adults, we decided to include a paediatric age cutoff of 10 in the model for VMMC coutries.
-
-% Models which including a temporal TMC effect were marginally better, with an average RMSE of x versus x for all other models.
-% In particular, Kenya, which had high historical TMC in most regions and was the most similar of the VMMC countries to WCA countries in terms of it's circumcision patterns, saw a marked improvement when this effect was included, with an average RMSE of x versus x.
-For completeness, we decided to include a temporal effect for TMC in the model specification for VMMC priority countries.
-
-% It was therefore ultimately decided to include a temporal effect for TMC in the model for both VMMC and non-VMMC countries, while only including a pedaitric age cutoff for VMMC countries.
-% A table with the full set of fit statistics for each model specification for each country can be found in section x of the appendix.
-
-% \subsection{Model Calibration and Choice of Temporal Prior}
-% \label{sec:orgbbc65cb}
-
-% For some VMMC priority countries, we did not have access to more recent survey data. 
-% One particular country where this is the case is Tanzania, whose most recent survey was the 2016 PHIA survey.
-% In these circumstances, there may have been a significant increase in MMC coverage due to VMMC programme implementation which was not captured within our survey period.
-% VMMC programme data was an available source of more recent circumcision data.
-% The DMPPT2 model explicitly used this data to estimate MMC. 
-% The results of DMPPT2, as well as those for countries with more recent surveys who have experienced significant MMC scaleups, suggest that VMMC may have scaled up at a rate not anticipated by threemc where only these older surveys are available.
-% This was consistent with out-of-sample (OOS) exploration of model fits to countries like Zimbabwe, where removing access to the most recent (2018 DHS) survey similarly underestimates VMMC scale up.
-% Hence, it was felt that threemc likely underestimates uncertainty with regards to predicting circumcision coverage for progressively later years from our last available surveys, particularly in the case of VMMC priority countries, which have seen rapid increases in historically low circumcision.
-% A more dramatic "fanning" out of our prediction interval as we forecast further from the last available survey data was therefore deemed desirable, consistent with having greater uncertainty in our future forecasts.
-
-% The two main drivers of uncertainty over time in threemc were:
-% \begin{itemize}
-% \item The variance hyperparameters relating to time, including the variance hyperparameters for space-time and age-time interactions, and
-% \item The choice of temporal prior, for which threemc supports the use of an AR1, RW1 or RW2 prior.
-% \end{itemize}
-% The "unpooled" optimised time-related variance hyperparameters for the model fit for each respective country varied significantly, but in general certain patterns and values for these hyperparameters could be associated with a having larger bounds for successive prediction years.
-
-% Due to computational constraints, we could not model the entire SSA region together as one singular area hierarchy, which, through partial pooling and the neighbourhood correlation structure inherent in the model, would allow the model to borrow information from countries with a large amount of available data to inform predictions in countries with older and/or fewer surveys.
-% One alternative to using a partially-pooled model was to use the uncertainty estimates which produce the best predictions for countries with more recent data to inform our uncertainty estimates in countries with less recent survey data available.
-% To quantitatively explore this hypothesis, we performed an OOS evaluation of the model fit to each country, removing their most recent survey data (or, in the case where there were two surveys in subsequent years, the two most recent surveys) and comparing posterior predictions to the survey-estimated circumcision coverage, as we did with our analysis of different model specifications.
-% A grid search over sensible variance hyperparameter values from the "naive" threemc fits for each country and temporal prior was employed, to determine the optimal values and temporal prior choice. 
-% For the AR 1 model, the effect of different time correlation parameters on our uncertainty bounds was determined to be minimal, and in the interests of parsimony, these parameters were ignored in our calibration efforts with this model.
-
-% TODO: Finish this write up!
-% TODO: Add results! Also add ternary plot
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{Fix links to HSRC surveys, no longer working!}
-\todo{Get reference for MICS surveys!}
-\todo{May have to reference every survey, as in Cork paper!}
-
-\printbibliography
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{appendix}

### 2024-04-16 paper/2_paper/figures/supp_figs/PPC_P1_Tables.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\ 
  \cmidrule(lr){4-5} 
  \cmidrule(lr){6-7} 
  \cmidrule(lr){8-9} 
  \cmidrule(lr){10-11} 
  \cmidrule(lr){12-13} 
  \cmidrule(lr){14-15} 
  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
  \hline 
    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
 & \bf MC & \bf NC &  2.57 &  2.59 &  0.03 &  0.03 &  0.04 &  0.04 & 70.14 & 68.75 & 84.72 & 86.11 & 95.14 & 93.75\\ 
  &  & \bf PC &  2.60 & \bf 2.50 &  0.03 & \bf 0.03 & \bf 0.04 &  0.04 & 70.14 & \bf72.92 & \bf87.50 & 86.11 & \bf95.83 & 95.14\\[3pt] 
  & \bf MMC & \bf NC & \bf 8.80 & 10.87 & \bf 0.12 &  0.14 & \bf 0.15 &  0.16 & \bf52.08 & 50.00 & \bf79.17 & 72.92 & \bf93.75 & 86.11\\ 
  &  & \bf PC & 11.63 & 11.13 &  0.14 &  0.14 &  0.17 &  0.16 & 45.14 & 49.31 & 68.75 & 68.06 & 84.03 & 85.42\\[3pt] 
  & \bf TMC & \bf NC & \bf 9.16 & 11.45 & \bf 0.13 &  0.14 & \bf 0.15 &  0.17 & 45.14 & \bf45.83 & \bf76.39 & 67.36 & \bf92.36 & 84.03\\ 
  &  & \bf PC & 12.43 & 11.65 &  0.15 &  0.14 &  0.17 &  0.17 & 36.81 & 43.75 & 65.28 & 67.36 & 81.25 & 82.64\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
 & \bf MC & \bf NC &  2.57 &  2.58 &  0.03 &  0.03 &  0.04 &  0.04 & 69.44 & 69.44 & 85.42 & \bf86.81 & \bf96.53 & 95.14\\ 
  &  & \bf PC &  2.57 & \bf 2.52 & \bf 0.03 &  0.03 & \bf 0.04 &  0.04 & 70.83 & \bf71.53 & 85.42 & \bf86.81 & 94.44 & 95.14\\[3pt] 
  & \bf MMC & \bf NC & \bf 8.43 & 10.84 & \bf 0.12 &  0.14 & \bf 0.15 &  0.16 & \bf50.69 & \bf50.69 & \bf83.33 & 70.83 & \bf95.14 & 86.11\\ 
  &  & \bf PC &  9.66 & 11.14 &  0.13 &  0.14 &  0.15 &  0.16 & 50.00 & 46.53 & 75.69 & 68.75 & 89.58 & 84.03\\[3pt] 
  & \bf TMC & \bf NC & \bf 8.77 & 11.40 & \bf 0.12 &  0.14 & \bf 0.15 &  0.17 & \bf47.92 & \bf47.92 & \bf81.94 & 68.06 & \bf94.44 & 84.72\\ 
  &  & \bf PC & 10.16 & 11.69 &  0.13 &  0.14 &  0.16 &  0.17 & 44.44 & 42.36 & 75.00 & 65.28 & 86.81 & 81.94\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
 & \bf MC & \bf NC &  2.58 &  2.61 &  0.03 &  0.03 &  0.04 &  0.04 & 68.06 & 69.44 & \bf86.11 & \bf86.11 & \bf95.83 & 94.44\\ 
  &  & \bf PC &  2.55 & \bf 2.54 & \bf 0.03 &  0.03 & \bf 0.04 &  0.04 & 70.14 & \bf72.22 & 84.03 & \bf86.11 & \bf95.83 & 95.14\\[3pt] 
  & \bf MMC & \bf NC & \bf 8.44 & 11.03 & \bf 0.12 &  0.14 & \bf 0.15 &  0.17 & \bf50.69 & 49.31 & \bf81.94 & 70.14 & \bf94.44 & 86.81\\ 
  &  & \bf PC &  9.55 & 11.16 &  0.13 &  0.14 &  0.15 &  0.16 & \bf50.69 & 47.92 & 77.08 & 68.75 & 90.28 & 84.72\\[3pt] 
  & \bf TMC & \bf NC & \bf 8.74 & 11.64 & \bf 0.12 &  0.14 & \bf 0.15 &  0.17 & \bf49.31 & 46.53 & \bf79.17 & 69.44 & \bf93.75 & 82.64\\ 
  &  & \bf PC &  9.99 & 11.66 &  0.13 &  0.14 &  0.15 &  0.17 & 45.14 & 44.44 & 75.69 & 67.36 & 88.89 & 82.64\\[3pt] 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in Angola. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), root mean square error (RMSE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1AGO} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\ 
  \cmidrule(lr){4-5} 
  \cmidrule(lr){6-7} 
  \cmidrule(lr){8-9} 
  \cmidrule(lr){10-11} 
  \cmidrule(lr){12-13} 
  \cmidrule(lr){14-15} 
  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
  \hline 
    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
 & \bf MC & \bf NC & 103.32 & 107.35 &   0.11 &   0.12 &   0.14 &   0.14 & \bf 49.35 &  48.67 &  73.93 & \bf 74.98 &  87.83 & \bf 88.63\\ 
  &  & \bf PC & \bf102.95 & 108.18 & \bf  0.11 &   0.12 & \bf  0.14 &   0.14 &  49.23 &  48.12 &  73.93 &  74.12 &  88.14 &  88.33\\[3pt] 
  & \bf MMC & \bf NC &  19.22 &  21.41 & \bf  0.02 &   0.03 & \bf  0.04 &   0.04 &  82.58 & \bf 82.71 &  90.92 &  90.74 & \bf 96.73 &  96.42\\ 
  &  & \bf PC & \bf 19.17 &  21.38 &   0.02 &   0.03 &   0.04 &   0.04 &  82.52 & \bf 82.71 & \bf 90.98 &  90.61 &  96.66 &  96.48\\[3pt] 
  & \bf TMC & \bf NC &  93.68 &  93.94 &   0.10 &   0.10 &   0.13 &   0.13 & \bf 52.25 &  51.76 &  75.66 &  75.79 &  89.75 & \bf 90.24\\ 
  &  & \bf PC & \bf 93.12 &  94.77 & \bf  0.10 &   0.11 & \bf  0.13 &   0.13 &  52.07 &  51.51 &  75.73 & \bf 76.03 &  89.87 & \bf 90.24\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
 & \bf MC & \bf NC & 103.16 & 107.12 &   0.11 &   0.11 &   0.14 &   0.14 & \bf 49.35 &  48.86 &  74.00 &  74.31 &  88.26 &  88.39\\ 
  &  & \bf PC & \bf102.58 & 108.10 & \bf  0.11 &   0.12 & \bf  0.14 &   0.14 &  49.10 &  48.49 & \bf 74.74 &  74.24 & \bf 88.45 &  88.20\\[3pt] 
  & \bf MMC & \bf NC &  19.19 &  21.42 & \bf  0.02 &   0.03 & \bf  0.04 &   0.04 &  82.64 &  82.46 & \bf 91.17 &  90.61 &  96.48 &  96.05\\ 
  &  & \bf PC & \bf 19.17 &  21.30 &   0.02 &   0.03 &   0.04 &   0.04 &  82.64 & \bf 82.71 & \bf 91.17 &  90.55 & \bf 96.54 &  96.36\\[3pt] 
  & \bf TMC & \bf NC &  93.67 &  93.67 &   0.10 &   0.10 &   0.13 &   0.13 &  52.50 &  52.38 &  75.73 & \bf 76.53 &  89.50 & \bf 90.55\\ 
  &  & \bf PC & \bf 92.88 &  94.65 & \bf  0.10 &   0.11 & \bf  0.13 &   0.13 & \bf 52.63 &  51.95 &  76.03 &  76.22 &  90.12 &  90.43\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
 & \bf MC & \bf NC & 102.75 & 108.16 & \bf  0.11 &   0.12 & \bf  0.14 &   0.14 &  49.60 &  48.73 &  73.50 &  73.19 &  87.96 &  87.83\\ 
  &  & \bf PC & \bf102.52 & 109.14 &   0.11 &   0.12 &   0.14 &   0.14 & \bf 49.97 &  47.93 & \bf 73.69 &  73.13 & \bf 88.14 &  87.71\\[3pt] 
  & \bf MMC & \bf NC &  19.14 &  21.29 & \bf  0.02 &   0.03 & \bf  0.04 &   0.04 &  82.71 &  82.33 &  90.74 &  90.61 &  96.48 & \bf 96.85\\ 
  &  & \bf PC & \bf 19.07 &  21.22 &   0.02 &   0.03 &   0.04 &   0.04 &  82.58 & \bf 82.89 & \bf 91.17 &  90.61 &  96.54 &  96.48\\[3pt] 
  & \bf TMC & \bf NC &  93.46 &  94.72 &   0.10 &   0.10 & \bf  0.13 &   0.13 & \bf 52.69 &  52.01 &  75.11 & \bf 75.73 & \bf 89.56 & \bf 89.56\\ 
  &  & \bf PC & \bf 93.03 &  95.62 & \bf  0.10 &   0.11 &   0.13 &   0.13 &  52.32 &  51.95 &  75.23 &  75.48 &  89.38 &  89.38\\[3pt] 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in Rwanda. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), root mean square error (RMSE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1RWA} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\linespread{1} 
  \begin{table}[H] 
  \centering 
  \footnotesize 
  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
  \hline  
  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\ 
  \cmidrule(lr){4-5} 
  \cmidrule(lr){6-7} 
  \cmidrule(lr){8-9} 
  \cmidrule(lr){10-11} 
  \cmidrule(lr){12-13} 
  \cmidrule(lr){14-15} 
  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 
  \hline 
    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
 & \bf MC & \bf NC & 269.89 & 269.82 &   0.20 &   0.20 &   0.26 &   0.26 &  60.49 &  60.34 & \bf 84.32 & \bf 84.32 &  95.22 &  95.41\\ 
  &  & \bf PC & 269.87 & \bf269.35 & \bf  0.20 &   0.20 &   0.26 & \bf  0.26 & \bf 61.46 &  60.75 &  84.02 &  83.91 &  95.33 & \bf 95.44\\[3pt] 
  & \bf MMC & \bf NC & \bf207.28 & 208.34 & \bf  0.15 &   0.15 & \bf  0.21 &   0.21 &  68.37 & \bf 68.75 & \bf 86.82 &  86.52 & \bf 96.12 &  95.86\\ 
  &  & \bf PC & 208.05 & 208.27 &   0.15 &   0.15 &   0.21 &   0.21 &  68.67 &  68.63 & \bf 86.82 &  86.56 &  96.08 &  95.86\\[3pt] 
  & \bf TMC & \bf NC & \bf192.53 & 193.70 &   0.15 &   0.15 &   0.21 &   0.21 &  66.73 & \bf 66.77 &  87.42 & \bf 87.68 &  96.38 &  96.15\\ 
  &  & \bf PC & 195.03 & 195.04 & \bf  0.15 &   0.15 & \bf  0.21 &   0.21 &  65.57 & \bf 66.77 &  86.37 &  86.82 &  95.93 & \bf 96.45\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
 & \bf MC & \bf NC & 268.77 & \bf268.14 &   0.20 &   0.20 &   0.26 &   0.26 &  60.60 &  60.38 &  84.84 & \bf 84.91 &  95.29 & \bf 95.86\\ 
  &  & \bf PC & 268.70 & 268.53 & \bf  0.20 &   0.20 & \bf  0.26 &   0.26 & \bf 61.20 &  60.72 &  84.06 &  84.54 &  95.37 &  95.71\\[3pt] 
  & \bf MMC & \bf NC & \bf206.15 & 207.60 & \bf  0.15 &   0.15 & \bf  0.21 &   0.21 &  68.89 &  68.60 & \bf 86.97 &  86.63 &  96.19 &  96.23\\ 
  &  & \bf PC & 206.97 & 207.50 &   0.15 &   0.15 &   0.21 &   0.21 &  68.26 & \bf 68.97 &  86.86 &  86.74 & \bf 96.27 &  96.04\\[3pt] 
  & \bf TMC & \bf NC & \bf187.90 & 189.39 & \bf  0.15 &   0.15 &   0.21 &   0.21 & \bf 68.19 &  67.74 &  88.65 & \bf 88.69 & \bf 97.12 &  97.01\\ 
  &  & \bf PC & 190.79 & 192.05 &   0.15 &   0.15 & \bf  0.21 &   0.21 &  67.18 &  67.36 &  87.79 &  88.01 &  96.90 &  96.83\\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
 & \bf MC & \bf NC & 269.67 & 269.03 &   0.20 &   0.20 &   0.26 &   0.26 &  60.60 &  60.53 &  84.24 & \bf 84.76 &  95.22 & \bf 95.71\\ 
  &  & \bf PC & 269.22 & \bf268.89 & \bf  0.20 &   0.20 & \bf  0.26 &   0.26 & \bf 61.09 &  60.60 &  83.94 &  84.35 &  95.44 &  95.63\\[3pt] 
  & \bf MMC & \bf NC & \bf206.24 & 207.68 & \bf  0.15 &   0.15 & \bf  0.21 &   0.21 &  68.71 & \bf 68.93 & \bf 86.97 &  86.56 &  96.23 & \bf 96.27\\ 
  &  & \bf PC & 207.47 & 208.20 &   0.15 &   0.15 &   0.21 &   0.21 &  68.19 &  68.45 &  86.78 &  86.67 &  96.19 &  96.23\\[3pt] 
  & \bf TMC & \bf NC & \bf188.42 & 190.27 & \bf  0.15 &   0.15 & \bf  0.21 &   0.21 &  67.70 & \bf 68.00 & \bf 88.27 &  88.13 & \bf 96.90 &  96.68\\ 
  &  & \bf PC & 191.18 & 192.74 &   0.15 &   0.15 &   0.21 &   0.21 &  66.69 &  66.95 &  87.49 &  87.90 &  96.79 &  96.60\\[3pt] 
  \hline 
  \end{tabular} 
  \caption{Results of the posterior predictive checking in total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC) from fitting the 12 candidate models in South Africa. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) temporal prior. For all combinations, the within-sample continuous ranked probability scores (CRPS), mean absolute error (MAE), root mean square error (RMSE), and the proportion of empirical observations that fell within the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1ZAF} 
\end{table}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-04-16 paper/2_paper/paper.tex
Updates from Overleaf

--- 2024-04-05 paper/paper.tex
@@
   \noindent \textbf{Methods} \\
-  \noindent We analysed self-reported data on male circumcision from x nationally representative household surveys conducted in x SSA countries between 2006-2020.
+  \noindent We analysed self-reported data on male circumcision from 
+  123
+  nationally representative household surveys conducted in 34 SSA countries between 2006 and 2020.
   A spatio-temporal Bayesian competing-risks time-to-event model was used to estimate rates of traditional and medical circumcision by age, location, and time.
@@
   \noindent \textbf{Results} \\
-  \noindent Across x countries, from 2010 to 2020 an estimated x million men (x\% CI x-x million)
-  were newly circumcised, of whom x million (x - x million) were medically circumcised, and
-  x million (x - x million) traditionally circumcised. In 2020, MC coverage among men 10-29
-  years ranged from x\% (x\% - x\%) in Zimbabwe (?) to x\% (x\%-x\%) in Togo. MMC coverage
-  ranged from x\% (x\%-x\%) in Malawi to x\% (x\%-x\%) in Tanzania, and TMC coverage
-  from x\% (x\%-x\%) in Eswatini to x\% (x\%-x\%) in Ethiopia. The largest increase in MMC
-  coverage was in Lesotho from x\% to x\%. Within countries, the median difference in MC
-  coverage between the districts with lowest and highest coverage was x\%, with the smallest
-  variation in Eswatini (x\% to x\%) and largest in Zambia (x\% to x\%). x million men aged
-  10-29 need to be circumcised to reach 90\% coverage in all countries.
+  \noindent Across 34 countries, from 2006 to 2020 an estimated 121.943 million men (95\% CI 107.021 - 141.729 million) were newly circumcised, of whom 60.732 million men (45.779 - 85.927 million) were medically circumcised, and 33.519 million men (27.143 - 37.422 million) traditionally circumcised.
+In 2020, MC coverage among men 10-29 years ranged from 34.31\% (32.39\% - 36.98\%) in Zimbabwe to 100\% (100\% - 100\%) in Niger.
+  MMC coverage ranged from 20.55\% (17.62\% - 24.99\%) in Benin to 79.63\% (77.9\% - 81.38\%) in Sierra Leone, and TMC coverage from 0.63\% (0.5\% - 0.78\%) in Eswatini to 75.46\% (71.71\% - 78.64\%) in Benin.
+  The largest increase in MMC coverage was in Lesotho Lesotho from 11.53\% to 66.9\%. 
+  Within countries, the median difference in MC coverage between the districts with lowest and highest coverage was 31.78\% with the smallest variation in Niger (99.99\% to 100\%) and largest in Zambia (9.2\% to 99.94\%).
+  In VMMC priority countries, 25.474 million men aged 10-29 need to be circumcised to reach 90\% coverage in VMMC priority countries, while 22.282 million circumcisions amongst 15-49 year olds are needed to reach 80\% coverage.
 
@@
 However, this study focused only on South Africa and the model was developed with many local dynamics in the provision to synthesise both data sources.
-\todo{Jeff - Feel like I need to expand this but not sure how much detaul to give here.}Here, we take a similar approach to Thomas et al.
+\todo{Jeff-Feel like I need to expand this but not sure how much detaul to give here.}Here, we take a similar approach to Thomas et al.
 and develop a discrete-time competing risks time-to-event model only using survey data in order to estimate the probabilities and coverage of medical and traditional male circumcision by sub-national area, single-year age, and time along with probabilistic uncertainty.
@@
 
-The study consisted of 33 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
+The study consisted of 34 sub-Saharan countries, that have conducted surveys that contained information on self-reported circumcision status since 2002: Senegal, Gambia, Guinea, Sierra Leone, Liberia, Mali, Burkina Faso, Côte d’Ivoire, Ghana, Togo, Benin, Niger, Nigeria, Cameroon, Chad, Ethiopia, Gabon, The Republic of the Congo (the Congo), The Democratic Republic of the Congo (DR Congo), Uganda, Kenya, Rwanda, Burundi, Tanzania, Angola, Zambia, Malawi, Mozambique, Zimbabwe, Namibia, Eswatini, Lesotho, South Africa.
 We excluded Equitorial Guinea, Guinea-Bissau and the Central African Republic because they either had no surveys conducted, or, where surveys were available, there was insufficient information available on age at circumcision.
@@
 
-Following a similar approach to Thomas {\it et al.} \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision stratified by region, age, time, and type.
+% Following a similar approach to Thomas {\it et al.} \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision stratified by region, age, time, and type.
 We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).
 
-In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
+% In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC).
 
-For the probability of TMC, a key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere.
+% For the probability of TMC, a key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere.
 For example, in some countries the level and practices of TMC have changed through time due to demographic shifts.
@@
 
-The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention.
+% The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention.
 VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention.
@@
 
-We modelled probability of MMC with {\it no paediatric cut-off} was modelled using logit-linear function with random effects for age, time, and district, and interactions for district-time, age-time, and age-district, to allow for inter-district/time/age variation in circumcision rates.
+% We modelled probability of MMC with {\it no paediatric cut-off} was modelled using logit-linear function with random effects for age, time, and district, and interactions for district-time, age-time, and age-district, to allow for inter-district/time/age variation in circumcision rates.
 For the probability of MMC with {\it a paediatric cut-off}, the probability of paediatric MMC-nT was modelled using a logit-linear function with random effects for age, district, an age-district interaction, to allow for different practices of paediatric circumcision observed across districts.
@@
 
-Whether a country used (i) a time-invariant or time-variant probability of TMC and (i) a paediatric cut-off or no cut-off in the probability of MMC, was decided based on which produced the best within-sample model fit (see Section XX for further details).
+% Whether a country used (i) a time-invariant or time-variant probability of TMC and (i) a paediatric cut-off or no cut-off in the probability of MMC, was decided based on which produced the best within-sample model fit (see Section XX for further details).
 
-Some countries did not have any surveys that collected information on the type of circumcision (see Supplementary Material for more detail), so we were unable to conduct an analysis of the probabilities of circumcision by type.
+% Some countries did not have any surveys that collected information on the type of circumcision (see Supplementary Material for more detail), so we were unable to conduct an analysis of the probabilities of circumcision by type.
 For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.
@@
 
-We calculated the estimated circumcision coverage by type (MMC/TMC/MC) within each cohort using the cumulative incidence function, which defines the marginal probability (or proportion/coverage of) individuals who were received an MMC, TMC, or MC by district, age and time, whilst accounting for the competing risk of other circumcision type.
+% We calculated the estimated circumcision coverage by type (MMC/TMC/MC) within each cohort using the cumulative incidence function, which defines the marginal probability (or proportion/coverage of) individuals who were received an MMC, TMC, or MC by district, age and time, whilst accounting for the competing risk of other circumcision type.
 
-Prior distributions were specified on all model parameters and were specified to allow areas, with little to no data, to borrow district-age-time information on circumcision.
+% Prior distributions were specified on all model parameters and were specified to allow areas, with little to no data, to borrow district-age-time information on circumcision.
 Furthermore, we wanted to ensure any correlation in circumcision practices across district, age and time was modelled.
@@
 
-Technical details of the model are in Supplementary Materials.
+% Technical details of the model are in Supplementary Materials.
 
@@
 
-\subsection{Model Specification}
+\subsection{Model specification}
 \label{sec:orgaf7fa2a}
@@
 
-\subsection{Model Calibration and Choice of Temporal Prior}
+\subsection{Model calibration and choice of temporal prior}
 \label{sec:orga44afa6}
@@
 
-Our data consisted of 109 nationally representative household surveys conducted in 33 SSA countries between 2002 and 2019.
-x sub-national areas amongst these coutries were included in these surveys and modelled.
-Of these 109 surveys, 104 contained sufficent information on circumcision, as outlined in the Methods section of this paper.
+\todo{Update these figures using survey calculations\!}
 
-These remaining surveys consisted of 711,715 individuals respondents from 108 birth cohorts from 1903 to 2016.
-The sample size per survey ranged from 21,114 in the South Africa 2017 HSRC survey to 1,459 in the Eswatini 2014 MICS survey.
+Our data consisted of 123 nationally representative household surveys conducted in 34 SSA countries between
+2002 and 2019. 5,290 subnational areas amongst these countries were included in these surveys and modelled.
+Of these 123 surveys, 120 contained sufficient information on circumcision, as outlined in the Methods section
+of this paper.
 
-There was significant censoring and missing data even in the remaining surveys. 
-Left censoring of circumcision status, analagous to unknown circumcision age, averaged  34.438\% across all surveys, and ranged from 0\% in the Rwanda 2008 DHS survey to 99.408\% in the Niger 2006 DHS survey.
-17 surveys had more than 90\% left censoring of circumcision age, with 42 surveys having less than 10\% left censoring.
-\todo{Rewrite now BWA has surveys!}
-No information on age at circumcision was present in the 2004 and 2008 Botswana Aids Impact Surveys.
-This complete left censoring of circumcised individuals meant that \verb|threemc| could not be fit to Botswana.
-Right censoring of circumcision status, indicating as of yet uncircumcised individuals, averaged 35.299\% across all surveys, ranging from 0.399\% in the The Gambia 2018 MICS survey to 91.432\% in the Eswatini 2006 DHS survey.
+These remaining surveys consisted of 835,463 individuals respondents from 108 birth cohorts from 1903 to
+2016. The sample size per survey ranged from 1,459 in the Eswatini 2014 MICS survey to 21,114 in the South
+Africa 2017 HSRC survey.
+There was significant censoring and missing data even in the remaining surveys. Left censoring of circumcision
+status, analagous to unknown circumcision age, averaged 1,821, or 31.02\% across all surveys, and ranged from
+0\% in the Botswana 2021 PHIA, Mozambique 2021 PHIA and Rwanda 2008 DHS surveys to 15,178/99.408\%
+in the Nigeria 2008 DHS survey. 17 surveys had more than 90\% left censoring of circumcision age, with
+53 surveys having less than 10\% left censoring. Right censoring of circumcision status, indicating as of yet
+uncircumcised individuals, averaged 2,561/35.776\% across all surveys, ranging from 18/0.399\% in the The
+Gambia 2018 MICS survey to 13,747/91.432\% in the South Africa 2017 HSRC survey.
 
-On average across all surveys, 1.788\% of respondents did not respond to either the circumcision location or provider question, and so had unknown circumcision type. 
-This was lowest in the Burundi 2010 DHS survey, at 0\%, and highest in the South Africa 2002 HSRC survey, at 29.545\%.
-5 countries had unknown circumcision type; DR Congo, Guinea, Liberia, Niger and Senegal. 
-Amongst these countries, left censoring averaged 98.457\%. 
-However, the mean survey circumcision coverage amongst these same countries was 98.457\%, which may explain the relative lack of circumcision information available in their surveys.
+On average across all surveys, 3,810/57.445\% respondents did not respond to either the circumcision location
+or provider question, and so had unknown circumcision type. This was lowest in absolute terms in the Mali
+2012 DHS survey, and as a percentage of the total sample size in the Gabon 2019 DHS survey. Unknown
+type was 100\% in 30 surveys, of which 19 are older than 2007, when VMMC programmes began. 5 countries
+had unknown circumcision type; DR Congo, Guinea, Liberia, Niger and Senegal. Amongst these countries,
+left censoring averaged 98.457\%. However, every left censored individual was also circumcised, which may
+explain the relative lack of circumcision information available in their surveys.
 
-\todo{Rewrite as BWA now has surveys}
-In addition to Botswana, Guinea-Bissau, Equatorial Guinea and the Central African Republic were additional SSA countries where we did not have any surveys containing circumcision information, and so we were unable to fit \verb|threemc| in these countries either.
+In Guinea-Bissau, Equatorial Guinea and the Central African Republic, did not have any surveys containing
+circumcision information, and so we were unable to fit threemc in these countries either.
 
-More information on individual surveys, including participation rates, can be found in section x of the appendix.
+More information on individual surveys, including participation rates, can be found in section x of the
+appendix.
 
-% Surveys Plot (may be moved to supp. figs)
-\begin{figure}[H]
-    \centering
-    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
-    \includegraphics[width=.9\linewidth]
-    {plots/01_survey_table.png}
-    \caption{\emph{Household surveys detailing circumcision patterns in SSA.
-The colour and size of points are determined by the provider and sample size of each respective survey.
-Triangular points have no information on circumcision type.
-Cent.
-Af.
-Rep.
-= Central African Republic}}
-\end{figure}
-
-\subsection{Subnational Variation in Total, Medical \& Traditional Circumcision over time}
+\subsection{Subnational variation in total, medical \& traditional circumcision over time}
 \label{sec:org0d1ffe6}
@@
     \includegraphics[width=1\linewidth]
-    % {plots/02_map_plot_facet.png}
-    {paper/plots/02_map_plot_facet.png}
+    {figures/paper/01_map_plot_facet.png}
     \caption{\emph{Estimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years.
 Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively.
-Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all.}}
+Countries with no information on circumcision type are grey in the Medical and Traditional figures/paper, while countries with no circumcision estimate are grey in all.}}
 \end{figure}
 
-% Between 2007, the year VMMC programme implementation began, and 2020, an estimated x million men(95\% CI: x - x million) were newly circumcised. 
-% Of these, x million (x - x million) were MMCS, along with x million (x - x million) TMCS. 
-% This translated to an increase in MC for the SSA region of x\% (x\% - x\%) in 2010 to x\% (x\% - x\%) in  2020. 
-% MC in 2020 ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x, while MMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x and TMC ranged from x\% (x\% - x\%) in x to x\% (x\% - x\%) in x.
-% The largest percentage increase in MC coverage from 2010 to 2020 was x\% (x\% - x\%) in x, from x\% (x\% - x\%) to x (x\% - x\%), while for MMC it was x\% (x\% - x\%) in x. 
+% Between 2007, the year VMMC programme implementation began, and 2020, an estimated x million men(95\% CI: x-x million) were newly circumcised. 
+% Of these, x million (x-x million) were MMCS, along with x million (x-x million) TMCS. 
+% This translated to an increase in MC for the SSA region of x\% (x\%-x\%) in 2010 to x\% (x\%-x\%) in  2020. 
+% MC in 2020 ranged from x\% (x\%-x\%) in x to x\% (x\%-x\%) in x, while MMC ranged from x\% (x\%-x\%) in x to x\% (x\%-x\%) in x and TMC ranged from x\% (x\%-x\%) in x to x\% (x\%-x\%) in x. 
+% The largest percentage increase in MC coverage from 2010 to 2020 was x\% (x\%-x\%) in x, from x\% (x\%-x\%) to x (x\%-x\%), while for MMC it was x\% (x\%-x\%) in x. 
 % The number of annual MCs performed increased from x (x to x) in 2006 to x (x to x) in 2020, a growth of x (x to x) annually. 
@@
 In 2006, the year before VMMC programme implementation began, an estimated 217.236 million men (95\%
-CI: 211.079 - 222.008 million) were circumcised in the 33 countries in SSA for which we have valid circumcision
+CI: 211.079-222.008 million) were circumcised in the 33 countries in SSA for which we have valid circumcision
 data. 
-Of these, 67.021 million (62.554 - 73.259 million) were MMCS, and 102.286 million (95.718 - 106.665
+Of these, 67.021 million (62.554-73.259 million) were MMCS, and 102.286 million (95.718-106.665
 million) were TMCS. 
-This contrasts with 2020, where an estimated 337.913 million males (316.265 - 362.898
-million) were circumcised in these same countries, of which 125.738 million (106.081 - 157.406 million) were
-performed as MMCS, and 136.555 million (124.189 - 144.146 million) as TMCS. 
+This contrasts with 2020, where an estimated 337.913 million males (316.265-362.898
+million) were circumcised in these same countries, of which 125.738 million (106.081-157.406 million) were
+performed as MMCS, and 136.555 million (124.189-144.146 million) as TMCS. 
+\todo{I believe this value is cumulative, not for each discrete year! May need to reword}
+% \todo{Can use n_circs_fun function for this\!}
 This constituted an increase
-of 120.677 million (105.185 - 140.89 million) newly circumcised males between 2006 and 2020, with 58.717
-million (43.528 - 84.147 million) new MMCs performed, and 34.269 million (28.471 - 37.481 million) new
+of 120.677 million (105.185-140.89 million) newly circumcised males between 2006 and 2020, with 58.717
+million (43.528-84.147 million) new MMCs performed, and 34.269 million (28.471-37.481 million) new
 TMCs performed. 
@@
 TMC. 
-This translated to a change in mean MC coverage for the SSA region from 57.62\% (59.13\% - 55.55\%
-) in 2006 to 63.2\% (66.94\% - 59.71\%) in 2020, or an increase of 5.58\% (4.16\% - 7.81\%). 
-MMC coverage increased from 18.75\% (17.75\% - 19.9\%  in 2006 to 26.09\% (23.11\% - 30.04\%) in 2020, an increase of 7.33\%
-(5.36\% - 10.14\%). 
-TMC changed from 24.64\% (23.57\% - 25.58\%) in 2006 to 22.75\% (21.34\% - 24.06\%) in 2020, a decrease of 1.89\% (1.51\% - 2.23\%).
+This translated to a change in mean MC coverage for the SSA region from 57.62\% (59.13\%-55.55\%
+) in 2006 to 63.2\% (66.94\%-59.71\%) in 2020, or an increase of 5.58\% (4.16\%-7.81\%). 
+MMC coverage increased from 18.75\% (17.75\%-19.9\%  in 2006 to 26.09\% (23.11\%-30.04\%) in 2020, an increase of 7.33\%
+(5.36\%-10.14\%). 
+TMC changed from 24.64\% (23.57\%-25.58\%) in 2006 to 22.75\% (21.34\%-24.06\%) in 2020, a decrease of 1.89\% (1.51\%-2.23\%).
 
-MC coverage in each country in 2006 ranged from 4.97\% (4.78\% - 5.16\%) in Zimbabwe to 95.99\% (86.43\% -
-(99.72\%) in Guinea, while MMC in 2006 ranged from 1.63\% (1.47\% - (1.76\%) in Zimbabwe to 60.05\% (56.56\%
-- (64.15\%) in Congo and TMC ranged from 0.93\% (0.75\% - (1.12\%) in Eswatini to 65.19\% (63.41\% - (66.94\%)
-in Benin. In contrast, in 2020 MC coverage was estimated to have ranged from 13.77\% (10.51\% - 18.87\%) in
-Zimbabwe to 96.95\% (89.74\% - (99.91\%) in Senegal, while MMC ranged from 11.55\% (8.24\% - (16.68\%) in
-Zimbabwe to 64.08\% (61.16\% - (67.11\%) in Sierra Leone and TMC ranged from 0.69\% (0.56\% - (0.84\%) in
-Eswatini to 63.02\% (59.34\% - (66.65\%) in Benin.
+MC coverage in each country in 2006 ranged from 4.97\% (4.78\%-5.16\%) in Zimbabwe to 95.99\% (86.43\% -
+(99.72\%) in Guinea, while MMC in 2006 ranged from 1.63\% (1.47\%-1.76\%) in Zimbabwe to 60.05\% (56.56\%-64.15\%) in Congo and TMC ranged from 0.93\% (0.75\%-1.12\%) in Eswatini to 65.19\% (63.41\%-6.94\%)
+in Benin. In contrast, in 2020 MC coverage was estimated to have ranged from 13.77\% (10.51\%-18.87\%) in
+Zimbabwe to 96.95\% (89.74\%-99.91\%) in Senegal, while MMC ranged from 11.55\% (8.24\%-16.68\%) in
+Zimbabwe to 64.08\% (61.16\%-67.11\%) in Sierra Leone and TMC ranged from 0.69\% (0.56\%-0.84\%) in
+Eswatini to 63.02\% (59.34\%-66.65\%) in Benin.
 
-The largest percentage increase in MC coverage from 2006 to 2020 was in Lesotho at 21.7\% (18.66\% - 25.93\%),
-from 30.06\% (29.53\% - 30.7\%) in 2006 to 51.76\% (48.19\% - 56.63\%) in 2020, while the highest percentage
-increase in MMC was also in Lesotho at 21.49\% (18.14\% - 26.13\%), from 6.37\% (5.93\% - 6.88\%) in 2006 to
-27.86\% (24.08\% - 33.01\%) in 2020. For TMC, the largest percentage decrease between 2006 and 2020 was in
-Ghana at 8.76\% (6.09\% - 9.61\%), from 58.2\% (55.2\% - 60.8\%) in 2006 to 49.44\% (45.58\% - 54.71\%) in 2020.
+The largest percentage increase in MC coverage from 2006 to 2020 was in Lesotho at 21.7\% (18.66\%-25.93\%),
+from 30.06\% (29.53\%-30.7\%) in 2006 to 51.76\% (48.19\%-56.63\%) in 2020, while the highest percentage
+increase in MMC was also in Lesotho at 21.49\% (18.14\%-26.13\%), from 6.37\% (5.93\%-6.88\%) in 2006 to
+27.86\% (24.08\%-33.01\%) in 2020. For TMC, the largest percentage decrease between 2006 and 2020 was in
+Ghana at 8.76\% (6.09\%-9.61\%), from 58.2\% (55.2\%-60.8\%) in 2006 to 49.44\% (45.58\%-54.71\%) in 2020.
 
-The number of annual MCs performed increased from 0.29 million (0.23 - 0.38 million) in 2006 to 0.29 million
-(0.23 - 0.38 million) in 2020, a growth of 0.1 million (0.056 - 0.127 million) annually, averaged across all
-interceding years. Amongst these, 0.29 million (0.23 - 0.38 million) were MMCs in 2006, while in 2020 0.391
-million (0.287 - 0.506 million) MMCs were performed, representing an increase in million (0.012 - 0.166
+The number of annual MCs performed increased from 0.29 million (0.23-0.38 million) in 2006 to 0.29 million
+(0.23-0.38 million) in 2020, a growth of 0.1 million (0.056-0.127 million) annually, averaged across all
+interceding years. Amongst these, 0.29 million (0.23-0.38 million) were MMCs in 2006, while in 2020 0.391
+million (0.287-0.506 million) MMCs were performed, representing an increase in million (0.012-0.166
 million) in MMCs performed annually. The number of TMCs performed annually did increase slightly from
-2006, from 0.12 million (0.115 - 0.125 million) to 0.128 million ( 0.085 - 0.159 million) in 2020. However,
+2006, from 0.12 million (0.115-0.125 million) to 0.128 million (0.085-0.159 million) in 2020. However,
 TMC coverage actually decreased in many countries from 2006 to 2020. This is the focus of section \ref{sec:org5fb5e18}.
@@
     \includegraphics[width=.9\linewidth]
-    {plots/03_subnat_plot.png}
+    {figures/paper/02_subnat_plot.png}
     \caption{\emph{District-level median percentage of men aged 15-29 years who were circumcised in 2020 in 33 SSA countries.
@@
 
-\todo{Anything else to add here?}
+\todo{Include comparisons of VMMC vs non-VMMC priority countries, as in below sections}
+\todo{Include more commments on results, as below}
 
 \todo{
- - Check UNAIDS target for 15-29 year olds, may be 80\%? May want to remove this line altogether?
+-Check UNAIDS target for 15-29 year olds, may be 80\%? May want to remove this line altogether?
 }
 
-% Within countries, the median difference in MC coverage between the districts with lowest and highest coverage in 2020 was x\% (x\% - x\%).
-% For ESA countries, this was x\% (x\% - x\%), in contrast to WCA countries, where it was x\% (x\% - x\%).
+% Within countries, the median difference in MC coverage between the districts with lowest and highest coverage in 2020 was x\% (x\%-x\%).
+% For ESA countries, this was x\% (x\%-x\%), in contrast to WCA countries, where it was x\% (x\%-x\%).
 % The largest variation overall (and ESA) was in x, from x\% in x to x\% in x, while the largest variation for WCA countries was x, from x\% in x to x\% in x. 
@@
 
-\subsection{Subnational Variation in Total, Medical \& Traditional Circumcision Across Different Ages}
-\label{sec:org92e0f37}
+\subsection{Subnational variation in total, medical \& traditional circumcision across different ages}
 
@@
     \includegraphics[width=.9\linewidth]
-    {plots/04_geo_age.png}
+    {figures/paper/03_geo_age.png}
     \caption{\emph{Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020.
@@
 Age at circumcision differed greatly by circumcision type and location.
-The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was x, reflecting VMMC focus on these ages. 
-The age group with the highest MC coverage in 2020 was x, in contrast to 2006, where this age group was x. 
-The age group with the highest MMC coverage in 2020 was x, while for TMC coverage this age group was x. 
-The average age of MC in 2020 in SSA was x, compared to x in 2006. 
-For MMC, the average age at circumcision in 2020 was x, compared to x in 2006, while for TMC the average age was x in 2020, compared to x in 2006. 
-The average age of MC in 2020 for ESA was x, while in WCA it was x.
+The five-year age group in 2006, the year before VMMC programme implementation began, which had the highest MC coverage across the SSA region was 25-29, at 74.1\% (73.13\%-74.73\%).
+In contrast, the age group with the highest MC coverage in 2020 was 20-24, at 84.04\% (82.23\%-86.18\%).
+The five-year age group in 2006 which had the highest MMC coverage was 20-24, at 25.33\% (23.84\%-26.87\%).
+The age group with the highest MMC coverage in 2020 was also 20-24, at 40.28\% (37.29\%-43.71\%). The five-year age group in 2006 which had the highest
+TMC coverage was 45-49, at 40.29\% (36.7\%-43.09\%). The age group with the highest TMC coverage in
+2020 was 54-59, 38.55\% (36.19\%-40.5\%).
+This decrease in the five-year age group with the highest MC coverage, increase in the age group for TMC with the highest coverage (as well as a decrease in coverage for
+the highest five-year age group), and increase in overall MMC coverage across the SSA region is indicative of
+the effect of VMMC programme implementation on the region.
 
-\subsection{Subnational Heterogeneity in Age at Medical and Traditional Circumcision}
-\label{sec:org92e0f37}
+We may compare changes in circumcision amongst two age groups; 15-29 year olds, which are a particular focus for VMMC implementation, and 30-49 year olds, which are not.
+MC coverage amongst 15-29 year olds increased from 71.91\% (70.81\%-72.47\%) in 2006 to 82.44\% (80.19\%-85.11\%) in 2020.
+In contrast, MC
+coverage amongst 30-49 year olds only increased from 73.62\% (72.66\%-74.39\%) in 2006 to 78.84\% (77.97\%
+- 79.91\%) in 2020. Therefore, MC coverage across SSA saw greater increases in this younger age group
+than in this older one, in line with VMMC programme age focus. Similarly, MMC coverage amongst 15-29
+year olds increased from 24.84\% (23.49\%-26.22\%) in 2006 to 39.05\% (35.63\%-43.08\%) in 2020, while
+MMC coverage amongst 30-49 year olds increased from 22.74\% (21\%-24.74\%) in 2006 to 31.25\% (29.4\% -
+33.38\%) in 2020. Therefore, MMC coverage across SSA also saw greater increases amongst 15-29 year olds
+than amongst 30-49 year olds. The changes seen in TMC, however, contrast to these larger increases in MC
+and MMC coverage for 15-29 year olds. TMC coverage amongst 15-29 year olds decreased from 32.01\% (
+30.68\%-33.33\%) in 2006 to 28.25\% (26.57\%-29.88\%) in 2020, while TMC coverage amongst 30-49 year
+olds decreased from 38.42\% (36.58\%-40.09\%) in 2006 to 35.1\% (33.64\%-36.58\%) in 2020. Thus, TMC
+coverage decreased less in absolute terms amongst 30-49 year olds than amongst 15-29 year olds, which is line
+with the greater focus on performing MMCs amongst this younger age group.
 
-Fill in! Take some of the last section and put it here.
+Finally, we can contrast patterns in circumcision pattern for different age groups amongst VMMC and
+non-VMMC priority countries, where differences in 2006 and 2020 levels and patterns of circumcision seem to
+be more pronounced.
+For VMMC priority countries, five-year age group MC coverage 2006 was highest amongst 35-39 year olds, at
+44.21\% (43.31\%-45.14\%), but in 2020 was highest amongst 20-24 year olds, at 66.08\% (62.71\%-70.35\%
+), respectively. This highlights both the increased prevalence of MC in VMMC priority countries, and the
+downward shift in age profile of those who are circumcised, since VMMC programme implementation began.
+In 2006 MMC coverage was highest amongst 30-34 year olds, at 18.48\% (17.48\%-19.52\%). This contrasts
+with 2020, where MMC coverage was highest amongst 20-24 year olds, at 46.71\% (x 43.1\%-x 51.26\%).
+This shows that much of the downward shift in age profile of circumcised individuals since 2006 has been
+“driven” by an increase in the number of MMCs performed amongst younger individuals. In 2006, TMC
+coverage was greatest in 54-59 year olds, at 27.82\% (26.6\%-29.09\%). while in 2020 it was most prevalent
+in 54-59 year olds, at 27.82\% (26.6\%-29.09\%, highlighting that VMMC implementation has been focused on areas where TMC has not historically been widely prevalent, and so seems to have had little effect on patterns of TMC in VMMC priority countries, both in terms of its age profile and prevalence.
+
+We can contrast this with the non-VMMC priority countries in SSA. The five-year age group MC coverage in
+both 2006 and 2020 was highest amongst 25-29 year olds, at 94.72\% (93.64\%-95.25\%) and 96.15\% (95.67\%
+- 96.59\%), respectively. This indicates that MC has increased slightly in non-VMMC priority countries,
+but the age profile (in terms of the five-year age group with the highest coverage) has not noticeably changed.
+However, in 2006 MMC coverage was highest amongst 15-19 year olds, at 31.13\% (29.27\%-33.01\%). This
+contrasts with 2020, where MMC coverage was highest amongst 20-24 year olds, at 36.11\% (x 33.52\%-38.81\%), showing an interesting shift upwards in age for MMCs in non-VMMC priority countries, as a result
+of VMMC focus on young adults, as well as a general increase in MMC coverage in these countries. 
+In 2006, TMC coverage was greatest in 45-49 year olds, at 49.27\% (43.79\%-53.39\%). while in 2020 it was most
+prevalent in 45-49 year olds, at 49.27\% (43.79\%-53.39\%, highlighting a shift upwards in TMCs in VMMC
+priority countries, likely resulting from previously TMCs being performed as TMCs.
+Similarly, we can compare the 2006 and 2020 circumcision levels amongst 15-29 and 30-49 year olds in both
+VMMC and non-VMMC countries, respectively.
+
+In VMMC priority countries, MC coverage amongst 15-29 year olds increased from 37.96\% (37.34\%-38.59\%
+) in 2006 to 63.22\% (58.98\%-68.58\%) in 2020. In contrast, MC coverage in 30-49 year olds went from
+43.88\% (43.14\%-44.67\%) in 2006 to 54.52\% (53.04\%-56.52\%) in 2020. Therefore, MC coverage in VMMC
+priority countries increased amongst 15-29 year olds at a higher rate than amongst 30-49 year olds, and
+indeed greater than in SSA as a whole, highlighting the effects of VMMC implementation in these countries
+since 2006. Similarly, MMC coverage amongst 15-29 year olds increased from 16.18\% (15.5\%-16.89\%) in
+2006 to 44.44\% (39.95\%-50.07\%) in 2020, while MMC coverage amongst 30-49 year olds increased from
+17.89\% (17.01\%-18.78\%) in 2006 to 29.9\% (28.28\%-32.11\%) in 2020. Therefore, MMC coverage in
+VMMC priority countries also saw greater increases amongst 15-29 year olds than amongst 30-49 year olds,
+and greater increases than for SSA as a whole. Again, TMC coverage amongst both fifteen year age groups
+contrast to these increases for MC and MMC. TMC coverage amongst 15-29 year olds decreased from 21.78\%
+(21.15\%-22.37\%) in 2006 to 18.78\% (18.08\%-19.42\%) in 2020, while TMC coverage amongst 30-49 year
+olds decreased from 25.99\% (25.24\%-26.74\%) in 2006 to 24.62\% (23.89\%-25.32\%) in 2020. This decrease
+in TMC coverage can partly be attributed to a combination of increased population in non-TMC practising
+areas, but TMC coverage also decreased less in absolute terms amongst 30-49 year olds than amongst 15-29
+year olds, which is line with the greater focus on performing MMCs, and hence replacing TMCs, amongst
+this younger age group.
+
+For non-VMMC priority countries, MC coverage in 15-29 year olds increased from 93.98\% (
+92.57\%-94.49\%) in 2006 to 94.94\% (93.98\%-95.85\%) in 2020, staying relatively similar. MC coverage in
+30-49 year olds also increased from 93.97\% (92.85\%-94.72\%) in 2006 to 95.48\% (95.03\%-95.92\%) in 2020,
+so again, when taking our credible intervals into account, there was little increase amongst this age group in
+non-VMMC priority countries. It is interesting that MC seems to have increased more amongst 30-49 year
+olds than amongst 15-29, defying the trend amongst VMMC priority countries and SSA as a whole. MMC
+coverage amongst 15-29 year olds increased from 30.48\% (28.69\%-32.28\%) in 2006 to 35.55\% (32.82\% -
+38.54\%) in 2020, while MMC coverage amongst 30-49 year olds increased from 26.06\% (23.72\%-28.81\%) in
+2006 to 32.17\% (30.17\%-34.24\%) in 2020. Hence, MMC coverage in non-VMMC countries also saw greater
+increases amongst 30-49 year olds than in 15-29 year olds, but not much change overall when factoring in our
+uncertainty. TMC coverage amongst 15-29 year olds decreased from 38.67\% (36.88\%-40.45\%) in 2006 to
+34.41\% (32.09\%-36.68\%) in 2020, while TMC coverage amongst 30-49 year olds decreased from 46.93\%
+(44.34\%-49.23\%) in 2006 to 42.26\% (40.3\%-44.29\%) in 2020. Thus, TMC coverage decreased less in
+absolute terms amongst 30-49 year olds than amongst 15-29 year olds, which is line with the greater focus on
+performing MMCs amongst this younger age group. TMC coverage decreased more amongst non-VMMC
+countries for both age groups, suggesting likely replacement of historical TMC with MMC.
+
+\subsection{Subnational heterogeneity in age at medical and traditional circumcision}
 
@@
     \includegraphics[width=.9\linewidth]
-    {plots/05_map_plot_mean_circ_age.png}
+    {figures/paper/04_map_plot_mean_circ_age.png}
     \caption{\emph{(A) Estimated distinct-level age at circumcision in 2020 in 33 sub-Saharan African countries.
@@
 
-% stimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years.
+The mean age at circumcision for MC in 2006 was 8.88 (8.53-9.62), while in 2020 it was 9.26 (8.76-9.78
+). Similarly, the mean age at circumcision for MMC in 2006 was 10.59 (10.19-11.38), and in 2020 it was
+10.8 (10.35-11.24). Finally, the mean age at circumcision in 2006 for TMC was 9.66 (9.36-10.32), and in
+2020 it was 9.35 (8.64-10.08). 
+Therefore, the mean age at circumcision for MC and MMC went up slightly from
+2006 to 2020. However, it is important to note that the uncertainty ranges in our credible intervals overlap,
+so this increase could be seen as “non-significant”, in some sense. In contrast, the mean age at circumcision
+for TMC was seen to decrease, altough again, not in a manor that exceeds our uncertainty bounds. This may
+suggest that VMMC implementation amongst 15-29 year olds has corresponded to an upward shift of mean
+age at circumcision for MC and MMC, and replaced some circumcisions which would previously have been
+performed as TMCs, which may explain the observed decrease in mean age of TMC.
+
+As in the previous section, we can also compare how the mean age of circumcision differs amongst VMMC
+priority countries, versus their non-VMMC prority counterparts in SSA.
+
+For VMMC priority countries, the mean age at circumcision for MC in 2006 was 14.05 (13.57-14.68), while
+in 2020 it was 15.45 (14.24-16.36). Similarly, for MMC in 2006 the mean age at circumcision was 15.82 (
+15.24-16.48), while in 2020 it was 16.41 (15.43-17.13). Lastly, the mean age at circumcision in 2006 for
+TMC was 12.29 (11.88-13.04), and in 2020 it was 11.46 (10.84-12.43. So the mean age at circumcision for
+all circumcision types is higher in VMMC priority countries than overall in SSA, highlighting the historically
+low levels of MC and TMC in these countries. Like in SSA overall, the mean age at circumcision for MC and
+MMC went up slightly, albeit not significantly when factoring in uncertainty bounds. Again, mean age at
+TMC also decreased in VMMC priority countries.
+
+For non-VMMC priority countries, the mean age at MC in 2006 was 5.51 (5.08-6.33), while in 2020 it was
+5.24 (5.01-5.5). Similarly, the mean age at MMC in 2006 was 6.07 (5.82-6.95), and in 2020 it was 5.93 (
+5.94-6.13). Finally, the mean age at TMC in 2006 for TMC was 7.38 (7.18-7.96), and in 2020 it was 7.52
+(6.73-8.06. In contrast to our VMMC priority countries, these countries have a lower mean at circumcision
+for all circumcision types, largely driven by high TMC levels historically. It is interesting that the age at
+circumcision for MC and MMC actually increased for non-VMMC priority countries, in contrast to SSA as a
+whole and the priority countries. Likewise, the mean age at TMC increased. This can be explained
+by a possible replacement of TMC with MMC in a traditional setting, so at generally younger ages than
+MMCs performed as part of VMMC programmes. This caused a natural shift upwards of the mean age at
+TMC, as younger individuals are now more likely to receive MMCs.
+
+% estimated percentage of men aged 15-29 years who were circumcised sub-nationally in 33 sub-Saharan African countries in 2006 and 2020, as well as the difference in coverage between the two years.
 Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), respectively.
-Countries with no information on circumcision type are grey in the Medical and Traditional plots, while countries with no circumcision estimate are grey in all
+Countries with no information on circumcision type are grey in the Medical and Traditional figures/paper, while countries with no circumcision estimate are grey in all
 
-\subsection{Decrease in TMC in SSA region Over Time}
+\subsection{Decrease in traditional male circumcision in sub-Saharan Africa over time}
 \label{sec:org5fb5e18}
@@
     \includegraphics[width=1\linewidth]
-    {plots/06_change_00_20.png}
+    {figures/paper/05_change_00_20.png}
     % \caption{\emph{Absolute difference, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region.
-Plots are split by circumcision type.
+figures/paper are split by circumcision type.
 Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.
 }}
-    \caption{\emph{Circumcision coverage in 2000 and 2020 amongst 15-29 year olds in all 33 sub-Saharan African countries, split by circumcision type.
+    \caption{\emph{Circumcision coverage in 2000 and 2020 amongst 15-29 year olds in all 34 sub-Saharan African countries, split by circumcision type.
 The countries below the horizontal black line are VMMC priority countries.}}
@@
 
-The average TMC coverage in SSA in 2006 was x\% (x\% to x\%). 
-This fell to x\% (x\% to x\%) in 2020, representing a decrease of x\% (x\% to x\%). 
-In ESA, TMC coverage was x\% (x\% to x\%) in 2006, compared to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) decrease.
-In constrast, TMC coverage in WCA was x\% (x\% to x\%) versus x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) fall.
-In 2006, x (x to x) TMCs were performed, while in 2020 this was reduced to x (x to x), representing a x (x to x) decrease in annual TMCs.
-In ESA, the annual number of TMCs performed dropped from x (x to x) in 2006 to x (x to x) in 2020, a x (x to x) drop. 
-In WSA, this number fell from x (x to x) in 2006 to x (x to x) in 2020, a fall of x (x to x).
-For the 10-29 age group, TMC coverage was reduced from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a drop of x\% (x\% to x\%).
-In VMMC countries, this was reduced from x\% (x\% to x\%) to x\% (x\% to x\%) from 2006 to 2020, while even in non-VMMC countries this decreased from x\% (x\% to x\%) to x\% (x\% to x\%). 
-The largest decrease in TMC coverage from 2006 to 2020 was in x, from x\% (x\% to x\%) to x\% (x\% to x\%). 
-[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from x\% (x\% to x\%) to x\% (x\% to x\%) in x.
+The average TMC coverage in SSA in 2006 was 24.3\% (23.19\% to 25.27\%).
+This fell to 21.88\% (20.35\% to 23.33\%) in 2020, a decrease of 2.42\%.
+In non-VMMC priority countries, TMC coverage was 31.26\% (29.71\% to 32.59\%).
+This fell to 27.66\% (25.4\% to 29.8\%) in 2020, representing a decrease of 3.59\%.
+In contrast, TMC coverage in VMMC priority countries was 14.36\% (13.88\% to 14.8\%).
+This fell to 13.63\% (13.13\% to 14.08\%) in 2020, representing a decrease of 0.74\%.
+Therefore, the decrease in TMC found throughout SSA is much more pronounced for non-VMMC countries.
 
-\subsection{UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries}
+\todo{Add thousand/million/billion suffix here (or at least commas), rather than whole number!}
+In 2006, 98009 (94028-102330) TMCs were performed, while in 2020 this increased to 102827 (63457-129829), representing a 4818 increase in annual TMCs.
+However, this increase must be taken within the context of a large increase in population in SSA over this period, from 1.23 billion in 2006 to 1.80 billion in 2020, and as seen in our coverage estimates above, constitutes a decrease in the number of TMCs performed per capita in the region (need to calculate this?!) In non-VMMC priority countries, the annual number of TMCs performed changed from 114700 (109648-120604) in 2006 to 117525 (54128-160432) in 2020, or by 2825.
+This is within the context of the population of non-VMMC priority countries increasing from 749 million to 1.11 billion from 2006 to 2020.
+In VMMC priority countries, the number of TMCs performed went from 74165 (71715-76224) in 2006 to 74165 (71715-76224) in 2020, a fall of 7665.
+In VMMC priority countries, the population increased from 481 million to 694 million.
+\todo{Comment on this}
+
+We can also compare the differences in TMC coverage change between 15-29 and 30-49 year olds, in SSA as a whole and in VMMC and non-VMMC priority countries.
+
+For the 15-29 age group, TMC coverage was reduced from 31.1\% (29.78\% to 32.41\%) in 2006 to 26.69\% (25.05\% to 28.31\%) in 2020, a drop of 4.41\%.
+This contrasted with the 30-49 age group, where TMC coverage went from 37.45\% (35.52\% to 39.18\%) in 2006 to 34.02\% (32.58\% to 35.48\%) in 2020, a drop of 3.42\%.
+Therefore, in SSA as a whole TMC coverage decreased slightly more amongst 15-29 year olds than in 30-49 year olds, likely as a result of VMMC programme focus on this age group.
+
+For the 15-29 year olds in non-VMMC priority countries, TMC coverage was reduced from 31.1\% (29.78\% to 32.41\%) in 2006 to 26.69\% (25.05\% to 28.31\%) in 2020, a drop of 4.41\%.
+This contrasted with the 30-49 age group, where TMC coverage went from 37.45\% (35.52\% to 39.18\%) in 2006 to 34.02\% (32.58\% to 35.48\%) in 2020, a drop of 3.42\%.
+Therefore in non-VMMC priority countries the decrease in TMC coverage was larger for both age groups than in SSA as a whole, but the difference between this decrease for 15-29 year olds versus 30-49 year olds is less pronounced.
+
+For VMMC priority countries, the 15-29 age group, TMC coverage was reduced from 31.1\% (29.78\% to 32.41\%) in 2006 to 26.69\% (25.05\% to 28.31\%) in 2020, representing a fall of 4.41\%.
+In the 30-49 age group, TMC coverage in VMMC priority countries dropped from 37.45\% (35.52\% to 39.18\%) in 2006 to 34.02\% (32.58\% to 35.48\%) in 2020, a drop of 3.42\%.
+Therefore, in VMMC priority countries there is a much greater disparity in the drop in TMC coverage between 15-29 and 30-49 year olds.
+15-29 year olds saw a much greater drop in TMC coverage, likely resulting from VMMC programme focus on these ages.
+
+The largest decrease in TMC coverage from 2006 to 2020 was in Côte d’Ivoire, where TMC coverage fell from 58.45\% (57.07\% to 59.5\%) to 48.85\% (46.87\% to 50.49\%, a decrease of 9.6\%.
+
+The largest decrease in TMC coverage amongst VMMC countries was from Côte d’Ivoire, where TMC coverage fell from 58.45\% (57.07\% to 59.5\%) to 48.85\% (46.87\% to 50.49\%, a decrease of 9.6\%.
+
+\todo{add smallest decrease here? Would be more interesting for non-VMMC countries, could show where MMC has not begun to replace TMC}
+\todo{add \# of countries in both regions which have experienced a drop in TMC coverage?? Might be interesting for non-VMMC}
+
+\subsection{UNAIDS goals progress amongst 10-29 year olds in Voluntary Male Medical Circumcision target countries}
 \label{sec:orgf9204d9}
 
-Amongst the 13 VMMC priority countries modelled, just x countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, x and x. 
-MC coverage across these countries increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020. 
-X (x to x) circumcisions were performed between 2007 and 2020 in these countries. 
-Of these, x (x to x) were MMCs. 
-No countries were expected to have reached this goal in all districts. 
-The number of annual MCs increased from x (x to x) in 2006 to x (x to x) in 2020. 
-x (x to x) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, x (x to x) times the projected number of MCs for 2020. 
-The largest increase in MC coverage amongst VMMC priority countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase. 
-In contrast, the lowest increase in MC coverage in these countries was in x, from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.
+As a reminder, in 2010 the WHO and UNAIDS set a 80\% MC target for 15-49 year olds in the VMMC
+priority countries by 2018. This target was expanded in 2016 to the new target of 90\% MC amongst 10-29
+year olds in VMMC priority countries by 2021.
+Amongst the 14 VMMC priority countries modelled, 3 countries were projected to have achieved the VMMC
+target of 80\% MC coverage amongst 15-49 year olds by 2020, Tanzania, Ethiopia and Kenya. None were
+expected to reach the 90\% target for 10-29 year olds. No countries were expected to have reached these goals
+in all districts.
+MC coverage amongst 10-29 year olds across VMMC priority countries increased from 30.94\% (30.4\% to
+31.53\%) in 2006 to 54.09\% (50.78\% to 58.36\%) in 2020, an increase of 23.15\% (20.38\%-26.83\%). MMC
+coverage amongst 10-29 year olds across VMMC priority countries increased from 13.68\% (13.07\% to 14.31\%
+) in 2006 to 39.24\% (35.76\% to 43.66\%) in 2020, an increase of 25.56\% (22.69\%-29.35\%). MC coverage
+amongst 15-49 year olds across VMMC priority countries increased from 38.29\% (37.71\%-38.88\%) in
+2006 to 58.7\% (56.58\% to 61.44\%) in 2020, an increase of 20.41\% (18.87\%-22.55\%). MMC coverage
+amongst 15-49 year olds across VMMC priority countries increased from 16.87\% (16.22\% to 17.58\%) in
+2006 to 39.57\% (37.31\% to 42.48\%) in 2020, an increase of 22.7\% (21.1\%-24.91\%).
+Between 2006 and 2020 in these countries, 2.396 million (2.066 million-2.81 million) MCs were performed
+on 10-29 year olds. Of these, 2.285 million (2.285 million-2.285 million) were MMCs, and 0.573 million
+(0.573 million-0.573 million) were TMCs. Over the same period, million (million-million) MCs were
+performed on 15-49 year olds, million (million-million) of which were MMCs, and million (million-million) of which were TMCs.
 
-However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries. 
-x/x districts in these countries were expected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from x/x in 2006, before VMMC programmes began. 
-Even in x, where MC was projected to be lowest in 2020, x/x districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
-MC coverage there increased from x\% (x\% to x\%) in 2006 to x\% (x\% to x\%) in 2020, a x\% (x\% to x\%) increase.
+The number of annual MCs amongst 10-29 year olds increased from 0.702 million (0.648 million to 0.757
+million) in 2006 to 1.694 million (1.418 million to 2.053 million) in 2020.
+The number of annual MMCs amongst 10-29 increased from 0.431 million (0.383 million to 0.485 million
+) in 2006 to 1.441 million (1.16 million to 1.8 million) in 2020, while in constrast, the number of TMCs
+decreased from 0.271 million (0.254 million to 0.29 million) in 2006 to 0.252 million (0.222 million to 0.283
+million) in 2020.
+For 15-49 year olds, the number of annual MCs increased from 0.335 million (0.305 million to 0.367 million)
+in 2006 to 0.727 million (0.578 million to 0.919 million) in 2020.
+Annual MMCs amongst 15-49 increased from 0.225 million (0.198 million to 0.253 million) in 2006 to 0.648
+million (0.498 million to 0.84 million) in 2020, while in constrast, the number of TMCs decreased from 0.11
+million (0.101 million to 0.122 million) in 2006 to 0.079 million (0.067 million to 0.092 million) in 2020.
+1.694 (1.418 to 2.053) additional circumcisions are required to achieve 90\% and 80\% MC coverage targets
+for 10-29 and 15-49 year olds, respectively, across all VMMC priority countries.
+This is equivalent to 16.7 (21.3 to 12.6) and 38.3 (38.3 to) times the projected number of MCs for 10-29
+and 15-49 year olds for 2020.
+MC coverage in 2020 for 10-29 year olds in VMMC priority countries was highest in Ethiopia, at 84.9\% (
+82.95\%-87.3\%), and lowest in Zimbabwe, at 29.51\% (27.21\%-32.77\% . For 15-49 year olds, the highest
+MC coverage was in Ethiopia, at 84.9\% (82.95\%-87.3\%), and lowest in Zimbabwe, at 29.51\% (27.21\% -
+32.77\% . MMC coverage for 10-29 year olds in VMMC priority countries was highest in Lesotho, at 58.11\% (
+55.3\%-62.45\%), and lowest in Malawi, at 22.57\% (21.23\%-24.54\% . For 15-49 year olds, the highest MMC
+coverage was in Lesotho, at 58.11\% (55.3\%-62.45\%), and lowest in Malawi, at 22.57\% (21.23\%-24.54\% .
+The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries
+was in Botswana, from 9.39\% (8.74\%-10.22\%) in 2006 to 52.52\% (52.52\%-52.52\%) in 2020, a 43.12\% (
+40.45\%-44.77\%) increase. In contrast, the lowest increase in MC coverage in these countries was in from
+9.39\% (8.74\%-10.22\%) in 2006 to 52.52\% (52.52\%-52.52\%) in 2020, a 43.12\% (40.45\%-44.77\%)
+increase.
+However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority
+countries. 213 (124-301) of 1072 districts in these countries were expected to have reached 90\% MC
+coverage amongst 10-29 year olds in 2020, up from 125 (60-203) of 1072 in 2006, before VMMC programmes
+began. Similarly, 422 (367-506) of 1072 districts in these countries were expected to have reached 80\% MC
+coverage for 15-49 year olds in 2020, compared to 344 (296-392) of 1072 in 2006.
+In 2020, 7 (5-8) of the 14 VMMC priority countries had no districts which satisfied the 90\% MC coverage
+target for 10-29 year olds.
+This was down from 10 (8-11) in 2006.
+Similarly, in 2020, 3 (3-4) countries had no districts which satisfied the 80\% MC coverage target for 15-49 year olds.
+This was down from 5 (5-5) in 2006.
 
-TODO: Add some kind of table here!
+\todo{Add table here?}
 
@@
 % 
-% TODO: Write this section!
+% \todo{Write this section!}
 
@@
 
-TODO: Flesh this out! Mention how this differs for VMMC and non-VMMC countries, and maybe there is some pattern for TMC-MMCs?
+\todo{Flesh this out! Mention how this differs for VMMC and non-VMMC countries, and maybe there is some pattern for TMC-MMCs?}
 
@@
 There were several limitations inherent in the \verb|threemc| model, and in this analysis. 
-TODO: Write these out!
+\todo{Write these out!}
 There is much scope for further developments from this analysis. 
@@
 
-TODO: Good conclusion of one line?
+\todo{Good conclusion of one line?}
 

### 2024-04-16 paper/2_paper/supp_figs.tex
Updates from Overleaf

--- 2023-09-26 paper/supp_figs.tex
@@
 where $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, and $P_{iat}$ is an estimate of the male population at age $a$ and time step $t$ in district $i$.
-The district probabilities of TMC, MMC and MC were replaced with the higher level aggregates in the likelihood above for surveys that did not collect information on the district level.
+The district probabilities of TMC, MMC and MC were sd with the higher level aggregates in the likelihood above for surveys that did not collect information on the district level.
 

### 2024-04-16 paper/2_paper/figures/scripts/00_funs.R

@@ -1,0 +1,129 @@
+#### Functions used across different scripts ####
+
+# function to load data from orderly archive
+load_archive <- function(task, 
+                         orderly_root = here::here(),
+                         file, 
+                         load_fun = readr::read_csv, 
+                         archives = NULL, 
+                         query = NULL, ...) {
+  
+  if (is.null(archives) && !is.null(query)) {
+    dir <- orderly::orderly_search(query = query, name = task, ...)
+  } else if (!is.null(archives)) {
+    dir <- archives %>% 
+      filter(name == task) %>% 
+      slice(n()) %>% 
+      pull(id)
+  } else stop("Please provide one of `archives` or `query` arguments")
+  
+  load_fun(file.path(
+    orderly_root, 
+    "archive",
+    task, 
+    dir,
+    "artefacts", 
+    file 
+  ))
+}
+
+# takes a data frame of parameters and performs an orderly search on each row.
+# By default, can also load these files (also ran parallel)
+load_orderly_data <- function(
+    # parameters fed to orderly::orderly_search
+  task,
+  parameters = NULL, # needs to be a df, not a list!
+  query = NULL, 
+  filenames = NULL, # name of specific artefact file to load, if desired
+  dirs = NULL, # optionally just provide dirs to skip orderly_search
+  load_fun = readr::read_csv, # function to load data with, if so desired
+  ncores = max(1, parallel::detectCores() - 2), 
+  ...
+) {
+  
+  # check that either parameters & query or just dirs have been provided
+  # (could also add a query parser here for the parameters!)
+  # stopifnot((!is.null(parameters) & !is.null(query)) || !is.null(dirs))
+  
+  if (is.null(dirs)) {
+    # search parameter space specified for previously run orderly tasks
+    if (!is.null(parameters)) {
+      dirs <- unlist(parallel::mclapply(seq_len(nrow(parameters)), function(i) {
+        # give progress (no longer works properly w/ mclapply rather than lapply)
+        # message(100 * (i / nrow(parameters)), "% completed") 
+        system(sprintf(
+          'echo "\n%s\n"', 
+          paste0(100 * (i / nrow(parameters)), "% completed", collapse = "")
+        ))
+        orderly::orderly_search(
+          query = query, 
[…]

### 2024-04-16 paper/2_paper/figures/scripts/020_methods_data.R

@@ -1,0 +1,316 @@
+#### Tables for Data section of Methods (and Sup. Figures) ####
+
+#### Initial ####
+
+### Libs ###
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(purrr)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+# source("Shiny/src/functions.R") # plotting functions
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
+
+### Metadata ###
+
+orderly_root <- getwd()
+
+# for tabulating surveys: 
+rm_missing_type <- FALSE # remove circumcisions with missing type?
+start_year <- 2000 # minimum survey year
+cens_age <- 59 # maximum circumcision age
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+### Load Data ###
+
+# pull most recent results for age groups
+archives <- orderly::orderly_list_archive()
+
+# pull shapefiles
+areas <- load_archive(
+  "00a2_areas_join", 
+  orderly_root, 
+  "areas.geojson", 
+  archives = archives, 
+  load_fun = read_sf
+)
+
+# pull surveys
+survey_circumcision_orig <- survey_circumcision <- load_archive(
+  "00b3_survey_join", 
+  orderly_root, 
+  "survey_circumcision.csv.gz", 
+  query = "latest(parameter:is_paper == TRUE)"
+)
+
+# survey_circumcision <- survey_circumcision %>% 
+  # filter(!iso3 %in% no_mod_iso3)
+
+# pull agegroup populations
+populations <- load_archive(
+  "00c4_pops_aggregate", 
+  orderly_root, 
+  "population_agegroup_aggr.csv.gz", 
+  archives = archives
+)
+
+# last surveys
+# TODO: Update these
+last_surveys <- readr::read_csv("global/most_recent_surveys.csv")
+
+# Prepare circ data, normalise survey weights and apply Kish coefficients.
+survey_circumcision <- prepare_survey_data(
+  areas               = areas,
+  survey_circumcision = select(survey_circumcision, -matches("area_level")),
+  area_lev            = threemc::datapack_psnu_area_level,
+  start_year          = start_year,
+  cens_year           = TRUE,
+  cens_age            = cens_age,
[…]

### 2024-04-16 paper/2_paper/figures/scripts/031_results_data.R

@@ -1,0 +1,707 @@
+#### Pull through data and plots required for Data subsection of Results ####
+
+# May end up joining this with other scripts or even copying to org file
+
+# This script also contains info on missing values etc which may be of 
+# interest in the appendix
+
+# TODO: Check number of surveys, seems very low
+# TODO: Remove BWA from plot
+
+# stopifnot(dirname(getwd()) == "threemc-orderly")
+while(basename(getwd()) != "threemc-orderly") setwd("../.")
+
+#### Libs ####
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(purrr)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+source("Shiny/src/functions.R") # plotting functions
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
+
+#### Metadata ####
+
+# TODO: remove unneeded here 
+orderly_root <- getwd()
+
+spec_age_group <- "10-29" # change? 
+spec_years <- c(2010, 2020)
+
+# for tabulating surveys: 
+rm_missing_type <- FALSE # remove circumcisions with missing type?
+start_year <- 2000 # minimum survey year
+cens_age <- 59 # maximum circumcision age
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+# VMMC countries  
+vmmc_iso3 <- c(
+  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA"
+)
+vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
+
[…]

### 2024-04-16 paper/2_paper/figures/scripts/032_results.R

@@ -1,0 +1,2181 @@
+#### Create plots for results ####
+
+# Produce summary stats here as well
+# must be run in threemc-orderly https://github.com/mrc-ide/threemc-orderly 
+# Orderly `archive/` found on Sharepoint https://tinyurl.com/ufpxymmb
+
+# stopifnot(dirname(getwd()) == "threemc-orderly")
+while(basename(getwd()) != "threemc-orderly") setwd("../.")
+
+#### Libs ####
+library(dplyr, warn.conflicts = FALSE)
+library(forcats)
+library(ggplot2)
+library(reactable)
+library(sf)
+library(threemc)
+library(orderly)
+library(ggsci)
+library(geofacet)
+library(glue)
+library(ggtext)
+# library(cowplot)
+library(patchwork)
+library(gridExtra)
+source("Shiny/src/functions.R") # plotting functions
+source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
+
+#### Metadata ####
+
+orderly_root <- here::here()
+
+spec_age_group <- "15-29" # changed from 10-29 upon Jeff's request
+spec_years <- c(2006, 2020)
+
+## for tabulating surveys
+# remove circumcisions with missing type?
+rm_missing_type <- FALSE
+
+start_year <- 2002
+cens_age <- 59
+
+# Revert to using planar rather than spherical geometry in `sf`
+sf::sf_use_s2(FALSE)
+
+# countries we attempted to model
+ssa_iso3 <- sort(c(
+  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
+  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
+  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
+  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
+))
+
+ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
+ssa_countries <- case_when(
+  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
+  ssa_countries == "Congo - Brazzaville" ~ "Congo",
+  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
+  ssa_countries == "Gambia"              ~ "The Gambia",
[…]

### 2024-04-16 paper/2_paper/figures/scripts/plots_ind/01_survey_plot.R

@@ -1,0 +1,164 @@
+#### Figure 1: Survey plot ####
+
+stopifnot(basename(getwd()) == "paper_poster_plots_threemc")
+
+#### Libraries ####
+
+library(ggplot2)
+library(dplyr)
+
+#### Setup ####
+
+# fig1data <- readr::read_csv("path/to/")
+fig1data <- readr::read_csv("paper/data/plots_ind/01_survey_plot.csv")
+
+vmmc_iso3 <- c(
+  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
+  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA"
+)
+# where to add horizontal line for VMMC vs non-VMMC
+country_positions <- length(vmmc_iso3) + 1
+
+plot_order <- c(
+  "BEN", "BFA", "CIV", "GHA", "GIN", "GNB", "LBR", "MLI", "NER", 
+  "NGA", "SEN", "SLE", "GMB", "TGO", "AGO", "CMR", "CAF", "TCD", 
+  "COG", "COD", "GAB", "BDI", "ETH", "KEN", "MWI", "MOZ", "RWA", 
+  "TZA", "UGA", "ZMB", "ZWE", "BWA", "SWZ", "LSO", "NAM", "ZAF"
+)
+
+country_name_convention <- function(x) {
+  x <- dplyr::case_when(
+    x == "Congo - Kinshasa"    ~ "DR Congo",
+    x == "Congo - Brazzaville" ~ "Congo",
+    grepl("Ivoire", x)         ~ "Cote d'Ivoire",
+    x == "Gambia"              ~ "The Gambia",
+    TRUE                       ~ x
+  )
+}
+
+country_pos_df <- data.frame(
+  "iso3"        = plot_order, 
+  "country_idx" = rev(seq_along(plot_order))
+) %>% 
+  mutate(
+    country_idx = ifelse(!iso3 %in% vmmc_iso3, country_idx + 1, country_idx), 
+    country = country_name_convention(
+      countrycode::countrycode(iso3, "iso3c", "country.name")
+    ),
+    country = case_when(
+      country == "Central African Republic" ~ "Cent. Af. Rep.", 
+      country == "Gambia"                   ~ "The Gambia",
+      TRUE                                  ~ country
+    )
+  )
+
+#### Plot & Save ####
+
+p1 <- fig1data %>%
+  # specify aesthetic variables
[…]

### 2024-04-16 paper/2_paper/figures/scripts/plots_ind/03_single_plots.R

@@ -1,0 +1,25 @@
+#### Single Country Plots ####
+
+#### Libraries ####
+
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(data.table)
+library(sf)
+library(here)
+library(gridExtra)
+library(data.table)
+library(geofacet)
+library(scales)
+library(ggridges)
+library(threemc)
+source("paper/scripts/plots_ind/functions.R")
+source("paper/scripts/00_funs.R")
+
+
+#### Setup ####
+
+
+
+#### Plot & Save ####

### 2024-04-16 paper/figures/supp_figs/PPC_P1_Tables.R

@@ -1,157 +1,0 @@
-#####################
-### Preliminaries ###
-#####################
-# Clearing Workspace
-rm(list = ls())
-
-# Loading required packages
-require(tidyverse)
-require(dplyr)
-require(reshape2)
-require(xtable)
-require(plyr)
-require(sf)
-
-# Reading in tables 
-results <- read_csv("~/Desktop/01e_new_final_ppc_models_fit_stats.csv")
-
-# Loading shapefiles 
-areas <- read_sf("~/Desktop/areas.geojson")
-
-####################################
-### Outputting PPC Part 1 Tables ###
-####################################
-# List of countries
-# cntry <- unique(results$cntry)
-cntry <- c('AGO', 'RWA', 'ZAF')
-
-# Opening text file
-sink('~/Desktop/PPC_P1_Tables.tex')
-
-cat("%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% \n")
-
-# Loop for each country 
-for (i in cntry){
-  # filtering for country
-  tmp <- results %>%
-    filter(cntry == i) %>%
-    as.data.frame()
-  
-  # Multiplying the coverage by 100 and rounding 
-  tmp[,c("ppd_0.500", "ppd_0.800", "ppd_0.950")] <- 100 * tmp[,c("ppd_0.500", "ppd_0.800", "ppd_0.950")]
-  
-  # Formatting dataset for output
-  tmp <- tmp %>%
-    # Altering labels 
-    mutate(rw = case_when(rw_order == 0 ~ "AR1",
-                          rw_order == 1 ~ "RW1",
-                          rw_order == 2 ~ "RW2"),
-           paed = case_when(paed_age_cutoff == "10" ~ "\\bf PC",
-                            paed_age_cutoff == "Inf" ~ "\\bf NC"),
-           type = case_when(type == "MC coverage" ~ "\\bf MC",
-                            type == "TMC coverage" ~ "\\bf MMC",
-                            type == "MMC coverage" ~ '\\bf TMC'),
-           tmc = case_when(inc_time_tmc == TRUE ~ "Time invariant",
[…]

### 2024-04-16 paper/scripts/020_methods_data.R

@@ -1,316 +1,0 @@
-#### Tables for Data section of Methods (and Sup. Figures) ####
-
-#### Initial ####
-
-### Libs ###
-library(dplyr, warn.conflicts = FALSE)
-library(forcats)
-library(ggplot2)
-library(reactable)
-library(sf)
-library(purrr)
-library(threemc)
-library(orderly)
-library(ggsci)
-library(geofacet)
-library(glue)
-library(ggtext)
-# source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
-
-### Metadata ###
-
-orderly_root <- getwd()
-
-# for tabulating surveys: 
-rm_missing_type <- FALSE # remove circumcisions with missing type?
-start_year <- 2000 # minimum survey year
-cens_age <- 59 # maximum circumcision age
-
-# Revert to using planar rather than spherical geometry in `sf`
-sf::sf_use_s2(FALSE)
-
-### Load Data ###
-
-# pull most recent results for age groups
-archives <- orderly::orderly_list_archive()
-
-# pull shapefiles
-areas <- load_archive(
-  "00a2_areas_join", 
-  orderly_root, 
-  "areas.geojson", 
-  archives = archives, 
-  load_fun = read_sf
-)
-
-# pull surveys
-survey_circumcision_orig <- survey_circumcision <- load_archive(
-  "00b3_survey_join", 
-  orderly_root, 
-  "survey_circumcision.csv.gz", 
-  query = "latest(parameter:is_paper == TRUE)"
-)
-
-# survey_circumcision <- survey_circumcision %>% 
-  # filter(!iso3 %in% no_mod_iso3)
-
-# pull agegroup populations
-populations <- load_archive(
-  "00c4_pops_aggregate", 
-  orderly_root, 
-  "population_agegroup_aggr.csv.gz", 
-  archives = archives
-)
-
-# last surveys
-# TODO: Update these
-last_surveys <- readr::read_csv("global/most_recent_surveys.csv")
-
-# Prepare circ data, normalise survey weights and apply Kish coefficients.
-survey_circumcision <- prepare_survey_data(
-  areas               = areas,
-  survey_circumcision = select(survey_circumcision, -matches("area_level")),
-  area_lev            = threemc::datapack_psnu_area_level,
-  start_year          = start_year,
-  cens_year           = TRUE,
-  cens_age            = cens_age,
[…]

### 2024-04-16 paper/scripts/031_results_data.R

@@ -1,707 +1,0 @@
-#### Pull through data and plots required for Data subsection of Results ####
-
-# May end up joining this with other scripts or even copying to org file
-
-# This script also contains info on missing values etc which may be of 
-# interest in the appendix
-
-# TODO: Check number of surveys, seems very low
-# TODO: Remove BWA from plot
-
-# stopifnot(dirname(getwd()) == "threemc-orderly")
-while(basename(getwd()) != "threemc-orderly") setwd("../.")
-
-#### Libs ####
-library(dplyr, warn.conflicts = FALSE)
-library(forcats)
-library(ggplot2)
-library(reactable)
-library(sf)
-library(purrr)
-library(threemc)
-library(orderly)
-library(ggsci)
-library(geofacet)
-library(glue)
-library(ggtext)
-source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots_threemc/paper/scripts/00_funs.R") # shared functions
-
-#### Metadata ####
-
-# TODO: remove unneeded here 
-orderly_root <- getwd()
-
-spec_age_group <- "10-29" # change? 
-spec_years <- c(2010, 2020)
-
-# for tabulating surveys: 
-rm_missing_type <- FALSE # remove circumcisions with missing type?
-start_year <- 2000 # minimum survey year
-cens_age <- 59 # maximum circumcision age
-
-# Revert to using planar rather than spherical geometry in `sf`
-sf::sf_use_s2(FALSE)
-
-# countries we attempted to model
-ssa_iso3 <- sort(c(
-  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
-  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
-  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
-  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
-))
-
-# VMMC countries  
-vmmc_iso3 <- c(
-  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
-  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA"
-)
-vmmc_cntries <- countrycode::countrycode(vmmc_iso3, "iso3c", "country.name")
-
[…]

### 2024-04-16 paper/scripts/032_results.R

@@ -1,2181 +1,0 @@
-#### Create plots for results ####
-
-# Produce summary stats here as well
-# must be run in threemc-orderly https://github.com/mrc-ide/threemc-orderly 
-# Orderly `archive/` found on Sharepoint https://tinyurl.com/ufpxymmb
-
-# stopifnot(dirname(getwd()) == "threemc-orderly")
-while(basename(getwd()) != "threemc-orderly") setwd("../.")
-
-#### Libs ####
-library(dplyr, warn.conflicts = FALSE)
-library(forcats)
-library(ggplot2)
-library(reactable)
-library(sf)
-library(threemc)
-library(orderly)
-library(ggsci)
-library(geofacet)
-library(glue)
-library(ggtext)
-# library(cowplot)
-library(patchwork)
-library(gridExtra)
-source("Shiny/src/functions.R") # plotting functions
-source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
-
-#### Metadata ####
-
-orderly_root <- here::here()
-
-spec_age_group <- "15-29" # changed from 10-29 upon Jeff's request
-spec_years <- c(2006, 2020)
-
-## for tabulating surveys
-# remove circumcisions with missing type?
-rm_missing_type <- FALSE
-
-start_year <- 2002
-cens_age <- 59
-
-# Revert to using planar rather than spherical geometry in `sf`
-sf::sf_use_s2(FALSE)
-
-# countries we attempted to model
-ssa_iso3 <- sort(c(
-  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
-  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
-  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
-  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
-))
-
-ssa_countries <- countrycode::countrycode(ssa_iso3, "iso3c", "country.name")
-ssa_countries <- case_when(
-  ssa_countries == "Congo - Kinshasa"    ~ "DR Congo",
-  ssa_countries == "Congo - Brazzaville" ~ "Congo",
-  grepl("Ivoire", ssa_countries)         ~ "Cote d'Ivoire",
-  ssa_countries == "Gambia"              ~ "The Gambia",
[…]

### 2024-04-16 paper/scripts/ind_supp_figs.R

@@ -1,827 +1,0 @@
-#### Individual Country Supplementary figures of final results ####
-
-# Must be run inside `threemc_orderly` repo, with this repo in top level of 
-# this directory, and called `paper_poster_plots_threemc`
-
-#### Libs ####
-
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(data.table)
-library(sf)
-library(here)
-library(gridExtra)
-library(data.table)
-library(geofacet)
-library(scales)
-library(ggridges)
-library(threemc)
-source("Shiny/src/functions.R")
-source("paper_poster_plots_threemc/paper/scripts/00_funs.R")
-
-
-#### Metadata ####
-
-orderly_root <- here::here()
-
-# save width for plots == width of page on paper
-save_width <- 6.3
-
-save_loc <- "paper_poster_plots_threemc/paper/plots/supp_figs/"
-if (!dir.exists(save_loc)) create_dirs_r(save_loc)
-
-# cntry <- "ZAF" # temp, run for one country, might loop thereafter
-
-spec_age_group <- "15-29"
-spec_age_group_double <- c(spec_age_group, "30-49")
-spec_years <- c(2006, 2020) # 2006 = first year of VMMC programmes
-spec_years_survey_comp <- spec_years
-if (cntry == "BWA") {
-  spec_years[2] <- 2021
-  spec_years_survey_comp[2] <- 2022
-}
-# spec_years_triple <- c(2006, 2015, 2020)
-spec_years_triple <- c(
-  spec_years[1], 
-  # find year midway between first and last year
-  spec_years[1] + ceiling(0.5 * (spec_years[2] - spec_years[1])), 
-  spec_years[2]
-)
-
-## for tabulating surveys
-# remove circumcisions with missing type?
-rm_missing_type <- FALSE
-
-start_year <- 2002
-cens_age <- 59
-
-# Revert to using planar rather than spherical geometry in `sf`
-sf::sf_use_s2(FALSE)
-
-# countries we attempted to model
-ssa_iso3 <- sort(c(
-  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
-  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
[…]

### 2024-04-16 paper/scripts/plots_ind/01_survey_plot.R

@@ -1,164 +1,0 @@
-#### Figure 1: Survey plot ####
-
-stopifnot(basename(getwd()) == "paper_poster_plots_threemc")
-
-#### Libraries ####
-
-library(ggplot2)
-library(dplyr)
-
-#### Setup ####
-
-# fig1data <- readr::read_csv("path/to/")
-fig1data <- readr::read_csv("paper/data/plots_ind/01_survey_plot.csv")
-
-vmmc_iso3 <- c(
-  "LSO", "MOZ", "NAM", "RWA", "TZA", "UGA", "MWI",
-  "SWZ", "ZWE", "ZMB", "ETH", "KEN", "ZAF", "BWA"
-)
-# where to add horizontal line for VMMC vs non-VMMC
-country_positions <- length(vmmc_iso3) + 1
-
-plot_order <- c(
-  "BEN", "BFA", "CIV", "GHA", "GIN", "GNB", "LBR", "MLI", "NER", 
-  "NGA", "SEN", "SLE", "GMB", "TGO", "AGO", "CMR", "CAF", "TCD", 
-  "COG", "COD", "GAB", "BDI", "ETH", "KEN", "MWI", "MOZ", "RWA", 
-  "TZA", "UGA", "ZMB", "ZWE", "BWA", "SWZ", "LSO", "NAM", "ZAF"
-)
-
-country_name_convention <- function(x) {
-  x <- dplyr::case_when(
-    x == "Congo - Kinshasa"    ~ "DR Congo",
-    x == "Congo - Brazzaville" ~ "Congo",
-    grepl("Ivoire", x)         ~ "Cote d'Ivoire",
-    x == "Gambia"              ~ "The Gambia",
-    TRUE                       ~ x
-  )
-}
-
-country_pos_df <- data.frame(
-  "iso3"        = plot_order, 
-  "country_idx" = rev(seq_along(plot_order))
-) %>% 
-  mutate(
-    country_idx = ifelse(!iso3 %in% vmmc_iso3, country_idx + 1, country_idx), 
-    country = country_name_convention(
-      countrycode::countrycode(iso3, "iso3c", "country.name")
-    ),
-    country = case_when(
-      country == "Central African Republic" ~ "Cent. Af. Rep.", 
-      country == "Gambia"                   ~ "The Gambia",
-      TRUE                                  ~ country
-    )
-  )
-
-#### Plot & Save ####
-
-p1 <- fig1data %>%
-  # specify aesthetic variables
[…]

### 2024-04-16 paper/scripts/plots_ind/03_single_plots.R

@@ -1,25 +1,0 @@
-#### Single Country Plots ####
-
-#### Libraries ####
-
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(data.table)
-library(sf)
-library(here)
-library(gridExtra)
-library(data.table)
-library(geofacet)
-library(scales)
-library(ggridges)
-library(threemc)
-source("paper/scripts/plots_ind/functions.R")
-source("paper/scripts/00_funs.R")
-
-
-#### Setup ####
-
-
-
-#### Plot & Save ####
